\section{Further Related Work}
\label{sec:morerelated}

\paragraph{Pretraining tasks}

One way to integrate domain knowledge into hierarchical agents is to learn primitives on simpler tasks and then compose them to solve more complex tasks afterwards. 
Learning primitives from manually specified tasks simplifies learning but requires human effort and limits the generality of the skills. 
DSN \citep{tessler2017dsn} explicitly specifies reward functions for the low-level policies and then trains a high-level policy on top to solve Minecraft tasks. 
MLSH \citep{frans2017mlsh} pretrains a hierarchy with separate low-level policies on easier tasks, alternating update phases between the two levels. 
HeLMS \citep{rao2021helms} learns reusable robot manipulation skills from a given diverse dataset. 
MODAC \citep{veeriah2021modac} uses meta gradients to learn low-level policies that are helpful for solving tasks. 
However, all these approaches require manually specifying a diverse distribution of training tasks, and it is unclear whether generalization beyond the training tasks will be possible. 
Instead of relying on task rewards for learning skills, Director learns the worker as a goal-conditioned policy with a dense similarity function in feature space.

\paragraph{Mutual information}

Mutual information approaches allow automatic discovery of skills that lead to future states. 
VIC \citep{gregor2016vic} introduced a scalable recipe for discovering skills by rewarding the worker policy for reaching states from which the latent skill can be accurately predicted, effectively clustering the trajectory space. 
Several variations of this approach have been developed with further improvements in stability and diversity of skills, including SSN4HRL \citep{florensa2017snn}, DIAYN \citep{eysenbach2018diayn} and VALOR \citep{achiam2018valor}. 
DISCERN \citep{warde2018discern} and CIC \citep{laskin2022cic} learn a more flexible similarity function between skills and states through contrastive learning. 
DADS \citep{sharma2019dads} estimates the mutual information in state-space through a contrastive objective with a learned model. 
DISDAIN overcomes a collapse problem by incentivizing exploration through ensemble disagreement \citep{strouse2021disdain}. 
LSP \citep{xie2020lsp} learns a world model to discover skills that have a high influence on future representations rather than inputs. 
While these approaches are promising, open challenges include learning more diverse skills without dropping modes and learning skills that are precise enough for solving tasks.

\paragraph{Goal reaching}

Learning the low-level controller as a goal-conditioned policy offers a stable and general learning signal. 
HER \citep{andrychowicz2017her} popularized learning goal-conditioned policies by combining a sparse reward signal with hindsight, which HAC \citep{levy2017hac} applied to learn an interpretable hierarchy with three levels by manually designing task-relevant goal spaces for each task. 
Instead of relying on hindsight with a sparse reward, HIRO \citep{nachum2018hiro} employs a dense reward in observation space based on the L2 norm and solves Ant Maze tasks given privileged information. 
NORL \citep{nachum2018norl} introduces a representation learning objective to learn a goal space from a low-resolution top-down image instead but still uses a dense ground-truth reward for learning the manager. 
HSD-3 \citep{gehring2021hsd3} also learns a hierarchy with three levels and uses the robot joint space combined with a mask to specify partial goals. 
While not learning a high-level policy, RIG \citep{nair2018rig} computes goal rewards in the latent space of an autoencoder, allowing them to reach simple visual goals. 
FuN \citep{vezhnevets2017fun} provides task and goal rewards to its low-level policy and is trained from pixels but provides limited benefits over a flat policy trained on task reward. 
SecTAR \citep{co2018sectar} learns a sequence autoencoder that serves to propose goals and compute distances for low-dimensional environments and shows fast learning in low-dimensional environments with sparse rewards by high-level planning. 
DDL \citep{hartikainen2019ddl} learns to reach goals from pixels by learning a temporal distance function. 
LEXA \citep{mendonca2021lexa} learns a goal conditioned policy inside of a world model that achieves complex multi-object goal images, but assumes goals to be specified by the user. 
By comparison, Director solves difficult sparse reward tasks end-to-end from pixels without requiring domain-specific knowledge by learning a world model.
