\section{Evaluating the Empirical Realism of Imitated $\mathbb{X}$ Users}
We evaluated the approaches for the different imitation tasks as described in Sect.~\ref{sec:twon} and Sect.~\ref{sec:fitting} to assess their empirical realism.

\include{figures/results.generative.tex}

\subsection{Evaluation of Imitated Posting and Replying Behavior}
The text-generation-based tasks are evaluated with two different approaches, in two different languages, using three text comparison metrics (see.~Table~\ref{tab:results:generative}).

\paragraph{In-context vs Fine-tuning}
An initial observation is that BLEU scores \cite{papineni2002bleu} in all in-context settings are low. This is also true for the n-gram metrics. However, the fine-tuning-based approach shows significant improvements specifically in the English reply task, but also for uni-gram matches and the overall length ratio. Beyond such token-overlap-metrics, we tested semantic similarity metrics: we embedded all samples using $\mathbb{X}$-fine-tuned BERT \citep{zhang2023twhin} and calculated the distance between generations and original samples. Again, the results generated from the fine-tuned model show a significantly shorter distance to its original counterpart compared to the in-context model. The correlation between the predicted emotions in the original and generated samples using a BERT-based multi-label emotion classifier \citep{barbieri2020tweeteval} is less clear. The fine-tuned approach only marginally outperforms the prompt-only approach on the posting task. 

However, the English fine-tuned reply generation task showed by far the best performance with significant improvements in all metrics. The BLEU score increased substantially from 0.019 to 0.239, uni-gram precision improved from 0.167 to 0.387, and the embedding distance was reduced significantly from 2.006 to 1.427. The model achieved a near-perfect length ratio of 1.003 and demonstrated strong TweetEval correlations across all categories.

\paragraph{English vs German}
In general, we see the same improvements through fine-tuning compared to in-context with respect to the German data in the post-generation task: The BLEU score increases and uni-gram precision improves. Also, the embedding distance was reduced from 2.530 to 1.499, and the length ratio moved closer to 1.0 after fine-tuning (1.023 vs 1.142). However, compared to English, the TweetEval metrics proved generally unreliable for German content, showing inconsistent patterns with high standard deviations. This suggests fundamental limitations in applying English-trained evaluation metrics to German content. Similarly, the German reply generation (history-based) task shows low empirical realism on all metrics compared to English and regardless of fine-tuning. There were minimal improvements in BLEU scores from 0.005 to 0.021, with high variance in metrics, exemplified by the bi-gram standard deviation of 0.044. The embedding distance remains high even after fine-tuning at 2.891.

\subsection{Evaluation of Replying Likelihood Behavior}
Similar to our evaluation of the generative tasks, we observe substantial performance disparities between English and German models (Table \ref{tab:results:probability:test}). Even on the German training set, our model achieves only moderate alignment with an F1-Score of $0.666$, in stark contrast to the English experiment, where the prediction scores are almost perfect. This performance gap suggests that the BERT encoder employed in our study represents English samples with semantically richer embeddings than their German counterparts. 

\input{figures/results.probability.test}

\subsection{Key Findings}
Several key findings emerge from this analysis. First, language-specific performance shows that English models significantly outperform German models across all metrics, with TweetEval metrics proving more reliable for English content while German models show limited success, particularly in reply generation. Second, task-specific patterns reveal that fine-tuning shows consistent improvements for post-generation in both languages. However, reply generation varies dramatically between languages, with English reply generation achieving remarkably high scores. Third, the impact of data volume is evident, with better performance in English likely due to larger LLM pre-training datasets. Fourth, in terms of evaluation metrics, BLEU scores and embedding distances provide consistent signals, TweetEval metrics are only meaningful for English content, and the length ratio serves as an intuitive indicator of style authenticity.

\subsection{Imitation Limitations}
\label{subsec:ImiLimi}
The stark contrast between English and German model performance, particularly in reply generation tasks, underscores the importance of data volume and language-specific considerations when utilizing generative-agent-based modeling for imitating user behavior on social networks. The success of the English models demonstrates the potential of the approach, while the limitations faced by the German models highlight that they require additional training and optimizations to provide robust levels of empirical realism.

Our experimental setup has further limitations regarding both data selection and the system's capacity to generate discourses containing well-structured standpoints and arguments. Although our models demonstrate such capabilities under certain conditions, their performance characteristics primarily reflect the behavioral patterns of the most active users within our dataset, thus mirroring the distinctive communication dynamics observed in the selected $\mathbb{X}$ community. This sampling bias raises questions about the generalizability of our findings in different contexts of social networks and user populations.
