\section{Introduction}
\label{sec:intro}
\input{figs/teaser}

Video world models, where future agent observations are generated based on past observations and actions, hold tremendous promise as a tool for embodied AI agents, and are useful for synthetic training~\cite{ali2025world, yang2024video}, inference-time planning~\cite{zhou2024dino, assran2025v}, and policy learning and evaluation~\cite{du2023learning, jang2025dreamgen, quevedo2026worldgym}. However, today’s world models are limited to simulating the observations of only a single agent at a time. In our fundamentally multi-agent world, video world models that are capable of simulating the perspectives of all agents in an environment are needed to capture an accurate world state. 

Toward this end, we study the creation of multiplayer video world models trained on multiplayer data collected from Minecraft. Modeling the perspectives of multiple players at once is significantly more challenging than single-player modeling. Generated observations need to be consistent not only across time but also across agent perspectives. Actions taken by one agent, such as movement or block placement, must be simultaneously and accurately reflected in the viewpoints of all other agents.


Minecraft serves as an ideal testbed for multi-agent modeling. Its unbounded, fully 3D worlds rigorously test challenging aspects of viewpoint modeling, such as perspective consistency, occlusion handling, and spatial memory. Its dynamic and malleable environment tests a model’s ability to keep track of alterations that occur over time. Furthermore, environmental stochasticity (e.g., mobs, weather) forces models to disentangle alterations caused by environmental randomness from those caused by controllable agents. And through its complex system of building, digging, and crafting, Minecraft allows for endless complexity. Lastly, its procedurally generated terrain naturally diversifies the environment. We believe Minecraft will continue to be a valuable research platform in the long-term.





Prior to this work, there were no existing publicly available systems for simulating multiplayer Minecraft gameplay, motivating us to build \solarisengine: a system for collecting gameplay from pre-programmed bots. In \solarisengine, our bots engage in non-trivial and realistic gameplay, including mining, attacking, building, and navigating terrains. Our system allows us to collect millions of frames in a matter of hours, and its modular design makes it easy to extend to new agent behaviors. We used this data engine to generate a multiplayer training dataset of 12.64 M frames (6.32 M per player) and an evaluation set testing multiplayer movement, memory, grounding, building, and view consistency.

Our model, called \solaris, is a video diffusion model with a general-purpose architecture that adapts a single-agent pre-trained video DiT to one that simulates multiple perspectives with minimal modifications. Our model takes in sequences of past player observations and actions and generates future observations using autoregressive diffusion. We show examples of our model's capabilities in~\cref{fig:teaser}.

To improve long-horizon autoregressive generations, we adopt the Self Forcing~\cite{huang2025selfforcingbridgingtraintest} paradigm. We extend the setting of Self Forcing to allow the student to benefit from a long-context teacher. Naively applying Self Forcing with sliding-window generation leads to excessive memory usage, a problem we mitigate with a novel technique called \oursf analogous to gradient checkpointing. We also make simplifications to the initialization of the student model, finding that the initialization method of CausVid~\cite{yin2025slowbidirectionalfastautoregressive} can be replaced by simply finetuning with causal masking. 

In summary, we present \solaris, a multi-agent video world model capable of simulating consistent multiplayer perspectives in Minecraft. We contribute a scalable data system, \solarisengine, a large-scale training dataset of multiplayer gameplay, an evaluation system, and a new architecture that adapts a pre-trained video DiT for multiplayer videos. Finally, we introduce \oursf, a memory-efficient extension of the Self Forcing paradigm, enabling effective autoregressive training.








