\section{Related work}
Leveraging human- and machine-generated natural language (NL) feedback for refining outputs has been effective for a variety of tasks, including summarization \cite{scheurerandperez2022training}, script generation \cite{tandon2021interscript}, program synthesis \cite{Le2022CodeRL, Yasunaga2020DrRepair}, 
and other tasks \cite{bai2022rlhf, Schick2022PEERAC, Saunders2022SelfCritique, bai2022constitutional, Welleck2022SelfCorrect}. Refinement methods differ in the source and format of feedback, and the way that a refiner is obtained.
Table \ref{tab:related_work_short_summary} summarizes some related approaches; see \Cref{app:related} for an additional discussion.



 

\paragraph{Source of feedback.}

Humans have been an effective source of feedback \cite{tandon2021interscript,elgohary2021nl,tandon2022learning,bai2022rlhf}. 
Since human feedback is costly, several approaches
use a scalar reward function as a surrogate of (or alternative to) human feedback~(e.g., \cite{bai2022rlhf, Liu2022RainierRK, Lu2022QuarkCT, Le2022CodeRL, Welleck2022SelfCorrect}).
Alternative sources such as compilers 
\cite{Yasunaga2020DrRepair} or Wikipedia edits \cite{Schick2022PEERAC} can provide domain-specific feedback.
Recently, LLMs have been used to generate feedback for general domains \cite{fu2023gptscore,Peng2023LLMAugmenter,Yang2022Re3GL},
However, ours 
is the only method that generates
feedback using an \llm on its \emph{own} output, for the purpose of refining with the same \llm.


\begin{table}[!t]  %
    \centering
    \small
    \begin{tabular}{p{0.4\textwidth}P{0.11\textwidth}P{0.12\textwidth}P{0.12\textwidth}P{0.08\textwidth}}
    \toprule
  & Supervision-free refiner & Supervision-free feedback & Multi-aspect feedback & Iterative \\ \midrule
  \textbf{Learned refiners}: PEER \cite{Schick2022PEERAC}, Self-critique 
  \cite{Saunders2022SelfcritiquingMF}, CodeRL \cite{Le2022CodeRLMC}, Self-correction \cite{Welleck2022SelfCorrect}.
  & \emoji[emoji]{x} & \emoji[emoji]{check} or \emoji[emoji]{x}  & \emoji[emoji]{x} & \emoji[emoji]{check} or \emoji[emoji]{x}
  \\ \midrule
  \textbf{Prompted refiners}: 
  Augmenter \cite{Peng2023LLMAugmenter}, Re$^3$ \cite{Yang2022Re3GL}, Reflexion \cite{shinn2023reflexion}. 
  & \emoji[emoji]{check} & \emoji[emoji]{check} or \emoji[emoji]{x}  & \emoji[emoji]{x} & \emoji[emoji]{x} 
  \\ \midrule
  \textbf{\ours} (this work) 
  & \emoji[emoji]{check} & \emoji[emoji]{check} & \emoji[emoji]{check} & \emoji[emoji]{check}
  \\ \bottomrule
    \end{tabular}
    \caption{A comparison of \ours to closely related prior refinement approaches.}
    \label{tab:related_work_short_summary}
\end{table}

\paragraph{Representation of feedback.}
The form of feedback can be generally divided into natural language (NL) and non-NL feedback.
Non-NL feedback can come in human-provided example pairs \cite{Dasgupta2019MachineTeaching} or scalar rewards \cite{Liu2022RainierRK, Le2022CodeRLMC}. 
In this work, we use NL feedback, since this allows the model to easily provide \emph{self}-feedback using the same LM that generated the output, while leveraging existing pretrained LLMs such as GPT-4. %


\paragraph{Types of refiners.} 
Pairs of feedback and refinement have been used to learn supervised refiners \cite{Schick2022PEERAC,du-etal-2022-r3, Yasunaga2020DrRepair,madaan2021graphcorr}. 
Since gathering supervised data is costly, some methods learn refiners using model generations 
\cite{Welleck2022SelfCorrect,Peng2023LLMAugmenter}. 
However, the refiners are trained for each new domain.
Finally, \cite{Yang2022Re3GL} use prompted feedback and refinement specifically tailored for story generation.
In this work, we avoid training a separate refiner, and show that the same model can be used as both the refiner and the source of feedback across multiple domains.

\paragraph{Non-refinement reinforcement learning (RL) approaches.}
Rather than having explicit refinement, an alternative way to incorporate feedback is by optimizing a scalar reward function, e.g. with reinforcement learning (e.g.,~\citet{stiennon2020learning,Lu2022QuarkCT,Le2022CodeRL}).
These methods differ from \ours 
in that the model does not access feedback on an intermediate generation. 
Second, these RL methods require updating the model's parameters, unlike \ours. %





