
\documentclass{article} % For LaTeX2e
\usepackage[preprint]{colm2025_conference}

\input{math_commands.tex}

\usepackage{microtype}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{lineno}


\usepackage[T1]{fontenc}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{colortbl}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{wrapfig}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{csquotes}
% \usepackage{natbib}
\usepackage[breakable]{tcolorbox}



\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}

\newcommand\eg[0]{\textit{e.g.}}
\newcommand\ie[0]{\textit{i.e.}}

\newcommand{\TODO}[1]{\textbf{\color{red}[TODO: #1]}}

\newcommand{\yg}[1]{\textcolor{blue}{{[Yu Gu: #1]}}}
\newcommand{\yuting}[1]{\textcolor{red}{{[Yuting: #1]}}}
\newcommand{\boyuan}[1]{\textcolor{green}{{[Boyuan: #1]}}}
\newcommand{\kai}[1]{{\color{red}[Kai: #1]}}
\newcommand{\hs}[1]{\textbf{\color{cyan}[(HS: #1 )]}}
\newcommand{\yu}[1]{\textcolor{purple}{{[Yu: #1]}}}
\newcommand{\peng}[1]{\textcolor{blue!60!red}{\small{[\textbf{Peng:} #1]}}}

\title{\textit{Is Your LLM Secretly a World Model of the Internet}?\\ Model-Based Planning for Web Agents}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \colmfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.


% two lines
% \author{Yu Gu$^{1}$, Kai Zhang$^{1}$, Yuting Ning$^{1}$, Boyuan Zheng$^{1}$, \textbf{Boyu Gou$^{1}$, Tianci Xue$^{1}$,} \\
% \textbf{Cheng Chang$^{2}$, Sanjari Srivastava$^{2}$, Yanan Xie$^{2}$, Peng Qi$^{2}$, Huan Sun$^{1}$, Yu Su$^{1}$}
% \\
% \\ \textsuperscript{1} The Ohio State University \textsuperscript{2} Orby AI
% \\
% }

% three lines with more visbility of our labmates.
\author{
\quad\quad\quad\quad\quad\quad Yu Gu$^{1}$\thanks{Equal Contribution. See the contribution statement for details.}~, Kai Zhang$^{1}$\footnotemark[1]~, Yuting Ning$^{1}$\footnotemark[1]~, Boyuan Zheng$^{1}$\footnotemark[1]~, \\
\textbf{Boyu Gou$^{1}$, Tianci Xue$^{1}$, Cheng Chang$^{2}$, Sanjari Srivastava$^{2}$, Yanan Xie$^{2}$, Peng Qi$^{2}$,} \\
\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad \textbf{Huan Sun$^{1}$\thanks{Equal Advising.}~, Yu Su$^{1}$\footnotemark[2]}
\\[1.2ex]
\quad\quad\quad\quad\quad\quad\quad\quad\quad 
\textsuperscript{1} The Ohio State University \quad \textsuperscript{2} Orby AI
\\
\quad\quad\quad\quad\quad\quad\quad\quad~~\small{\{gu.826, zhang.13253, sun.397, su.809\}@osu.edu}}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\OurMethod}{\textsc{WebDreamer}\xspace}

\begin{document}

\ifcolmsubmission
\linenumbers
\fi

\maketitle

\begin{abstract}
Language agents based on large language models (LLMs) have demonstrated great promise in automating web-based tasks.
Recent work has shown that incorporating advanced planning algorithms, \eg, tree search, is advantageous over reactive planning for web agents.
However, unlike simulated sandbox environments, real-world environments such as the web are rife with irreversible actions. 
This undermines the feasibility of backtracking, a cornerstone of (tree) search.  
Overly relying on test-time search also hurts efficiency. 
We advocate \textit{model-based planning} for web agents that employs a world model to simulate and deliberate over the outcome of each candidate action before committing to one. 
We systematically explore this paradigm by: \textbf{(1)} Proposing a model-based planning framework, \OurMethod, which employs LLMs to serve as both world models and value functions; \textbf{(2)} Training specialized LLMs as world models with a scalable data synthesis pipeline.
Empirical results demonstrate that \OurMethod achieves substantial performance improvements over reactive baselines.
It is competitive, while being $4$--$5$ times more efficient, with tree search in sandbox environments (VisualWebArena) and also works effectively on real-world websites (Online-Mind2Web and Mind2Web-Live).
Furthermore, our trained world model, Dreamer-7B, performs comparable to GPT-4o, highlighting the potential of specialized world models for efficient and effective planning in complex web environments.\footnote{All resources are available at \url{https://github.com/OSU-NLP-Group/WebDreamer}.}
\end{abstract}


\input{sections/01-introduction}
\input{sections/02-related}
\input{sections/04-method}
\input{sections/05-experiments}
\input{sections/06-discussion}
\input{sections/07-conclusion}


\section*{Acknowledgments} 
We would like to extend our appreciation to colleagues from the OSU NLP group and Orby AI for their insightful comments. 
This work is supported in part by Orby AI and ARL W911NF2220144. 
The views and conclusions contained herein are those of the authors and should not be interpreted as representing the official policies, either expressed or implied, of the U.S.\ government. The U.S.\ government is authorized to reproduce and distribute reprints for government purposes notwithstanding any copyright notice herein.



\bibliography{colm2025_conference}
\bibliographystyle{colm2025_conference}

\newpage
\appendix
% \section{Appendix}
% You may include other additional sections here.
\input{sections/appendix}
\end{document}
