\begin{abstract}
Large-scale generative models have achieved remarkable success in a number of domains. However, for sequential decision-making problems, such as robotics, action-labelled data is often scarce and therefore scaling-up foundation models for decision-making remains a challenge. 
%
A potential solution lies in leveraging widely-available unlabelled videos to train world models that simulate the consequences of actions. 
%
If the world model is accurate, it can be used to optimize decision-making in downstream tasks. 
%
Image-to-video diffusion models are already capable of generating highly realistic synthetic videos. 
%
However, these models are not action-conditioned, and the most powerful models are closed-source which means they cannot be finetuned.
%
In this work, we propose to adapt pretrained video diffusion models to action-conditioned world models, without access to the parameters of the pretrained model.
%
Our approach, AVID, trains an adapter on a small domain-specific dataset of action-labelled videos. AVID uses a learned mask to modify the intermediate outputs of the pretrained model and generate accurate action-conditioned videos. We evaluate AVID on video game and real-world robotics data, and show that it outperforms existing baselines for diffusion model adaptation.\footnote{Code is available on 
\href{https://github.com/microsoft/causica/tree/main/research_experiments/avid}{\textcolor{blue}{GitHub}}. Examples available at \href{https://sites.google.com/view/avid-world-model-adapters/home}{\textcolor{blue}{Project Webpage}}.}
%
Our results demonstrate that if utilized correctly, pretrained video models have the potential to be powerful tools for embodied AI.
 
\end{abstract}