\section{Discussion}
\textbf{Limitations\ } AVID adapters are tailored to a specific pretrained model and therefore cannot be composed with different models. Developing a method that works across different pretrained models is an exciting direction for future work.
%
AVID does not require access to pretrained model weights, but it does require access to intermediate predictions during denoising, including the outputs of the encoder and decoder in the case of latent diffusion.  Many closed-source APIs do not provide access to these quantities, and therefore we advocate for model providers to provide API access to the outputs of the denoising model and autoencoder to facilitate more flexible use of their models.
%

In the RT1 domain we found that training an action-conditioned diffusion model from scratch resulted in the best Action Error Ratio, despite the videos being less visually accurate. For some downstream applications, action consistency might be the most important performance metric. If this is the case, training from scratch may be the preferred approach for some domains.


\textbf{Conclusion\ } We introduced the novel problem of adapting pretrained video diffusion models to action-conditioned world models without requiring access to the pretrained model's parameters. Our proposed approach, AVID, generates accurate videos with similar performance to ControlNet variants without requiring access to the pretrained model parameters. AVID obtains superior overall performance to existing baselines that do not require access to the internals of the pretrained model. Our results demonstrate that AVID benefits from the pretrained model by maintaining better consistency with the initial image across both pixel-space and latent diffusion models. 

As general image-to-video diffusion models continue to advance in capability, our findings highlight the considerable potential of adapting these models to  world models that are suitable for planning and decision-making. This work represents an initial step in that direction. In future research, we aim to explore the use of synthetic data generated by AVID adapters for planning tasks and integrate AVID with more powerful pretrained models.

\vfill
{\large\textbf{Contribution Statement}}

\small 
\smallskip
\textbf{Marc Rigter:}
\vspace{-2mm}
\begin{itemize}[noitemsep, left=0pt]
    \item Conceived initial concept of adapting video diffusion models to world models
    \item Co-conceived the final approach
    \item Implemented training and model code for both latent and pixel-space diffusion
    \item Implemented all dataloading, preprocessing, and evaluation metrics
    \item Implemented AVID and all baselines except those mentioned below
    \item Trained all models and ran all evaluation except for IRASim
    \item Led paper writing
    \item Contributed to discussions throughout project
\end{itemize}

\textbf{Tarun Gupta:}
\vspace{-2mm}
\begin{itemize}[noitemsep, left=0pt]
    \item Co-conceived the final approach
    \item Implemented Action Classifier-Free Guidance in pixel-space diffusion codebase and all ControlNet variants
    \item Ran evaluation of IRASim
    \item Contributed to paper writing
    \item Contributed to discussions throughout project
\end{itemize}

\textbf{Agrin Hilmkil:}
\vspace{-2mm}
\begin{itemize}[noitemsep, left=0pt]
\item Reviewed dataloading code
\item Set up development environment
\end{itemize}

\textbf{Chao Ma:}
\vspace{-2mm}
\begin{itemize}[noitemsep, left=0pt]
    \item Contributed to paper writing
    \item Contributed to early project discussions
\end{itemize}
