
\section{Introduction}\label{sec: introduction}
NP-hard combinatorial optimization problems (COPs) pervade numerous real-world systems, each characterized by distinct constraints and objectives. The intrinsic complexity and heterogeneity of these problems compel domain experts to laboriously develop heuristics for their approximate solutions \cite{hromkovivc2013algorithmics_for_hard_problems}. Automation of heuristic designs represents a longstanding pursuit.

Classic Hyper-Heuristics (HHs) automate heuristic design by searching for the best heuristic (combination) from a set of heuristics or heuristic components \cite{pillay2018hh_book}. Despite decades of development, HHs are limited by heuristic spaces predefined by human experts \cite{pillay2018hh_book}. The rise of large language models (LLMs) opens up new possibilities for HHs. This paper introduces the general concept of \textit{Language Hyper-Heuristics (LHH)} to advance beyond preliminary attempts in individual COP settings \cite{romera2023funsearch, liu2023algorithm_evolution}. LHH constitutes an emerging variant of HH that utilizes LLMs for heuristic generations. It features minimal human intervention and open-ended heuristic spaces, showing promise to comprehensively shift the HH research paradigm.

Pure LHH (e.g., LLM generations alone) is sample-inefficient and exhibits limited inference capability for black-box COPs. This work elicits the power of LHH with \textit{Reflective Evolution} (\our{}). \our{} couples evolutionary search for efficiently exploring heuristic spaces, with self-reflections to boost the reasoning capabilities of LLMs. It emulates human experts by reflecting on the relative performance of two heuristics and gathering insights across iterations. 
This reflection approach is analogous to interpreting genetic cues and providing "\textit{verbal gradient}" within search spaces.
We introduce fitness landscape analysis and black-box prompting for reliable evaluation of LHHs. The dual-level reflections are shown to enhance heuristic search and induce verbal inference for black-box COPs, enabling \our{} to outperform prior state-of-the-art (SOTA) LHH \cite{liu2024_llm_gls}.

We introduce novel applications of LHHs and yield SOTA solvers with \our{}: (1) We evolve penalty heuristics for Guided Local Search (GLS), which outperforms SOTA learning-based \cite{ma2023neu_kopt, hudson2022_gnn_gls, sui2023neuralgls} and knowledge-based \cite{arnold2019_KGLS_VRP} (G)LS solvers. (2) We enhance Ant Colony Optimization (ACO) by evolving its heuristic measures, surpassing both neural-enhanced heuristics \cite{ye2023deepaco} and expert-designed heuristics \cite{skinderowicz2022_aco_tsp_human_bl, cai2022_aco_cvrp_human_bl, sohrabi2021_aco_op_human_bl, fidanova2020_aco_mkp_human_bl, levine2004_aco_bpp_human_bl}. (3) We refine the genetic algorithm (GA) for Electronic Design Automation (EDA) by evolving genetic operators, outperforming expert-designed GA \citep{park2023versatile} and the SOTA neural solver \citep{kim2023devformer} for the Decap Placement Problem (DPP). (4) Compared to a classic HH \cite{duflo2019gp_hh_tsp}, \our{} generates superior constructive heuristics for the Traveling Salesman Problem (TSP). (5) We enhance the generalization of SOTA neural combinatorial optimization (NCO) solvers \cite{kwon2020pomo,luo2023nco_heavy_decoder} by evolving heuristics for attention reshaping. For example, we improve the optimality gap of POMO \cite{kwon2020pomo} from 52\% to 29\% and LEHD \cite{luo2023nco_heavy_decoder} from 3.2\% to 3.0\% on TSP1000, with negligible additional time overhead and no need for tuning neural models.


We summarize our contributions as follows. (1) We propose the concept of Language Hyper-Heuristics (LHHs), which bridges emerging attempts using LLMs for heuristic generation with a methodological group that enjoys decades of development. (2) We present Reflective Evolution (\our{}), coupling evolutionary computation with humanoid reflections to elicit the power of LHHs. We introduce fitness landscape analysis and black-box prompting for reliable LHH evaluations, where \our{} achieves SOTA sample efficiency. (3) We introduce novel applications of LHHs and present SOTA COP solvers with \our{}, across five heterogeneous algorithmic types and six different COPs.