\documentclass[sigconf]{acmart}

\usepackage{pifont}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{threeparttable}
\usepackage{tabularx}  %
\usepackage{ragged2e}
\usepackage{array}     %
\usepackage{amsthm, thmtools}
\usepackage{amsthm, thmtools}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\usepackage{makecell, cellspace}
\usepackage{multirow}
\usepackage{threeparttable}


\declaretheorem[style=definition, name=Definition, numbered=no]{definition}


\newcommand{\appname}{{\textsc{PatchDiff}}\xspace}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

\copyrightyear{2026}
\acmYear{2026}
\setcopyright{rightsretained}
\acmConference[ICSE '26]{2026 IEEE/ACM 48th International Conference on Software Engineering}{April 12--18, 2026}{Rio de Janeiro, Brazil}
\acmBooktitle{2026 IEEE/ACM 48th International Conference on Software Engineering (ICSE '26), April 12--18, 2026, Rio de Janeiro, Brazil}
\acmPrice{}
\acmDOI{10.1145/3744916.3764576}
\acmISBN{979-8-4007-2025-3/26/04}





\begin{document}

\title[Are ``Solved Issues'' in SWE-bench Really Solved Correctly?]{Are ``Solved Issues'' in SWE-bench Really Solved Correctly? \\An Empirical Study}

\author{You Wang}
\affiliation{%
\institution{The State Key Laboratory of Blockchain and Data Security, Zhejiang University}
\city{Hangzhou}
\country{China}}
\email{prinzywang@zju.edu.cn}

\author{Michael Pradel}
\affiliation{%
  \institution{CISPA Helmholtz Center for Information Security}
  \city{Stuttgart}
  \country{Germany}}
\email{michael@binaervarianz.de}

\author{Zhongxin Liu}
\authornote{Corresponding Author}
\affiliation{%
  \institution{The State Key Laboratory of Blockchain and Data Security, Zhejiang University}
  \city{Hangzhou}
\country{China}}
\email{liu_zx@zju.edu.cn}










\begin{abstract}


Automated issue solving aims to resolve real-world issues in software repositories.
The most popular benchmarks for automated issue solving are SWE-bench and its human-filtered subset SWE-bench Verified, which are widely used to evaluate foundation models and software engineering agents.
These benchmarks leverage testing to validate generated patches.
However, because testing is rarely exhaustive, a patch may pass the tests but nevertheless fail to match the developers' expectations.
Unfortunately, it is currently unclear to what extent evaluations performed with SWE-bench suffer from such \emph{plausible but incorrect patches}.
This paper presents an in-depth empirical study of the correctness of plausible patches generated by three state-of-the-art issue-solving tools (CodeStory, LearnByInteract, and OpenHands) evaluated on SWE-bench Verified.
We extensively test and inspect generated patches, and compare them against human-written ground truth patches.
The core of our methodology is a novel technique for differential patch testing, called \appname, which automatically exposes behavioral discrepancies between two patches.
Our findings reveal critical weaknesses in SWE-bench's patch validation mechanism, which causes 7.8\% of all patches to count as ``correct'' while failing the developer-written test suite.
Moreover, our novel automated technique reveals that even more (29.6\%) plausible patches induce different behavior than the ground truth patches.
These behavioral differences are often due to similar, but divergent implementations (46.8\%) and due to generated patches that adapt more behavior than the ground truth patches (27.3\%).
Our manual inspection shows that 28.6\% of behaviorally divergent patches are certainly incorrect.
Combined, the different weaknesses lead to an inflation of reported resolution rates by 6.4 absolute percent points.
Our findings are a call to arms for more robust and reliable evaluation of issue-solving tools.
We envision our automated differential patch testing technique to be useful for this purpose.
\end{abstract}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007</concept_id>
       <concept_desc>Software and its engineering</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[300]{Software and its engineering}

\keywords{Automated Issue Solving, Differential Testing, Patch Evaluation}


\pagestyle{plain}

\maketitle

\input{tex/introduction}
\input{tex/preliminary}
\input{tex/approach}
\input{tex/empirical}
\input{tex/discussion}
\input{tex/related_work}
\input{tex/conclusion}
\input{tex/data}
\input{tex/acks}

\bibliographystyle{ACM-Reference-Format}
\balance
\bibliography{references,referencesMichael}

\end{document}
