\section{Conclusion}\label{sec:conclusion}

This paper has proposed Evolution of Heuristics (EoH), which combines large language models (LLMs) and evolutionary computation (EC) methods to design heuristics in an automatic manner. By introducing the evolution of both thoughts and codes and using five prompt strategies, EoH mimics the process of heuristic design by human experts. We have tested EoH on three well-studied optimization problems, namely the online bin-packing problem, travel salesman problem, and flow shop scheduling problem. Experiments have shown that EoH can outperform human hand-crafted heuristics in some problem instances. EoH requires only a few thousand LLM requests while achieving better performance on most test instances. EoH offers a principled approach to automatic algorithm design. The source code can be found in \url{https://github.com/FeiLiu36/EoH}.


\newpage
\section*{Acknowledgements}
The work described in this paper was supported by the Research Grants Council of the Hong Kong Special Administrative Region, China (GRF Project No. CityU11215622), the National Natural Science Foundation of China (Grant No. 62106096), the Natural Science Foundation of Guangdong Province (Grant No. 2024A1515011759), the National Natural Science Foundation of Shenzhen (Grant No. JCYJ20220530113013031).


\section*{Impact Statement}

This paper presents work whose goal is to advance the field of Machine Learning. There are many potential societal consequences of our work, none of which we feel must be specifically highlighted here.

\vspace{1pt}