\section{Background}

We consider a partially observed Markov decision process (POMDP) setting where the problem is defined by $\mathcal{M} = (\mathcal{S}, \mathcal{A}, \mathcal{O}, p_0, P, O, r, \gamma)$. 
%
At each episode, an initial state $s_0 \in \mathcal{S}$ is sampled from the initial state distribution $p_0$. 
At each time step $t$, the agent observes $o_t \in \mathcal{O}$
which is computed by the emission function $O(s_t)$,  and takes an action $a_t \in \mathcal{A}$. 
This action causes the environment to transition to a new state, $s_{t+1} \sim p(s_t, a_t)$. A new observation $o_{t+1}$ and reward $r_{t+1} = r(o_{t+1})$ are given to the agent, and the process continues. The goal of the agent is to learn a policy $\pi: \mathcal{O} \rightarrow \Delta(\mathcal{A})$ which maximizes the expected return $\mathbb{E}_{\pi}\left[\sum_t \gamma^t r_t\right]$. In this work, we additionally assume each observation $o_t$ includes a textual caption $c_t$, which could be empty. 
%
For observation spaces without textual captions, $c_t$ could in principle be provided by a captioning model as well. \looseness=-1

In many situations, the extrinsic environment reward $r$ is sparse, and the resulting return objective is challenging to optimize. We therefore consider methods which make use of an auxiliary \textit{intrinsic} reward $\rint$ and define a composite surrogate reward:
\begin{equation}
\bar{r}(o_t) =  r(o_t) + \beta \cdot \rint(o_t).
\label{eq:composed_reward}
\end{equation}
A key research question is how to define or learn the intrinsic reward $\rint$. 
A first option is to manually define $\rint$ based on task-specific goals, for example a measure of the distance between the agent's current state and the goal state. However, handcrafting the intrinsic reward function can require significant domain knowledge and must be redone for each new task.
A second option is to define $\rint$ to measure some notion of observation novelty, which encourages the agent to systematically explore the environment. This can work well in smaller environments, but fails in ones that cannot be exhaustively explored in a tractable amount of time. 
A third class of methods, which we focus on in this work, leverage LLMs to automatically synthesize $\rint$ to reflect prior knowledge about the task. We discuss all three classes of methods in more detail in \Cref{sec:related}. 


%

%
%
%
%
