\section{Preliminaries and Related Work}
\label{section:related}
\vspace{-2px}

Imitation learning methods \cite{pomerleau1988alvinn, schaal1999imitation, argall2009survey, hussein2017imitation} seek to construct a policy that accurately models the distribution of behavior in some dataset $D = \{(o_i, a_i)\}, ~ i \in \{1...N\}$ of action-observation pairs. In order to roll out these policies in an environment, they must be \emph{causal}, meaning they condition on observations from the current timestep $t$ and past timesteps only, i.e. $\pi \sim p(a_t | o_1...o_t)$. Imitation learning is simplest when demonstrations are labeled with corresponding actions. Imitating labeled trajectories has seen success in aerial vehicles, \cite{sammut1992learning, giusti2015machine} self-driving cars, \cite{bojarski2016end, codevilla2018end} board games, \cite{coulom2007computing, silver2016mastering} and video games.\cite{hester2018deep, vinyals2019grandmaster}

When labeled demonstrations are not available, standard behavioral cloning will not work; however, there is a large body of work in imitating behavior from unlabeled demonstrations. \cite{torabi2019recent} For instance, GAIL \cite{ho2016generative} constructs an adversarial objective incentivizing the trained policy to exhibit behaviors indistinguishable from those in the target dataset.
\citet{edwards2019imitating} propose to first learn a latent policy using unlabeled demonstrations and then map the learned latent actions to real actions with a small amount of environment interaction.
\citet{peng2018sfv} first use motion-capture methods to track agent positions in videos and then train RL agents to match these waypoints.
Similarly, \citet{behbahani2019learning} and \citet{aytar2018playing} task a RL agent to match waypoints; however, they construct waypoints that are embeddings from unsupervised feature learning models. 
\citet{pathakICLR18zeroshot} and \citet{nairICRA2017combine} train goal conditioned policies to take actions that advance the current state towards expert-provided goal states expressed as high dimensional visual waypoints.
Most similar to our own work, \citet{torabi2018behavioral} simultaneously train (1) an inverse dynamics model (IDM),\cite{nguyen2008learning} which aims to uncover the underlying action between timesteps given observations of past and future timesteps, e.g.\ $p_{\textrm{\textsubscript{IDM}}}(a_t | o_t, o_{t+1})$, and (2) a behavioral cloning (BC) model on trajectories of observations labeled with the IDM.
Data to train the IDM is collected by rolling out the BC model in the target environment such that both models improve in tandem.
However, at any point in training if there are sequences in the dataset that the IDM performs poorly on, it requires that the BC model perform those or similar sequences in order for the IDM to improve and correctly label them.
Therefore, if the BC model does not explore efficiently, it could severely slow down learning.
In order to avoid this potential issue we opted for a simpler two-stage approach: we first train an IDM on a small number of labeled trajectories collected from human contractors (they play the game as would normally as we record their keypresses and mouse movements). Because human contractors reach most relevant parts of the state space, we can hold the IDM fixed throughout BC training.

Compared to most previous work in semi-supervised imitation learning, we experiment in the much more complex and open-ended environment of Minecraft. Minecraft is a voxel-based 3D video game that, due its popularity and wide variety of mechanics, has attracted a vast amount of RL research.\cite{guss2019minerl, tessler2017deep, kanitscheider2021multi, oh2016control, abel2016exploratory, arumugam2019deep, trott2019keeping, alaniz2018deep, udagawa2016fighting, shu2017hierarchical, oh2017zero, shi2022learning, matiisen2019teacher, patil2020align, skrynnik2020forgetful, lin2021juewu}
A large body of work focuses on small, custom-made Minecraft worlds with tasks such as navigation,\cite{arumugam2019deep, matiisen2019teacher} block placing,\cite{trott2019keeping, alaniz2018deep} instruction following,\cite{oh2017zero, shi2022learning} combat,\cite{udagawa2016fighting} and others.\cite{oh2016control, tessler2017deep, shu2017hierarchical}
Work operating in the massive, randomly generated environments of Minecraft itself has included hill climbing,\cite{abel2016exploratory} automated curriculum learning~\cite{kanitscheider2021multi} and, most closely related to the RL experiments presented in Sec.~\ref{section:RL_finetuning}, diamond mining.\cite{guss2019minerl, patil2020align, skrynnik2020forgetful, lin2021juewu}
However, to the best of our knowledge, there is no published work that operates in the full, unmodified human action space, which includes drag-and-drop inventory management and item crafting.