
\documentclass{article} %
\usepackage[accepted]{icml2024}

\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
\usetikzlibrary{backgrounds}

\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{tabularx}
\usepackage{pifont}

\usepackage{listings}


\definecolor{darkgold}{rgb}{0.72, 0.525, 0.043}

\newcommand{\website}{{\href{https://research.memgpt.ai}{https://research.memgpt.ai}}\xspace}

\newcommand{\ours}{{{MemGPT}}\xspace}
\newcommand{\ourslong}{{{MemoryGPT}}\xspace}






\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\newcommand{\api}{\textcolor{orange}{API}}
\newcommand{\apilim}{\textcolor{red}{Limited API}}
\definecolor{darkgreen}{rgb}{0.0, 0.6, 0.0}
\newcommand{\opensource}{\textcolor{darkgreen}{Open source}}
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

\newcommand{\allnotes}[1]{}
\renewcommand{\allnotes}[1]{#1} %

\newcommand{\sarah}[1]{\allnotes{{\it\color{purple}[Sarah: #1]}}}
\newcommand{\charles}[1]{\allnotes{{\it\color{blue}[Charles: #1]}}}
\newcommand{\joey}[1]{\allnotes{{\it\color{cyan}[joey: #1]}}}
\newcommand{\ion}[1]{\allnotes{{\it\color{blue}[ion: #1]}}}

\definecolor{ForestGreen}{RGB}{34,139,34}
\newcommand{\green}[1]{\textcolor{ForestGreen}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\cmark}{\green{\ding{51}}}  %
\newcommand{\xmark}{\red{\ding{55}}}  %


\usepackage[textsize=tiny]{todonotes}



\icmltitlerunning{\ours: Towards LLMs as Operating Systems}

\begin{document}

\twocolumn[
\icmltitle{\ours: Towards LLMs as Operating Systems}





\begin{icmlauthorlist}
\icmlauthor{Charles Packer}{yyy}
\icmlauthor{Sarah Wooders}{yyy}
\icmlauthor{Kevin Lin}{yyy}\\
\icmlauthor{Vivian Fang}{yyy}
\icmlauthor{Shishir G. Patil}{yyy}
\icmlauthor{Ion Stoica}{yyy}
\icmlauthor{Joseph E. Gonzalez}{yyy}
\end{icmlauthorlist}

\icmlaffiliation{yyy}{University of California, Berkeley}

\icmlcorrespondingauthor{Charles Packer}{cpacker@berkeley.edu}

\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]



\printAffiliationsAndNotice{}  %

\begin{abstract}
\input{sections/abstract}
\end{abstract}

\section{Introduction}
\input{sections/intro}


\section{\ours (\ourslong)}
\input{sections/method_rewrite}

\input{sections/experiments}

\section{Related Work}

\input{sections/related_work}

\section{Conclusion}





In this paper, we introduced \ours, a novel LLM system inspired by operating systems to manage the limited context windows of large language models. By designing a memory hierarchy and control flow analogous to traditional OSes, \ours provides the illusion of larger context resources for LLMs. This OS-inspired approach was evaluated in two domains where existing LLM performance is constrained by finite context lengths: document analysis and conversational agents. For document analysis, \ours could process lengthy texts well beyond the context limits of current LLMs by effectively paging relevant context in and out of memory. For conversational agents, \ours enabled maintaining long-term memory, consistency, and evolvability over extended dialogues. Overall, \ours demonstrates that operating system techniques like hierarchical memory management and interrupts can unlock the potential of LLMs even when constrained by fixed context lengths. This work opens numerous avenues for future exploration, including applying \ours to other domains with massive or unbounded contexts, integrating different memory tier technologies like databases or caches, and further improving control flow and memory management policies. By bridging concepts from OS architecture into AI systems, \ours represents a promising new direction for maximizing the capabilities of LLMs within their fundamental limits.






\bibliography{refs}
\bibliographystyle{iclr2024_conference}

\newpage
\section{Appendix}
\input{sections/appendix}

\end{document}
