\section{Introduction}
Humans' ability to achieve and balance complex, multifaceted social goals in our interactions with others is a crucial part of our social intelligence as a species \citep{kihlstrom_cantor_2020,Tomasello2021becoming}.
Even a simple social goal such as sharing a blanket with a friend requires reconciling one's need to stay warm with the friend's need for personal space %
(Figure~\ref{fig:teaser}).
Successful interaction requires understanding others' intentions and beliefs \citep{premack_woodruff_1978}, while taking into account different---and potentially conflicting---social norms and expectations \citep{Goffman2022-ko}.


Even though recent AI systems have exhibited impressive social skills in certain settings, their social intelligence has yet to be ascertained in a robust way \citep{shapira2023cleverHans, ullman2023large}.
On one hand, many of the social intelligence benchmarks are not interactive \citep{sap-etal-2019-social, le-etal-2019-revisiting, zadeh2019social}, which is sub-optimal for evaluating social intelligence (\citep{mehri-etal-2022-interactive, hoppler2022six, lee2023evaluating}). On the other hand, existing interactive evaluation falls short of studying diverse goal-driven behaviors \citep{zhang2018personalizing,Park2023GenerativeAI} or focuses on specific tasks \citep{wang-etal-2019-persuasion, padmakumar2022teach, cecero2022meta}.

To study \textit{dynamic} and \textit{goal-driven} social intelligence,
we present \sotopia (Figure \ref{fig:teaser}), an open-ended general-domain environment that situates social agents in diverse social scenarios.
\sotopia is \emph{interactive}: in multi-turn simulated communication, agents can use 
verbal and non-verbal communication together with physical actions.\footnote{represented in text form.} It also has a \emph{diverse task space}: the combination of automatically generated scenarios, goals, characters, relationships, and other agents' policies creates a huge and diverse space of tasks. \sotopia evaluates agent performance from multiple dimensions besides the completion of social goals. 


In \sotopia, we create 90 social scenarios spanning a range of cooperative, competitive, and mixed social goals along with 40 characters with individual personalities, occupations, secrets, background stories, and relationships with other characters (\S\ref{sec:sotopia_characters_relationships}), the cross product of which constructs a large task space.
Through sampling tasks from this space, we simulate the interaction ``episodes'' where agents role-play their respective characters and interact based on their private social goals. 
In this simulation, we not only create and use LLM-based agents, but also involve human participants in role-playing to study the differences between the models' and humans' social intelligence. 

To evaluate \emph{multi-faceted} social interactions, we cannot only consider completing major social goals, as humans' motives often balance multiple implicit goals, such as maintaining relationships, preserving finances, gaining information, keeping secrets, and following social rules. 
Therefore, we propose \sotopiaeval (\S\ref{sec:social_dimensions}) to evaluate agents using multi-dimensional criteria inspired by previous research on sociology, psychology, and economics. We then apply \sotopiaeval to the episodes in the aforementioned simulation by leveraging both humans and GPT-4 as judges. We find GPT-4 could serve as a proxy to human judgments on \sotopiaeval, especially for the criteria of goal completion, maintaining finances, and preserving relationships.

Despite larger LLMs typically achieving higher social intelligence than smaller ones, they fall short of collaborating and competing with humans on more challenging tasks (\S\ref{sec:human_performance}). They are also highly influenced by their conversational partners and at risk of divulging secrets and violating social rules. However, we do find a few cases, where the models produced creative solutions to a problem (\S\ref{sec:model_performance}). 



Our contributions are as follows: (A) We introduce and will release \sotopia, a general-domain interactive environment for simulating goal-oriented social interactions. Designed to be extensible, \sotopia could be used by future researchers to study and train artificial social intelligence agents with more challenging and diverse tasks.
(B) We create \sotopiaeval, a multi-dimensional evaluation framework that analyzes agent performance from a range of social dimensions.
(C) We automate \sotopiaeval by leveraging LLMs, which we find could serve as a proxy of human judgment on some of the social dimensions, especially goal completion. 
(D) We demonstrate that by leveraging \sotopia, we can assess disparities in social intelligence between models, as well as disparities between models and humans. 

In summary, \sotopia is a novel, challenging, and interactive benchmark that could serve as the perfect test-bed and potential incubator for social intelligence in language agents.