\section{Differences between models and humans in social interaction}
\label{sec:human_performance}

To understand how humans and models interact differently in \sotopia, 
we conduct a study where humans interact with models or each other under this role-playing setting (\S\ref{sec:sotopia_characters_relationships}). 
Specifically, we build a chat interface that allows humans and models to interact with each other in a turn-based manner.

To fully see the difference between humans and models, we select the most challenging scenarios following \citet{dennis2020emergent, swayamdipta-etal-2020-dataset}. 
Specifically, we consider the gap between the estimated maximum rewards (average reward plus three standard deviations) of all models and the estimated minimal rewards (average reward minus three standard deviations) of the target model as the difficulty of the task for the model. 
All maximum and minimum rewards are bounded by the corresponding range.
Estimating maximum and minimum rewards with standard deviation helps filter outliers.

With this method, we select the top 20 challenging tasks for GPT-4, and we find the scenarios are commonly challenging for other models as well (compare Figure \ref{app_fig:heat_map} and \ref{app_fig:heat_map_hard}).
We use \sotopia-hard to refer to these 20 challenging tasks.


We run two experiments: (1) humans interact with GPT-4, and (2) humans interact with each other, both under the \sotopia -hard setting. 
We collect 20 human-human interactions and 40 human-GPT-4 interactions covering all 20 tasks in \sotopia -hard.
Note that humans are not aware of the identity of their partners during the interaction.%
\footnote{See Appendix \ref{app:human_performance} for the detailed instructions and the chat interface.}

\input{tabs/human_baseline_gpt4_eval.tex}
We then evaluate humans and GPT-4's interactions with GPT-4 and human annotators as the evaluators.
As shown in Table \ref{tab:human_baseline_gpt4_eval}, humans perform significantly better than GPT-4 in the \goalcompletion dimension.

It is also worth noting that humans on average produce $16.8$ words per turn, while GPT-4 produces $45.5$ words per turn, which indicates humans are more efficient in social interactions.
Specifically, we find that GPT-4 always rephrases the utterance back at the other agent and then answers, which is a communication skill called active listening \citep{weger2014relative}, whereas humans typically directly answer.
This is likely due to the fact that GPT-4 is trained with a large amount of human feedback, which makes it overly helpful in the conversation.

Qualitatively, Humans are usually more strategic than GPT-4 during interaction. When bargaining, if the GPT-4 agent has a buying target set at \$454, it sometimes starts its bid at that exact price (Figure \ref{fig:qualitative_example_strategic_gpt4}). Consequently, any subsequent negotiations push the final agreed price above its initial target. In contrast, human annotators (e.g. Figure \ref{fig:qualitative_example_strategic_human}) begin the negotiation at a lower bid of \$400, and often reaches an agreement with the seller at a price that's still below the GPT-4's target.
Humans are also more persistent in their goals.
When trying to settle one a music to listen to, the model tends to propose a compromised solution (e.g. Figure \ref{fig:qualitative_example_music_gpt4}), such as each one listening to a few selected songs. Humans, however, tend to persist in adhering to their set goals (e.g. Figure \ref{fig:qualitative_example_music_human}).









