\section{Introduction}~\label{sec:intro}

Automated issue solving aims to address real-world issues in software repositories, and holds great potential to reduce maintenance costs and improve software quality.
SWE-bench~\cite{jimenez2023swe} stands out as the most popular benchmark for automated issue solving, comprising 2,294 tasks from 12 well-maintained Python repositories.
Each task is provided with an issue statement describing the specific task to accomplish and the repository version where the issue is to be solved.
The tool to be evaluated is then required to generate a patch to address the issue. 
SWE-bench evaluates the generated patch by running tests associated with the issue, including at least one fail-to-pass test to confirm the issue is resolved, and, where available, several pass-to-pass tests to ensure no regression in existing functionality.
Recently, OpenAI hired 93 developers to manually identify and filter out those SWE-bench tasks with overly specific and even issue-unrelated tests, and curated a subset comprising 500 tasks, known as SWE-bench Verified~\cite{swebenchverified}.
The SWE-bench leaderboard is getting immense attention.
It has been used to judge the merit of new techniques proposed in academic papers~\cite{zhang2024autocoderover,xia2024agentless}, and also to evaluate commercial tools for assessing their potential value~\cite{wandbai, isoformai, blackboxai}.
Moreover, SWE-bench Verified has been widely used to evaluate the coding abilities of state-of-the-art foundation models, such as OpenAI GPT-o1~\cite{gpt-o1} and Anthropic Claude-3.5~\cite{claude-3.5}.




However, due to practical limitations, test suites are rarely exhaustive and often suffer from weaknesses~\cite{smith2015cure}.
Following the literature on automated program repair~\cite{liu2019tbar}, we refer to patches that pass their corresponding validation process as \emph{plausible patches}.
Validation with weak test suites can result in \emph{plausible but incorrect patches}, inflating the performance of the evaluated tools, and possibly leading to incorrect conclusions about their abilities.
Although others have noticed the problem of weak test suites in SWE-bench~\cite{swebenchverified, aleithan2024swe}, it is unclear to what extent evaluations performed with SWE-bench suffer from this problem, and there is a notable lack of effective methodologies for detecting plausible but incorrect patches.

This paper conducts an in-depth empirical study of the correctness of plausible generated patches on SWE-bench.
We focus on the high-quality, human-filtered, and widely used subset SWE-bench Verified, and conduct this study on the plausible patches generated by the state-of-the-art issue-solving tools, i.e., CodeStory~\cite{codestory}, LearnByInteract~\cite{su2025learn}, and OpenHands~\cite{wang2024openhands}.
Our study addresses four research questions:

\noindent \textbf{RQ1: What is the impact of executing all developer tests in SWE-bench?}
We first analyze the validation process of SWE-bench and identify a flaw that weakens the test suites.
Specifically, when validating a generated patch, SWE-bench only uses the developer-written test files modified in the pull request (PR) for fixing the target issue, potentially leaving functionality covered by other test files untested. 
To quantify the impact of this flaw,
we execute all available test files in the corresponding repository to re-validate each patch.
The results show that, on average, 7.8\% of plausible patches are incorrect, leading to an absolute drop of the issue resolution rate of 4.5\%, on average. 
This indicates that neglecting the test files not modified in the PR weakens the test suite and can inflate reported performance. 

%

The findings from RQ1 further raise two critical questions:
Are there any patches that pass all developer tests but remain incorrect? 
If yes, how many?
Answering these questions is non-trivial.
One option is to manually inspect generated plausible patches and compare them with their corresponding developer-written ground truth patch (hereon, \emph{oracle patches}).
However, this approach is labor-intensive, error-prone, and does not scale.
Another option is to generate more regression tests based on the fixed repository version to strengthen the validation~\cite{xin2017identifying,yu2019alleviating}.
However, this approach typically generates plenty of test cases with most of them unrelated to the generated patch, suffering from limited effectiveness.
Moreover, according to our investigation (Section~\ref{subsec:comparison}), there is a lack of robust and effective test generation tools for real-world Python projects.

To enable this study, we present a novel differential patch testing technique, named \appname, which aims to generate test cases that expose behavioral discrepancies between the plausible patch and the developer-written oracle patch.
We refer to such generated tests as \emph{differentiating tests}.
\appname leverages Large Language Models (LLMs) for test generation and is enabled by a call-trace-based method to identify appropriate target functions and construct useful contextual information for LLMs.
Specifically, we first leverage \appname to generate differentiating tests for each plausible patch and identify behaviorally divergent patches, and then manually assess the correctness of these suspicious patches with the help of the differentiating tests.
This approach provides concrete evidence of invalid functionality, enables more focused and objective patch validation, and reduces manual validation effort.




With the help of \appname, we address the following research questions: 

\noindent \textbf{RQ2: How many generated plausible patches exhibit behavioral discrepancies compared to their oracle patches?}
To answer this question, we leverage \appname to generate differentiating tests for the plausible patches assessed in RQ1.
Our findings reveal that, on average, 29.6\% of plausible patches can be differentiated from their oracle patches through the tests generated by \appname.
We refer to such patches as \emph{suspicious patches}.
This highlights that a substantial proportion of plausible patches are likely to diverge from the expected behavior, raising concerns about their correctness.

\noindent \textbf{RQ3: What are the patterns of differences between plausible and oracle patches that lead to behavioral discrepancies?}
Understanding these patterns offers valuable insights into how suspicious patches deviate from their oracle patches and can inspire the development of more human-aligned issue-solving tools.
To answer this question, 
we sample 77 (30\%) suspicious patches from those identified in RQ2, manually compare them with their oracle patches, and craft a taxonomy of the patch differences leading to behavioral discrepancies.
Our analysis reveals that behavioral discrepancies between plausible and oracle patches are often due to similar but divergent implementations (46.8\%) and due to plausible patches adapting more behavior than their oracle patches (27.3\%)

\noindent \textbf{RQ4: In cases of behavioral discrepancies, how many generated plausible patches are incorrect?}
A behavioral discrepancy reveals incorrectness only when the behavior of the generated patch violates the expected behavior. 
Therefore, the correctness of a suspicious patch requires further validation.
To answer this question, 
we manually assess the correctness of each suspicious patch evaluated in RQ3 based on its differentiating tests, developer-written tests, the repository, the issue statement, and the oracle patch. 
We find that 28.6\% of suspicious patches are certainly incorrect.
If we assume that incorrect patches are distributed evenly among suspicious patches, this result extrapolates to an approximated incorrectness rate of 11.0\% among plausible patches, which inflates the resolution rates of the studied tools by 6.4 absolute percent points, on average.
This result further raises concerns about the reliability of SWE-bench's validation mechanism. 

Our findings provide actionable insights for users and maintainers of issue-solving benchmarks, such as carefully selecting developer tests for patch validation, checking and filtering out plausible but incorrect patches for more accurate evaluation, and paying more attention to supplementary semantic changes in plausible patches.
In addition, the under-specified issue statements in SWE-bench Verified call for better issue-solving tools that are capable of detecting and refining vague specifications and better issue-solving benchmarks where issues are well specified.
We also envision \appname to be useful for sustainably strengthening issue-solving benchmarks.
Specifically, practitioners can use the differentiating tests generated by \appname to ease their check for incorrect patches.
The generated tests that successfully identify plausible but incorrect patches can be incorporated into the test suites in benchmarks.
Over time, as test suites continue to evolve and become comprehensive, fewer manual efforts are required and a sustainable and robust patch validation ecosystem for issue-solving tools can be built.


In summary, the main contributions of this paper are as follows:

\vspace{-2pt}

\begin{itemize}[leftmargin=*]

    \item \emph{In-depth study}. The first in-depth study on the correctness of generated plausible patches on SWE-bench. 

    \item \emph{Technique}. A novel differential patch testing technique \appname that can generate tests to reveal meaningful behavioral differences between patches.

    \item \emph{Insights}. Insights for users and maintainers of issue-solving benchmarks towards more robust and sustainable evaluation.

    \item \emph{Replication package}. A replication package~\cite{package} including the implementation of \appname and the results of our study.
    





\end{itemize}


