\subsection{RQ1: Impact of Executing All Developer Tests}
As described in Section~\ref{sec:background}, the validation process of SWE-bench (Verified) assesses patch correctness only based on modified test files, which can lead to plausible but incorrect patches.
However, the severity of this flaw remains unclear. 
In this RQ, we aim to systematically evaluate the impact of this flaw on the reported performance of issue-solving tools.

\noindent \textbf{Approach:}
To answer RQ1, for each generated plausible patch,  we first apply the test patch to the repository and collect all available test files from the repository.
Next, we run these test files sequentially after applying the generated patch or the oracle patch separately. 
We then compare the test results of the two patches and record any generated patch that shows inconsistent behavior with the corresponding oracle patch, i.e., at least one test passes with the oracle patch but fails with the generated patch.
We further execute the tests that trigger inconsistent behaviors 20 times with the oracle patch to filter out flaky tests.
We observe that some developer tests focus on coding conventions rather than functionality, e.g., detecting trailing whitespace or ensuring files end with no more than one newline.
To prioritize functional correctness, we exclude the generated patches that only show inconsistencies related to coding conventions. 
The remaining generated patches introduce regression errors and are therefore incorrect.

\input{tex/tables/rq1}

\noindent \textbf{Results:}
Executing all available developer tests exposes notable overestimation in the reported performance of issue-solving tools. 
Among the plausible patches generated by the three tools, 7.2\% to 8.4\% of them are functionally incorrect when subjected to all developer tests. 
This translates to an absolute drop of 3.8\% to 5.2\% in reported resolution rates, highlighting the systematic overestimation inherent in the current validation process. 
These findings confirm the existence of plausible but incorrect patches on SWE-bench Verified and underscore the necessity of leveraging all available developer tests to enable a more robust and comprehensive assessment of patch correctness.

%
%
An example is the plausible patch produced by CodeStory to resolve django-13279. 
This issue is to use legacy \verb|encode| function to decode session data when \verb|DEFAULT_HASHING_ALGORITHM| is set to \verb|sha1|. 
Although the generated patch passes the tests in the PR-modified test files, 
it fails on another developer test where the \verb|_legacy_decode| function is tested, 
suggesting that the implementation of legacy \verb|encode| in the generated patch is not compatible with the original \verb|_legacy_decode| function. 

\noindent \fbox{
	\parbox{0.95\linewidth}{\textbf{Answers to RQ1}: Executing all developer tests reveals that on average 7.8\% of plausible patches are incorrect, which leads to an absolute performance drop of 4.5\% on average. This emphasizes the necessity of leveraging all developer tests for more robust patch validation. }
}

