\section{Conclusion}
\label{sec:conclusion}

We provide SICA, a self-improving coding agent.
Our results demonstrate that self-improvement, implemented via an agent system
editing its own codebase, is indeed possible, particularly in longer-horizon
`agentic' tasks where the base \acr{LLM}s stand to gain more from the structure
and guidance of a scaffolding system---for instance showing improvements from
17\% to 53\% on a random subset of SWE-Bench Verified, while also achieving a
slight decrease in the average time spent per problem on average.
The framework we present offers both a practical approach to automated
agent system design and a foundation for future work in jointly training
foundation models with their agent systems.
\subsection{Limitations}
\label{sec:limitations}

Our initial attempt at a self-improving coding agent is not without
limitations. One key difficulty was getting the LLM-based agent to autonomously
come up with truely novel, innovative, feasible and interesting modification
ideas at each meta-improvement step, which is a theme which has been commented
on in the open-ended learning literature
\citep{nathaniMLGymNewFramework2025,yamadaAIScientistv2WorkshopLevel2025,hughesOpenEndednessEssentialArtificial2024}.
The cost of settling on a bad idea which suffered from poor `taste' was a
lengthy agent editing step followed by an even more expensive run through the
benchmarks. While the failed iteration persists in the archive, in principle
acting as an example of what not to do, we found that the initial feature ideas
would often heavily influence later feature ideas as variations on the same
theme. This path dependency may lead to higher variance agent runs; with poor
quality initial feature suggestions (e.g. fixating on caching open files)
often lowering the quality of subsequent feature suggestions.

We also note that in optimizing for agent running time and cost, our relatively
short 5-minute timeouts (and to a lesser degree per-problem cost limits) cause
the initial benchmark scores to perhaps be lower than expected for the
underlying language model (e.g. Sonnet 3.5 v2), especially for longer-horizon
benchmark tasks like SWE-Bench. Indeed, much of the initial improvement we report
arises from features speeding up file editing and agent cost, which are not
traditionally reflected to the same degree in SWE-Bench numbers.

\subsection{Future Work}
\label{sec:future}

Our approach reflects a non weight-based learning mechanism, where we update the
system's behaviour through a combination of optimising the prompts on which the
model is conditioned, as well as the way the \acr{LLM} calls are orchestrated by
editing the underlying code. This is in some sense very sample-efficient, where
a detailed inspection of the archive of outcomes informs substantial
modifications at each step. However, we recognize the potential of jointly
updating the foundation model's weights with the agent system. The work of
AlphaEvolve \citep{novikovAlphaEvolveCodingAgent2025} demonstrates a proof of
this principle, and it may be fruitful to more explicitly fine-tune the foundation
model to work with new newly created tools and scaffold at each iteration.

While we did not get to the point of benchmark saturation in our relatively
short runs, we expect that future systems may run out of things to learn from a
static benchmark set. One way this problem may be solved is through the
automated design and curation of benchmarks, as initially demonstrated in the
work of \cite{faldorOMNIEPICOpenendednessModels2024} where RL environments are
designed in code. By including two synthetic benchmarks in our work which were
curated entirely by the agent through manual prompting (the file editing and
symbol navigation benchmark) we demonstrate that \acr{SICA} is flexible enough
to support creating new benchmarks and evaluations for itself.

\section{Safety Considerations}%
\label{subsec:safety}

It is vitally important to carefully consider the safety implications posed by systems designed to be self-improving.
While our self-improving coding agent shows improvement in certain agentic tasks, there seem to be limits to what
can be achieved with such purely scaffolding based systems (as seen in Figure~\ref{fig:aime_gpqa}), which do not modify the model weights.
If the system updated the model weights as well as the scaffolding, we would expect that the risks of recursively self-improving systems would be higher. We highlight two key mechanisms for mitigating any risks.

First, a key safety mitigation in such systems is observability: that humans can and do oversee all aspects of potentially self-improving systems.
We have thus architected \acr{SICA} with sophisticated yet user-friendly observability mechanisms, which provide rich insight into the chain-of-thought, actions and sub-agent invocations at each step. These include an interactive web interface for easy oversight of all events occurring in the agent system, as well as the asynchronous LLM-based overseer, which may be prompted to treat various behaviors as grounds for canceling an agent, and which may also use a different LLM to the running agent.
See Appendix~\ref{subsec:overseer_prompt} for an example overseer judgement and
the control afforded to it at each asynchronous invocation.
Given the lack of model weight updates, which make it difficult but not impossible for the model to encode e.g.\ stenographic messages \citep{motwani2023perfect,motwani2024secret} in the chain-of-thought, we believe this provides strong safety mitigation.
That said, for recursively self-improving systems where the model weights are also updated, observability mechanisms, on their own, are clearly inadequate, and further research on safety mechanisms is clearly necessary.

The second opportunity for safety mitigation is inherent to the iterative, evaluation-based update procedure. While our initial benchmark set focuses on measuring capabilities we wish to improve, it is entirely possible to include safety-related evaluations in this benchmark set, to validate each agent before it progresses to the next iteration as the meta-agent.

We do not believe there to be any significant, direct adverse societal
consequences to this work. Our objectives either focus on improving the
mechanics of code editing or the effectiveness of multi-step reasoning through
longer-horizon coding tasks.
