
\documentclass{article} %
\usepackage{iclr2024_conference,times}

\input{math_commands.tex}

\usepackage{url}
\usepackage{booktabs}       %
\usepackage{amsfonts}       %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage{amsmath,amsthm}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[font=small]{caption} 
\usepackage{listings}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{xspace} 
\usepackage{bbm}

\usepackage[toc,page,header]{appendix}
\usepackage{minitoc}
\usepackage{xpatch}

\usepackage{subcaption}
\usepackage{multirow, makecell}
\usepackage{multicol}
\usepackage{array}
\usepackage{amssymb,bm,amsthm}
\usepackage{enumitem}
\usepackage[misc,geometry]{ifsym}
\usepackage{adjustbox}
\usepackage{xfrac}
\usepackage{listings}
\usepackage{ltablex}  %
\usepackage{tabularx}
\setlength{\extrarowheight}{2pt}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepink}{RGB}{252, 142, 172}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{RGB}{245,245,245}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{magenta},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\fontfamily{\ttdefault}\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    keepspaces=true,    
    frame=single,
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    classoffset=1, %
    keywordstyle=\color{violet},
    classoffset=0,
}
\lstset{style=mystyle}
\usepackage{color}
\usepackage{xcolor}
\definecolor{citecolor}{HTML}{3498DB}
\definecolor{linkcolor}{HTML}{E74C3C}
\usepackage[pagebackref=false,breaklinks=true,colorlinks,bookmarks=false,citecolor=citecolor,linkcolor=black]{hyperref}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\usepackage{tabularx}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{Y}{>{\centering\arraybackslash}X}


\usepackage{soul}
\DeclareRobustCommand{\hlorange}[1]{{\color{White}\sethlcolor{Orange}\hl{#1}}}
\DeclareRobustCommand{\hlpink}[1]{{\color{White}\sethlcolor{VioletRed}\hl{#1}}} %
\DeclareRobustCommand{\hlpurple}[1]{{\color{White}\sethlcolor{Purple}\hl{#1}}}
\DeclareRobustCommand{\hlred}[1]{{\color{White}\sethlcolor{Red}\hl{#1}}}

\newcommand{\Todo}[1]{\hlpink{\textbf{TODO:} #1}}
\newcommand{\Urgent}[1]{\hlred{\textbf{URGENT:} #1}}
\newcommand{\Tocite}[1]{\colorbox{Orange!90}{\color{White} cite:#1}\xspace}
\newcommand{\Highlight}[1]{{\sethlcolor{Yellow}\hl{#1}}}






\definecolor{snsgray}{RGB}{179, 179, 179}
\definecolor{snsorange}{RGB}{252, 141, 98}
\definecolor{snsblue}{RGB}{141, 160, 203}

\definecolor{coolgrey}{RGB}{157,157,157}
\definecolor{lightgrey}{RGB}{235,238,238}
\definecolor{lightteal}{RGB}{198,211,222}
\definecolor{cyan}{RGB}{136, 204, 238}
\definecolor{teal}{RGB}{68, 170, 153}
\definecolor{sand}{RGB}{221, 204, 119}
\definecolor{rose}{RGB}{204, 102, 119}
\definecolor{red}{RGB}{250, 94, 91}
\definecolor{orange}{RGB}{255, 200, 63}
\definecolor{yellow}{RGB}{254, 239, 109}

\definecolor{darkred}{RGB}{255, 184, 119}
\definecolor{darkgreen}{rgb}{0.09, 0.45, 0.27}
\newcommand{\textcolorbox}[2]{\colorbox{#1}{\strut #2}}
\newcommand{\narrowcolorbox}[2]{\setlength{\fboxsep}{2pt}\colorbox{#1}{#2}}

\newcommand{\anima}[1]{\textcolor{blue}{Anima:~#1}}

\newcommand{\redscore}[1]{\textcolor{red}{\mathbf{#1}}}
\newcommand{\bestscore}[1]{\textcolor{darkgreen}{\mathbf{#1}}}
\newcommand{\bestpercent}[1]{\textcolor{darkgreen}{\text{#1\%}}}
\newcommand{\para}[1]{\paragraph{#1}\looseness=-1}
\newcommand{\arxiv}[1]{\textcolor{black}{#1}}

\newtheorem*{remark}{Remark}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{example}{Example}

\usepackage[toc,page,header]{appendix}
\usepackage{minitoc}

\renewcommand \thepart{}
\renewcommand \partname{}

\title{\ourmethod: Human-level Reward Design via \\ Coding Large Language Models}



\newcommand{\weburl}{\url{https://eureka-research.github.io}}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\author{%
    Yecheng Jason Ma$^{1\,2 \text{ \Letter}}$ , William Liang$^2$, Guanzhi Wang$^{1\,3}$, De-An Huang$^{1}$, Osbert Bastani$^{2}$,\\
    \textbf{Dinesh Jayaraman$^{2}$, Yuke Zhu$^{1\,4}$, Linxi ``Jim'' Fan$^{1\text{ \Letter}\,\dag}$, Anima Anandkumar$^{1\,3\,\dag }$}\\
    \hspace{2.3cm} $^1$NVIDIA, $^2$UPenn, $^3$Caltech, $^4$UT Austin; $^\dag$Equal advising\\
    \hspace{3cm} \weburl
}


\newcommand{\ourmethod}{\mbox{\textsc{Eureka}}\xspace}
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy %
\begin{document}
\doparttoc %
\faketableofcontents %

\maketitle

\begin{abstract}

Large Language Models (LLMs) have excelled as high-level semantic planners for sequential decision-making tasks. However, harnessing them to learn complex low-level manipulation tasks, such as dexterous pen spinning, remains an open problem. We bridge this fundamental gap and present \ourmethod, a human-level reward design algorithm powered by LLMs. \ourmethod exploits the remarkable zero-shot generation, code-writing, and in-context improvement capabilities of state-of-the-art LLMs, such as GPT-4, to perform evolutionary optimization over reward code. The resulting rewards can then be used to acquire complex skills via reinforcement learning. Without any task-specific prompting or pre-defined reward templates, \ourmethod generates reward functions that outperform expert human-engineered rewards. In a diverse suite of 29 open-source RL environments that include 10 distinct robot morphologies, \ourmethod outperforms human experts on \textbf{83\%} of the tasks, leading to an average normalized improvement of \textbf{52\%}. The generality of \ourmethod also enables a new gradient-free in-context learning approach to reinforcement learning from human feedback (RLHF), readily incorporating human inputs to improve the quality and the safety of the generated rewards without model updating. Finally, using \ourmethod rewards in a curriculum learning setting, we demonstrate for the first time, a simulated Shadow Hand capable of performing pen spinning tricks, adeptly manipulating a pen in circles at rapid speed. 





\end{abstract}


\input{intro}
\input{problem-setting}
\input{method}
\input{experiments}
\input{related-work}










\vspace{-0.3cm}
\section{Conclusion}
\vspace{-0.3cm}

We have presented \ourmethod, a universal reward design algorithm powered by coding large language models and in-context evolutionary search. Without any task-specific prompt engineering or human intervention, \ourmethod achieves human-level reward generation on a wide range of robots and tasks. \ourmethod's particular strength in learning dexterity solves dexterous pen spinning for the first time with a curriculum learning approach. Finally, \ourmethod enables a gradient-free approach to reinforcement learning from human feedback that readily incorporates human reward initialization and textual feedback to better steer its reward generation. The versatility and substantial performance gains of \ourmethod suggest that the simple principle of combining large language models with evolutionary algorithms are a general and scalable approach to reward design, an insight that may be generally applicable to difficult, open-ended search problems. 





\newpage 

\section*{Acknowledgement}
We are grateful to colleagues and friends at NVIDIA and UPenn for their helpful feedback and insightful discussions. We thank Viktor Makoviychuk, Yashraj Narang, Iretiayo Akinola, Erwin Coumans for their assistance on Isaac Gym experiment and rendering. This work is done during Yecheng Jason Ma's internship at NVIDIA. We acknowledge funding support from NSF CAREER Award 2239301, ONR award N00014-22-1-2677, NSF Award CCF-1917852, and ARO Award W911NF-20-1-0080.


\newpage 

\bibliography{iclr2024_conference}
\bibliographystyle{iclr2024_conference}

\newpage 

\appendix
\input{appendix/0-main-appendix}

\end{document}
