\section{Introduction}
\label{sec:introduction}
\input{figs/pull_figure}
Developing autonomous embodied agents that can attain human-level performance across a wide spectrum of tasks has been a long-standing goal for AI research. There has been impressive progress towards this goal, most notably in games \cite{mnih2013playing, openai2019dota, vinyals2019alphastar} and robotics \cite{kolve2017ai2thor, savva2019habitat, zhu2020robosuite, xia2019igibson0.5, shen2020igibson}. These embodied agents are typically trained \textit{tabula rasa} in isolated worlds with limited complexity and diversity. Although highly performant, they are specialist models that do not generalize beyond a narrow set of tasks. 
In contrast, humans inhabit an infinitely rich reality, continuously learn from and adapt to a wide variety of open-ended tasks, and are able to leverage large amount of prior knowledge from their own experiences as well as others.  

We argue that \textbf{three main pillars} are necessary for generalist embodied agents to emerge. First, the environment in which the agent acts needs to \textbf{enable an unlimited variety of open-ended goals} \cite{standish2003open, langdon2005pfeiffer, taylor2016open, stanley2017open}. Natural evolution is able to nurture an ever-expanding tree of diverse life forms thanks to the infinitely varied ecological settings that the Earth supports \cite{stanley2017open, wang2019paired}. This process has not stagnated for billions of years. In contrast, today's agent training algorithms cease to make new progress after convergence in narrow environments \cite{mnih2013playing,zhu2020robosuite}.
Second, a \textbf{large-scale database of prior knowledge} is necessary to facilitate learning in open-ended settings. Just as humans frequently learn from the internet, agents should also be able to harvest practical knowledge encoded in large amounts of video demos~\cite{goyal2017something, miech2019howto100m}, multimedia tutorials~\cite{minecraftwiki}, and forum discussions~\cite{volske-etal-2017-tl, DBLP:conf/naacl/KimKK19, henderson2019repository}. In a complex world, it would be extremely inefficient for an agent to learn everything from scratch through trial and error.  
Third, the \textbf{agent's architecture} needs to be flexible enough to pursue any task in open-ended environments, and scalable enough to convert large-scale knowledge sources into actionable insights~\cite{ranzato2021decisiontransformer,reid2022wikipedia}. This motivates the design of an agent that has a unified observation/action space, conditions on natural language task prompts, and adopts the Transformer pre-training paradigm~\cite{devlin2018bert,radford2019gpt2, brown2020gpt3} to internalize knowledge effectively. 

In light of these three pillars, we introduce \minedojo, a new framework to help the community develop open-ended, generally-capable agents. It is built on the popular Minecraft game, where a player explores a procedurally generated 3D world with diverse types of terrains to roam, materials to mine, tools to craft, structures to build, and wonders to discover. 
Unlike most other games \cite{mnih2013playing, openai2019dota, vinyals2019alphastar}, Minecraft defines no specific reward to maximize and no fixed storyline to follow, making it well suited for developing open-ended environments for embodied AI research. 
We make the following three major contributions: 

\para{1. Simulation platform with thousands of diverse open-ended tasks.}\minedojo provides convenient APIs on top of Minecraft that standardize task specification, world settings, and agent's observation/action spaces. We introduce a benchmark suite that consists of thousands of natural language-prompted tasks, making it \textit{two orders of magnitude} larger than prior Minecraft benchmarks like the MineRL Challenge \cite{guss2019minerl,kanervisto2022minerl}. 
The suite includes long-horizon, open-ended tasks that cannot be easily evaluated through automated procedures, such as ``\textit{build an epic modern house with two floors and a swimming pool}''. %
Inspired by the Inception score~\cite{DBLP:conf/nips/SalimansGZCRCC16} and FID score~\cite{DBLP:conf/nips/HeuselRUNH17} that are commonly used to assess AI-generated image quality, we introduce a novel agent evaluation protocol using a large video-language model pre-trained on Minecraft YouTube videos. 
This complements human scoring \cite{shah2021basalt} that is precise but more expensive. 
Our learned evaluation metric has good agreement with human judgment in a subset of the full task suite considered in the experiments.

\para{2. Internet-scale multimodal Minecraft knowledge base.} Minecraft has more than 100 million active players \cite{enwiki:1092238294}, who have collectively generated an enormous wealth of data. They record tutorial videos, stream live play sessions, compile recipes, and discuss tips and tricks on forums. \minedojo features a massive collection of 730K+ YouTube videos with time-aligned transcripts, 6K+ free-form Wiki pages, and 340K+ Reddit posts with multimedia contents (Fig. \ref{fig:dataset}). We hope that this enormous knowledge base can help the agent acquire diverse skills, develop complex strategies, discover interesting objectives,  and learn actionable representations automatically.

\para{3. Novel algorithm for embodied agents with large-scale pre-training.} 

We develop a new learning algorithm for embodied agents that makes use of the internet-scale domain knowledge we have collected from the web. Using the massive volume of YouTube videos from \minedojo, we train a video-text contrastive model in the spirit of CLIP \cite{radford2021clip}, which associates natural language subtitles with their time-aligned video segments. 
We demonstrate that this learned correlation score can be used effectively as an \textit{open-vocabulary, massively multi-task reward function} for RL training. Our agent solves the majority of 12 tasks in our experiment using the learned reward model (Fig.~\ref{fig:behavior_visualization}). It achieves competitive performance to agents trained with meticulously engineered dense-shaping rewards, and in some cases outperforms them, with up to 73\% improvement in success rates. For open-ended tasks that do not have a simple success criterion, our agents also perform well without any special modifications.

In summary, this paper proposes an open-ended task suite, internet-scale domain knowledge, and agent learning with recent advances on large pre-trained models \cite{bommasani2021foundation}. \Rebuttal{We have open-sourced \minedojo's simulator, knowledge bases, algorithm implementations, pretrained model checkpoints, and task curation tools at \mbox{\url{https://minedojo.org/}}.} We hope that \minedojo will serve as an effective starter framework for the community to develop new algorithms and advance towards generally capable embodied agents. 



