\section{Conclusion}
\label{sec:conclusion}

In this work, we introduce the \minedojo framework for developing generally capable embodied agents. \minedojo features a benchmarking suite of thousands of Programmatic and Creative tasks, and an internet-scale multimodal knowledge base of videos, wiki, and forum discussions. As an example of the novel research possibilities enabled by \minedojo, we propose \mineclip as an effective language-conditioned reward function trained with in-the-wild YouTube videos. \mineclip achieves strong performance empirically and agrees well with human evaluation results, making it a good automatic metric for Creative tasks. We look forward to seeing how \minedojo empowers the community to make progress on the important challenge of open-ended agent learning.


\section{Acknowledgement}
\label{sec:acknowledgement}

We are extremely grateful to Anssi Kanervisto, Shikun Liu, Zhiding Yu, Chaowei Xiao, Weili Nie, Jean Kossaifi, Jonathan Raiman, Neel Kant, Saad Godil,  Jaakko Haapasalo, Bryan Catanzaro, John Spitzer, Zhiyuan ``Jerry'' Lin, Yingqi Zheng, Chen Tessler, Dieter Fox, Oli Wright, Jeff Clune, Jack Parker-Holder, and many other colleagues and friends for their helpful feedback and insightful discussions. We also thank the anonymous reviewers for offering us highly constructive advice and kind encouragement during the review and rebuttal period. NVIDIA provides the necessary computing resource and infrastructure for this project. Guanzhi Wang is supported by the Kortschak fellowship in Computing and Mathematical Sciences at Caltech. 