\section{Related Works}
\label{sec:related}
\paragraph{Prompts in LLMs} Prompting is an efficient method for employing LLMs in specialized tasks. However, the performance is heavily influenced by the choice of the prompt. Recently, automatic prompt optimization has obtained wide attention.
Continuous prompt-based methods, which only tune parameters of some input tokens~\citep{li2021prefix,liu2021gpt,liu2021p,zhang2021differentiable} attract lots of attention. In spite of their effective performance, two drawbacks of such paradigms can not be ignored: \textbf{1)} The optimization of continuous prompts requires parameters of LLMs that are inaccessible for black-box APIs. 
\textbf{2)} Soft prompts often fall short of interpretability~\citep{lester2021promptuning}. Discrete prompts, simply adding several discrete tokens, such as ``It was''~\citep{schick2021exploiting}, or task-specific descriptive instructions, such as ``Classify the comment into positive or negative.'', to the input text, can offer an interactive interface to humans with better interpretability and show promising performance in various NLP tasks~\citep{liu2023pre}.


\paragraph{Discrete Prompts} 
Various approaches have been proposed for automatic discrete prompt searching and generation~\citep{shin2020autoprompt,shi2022toward,wallace2019universal,deng2022rlprompt,zhang2023tempera}, while these methods still rely on the gradients or the token probabilities from the output layer. More recently, considering the high variance of different prompts for downstream tasks, some works focus on \emph{exploration} by enumerating and selecting the best prompt from a number of candidates, mainly augmented by re-sampling~\citep{zhou2022large,jiang2020can}. Approaches based on prompt edit~\citep{zhang2023tempera,prasad2022grips} emphasize \emph{exploitation}, which may potentially lead to local optima. Another approach collects the incorrectly predicted cases and analyzes the corresponding root cause to improve existing prompts~\citep{pryzant2023automatic,guo2023learning}, which also emphasizes \emph{exploitation}. Additionally, such approaches are constrained to tasks with standard answers and cannot be directly applied to generation tasks. Our proposed \modelname empowered with evolutionary algorithms strikes a balance between \emph{exploration} and \emph{exploitation} without requiring any parameters or gradients.

\paragraph{LLMs and Optimization Algorithms}
LLMs demonstrate the potential to serve as black-box optimizers~\citep{zheng2023can}; however, this black-box approach lacks explainability. Some works have revealed that LLMs have the capability to imitate specific operations in conventional algorithms. For instance, LLMs can perform ``Gradient Descent'' in discrete space by collecting incorrectly predicted samples~\citep{pryzant2023automatic, guo2023learning}. Meanwhile, it has been demonstrated that LLMs can imitate the mutation~\citep{Lehman2023evolution} or crossover~\citep{meyerson2023language} operator in the genetic algorithm (GA). \cite{chen2023evoprompting} further integrates LLMs and GA for neural architecture search, while \cite{lanzi2023chatgpt} introduce a similar approach to game design. Our work has taken a significant step forward by proposing a general framework that connects LLMs with evolutionary algorithms, which can be instantiated to a diverse range of evolutionary algorithms through customization of evolutionary and selection processes, thereby broadening its applicability and potential influence in the domain. We aspire this work to inspire broader applications of combining LLMs and conventional algorithms.



