
\documentclass{article} %
\usepackage{iclr2024_conference,times}

\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage[utf8]{inputenc} %
\usepackage[T1]{fontenc}    %
\usepackage{hyperref}       %
\hypersetup{
    colorlinks,
    citecolor=[rgb]{0.00, 0.45, 0.70},
    linkcolor=[rgb]{0.01, 0.62, 0.45},
    urlcolor=[rgb]{0.80, 0.47, 0.74},
    }
\usepackage{url} 
\usepackage{booktabs}       %
\usepackage{amsfonts}       %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage[most]{tcolorbox}
\usepackage{arydshln}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{comment}
\usepackage{tcolorbox}
\usepackage{color,xcolor,colortbl}
\usepackage{amsmath}  
\usepackage{wrapfig}

\usepackage{textcomp}
\usepackage{threeparttable}
\usepackage{enumitem}
\usepackage{inconsolata}
\usepackage{algpseudocode}
\usepackage{soul}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{algorithm,algpseudocode}
\usepackage{xspace}
\usepackage{marginnote}
\usepackage{amssymb}

\newcommand{\modelname}{{{\textsc{EvoPrompt}}}\xspace}
\definecolor{Blue}{HTML}{6A9AD0}  
\definecolor{Red}{rgb}{0.746, 0.0039, 0}  
\definecolor{Green}{HTML}{7EAB55}  
\definecolor{Orange}{HTML}{DE8344}
\definecolor{Pink}{HTML}{FF7AA1}
\definecolor{Yellow}{HTML}{FFC000}
\definecolor{Gray}{gray}{0.95}
\definecolor{Purple}{HTML}{E5CBFF}
\definecolor{ShallowGreen}{HTML}{E2F0D9}
\definecolor{ShallowGray}{HTML}{D6DCE5}
\newcommand{\purplebox}{\textcolor{Purple}{$\blacksquare$}}
\newcommand{\graybox}{\textcolor{ShallowGray}{$\blacksquare$}}
\newcommand{\greenbox}{\textcolor{ShallowGreen}{$\blacksquare$}}

\newcommand{\scriptnumber}[1]{\textcolor{gray}{\scriptsize (#1)}}

\usepackage{pifont}%
\newcommand{\cmark}{{\color{Green} \ding{51}}}
\newcommand{\xmark}{{\color{Red} \ding{55}}}
\newcommand{\bei}[1]{\textcolor{blue}{[Bei: #1]}}

\title{EvoPrompt: Connecting LLMs with Evolutionary Algorithms Yields Powerful Prompt Optimizers}


\author{Qingyan Guo$^{12\dag}$\thanks{Work done during an internship at Microsoft Research Asia.
}~~,
Rui Wang$^{2}$\thanks{Equal Contribution.}~~, Junliang Guo$^{2}$, Bei Li$^{23}$, Kaitao Song$^{2}$, Xu Tan$^{2}$\thanks{Corresponding Author.}~~,\\
\textbf{
Guoqing Liu$^{2}$, Jiang Bian$^{2}$, 
Yujiu Yang$^{1\ddag}$~~ } \\
$^1$Tsinghua University\quad 
$^2$Microsoft Research\quad 
$^3$Northeastern University \\
\texttt{gqy22@mails.tsinghua.edu.cn},
\texttt{libei\_neu@outlook.com},\\
\texttt{\{ruiwa,junliangguo,kaitaosong,xuta,guoqingliu,jiabia\}@microsoft.com}\\
\texttt{yang.yujiu@sz.tsinghua.edu.cn}
}

\iclrfinalcopy 
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\begin{document}


\maketitle

\begin{abstract}












Large Language Models (LLMs) excel in various tasks, but they rely on carefully crafted prompts that often demand substantial human effort. To automate this process, in this paper, we propose a novel framework for discrete prompt optimization, called \modelname, which borrows the idea of evolutionary algorithms (EAs) as they exhibit good performance and fast convergence. To enable EAs to work on discrete prompts, which are natural language expressions that need to be coherent and human-readable, we connect LLMs with EAs. This approach allows us to simultaneously leverage the powerful language processing capabilities of LLMs and the efficient optimization performance of EAs. Specifically, abstaining from any gradients or parameters, \modelname starts from a population of prompts and iteratively generates new prompts with LLMs based on the evolutionary operators, improving the population based on the development set. We optimize prompts for both closed- and open-source LLMs including GPT-3.5 and Alpaca, on 31 datasets covering language understanding, generation tasks, as well as BIG-Bench Hard (BBH) tasks. \modelname significantly outperforms human-engineered prompts and existing methods for automatic prompt generation (e.g., up to $25\%$ on BBH). Furthermore, \modelname demonstrates that connecting LLMs with EAs creates synergies, which could inspire further research on the combination of LLMs and conventional algorithms. 
Our code is available at \url{https://github.com/beeevita/EvoPrompt}.


\end{abstract}

\input{1intro}
\input{2related}
\input{3method}
\input{4exp}
\input{ana_short}
\input{7con}

\bibliography{iclr2024_conference}
\bibliographystyle{iclr2024_conference}


\input{appendix}
\end{document}
