\section{Discussion and Conclusion}
\label{section:discussion}
The results presented in this paper help pave the path to utilizing the wealth of unlabeled data on the web for sequential decision domains. 
Compared to generative video modeling or contrastive methods that would only yield representational priors, 
VPT offers the exciting possibility of directly \emph{learning to act} during pretraining and using these learned behavioral priors as extremely effective exploration priors for RL.
VPT could even be a better general representation learning method even when the downstream task is not learning to act in that domain—for example, fine-tuning to explain what is happening in a video—because arguably the most important information in any given scene would be present in features trained to correctly predict the distribution over future human actions. We leave this intriguing direction to future work.

Future work could improve results with more data (we estimate we could collect >1M hours) and larger, better-tuned models. Furthermore, all the models in this work condition on past observations only; we cannot ask the model to perform specific tasks. Appendix~\ref{appendix:text_conditioning} presents preliminary experiments on conditioning our models on closed captions (text transcripts of speech in videos), showing they become weakly steerable; we believe this a rich direction for future research.
Also, loss was not consistently correlated with downstream evaluation metrics (Sec.~\ref{section:results_foundation}), which often made progress slow and hard-won.
Another fruitful future direction would be to investigate the correlation between various training metrics and downstream evaluations.
Finally, while we do not anticipate any direct negative societal impacts from the models trained in this work, as VPT improves and expands to other domains it will be important to assess and mitigate harms that emerge with other forms of pretraining on internet datasets, such as emulating inappropriate behavior.\cite{bender2021dangers} 

In conclusion, VPT extends the paradigm of training large and general purpose behavioral priors from freely available internet-scale data to sequential decision domains.
Our models exhibited impressive zero-shot behavior and, when fine-tuned with RL, achieved an unprecedented result of crafting a diamond pickaxe in Minecraft (all the more difficult given the human interface).
We further showed that contractor data is far better used within the VPT pipeline than to train a foundation model directly and that only a small amount of contractor data (about \$2000 USD) was required to unlock massive amounts of unlabeled online data for use in BC. 
Finally, learning with the human keyboard and mouse interface is highly general and allows losslessly modeling the entire distribution of human behavior.
While we only experiment in Minecraft, we believe that VPT provides a general recipe for training behavioral priors in hard, yet generic, action spaces in any domain that has a large amount of freely available unlabeled data, such as computer usage.
