\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2021

% ready for submission
%\usepackage{neurips_2021}
\PassOptionsToPackage{super,sort&compress,comma,compress}{natbib}

\usepackage[preprint]{neurips_2021}

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2021}

% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2021}

% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2021}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage[hidelinks]{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{multicol}
\usepackage[normalem]{ulem} % for sout (strikethrough)
\usepackage{wrapfig}
\usepackage[percent]{overpic}
\usepackage{lipsum}
\usepackage{csquotes}
\usepackage[OT2,T1]{fontenc}
\usepackage[russian,greek,english]{babel}
%%%%%%%%%%%%%%%%%%%%%%

\DeclareUnicodeCharacter{FFFD}{?}

\newcommand{\eqn}[1]{\begin{equation}#1\end{equation}}

\newif\ifcomment
% \commentfalse
\newcommand{\bb}[1]{\textcolor{red}{\ifcomment(BB: #1)\else\fi}}
\newcommand{\jc}[1]{\textcolor{blue}{\ifcomment JC: #1\else\fi}}
\newcommand{\jcc}[1]{\textcolor{violet}{\ifcomment(JC Comment: #1)\else#1\fi}}
\newcommand{\jcsout}[1]{\textcolor{blue}{\ifcomment(JC: \sout{#1})\else\fi}}
\newcommand{\jh}[1]{\textcolor{olive}{\ifcomment(JH: #1)\else\fi}}
\newcommand{\jhs}[1]{\textcolor{olive}{\ifcomment #1\else#1\fi}}
\newcommand{\pz}[1]{\textcolor{cyan}{\ifcomment(PZ: #1)\else\fi}}
\newcommand{\pzout}[1]{\textcolor{cyan}{\ifcomment(PZ: \sout{#1})\else\fi}}
\newcommand{\ia}[1]{\textcolor{orange}{\ifcomment(IA: #1)\else\fi}}
\newcommand{\ale}[1]{\textcolor{teal}{\ifcomment(AE: #1)\else\fi}}
\newcommand{\alesout}[1]{\textcolor{teal}{\ifcomment(AE: \sout{#1})\else\fi}}
\newcommand{\jt}[1]{\textcolor{violet}{\ifcomment(JT: #1)\else\fi}}
\newcommand{\bh}[1]{\textcolor{purple}{\ifcomment(BAH: #1)\else\fi}}
\newcommand{\todo}[1]{\textcolor{red}{\ifcomment(\textbf{TODO}: #1)\else\fi}}


\title{Video PreTraining (VPT): Learning to Act by Watching Unlabeled Online Videos}

\author{
Bowen Baker\footnotemark[1]\hspace{4px}\footnotemark[2]\\bowen@openai.com\And
Ilge Akkaya\footnotemark[1]\hspace{4px}\footnotemark[2]\\ilge@openai.com\And
Peter Zhokhov\footnotemark[1]\hspace{4px}\footnotemark[2]\\peterz@openai.com\And
Joost Huizinga\footnotemark[1]\hspace{4px}\footnotemark[2]\\joost@openai.com\And
Jie Tang\footnotemark[1]\hspace{4px}\footnotemark[2]\\jietang@openai.com\And
Adrien Ecoffet\footnotemark[1]\hspace{4px}\footnotemark[2]\\adrien@openai.com\And
Brandon Houghton\footnotemark[1]\hspace{4px}\footnotemark[2]\\brandon@openai.com\And
Raul Sampedro\footnotemark[1]\hspace{4px}\footnotemark[2]\\raulsamg@gmail.com\And
Jeff Clune\thanks{This was a large effort by a dedicated team. Each author made huge contributions on many fronts over long time periods. All members were full time on the project for over six months. BB, IA, PZ, and JC were on the original VPT project team and were thus involved for even longer (over a year). Aside from those original team members, author order is random. It was also randomized between IA and PZ.}\hspace{4px}\thanks{OpenAI}\hspace{4px}\thanks{University of British Columbia}\\jclune@gmail.com
}

\begin{document}
\commenttrue % Set \commentfalse to togle inline coments off

\maketitle

\renewcommand{\thefootnote}{(\roman{footnote})}

\begin{abstract}
Pretraining on noisy, internet-scale datasets has been heavily studied as a technique for training models with broad, general capabilities for text, images, and other modalities.\cite{brown2020language,devlin2018bert,liu2019roberta,raffel2019exploring,mahajan2018exploring,radford2021learning}
However, for many sequential decision domains such as robotics, video games, and computer use, publicly available data does not contain the labels required to train behavioral priors in the same way. We extend the internet-scale pretraining paradigm to sequential decision domains through semi-supervised imitation learning wherein agents learn to act by watching online unlabeled videos.
Specifically, we show that with a small amount of labeled data we can train an inverse dynamics model accurate enough to label a huge unlabeled source of online data -- here, online videos of people playing Minecraft -- from which we can then train a general behavioral prior.
Despite using the native human interface (mouse and keyboard at 20Hz), we show that this behavioral prior has nontrivial zero-shot capabilities and that it can be fine-tuned, with both imitation learning and reinforcement learning, to hard-exploration tasks that are impossible to learn from scratch via reinforcement learning. For many tasks our models exhibit human-level performance, and we are the first to report computer agents that can craft diamond tools, which can take proficient humans upwards of 20 minutes (24,000 environment actions) of gameplay to accomplish. 
\end{abstract}

\input{0_introduction}
\input{1_related_work}
\input{2_method}
\section{Results}
\label{section:results}
\input{3_0_IDM_results}
\input{3_1_foundation_results}
\input{3_2_BC_finetuning}
\input{3_3_RL_finetuning}
\input{3_4_data_scaling}
\input{4_discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{references}{}
\bibliographystyle{unsrtnat}


\section*{Acknowledgements} %commenting out so we do not accidentally forget and deanonymize during submission

 We thank the following people for helpful discussions and support: Bob McGrew, Ken Stanley, Joel Lehman,
 Ilya Sutskever, 
 Wojciech Zaremba, 
 Ingmar Kanitscheider, 
 David Farhi,
 Glenn Powell,
 Jonathan Gordon, and the OpenAI supercomputing team, especially Christian Gibson, Ben Chess, and Christopher Berner.

\newpage
\begin{center}
\textbf{\Large{Supplementary Information}}    
\end{center}
\appendix
\input{a_0_collecting_internet_data}
\input{a_1_contractor_data}
\input{a_2_minecraft_environment}
\input{a_3_training_details}
\input{a_4_rl_training_details}
\input{a_5_foundation_model_scaling}
\input{a_6_text_conditioning}



\end{document}