\section{Extended discussions} \label{app: further discussions}

\subsection{Comparisons with EoH}\label{app: comparisons with eoh}
Our work is developed concurrently with Evolution of Heuristics (EoH) \cite{liu2024_llm_gls}, which establishes the groundwork for this emerging field. Nonetheless, our work extends the boundaries of LHH through three primary lenses: (1) the search algorithm, (2) the downstream CO applications, and (3) the evaluation methodologies.
\begin{itemize}[left=10pt]
    \item Search Algorithm: We introduce the Reflective Evolution, demonstrating its superior sample efficiency.
    \item Applications: Our work broadens the scope by applying LHH to five heterogeneous algorithmic types and six different COPs, advancing the state-of-the-art in GLS, EDA, ACO, and NCO.
    \item Evaluation Methodologies: We employ fitness landscape analysis to explore the underlying mechanisms of our proposed method; we establish black-box experimental settings to ensure reliable comparisons and practical relevance to real-world applications.
\end{itemize}


\subsection{Extended applications} \our{} is generally applicable to other string-based optimization scenarios \cite{meyerson2023lm_crossover} as long as reflecting the relative performance of strings is meaningful. Preliminary experiments on prompt tuning verify the advantage of \our{} over random search and vanilla genetic programming. Furthermore, we identify in reasoning-capable LLM approaches released after \our{} such as OpenAI o1 \citep{zhong2024evaluation} an interesting avenue of future works and experimentation that could yield even better sample efficiency and performance.
