
\section{Introduction}
Building generalist agents that can solve open-ended tasks in visually rich, open-world environments is a long-standing vision of embodied AI \cite{hafner2023mastering,tan2024towards,raad2024scaling,yang2024video}. Among such environments, Minecraft \cite{guss2019minerl,fan2022minedojo} has emerged as a compelling benchmark for studying open-world agents, due to its diverse scenes and objects, vast action space, and the open-ended nature of tasks. Recent advances in Minecraft \cite{wang2023voyager,qin2023mp5,wang2023jarvis,wang2023describe,li2024optimus,li2025optimus} have empowered agents with Multimodal Large Language Models (MLLMs) \cite{bai2025qwen2,chen2024lion,liu2024visual}, enabling impressive performance on programmatic, pre-defined objectives. However, these agents often exhibit brittle behavior when confronted with dynamic and open-ended instructions, where success necessitates both immediate responsiveness to dynamic changes and deliberate analysis of visual cues.

To achieve this, we argue that an agent must emulate the \textbf{Dual-Process Theory} of human cognition \cite{kahneman2011thinking}: synergizing System 1 (fast, reflexive, intuitive) and System 2 (slow, deliberative, analytic) processes. As illustrated in Figure~\ref{fig:fig1}, consider the instruction \emph{``Craft a diamond sword based on the current inventory''}. This open-ended task demands a seamless interplay between two cognitive modes. \textbf{System 2} takes charge of the deliberative reasoning loop, encompassing Planning, Reflection, and notably, Active Perception (Grounding, Embodied QA). We classify these visual tasks as System 2 processes because they transcend passive detection: they demand a deliberative analysis of visual evidence to verify the factual existence of queried entities before decision-making. \textbf{System 1} governs the high-frequency visuomotor loop, executing low-latency control commands (Action) to interact with the environment. Existing Minecraft agents, however, typically possess only a fragmented subset of these abilities, lacking the organic synergy required for robust performance. This raises a fundamental research question: \textbf{Can we develop a generalist agent that organically integrates System 1 action loops with System 2 reasoning capabilities within a unified framework?} Toward this goal, we identify three fundamental challenges centered around the acquisition, modeling, and activation of these dual capabilities.

\input{figures/fig-1}

\textbf{Challenge \uppercase\expandafter{\romannumeral 1}: Scarcity of Domain-Specific System 2 Reasoning Traces.}  While raw gameplay data (action trajectories) is abundant \cite{vpt,lifshitz2024steve}, there is a critical scarcity of data capturing the reasoning processes, such as hierarchical planning, visual grounding, and reflection. Manually annotating these complex cognitive traces is prohibitively expensive. A naive strategy is to leverage general-domain MLLMs \cite{liu2024visual,chen2024lion,bai2025qwen2} for automated annotation. However, these models, while possessing strong general reasoning, lack the ``knowledge'' of Minecraft (e.g., crafting recipes, physics rules). Consequently, they frequently generate unfeasible plans or hallucinated responses \cite{bai2025qwen2,lu2024deepseek}. Bridging the gap between general-purpose reasoning and domain-specific knowledge to construct high-quality System 2 reasoning traces remains a significant hurdle.



\textbf{Challenge \uppercase\expandafter{\romannumeral 2}: Computational Conflicts in Coupling System 1 and System 2.}  System 1 (Action) demands high-frequency inference with low latency, relying on shallow, reflexive processing of local context. In contrast, System 2 (Planning, Reflection) operates at a lower frequency but requires deep, computation-intensive reasoning over long horizons. Standard dense architectures or conventional Mixture-of-Experts (MoE) \cite{moesurvey,huang2025modes}  enforce a uniform computational depth, resulting in a dilemma: they are either too computationally heavy for real-time control or too shallow for complex reasoning. Furthermore, training these heterogeneous tasks within a shared parameter space often leads to task interference \cite{shen2025mome,dai2401deepseekmoe}. Designing an architecture that adaptively allocates computational resources, provides a \emph{fast path} for System 1 and a \emph{deep path} for System 2, and simultaneously avoids task interference is highly challenging.



\input{figures/fig-2}
\textbf{Challenge \uppercase\expandafter{\romannumeral 3}: Optimizing System 2 Reasoning under Sparse Outcome Feedback.} Given Minecraft's infinite diversity in scenes and dynamics, Supervised Fine-Tuning (SFT) is insufficient for agent training. While Reinforcement Learning (RL) \cite{schulman2017ppo,rafailov2023dpo} offers a pathway to activate such reasoning capabilities through exploration \cite{guo2025deepseek,shao2024deepseekmath}, adapting it to Minecraft presents distinct challenges. (i) Visual-Logic Misalignment: Unlike text-only tasks, Minecraft requires reasoning over high-dimensional visual inputs. Existing methods \cite{schulman2017ppo,rafailov2023dpo,shao2024deepseekmath} often struggle to ground reasoning in visual evidence, leading to perceptual hallucinations. (ii) Lack of Process Supervision: Standard RL typically relies on sparse outcome rewards, treating the reasoning process as a black box. This coarse supervision fails to penalize flawed intermediate logic that accidentally yields correct answers, hindering the acquisition of strictly valid and grounded reasoning chains.



In this paper, we propose \textbf{Optimus-3}, a generalist agent in open-world of Minecraft, which is endowed with comprehensive capabilities in perception, planning, action, and reflection (depicted in Figure \ref{fig:fig2}). To address the aforementioned challenges, we propose targeted improvements across three key dimensions: data generation, model architecture, and training methodology. 


\textbf{Knowledge-Enhanced Data Generation Pipeline for System 2 Tasks.} To address the scarcity of domain-specific reasoning data (Challenge \uppercase\expandafter{\romannumeral 1}), we introduce a knowledge-enhanced pipeline that synthesizes high-quality  reasoning traces from raw action trajectories. Distinct from conventional pipelines that rely solely on the generative priors of generalist MLLMs, our framework explicitly injects Minecraft-specific knowledge (e.g., expert models, knowledge bases, environment feedback) as ground-truth constraints. It employs such knowledge to guide and verify the accuracy of the reasoning content, significantly reducing the hallucinated content in the annotations. This yields \textbf{OptimusM$^4$}, a large-scale, \textbf{M}ulti-\textbf{M}odal \textbf{M}ulti-task \textbf{M}inecraft dataset that provides the rigorous supervision needed to bootstrap the agent's reasoning capabilities.


\textbf{Dual-Router Aligned MoE Architecture for System 1/2 Synergy.} To reconcile the computational conflicts between reflexive action and deliberative reasoning (Challenge \uppercase\expandafter{\romannumeral 2}), we propose the \textbf{Dual-Router Aligned MoE} architecture. As depicted in Figure \ref{fig:fig2}, it structurally enforces the organic coupling of System 1 and System 2 through a novel two-dimensional routing mechanism. Horizontally, we employ a Task Router to assign distinct experts to heterogeneous tasks, achieving orthogonal parameter decoupling to prevent task interference.  Vertically, we introduce a Layer Router that dynamically modulates the inference depth based on the task's cognitive complexity. It constructs a computational ``Fast Path'' with reduced layer activation for latency-sensitive System 1 actions, while preserving a ``Deep Path'' utilizing the full network depth for complex System 2 reasoning. This design breaks the redundancy of static models, enabling efficient, conflict-free coexistence of dual cognitive processes.


\input{figures/fig-3}
\textbf{Dual-Granularity Reasoning-Aware Policy Optimization for System 2.} To endow agents with rigorous System 2 capabilities, we propose a \textbf{D}ual-\textbf{G}ranularity \textbf{R}easoning-Aware \textbf{P}olicy \textbf{O}ptimization (DGRPO) algorithm. Unlike conventional RL that relies on sparse outcome signals, DGRPO establishes a novel Process-Outcome Co-Supervision paradigm to mitigate inconsistencies between reasoning process and answers. Central to this framework is our Dual-Granularity Dense Reward mechanism, designed to address specific reasoning failures: (i) The Dependency-Aware Synthesis Reward incorporates domain knowledge graphs to enforce topological consistency, ensuring the agent's thought process strictly adheres to hierarchical logic; (ii) The Hallucination-Aware Consistency Reward acts as a fine-grained perceptual verifier, explicitly penalizing non-existent entities within the reasoning trace to align high-level thought with low-level visual evidence. By providing dense feedback on reasoning process, DGRPO compels the agent to ``think-before-act,'' significantly enhancing robustness and generalization in open-ended dynamic environments.


We conducted comprehensive evaluations in the open-world environment of Minecraft. Experimental results show that Optimus-3 outperforms both general MLLMs and previous SOTA agents in Minecraft across a wide range of tasks. Compared to previous SOTA, Optimus-3 achieves improvements of 21$\%$ on \textit{Planning}, 3$\%$ on \textit{Long-Horizon Action}, 66$\%$ on \textit{Captioning}, 76\% on \textit{Embodied QA}, 3.4$\times$ on \textit{Grounding}, and 18$\%$ on \textit{Reflection}, respectively. Notably, on \textit{Open-Ended} tasks, Optimus-3 achieves an average success rate of 60$\%$, whereas existing agents almost never succeed due to their lack of multi-dimensional capabilities. In summary, our contributions are as follows:
\begin{itemize}
    \item We propose Optimus-3, the first generalist Minecraft agent that organically integrates System 1 action loops with System 2 reasoning capabilities (planning, perception, reflection) within a unified framework. 
    \item We propose a knowledge-enhanced data generation pipeline that synthesizes high-quality System 2 reasoning traces from interaction trajectories. Based on it, we release Multi-Modal, Multi-task Minecraft dataset \textbf{OptimusM$^4$} for the community. 
    \item We design the Dual-Router Aligned MoE architecture, which resolves computational conflicts by decoupling task parameters horizontally and adapting reasoning depth vertically, enabling efficient System 1/2 synergy.
    \item We propose a Dual-Granularity Reasoning-Aware Policy Optimization algorithm. It introduces a process-outcome co-supervision mechanism to align reasoning chains with visual evidence, enabling robust decision-making under dense feedback.
\end{itemize}




