\section{Related Work}

\noindent\textbf{Minecraft Agents}. The existing Minecraft agent frameworks are illustrated in Figure \ref{fig:fig3}. Early work \cite{vpt,fan2022minedojo,lifshitz2024steve,cai2023groot,deng2025open} build goal-conditioned policies based on Transformer-XL architecture, refer to Figure \ref{fig:fig3} \textbf{(A)}. Such policies have limited capability in instruction-following and long-horizon planning, and thus can only execute a few simple, atomic tasks. Figure \ref{fig:fig3} \textbf{(B)} show that several works \cite{wang2023voyager,liu2024rl,liu2024odyssey,li2024auto,li2024larm,zhou2024wall} leverage Large Language Models (LLM) to generate executable code, enabling agent-environment interaction through function calling mechanisms. However, this API-call paradigm is fundamentally different from how humans execute low-level actions. To endow agents with human-like coupling between high-level planning and low-level execution, several work \cite{qin2023mp5,wang2023describe,wang2023jarvis,li2024optimus,li2025optimus} employ MLLMs as planners and use the policy as the executor, refer to Figure \ref{fig:fig3} \textbf{(C)}. Moreover, some work \cite{wang2024omnijarvis,cai2025rocket1} leverage MLLMs to generate latent tokens as conditions for the policy, rather than using explicit textual instructions (Figure \ref{fig:fig3} \textbf{(D)}). Despite significant advances, these agents still underperform open-ended tasks depicted in Figure \ref{fig:fig1}, due to their lack of multidimensional competencies. As shown in Figure \ref{fig:fig3} \textbf{(E)}, we develop an end-to-end generalist agent Optimus-3, which is equipped with comprehensive capabilities in Minecraft.

\input{figures/fig-4}
\noindent\textbf{Mixture-of-Experts Architectures}. In recent years, Mixture of Experts (MoE) architectures \cite{mu2025comprehensive,moesurvey} have garnered significant attention in the field of Large Language Models (LLMs), owing to their scalability and sparsity in activation \cite{lepikhin2020gshard,fedus2022switch,du2022glam}. To further enhance expert specialization, DeepSeekMoE \cite{dai2401deepseekmoe} proposed more differentiated expert training strategies, significantly boosting downstream task performance, albeit with increased training complexity. Recently, MoE architectures have been incorporated into MLLMs \cite{shen2025mome,li2025uni,lin2024moma,wu2024omni,huang2025modes}, significantly enhancing their generalization capabilities and computational efficiency. Despite these advancements, existing MoE architectures still face notable challenges in load balancing and routing optimization \cite{shen2025mome}. In this paper, we propose a dual-router aligned MoE architecture, in which a task router to achieve orthogonal parameter decoupling, a layer router implements adaptive reasoning depth.

\noindent\textbf{Reinforcement Learning}. Early deep Reinforcement Learning (RL) algorithms \cite{mnih2015dqn,lillicrap2015ddpg,schulman2015trpo} established the foundations of learning control policies from high-dimensional feedback but suffered from instability and limited scalability to large models. Proximal Policy Optimization (PPO) \cite{schulman2017ppo} has since become the mainstream on-policy algorithm for continuous control and LLM fine-tuning, thanks to its clipped surrogate objective that stabilizes policy updates, yet it remains sample-inefficient and sensitive to reward shaping. Building on PPO, Reinforcement Learning from Human Feedback (RLHF) \cite{christiano2017rlhf,ouyang2022instructgpt} trains a reward model from human preferences and then applies PPO-style optimization to align models with nuanced human objectives, but introduces substantial annotation cost and training instability. To simplify this pipeline, Direct Preference Optimization (DPO) \cite{rafailov2023dpo} removes the explicit RL loop by recasting preference alignment as a supervised objective over paired responses, yielding more stable and implementation-friendly training. More recently, Group Relative Policy Optimization (GRPO) \cite{shao2024deepseekmath} replaces the critic in PPO with group-wise relative baselines, significantly reducing memory and computation for large-scale LLMs while preserving on-policy updates. DeepSeek-R1 \cite{guo2025deepseek} enhances the reasoning ability of LLM via GRPO, yet its reward design remains relatively coarse, lacking fine-grained supervision for thinking process and final answers. In this paper, we propose Multimodal Reasoning-Augmented Reinforcement Learning, which assigns task-specific fine-grained rewards to heterogeneous tasks and leverages multimodal reasoning to guide the model to focus on informative visual cues.

