\section{Ethics and Normative Aspects}
\label{sec:ethics}
Ethics, trust, and transparency are an integral part of Salesforce’s approach to AI research.
While the current version of the AI Economist provides only a limited representation of the real world, we recognize that it could be possible to manipulate future, large-scale iterations of the AI Economist to increase inequality and hide this action behind the results of an AI system.

Furthermore, either out of ignorance or malice, bad training data may result in biased recommendations, particularly in cases where users will train the tool using their own data. For instance, the exclusion from the model of communities and segments of the work-force that are under-represented in training data might lead to bias in AI-driven tax models. This work also opens up the possibility of using richer, observational data to set individual taxation, an area where we anticipate a strong need for robust debate.


Economic simulation enables studying a wide range of economic incentives and their consequences, including models of stakeholder capitalism.
However, the simulation used in this work is not an actual tool that can be currently used with malintent to reconfigure tax policy.
We encourage anyone utilizing the AI Economist to publish a model card and data sheet that describes the ethical considerations of trained AI-driven tax models to increase transparency, and by extension, trust, in the system.
Furthermore, we believe any future application or policy built on economic simulations should be built on inspectable code and subject to full transparency.

In order to responsibly publish this research, we have taken the following measures:

\begin{itemize}
\item To ensure accountability on our part, we have consulted academic experts on safe release of code and ensured we are in compliance with their guidance. We shared the paper and an assessment of the ethical risks, mitigation strategies, and assessment of safety to publish with the following external reviewers:
Dr. Simon Chesterman, Provost’s Chair and Dean of the National University of Singapore Faculty of Law, and Lofred Madzou, AI Project Lead at the World Economic Forum's Center for the Fourth Industrial Revolution.
None of the reviewers identified additional ethical concerns or mitigation strategies that should be employed. All affirmed that the research is safe to publish.
\item To increase transparency, we are publishing this technical paper, as well as a blog post, thereby allowing robust debate and broad multidisciplinary discussion of our work.
\item To further promote transparency, we will have a timed open-source release of our environment and sample training code for the simulation.
This does not prevent future misuse, but we believe, at the current level of fidelity, transparency is key to promote grounded discussion and future research.
\end{itemize}

With these mitigation strategies and other considerations in place, we believe this research is safe to publish.
Furthermore, this research was not conducted with any corporate or commercial applications in mind.
