\vspace*{-1ex}
\section{Discussion}
\label{sec:discussion}
\vspace*{-1.5ex}

We present Director, a reinforcement learning agent that learns hierarchical behaviors from pixels by planning in the latent space of a learned world model. 
To simplify the control problem for the manager, we compress goal representations into compact discrete codes. 
Our experiments demonstrate the effectiveness of Director on two benchmark suites with very sparse rewards from pixels. 
We also show that Director learns successfully across a wide range of different domains without giving task reward to the worker, underlining the generality of the approach. 
Decoding the latent goals into images using the world model makes the decision making of Director more interpretable and we observe it learning a diverse range of strategies for breaking tasks down into subgoals.

\paragraph{Limitations and future work}

We designed Director to be as simple as possible, at the expense of design choices that could restrict its performance.
The manager treats its action space as a black box, without any knowledge that its actions correspond to states. For example, one could imagine regularizing the manager to choose goals that have a high value under its learned critic. 
Lifting the assumption of changing goals every fixed number of time steps, for example by switching based on a separate classifier or as soon as the previous goal has been reached, could enable the hierarchy to adapt to the environment and perform better on tasks that require precise timing. 
Moreover, goals are points in latent space, whereas distributional goals or masks would allow the manager to only specify targets for the parts of the state that are currently relevant.
Learning temporally-abstract dynamics would allow efficiently learning hierarchies of more than two levels without having to use exponentially longer batches.
We suspect that these ideas will improve the long-term reasoning of the agent.
Besides improving the capabilities of the agent, we see disentangling the reasons for why Director works well, beyond the ablation experiments in the appendix, as promising future work.

\paragraph{Acknowledgements}

We thank Volodymyr Mnih, Michael Laskin, Alejandro Escontrela, Nick Rhinehart, and Hao Liu for insightful discussions. We thank Kevin Murphy, Ademi Adeniji, Olivia Watkins, Paula Gradu, and Younggyo Seo for feedback on the initial draft of the paper.
