\section{Introduction}
Economic inequality is accelerating globally and is a key social and economic concern.
Many studies have shown that large income inequality gaps can have significant negative effects,  leading for example to diminished economic opportunity \citep{inequality_matters_2013} and adverse health effects \citep{subramanian2004income}.
In this light, tax policy provides governments with an important tool to reduce inequality, supporting the possibility of the redistribution of wealth through government provided services and benefits.
And yet, finding the optimal tax policy is challenging.
The basic reason is that while more taxation can improve equality, taxation can also discourage people from working, leading to lower productivity.

The problem of optimally balancing equality and productivity has not been solved for general economic settings, and even when the policy objectives can be agreed upon.
Part of the challenge is that is hard to experiment with real-world tax policies.
In the place of experimentation, economic theory often relies on simplifying assumptions that are hard to validate, for example about people’s sensitivity to taxes.
Tax systems that have been proposed range from no taxes at all (“free market”), to progressive and regressive tax systems (reflecting whether the tax rate increases or decreases as income increases), to total redistribution.

In this paper, we introduce “The AI Economist,” a {\em two-level deep reinforcement learning} (RL) framework to train \emph{social planners}. The economic actors are adaptive, learning behaviors in the simulated world and including in response to tax policy. The planner is also adaptive, learning  tax policies that adapt to agent behaviors and seek to achieve a particular policy objective.
Neither economic actors nor the AI Economist have prior knowledge, whether about the simulated world environment or  economic theory.
The AI Economist learns a tax policy based only on observable data and without knowledge of the skill or utility functions of workers or prior assumptions about the behavior of workers, and can be used to optimize for any desired social outcome.

The AI Economist learns a {\em tax schedule}, analogous to the way in which US federal income taxes are described. Taxes are computed by applying a tax rate to each part of an individual's income that falls within a tax bracket.
For simplicity, we fix the intervals that correspond to  each of these income brackets and  learn the tax rate for each bracket.
The tax schedule learned by the AI Economist is not personalized;  each agent faces the same rates and bracket cutoffs. In a single tax period the tax schedule is determined via a deep neural network, able to observe all public information about the world, including the position, income, and resources held by agents.

Our approach to economic design is based on the use of   simulations, making use of AI agents that learn optimal behaviors.
This use of  simulation enables the testing of economic policies at large-scale, and including the ability to measure a range of different metrics.
In effect, we can  compare the performance of millions of economic designs, making use of economic agents whose behavior is learned in parallel.
The simulation framework can also be used to speed up experiments with existing proposals for tax systems, validating assumptions and offering the ability to test ideas that come from  economic theory. 

We make the following contributions:

\begin{itemize}
  \item We introduce a principled economic simulation that features competitive pressures, trade, and resource scarcity.
  \item We validate that learned  behavior conforms to results known from economic theory, for example agent specialization.
  \item We frame the problem of learning optimal taxes in a dynamic economy as a \emph{two-level, inner-outer reinforcement learning problem} and   describe a range of techniques to stabilize training for this two-level RL problem, including the use of learning curricula and entropy-based regularization.
  \item The AI-driven tax policies make use of different kinds of tax rate schedules than those suggested by baseline policies, and our experiments demonstrate that the AI-driven tax policy can improve the trade-off between equality and productivity by 16\% when compared to the prominent Saez tax framework.
  \item We show that AI agents can learn tax-avoidance behaviors, modulating their incomes across tax periods. The tax schedule generated by the AI Economist performs well despite this kind of strategic behavior.
  \item Without endorsing the particular tax schedules, we show that a learned policy can also be effective in experiments with human participants and without additional recalibration. The policy achieves an equality-productivity trade-off that is competitive with the state-of-the-art, together with higher inverse-income weighted social welfare. This provides a preliminary suggestion that the AI Economist methodology could also be applicable to more general, real world settings.
\end{itemize}

