\section{Details of Environment}
\label{sec:details_of_environment}

This section provides a more exhaustive description of the environment dynamics and the observations (and, where appropriate, actions) available to agents and the social planner.
We describe these separately for each of the mechanics used to construct the simulation.
Note that observations and actions are essentially the inputs and outputs of the neural network policies trained using RL.
Planner observations/actions are irrelevant for baseline tax models, where tax rates are either fixed or calculated formulaically.

\paragraph{World Dynamics.}
The \textit{Gather-and-Build} environment is organized over a 2D grid.
Grid cells can be occupied by agents, resources, houses, or other landmarks such as water.
At the start of each episode, certain cells are designated as `source' cells that function to spawn new resource units.\footnote{For our purposes, we use the same, fixed layout of source cells each episode.}
A given source cell only spawns a single type of resource, i.e. wood or stone.
If an agent moves to a cell that contains a resource, that resource is added to the agent's inventory and removed from the world at that location.
At the start of each timestep, resources randomly re-spawn at empty source cells according to the regeneration probability.

The state of the world is represented as a $H \times W \times C$ tensor, where $H$ and $W$ are the size of the world and $C$ is the number of unique entities that may occupy a cell, and the value of a given element indicates that a particular entity is occupying the associated location.
The social planner is able to observe the full world state tensor, while agent observations are restricted to views of the state tensor from a narrower, egocentric spatial window.
Our experiments use a world of size 25-by-25, where agent observations have size 11-by-11.
Agent spatial observations are padded as needed when their observation window extends beyond the world grid.


\paragraph{Movement and Gathering.}
Agents must navigate the world in order to collect resources and build new houses.
The action space of the agents includes 4 actions for moving up, down, left, and right.
Agents are restricted from moving on top of water cells, cells occupied by other agents, and cells containing houses built by other agents.
In this way, agents may create difficulty for other agents by restricting their available paths.

Before resources may be sold or used to build houses, they must be collected from the world.
An agent collects resources by moving itself on top of a resource-populated source cell.
By default, this adds a single unit of the collected resources to the agent's inventory, with the possibility of a bonus unit also being collected, the probability of which is determined by the agent's collecting skill.

Agents observe the state of their inventories (including wood, stone, and coin) as well as their own collecting skill.
The planner is also able to observe agents' inventories but cannot observe skill values.


\paragraph{Building.}
When an agent has both stone and wood in its inventory, it may spend one unit of each in order to construct a house.
The action space of the agents includes 1 action for building.
Agents are restricted from building on source cells as well as locations where a house already exists.
Building places a house at the location occupied by the agent and adds coin to the agent's inventory, the amount of which is determined by its building skill.
Agents observe their own building skill, which the planner is not able to observe.


\paragraph{Trading.}
Agents can buy and sell resources from one another through a trading mechanism structured as a \textit{continuous double auction}.
This is conceptually similar to a commodities or stock exchange, where participants do not interface directly but instead submit bids and asks to a market, which identifies and executes valid trades.
The action space of the agents includes 44 actions for trading, representing the combination of 11 price levels ($0, \ldots, 10$ coin), 2 directions (bids and asks), and 2 resources (wood and stone).
Note: agents buy resources by submitting bids and sell resources by submitting asks.
Each trade action therefore maps to a single order (i.e. bid 3 coin for 1 wood, ask for 5 coin in exchange for 1 stone, etc.).
Once an order is submitted, it remains open until either it is matched (in which case a trade occurs) or it expires (after 50 timesteps).
Agents are restricted from having more than 5 open orders for each resource and are restricted from placing orders that they cannot complete: they cannot bid with more coin than they possess and cannot submit asks for resources that they do not have.

A bid/ask pair form a valid trade if they are for the same resource and the bid price matches or exceeds the ask price.
When a new order is received (i.e. bid 3 coin for 1 wood) it is compared against complementary orders to identify potential valid trades.
When a single bid (ask) could be paired with multiple existing asks (bids), priority is giving the ask (bid) with the lowest (highest) price; in the event of ties, priority then is given to the oldest existing order.
Once a match is identified, the trade is executed using the price of whichever order was placed first.
As an example, if the market receives a new bid that offers 8 coin for 1 stone and the market has two open asks offering 1 stone for 3 coin and 1 stone for 7 coin, respectively, the market would pair the bid with the first ask and a trade would be executed for 1 stone at a price of 3 coin:
the bidding agent loses 3 coin and gains 1 stone and the asking agent loses 1 stone and gains 3 coin.
Once a bid and ask are paired and the trade is executed, both orders are removed from the market.

The state of the market is captured by the number of outstanding bids and asks at each price level for each resource.
Agents observe these counts both for their own bids/asks as well as the cumulative bids/asks of other agents (representing the bids/asks that they could respond to).
The planner observes the cumulative bids/asks of all agents.
In addition, both agents and the planner observe some historical information from the market: (for each resource) the average trading price as well as the number of trades at each price level.


\paragraph{Taxation and Redistribution.}
The main text describes the general implementation of periodic, bracketed taxes used in our environment (Section \ref{sect:brackettax}).
On the first timestep of each tax period, the planner sets the marginal tax rates that will be used to collect taxes when the tax period ends.
For baseline models, these are set either formulaically or using fixed rates.
For taxes controlled by a deep neural network (i.e. AI Economist), the action space of the planner is divided into seven action subspaces, one for each tax bracket: $\{0, 0.05, 0.10, \ldots, 1.0\}^7$.
Each subspace denotes the set of discretized marginal tax rates that the planner may select.\footnote{Discretization of tax rates only applies to deep learning networks.}
The action space takes this form because, when setting new rates, the planner samples 7 rates at once.

Agents observe:
\begin{itemize}
    \item The tax rates of the current tax period
    \item The marginal rate at the income level earned within the current period so far
    \item Indicators of the temporal progress of the current tax period
    \item The set of sorted and anonymized incomes the agents reported in the previous period
\end{itemize}
The planner observes the same information as well as the non-anonymized income and marginal tax rate (at that income) of each agent in the previous period.


\paragraph{Action Details.}
In our implementation, both agents and planners use discrete action spaces.
One advantage of this choice is that it grants easier control over which actions the agent/planner models can sample at a given time.
We encode this using `action masks' which we use to ensure that the policy network assigns effectively 0 probability to restricted actions.
Action masking is useful for preventing invalid actions and is how we control the tax annealing (see Section \ref{sec:trainingstrategy}) for the AI Economist experiments.

In addition to the actions described above, we include a \texttt{NO-OP} action (``no operation'') in each action space.
(For the planner, each of the 7 action subspaces includes a \texttt{NO-OP} action.)
The \texttt{NO-OP} action is interpreted as essentially taking no action, allowing the agent to ``idle'' and the planner to leave a bracket's tax rates unchanged between periods.

Most importantly, we use these implementation features to enable the planner to observe every timestep while only acting at the start of each new tax period.
For timesteps other than those at the start of a tax period we simply use the action mask to enforce that only \texttt{NO-OP} actions are sampled.
This allows the planner to use rich temporal information while also ensuring that policy gradients are only propagated from the action samples used to control taxes.









