\section{Discussion}
This work introduces the \textit{LLM Economist}, a fully language-based framework that embeds a population of persona-conditioned agents and a tax planner in a two-tier Stackelberg game.  Our results show that a Llama-3 model can \textit{(i)} recover the Mirrleesian trade-off between equity and efficiency, \textit{(ii)} approach Saez-optimal schedules in heterogeneous settings where analytical formulas are unavailable, and \textit{(iii)} reproduce political phenomena—such as majority exploitation and welfare-enhancing leader turnover—without any hand-crafted rules.  Taken together, the experiments suggest that large language models can serve as tractable test beds for policy design long before real-world deployment, providing a bridge between modern generative AI and classical economic theory.

\paragraph{Limitations.}
The simulator makes several strong assumptions.  First, skills are static and labor responds instantaneously within each tax year; relaxing either assumption would require substantially longer horizons and may expose stability issues in in-context learning.  Second, we rely on a single 8-billion-parameter backbone; larger or smaller models could shift both convergence speed and welfare levels.  Third, persona prompts are sampled from ACS marginals rather than joint distributions, so demographic correlations are only approximated.  
% Fourth, bounded-utility satisfaction is judged by the same LLM that optimizes labor, raising concerns about self-evaluation bias.  
Finally, our evaluation is limited to 100 agents and U.S. tax brackets; scaling to millions of agents, multi-country settings, or richer actions, such as trade, remains future work.

\paragraph{Broader impacts.}
The \emph{LLM Economist} offers a safe testbed for tax-policy ideas but could also be misused to craft policies that prefer select groups or to generate persuasive yet problematic economic narratives.  Since the framework inherits priors from ACS data and the base LLM, uncritical use may amplify existing issues.  We release the code under a non-commercial license and log all agent actions to enable external audit before any high-stakes deployment.



 % This ASCII Pikachu brings luck for paper acceptance.
 % $$$b  `---.__
 %  "$$b        `--.                          ___.---uuudP
 %   `$$b           `.__.------.__     __.---'      $$$$"              .
 %     "$b          -'            `-.-'            $$$"              .'|
 %       ".                                       d$"             _.'  |
 %         `.   /                              ..."             .'     |
 %           `./                           ..::-'            _.'       |
 %            /                         .:::-'            .-'         .'
 %           :                          ::''\          _.'            |
 %          .' .-.             .-.           `.      .'               |
 %          : /'$$|           .@"$\           `.   .'              _.-'
 %         .'|$u$$|          |$$,$$|           |  <            _.-'
 %         | `:$$:'          :$$$$$:           `.  `.       .-'
 %         :                  `"--'             |    `-.     \
 %        :##.       ==             .###.       `.      `.    `\
 %        |##:                      :###:        |        >     >
 %        |#'     `..'`..'          `###'        x:      /     /
 %         \                                   xXX|     /    ./
 %          \                                xXXX'|    /   ./
 %          /`-.                                  `.  /   /
 %         :    `-  ...........,                   | /  .'
 %         |         ``:::::::'       .            |<    `.
 %         |             ```          |           x| \ `.:``.
 %         |                         .'    /'   xXX|  `:`M`M':.
 %         |    |                    ;    /:' xXXX'|  -'MMMMM:'
 %         `.  .'                   :    /:'       |-'MMMM.-'
 %          |  |                   .'   /'        .'MMM.-'
 %          `'`'                   :  ,'          |MMM<
 %            |                     `'            |tbap\
 %             \                                  :MM.-'
 %              \                 |              .''
 %               \.               `.            /
 %                /     .:::::::.. :           /
 %               |     .:::::::::::`.         /
 %               |   .:::------------\       /
 %              /   .''               >::'  /
 %              `',:                 :    .'
 %                                   `:.:' 
