\clearpage
\section{Related Work}


\paragraph{Video generative models.} 
Video generative models are neural networks that can generate realistic video samples. They can be grouped in four categories: VAE-based (variational autoencoder \citep{kingma14}, GAN-based (generative adversarial network \citep{goodfellow14}), diffusion-based \citep{sohl-dickstein15}, and autoregressive-based \citep{pixelcnn16}. 

Latent-variable video models (VAE-based) try to infer the underlying latent process that generated the videos \citep{babaeizadeh18,denton18,villegas19,franceschi20,fitvid21}. One known limitation of those models is that they tend to generate blurry outputs due to limited representational power, inadequate choice of prior distribution, and the optimization of a lower-bound instead of the true likelihood. GAN-based methods produce more realistic videos \citep{vondrick16,tulyakov18,clark19,kim2021drivegan,skorokhodov22,brooks22} but are known to suffer from training instability and a lack of generation diversity \citep{goodfellow2016tutorial}. Diffusion-based methods have yielded significant enhancements in realism, controllability, and temporal consistency. They can operate either at the pixel level \citep{ho2022video,harvey2022flexible,voleti22,hoppe22,singer22,molad2023dreamix,ho2022imagen} or in the latent space of a pre-trained image tokenizer \citep{Zhou2022MagicVideoEV,esser2023structure,blattmann2023align}. Diffusion models are expressive neural networks that can fit complex data distributions, but rely on a long Markov chain of diffusion steps to generate samples. Lastly, autoregressive-based methods are conceptually simple and rely on tractable exact likelihood optimization (fits the entire data distribution). Likewise, they can operate at the pixel level \citep{kalchbrenner16,Weissenborn20}, or in a discrete learned token space \citep{yan2021videogpt,moing21,ge2022long,seo22}. A known limitation is the slow generation speed, but this issue could be alleviated by future research on parallel sampling \citep{teco22yan,villegas22phenaki,yu2023magvit}, reducing the number of latent variables \citep{hawthorne22}, and improvements in hardware accelerators.

\paragraph{World models.} 
A world model is a predictive model of the future that learns a general representation of the world in order to understand the consequences of its actions \citep{ha18,lecun22}. The main use cases are: pure representation learning, planning (look-ahead search), or learning a policy in the world model (neural simulator). 

World modeling has been used as a pre-training task to learn a compact and general representation in a self-supervised way \citep{Schwarzer2020DataEfficientRL,wu2023masked}. Subsequently, using this representation as a state for traditional reinforcement learning (RL) algorithms significantly accelerated convergence speed. World models can also be utilized for look-ahead search, in order to plan by imagining the outcomes of future actions. They have proven to be highly effective in game environments or board games \citep{schrittwieser2020mastering,ye2021mastering}. Additionally, world models can be a solution to the sample efficiency issues of RL algorithms by acting as a simulator of the environment \citep{ha18,kaizer19,hafner2021dreamerv2,kim2021drivegan,hafner2023mastering,wu2023daydreamer,wang2023drive}, although this assumes the world model is an accurate model of the environment. 

A recent line of work suggests casting world modeling as a single sequence model, treating states, actions and rewards as simply a stream of data \citep{janner2021sequence,chen2021decisiontransformer,reed22gato,liu2022masked,micheli2023transformers,commavq2023}. The advantage of such a perspective is that world models can benefit from scaling properties of high-capacity sequence model architectures applied to large-scale unsupervised training \citep{brown20}. This is the approach that GAIA-1 takes, leveraging those scaling properties to model  complex environments such as real-world driving scenes.



\paragraph{Scaling.} 
Large language models have shown clear benefits in scaling model size and data \citep{devlin-bert19,2020t5,brown20,megatron22,Chowdhery2022PaLMSL,llama23,openai2023gpt4}. In particular, \citep{kaplan20} showed predictable relationships between model/data size and loss over multiple orders of magnitude. 
\citep{kaplan20} derived power laws for transformer based language models in order to optimally allocate the compute budget between the model and data size. Those laws were then refined by \citep{hoffmann22} by adapting the learning rate schedule when changing the dataset size. Another direction of research to improve the training efficiency of language models is data quality. \citep{du22} showed that the quality of the training data plays a critical role in the performance of language models in downstream tasks. 

Transferring the scaling principles from large language models to the visual domain holds the potential for delivering consistent and expected performance improvements \citep{tay2022scale,dehghani2023scaling,hoogeboom2023simple,ho2022imagen,peebles2023scalable}. In this work, by casting the problem of world modeling as unsupervised sequence modeling, we have shown that similar scaling trends from language models also applied to world models.
