\section{\label{sec:bayes}A Bayesian Framework}

We briefly review the relevant background in Bayesian neural networks and two
variational inference methods, specifically mean-field approximation and
structured approximation. We the proceed to show that NAS can be casted as an
instance of Bayesian neural networks and that this formulation of NAS inspires
our novel approach.

\subsection{\label{sec:bayesian}The Bayesian Framework}
Suppose we want to model an unknown distribution $p(\x)$ of our data. In the
Bayesian framework~\citep{bayes_nn}, we seek to learn a latent variable $\z$ in
the probability space $Z$ such that $z$ is likely to generate our data $\x$. We
start by postulating a prior distribution $p(\z)$ over the possible hidden
variables $\z$, which represents our initial belief in how $z$ should look
like. We then attempt to learn a distribution $q(\z)$ over $\Z$ that minimizes
the Kullback-Leiber divergence between $q(\z)$ and the true posterior $p(\z |
\x)$. Using Bayes rule, we can write the KL divergence as follows.
\begin{align}
  \text{KL}\left( q(\z) \parallel p(\z | \x) \right)
    &= \mathbb{E}_{\z \sim q} \left[ \log{q(\z)} \right]
     - \mathbb{E}_{\z \sim q} \left[ \log{p(\x | \z)} \right]
     - \mathbb{E}_{\z \sim q} \left[ \log{p(\z)} \right] + \log{p(\x)} \\
    &= -\mathbb{E}_{\z \sim q} \left[ \log{p(\x | \z)} \right]
     + \mathbb{E}_{\z \sim q}\left[ \log{q(\z)} - \log{p(\z)} \right] + \log{p(\x)} \\
    \label{eqn:elbo}
    &\leq -\mathbb{E}_{\z \sim q} \left[ \log{p(\x | \z)} \right] + \text{KL}(q(\z) \parallel p(\z))
\end{align}
The right-hand side of Eqn~\ref{eqn:elbo} is called the \textit{Evidence Lower
Bound} (ELBO) of the hypothesized distribution $q(\z)$. The ELBO captures the
expected log-likelihood $\mathbb{E}_{z \sim q} \left[ \log{p(\x | \z)} \right]$
of the data $\x$ given the latent variable $\z$, which we can observe from our
training data. In recent work, the divergence $\text{KL}(q(\z) \parallel
p(\z))$ was treated as a regularization term. For
instance,~\cite{variational_dropout,variational_dropout_rnn} approximated the
KL divergence with an $\ell_2$ regularization on their parameters, equivalently
assuming a prior $p(\z)$ to put weights on the all parameters being $0$. The
take-away message is that in practice, one can approximate the ELBO term in
different ways, leading to different learning algorithms.

\subsection{\label{sec:mean_field_and_structured}Mean-field and Structured Variational Approximation}
If the latent variable $\z$ can take on an arbitrary form, then the ELBO term
is intractable. Mean-field approximation relaxes all the dependencies among
components of $\z$. Specifically, mean-field approximation assumes that if $\z
= (z_1, z_2, ..., z_m)$ then
\begin{align}
  q(\z) = \prod_{i=1}^{m} q_i(z_i)
\end{align}
While such independence assumption makes it easier to learn $q(\z)$, it
introduces a bias in the space of latent variables $\Z$. This is because the
true posterior $p(\z | \x)$, which we aim to approximate with $q(\z)$, may have
a degree of dependencies between the components $z_i$'s. In contrast to
mean-field approximiation,structured variational approximation
methods~\citep{struct_approx} assume a certain degree of dependencies on the
components of $\z$, leading to a model with a higher fidelity to the true
posterior $p(\z | \x)$, at the tradeoff of more complex learning problem.

\subsection{\label{sec:bayesian_nas}Connection to Neural Architecture Search}
In~\cite{variational_inference_reviews}, it is noted that the ELBO
can be used as a criterion for model selection, effectively drawing a
connection from variational methods to NAS methods, which aim to select the
best models, a.k.a.  network architectures.

To cast the NAS problem as an instance of the described Bayesian framework, we
let $\z$ be a pair $(\m, \theta_{\m})$ of an architecture $\m$ and its
parameters $\theta_{\m}$, and note that $\m$ is a discrete latent variable. Now
we can write
\begin{align}
  \text{ELBO}(q)
    &= -\mathbb{E}_q \left[ \log{p(\x | \z)} \right]
     + \text{KL}(q(\m, \theta_\m) \parallel p(\m, \theta_\m | \x)) \\
    \label{eqn:models_and_params}
    &= -\sum_{\m} q(\m) \int{\log{p(\x | \m, \theta_\m)} q(\theta_{\m} | \m) d\theta_{\m}}
     + \text{KL}(q(\m, \theta_\m) \parallel p(\m, \theta_\m | \x))
\end{align}
Eqn.~\ref{eqn:models_and_params} exhibits an instance of structured variational
approximation as described in Section~\ref{sec:mean_field_and_structured}, as
$\theta_\m$ depends on $\m$ and has to be learned to fit with each model $\m$.
Some existing approaches for NAS falls into this
category~\citep{nas,nas_module,nas_dqn,nas_module_dqn}. As noted, structured
variational approximation has a high fidelity to the true posterior, which
means that the aforementioned methods can better approximate the true posterior
$p(\x | \z)$, at the cost of solving a more difficult learning problem. In the
case of NAS, the learning problem is to learn the parameters $\theta_\m$, which
means to optimize a neural network $\m$ from scratch. This is an expensive
process, and it leads to the notorious computational expense of these NAS
approaches.

On the other hand, mean-field variational approximation seems inappropriate for
NAS, because not all models $\m$ can be compatible with the parameters
$\theta_{\m'}$ of another model, e.g. the number of parameters can differ, not
to mention further structures in $\theta_\m$. However, in
Section~\ref{sec:enas}, we show that we are able to enforce a novel structure
on $\theta_\m$ which leads to a succesful mean-field approximation of
Eqn.~\ref{eqn:models_and_params}.