\pdfoutput=1

\documentclass[11pt]{article}

\usepackage[]{acl}

\usepackage{times}
\usepackage{latexsym}

\usepackage[T1]{fontenc}

\usepackage[utf8]{inputenc}

\usepackage{microtype}

\usepackage{inconsolata}


\usepackage{graphicx} %
\usepackage{natbib}  %
\usepackage{caption} %
\usepackage{algorithm}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[outdir=./]{epstopdf}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{subfloat}
\usepackage{newfloat}
\usepackage{graphicx}
\usepackage{svg} %
\usepackage[normalem]{ulem}
\usepackage{framed}
\usepackage{mdframed}
\usepackage{xcolor}
\usepackage{lipsum}
\usepackage{float}
\usepackage{hyperref}

\definecolor{shadecolor}{gray}{0.9}

\DeclareMathOperator*{\argmax}{arg\,max}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

\newcommand{\quanming}[1]{{\color{blue} \textbf{QM}. #1}}
\newcommand{\yong}[1]{{\color{red} \textbf{Yong}: #1}}
\newcommand{\gao}[1]{{\color{pink} \textbf{Gao}: #1}}
\newcommand{\chen}[1]{{\color{red} \textbf{Chen}: #1}}
\newcommand{\chenf}[1]{\footnote{+chen+:#1}}
\newcommand{\yongrevised}[1]{{\color{pink} \textbf{Yong}: #1}}
\newcommand{\req}[1]{\textcolor{black}{#1}}
\newcommand{\rev}[1]{#1}
\newcommand{\yantex}[1]{{\color{black} \textbf{Yan}: #1}}
\newcommand{\yanf}[1]{\footnote{+yanf+:#1}}
\newcommand{\reviewf}[1]{\footnote{\color{blue}+rev+:#1}}


\newtheorem{mdefinition}{Definition}

\newtheorem{problem}{Problem}
\newcommand{\para}[1]{{\vspace{4pt} \bf \noindent #1 \hspace{0pt}}}

\setlength{\belowcaptionskip}{-0.1cm} 

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline  \\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline \\\arraybackslash\hspace{0pt}}m{#1}}


\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}
}

\title{EconAgent: Large Language Model-Empowered Agents\\ for Simulating Macroeconomic Activities}

\author{Nian Li$^1$ \ \ \ Chen Gao$^2$\thanks{Corresponding author.} \ \ \ Mingyu Li$^2$ \ \ \ Yong Li$^2$\footnotemark[1] \ \ \ Qingmin Liao$^1$ \\
$^1$Shenzhen International Graduate School, Tsinghua University \ \ \ $^2$Tsinghua University \\
\small \texttt{linian21@mails.tsinghua.edu.cn} \ \ \ \texttt{chgao96@gmail.com} \ \ \ \texttt{liyong07@tsinghua.edu.cn}
}

\begin{document}
\maketitle
\begin{abstract}
The advent of artificial intelligence has led to a growing emphasis on data-driven modeling in macroeconomics, with agent-based modeling (ABM) emerging as a prominent bottom-up simulation paradigm. In ABM, agents~(\textit{e.g.}, households, firms) interact within a macroeconomic environment, collectively generating market dynamics. 
Existing agent modeling typically employs predetermined rules or learning-based neural networks for decision-making. However, customizing each agent presents significant challenges, complicating the modeling of agent heterogeneity. Additionally, the influence of multi-period market dynamics and multifaceted macroeconomic factors are often overlooked in decision-making processes.
In this work, we introduce \textbf{EconAgent}, a large language model-empowered agent with human-like characteristics for macroeconomic simulation. We first construct a simulation environment that incorporates various market dynamics driven by agents' decisions regarding work and consumption. Through the perception module, we create heterogeneous agents with distinct decision-making mechanisms. Furthermore, we model the impact of macroeconomic trends using a memory module, which allows agents to reflect on past individual experiences and market dynamics.
Simulation experiments show that EconAgent can make realistic decisions, leading to more reasonable macroeconomic phenomena compared to existing rule-based or learning-based agents. Our codes are released at \url{https://github.com/tsinghua-fib-lab/ACL24-EconAgent}.

\end{abstract}

\input{1.intro}
\input{3.system}
\input{4.method}
\input{5.exp}
\input{2.related}


\section{Conclusion}\label{sec::conclusion}
In this work, we ventured into the novel integration of LLMs with macroeconomic simulation, designing EconAgent with the abilities of perception, reflection, and decision-making based on the context of real-world economic environments. Classic macroeconomic phenomena are reproduced and more reasonable compared to traditional rule-based or learning-based agents. Through this endeavor, it has become evident that the capabilities of LLMs offer a promising avenue to simulate more realistic macroeconomics.


\section{Limitations}
\paragraph{Simulation Environment} Although our constructed simulation environment encompasses a variety of market dynamics, it currently only simulates the labor and consumption behavior of households. More complex agents (\textit{e.g.}, firms) and their behaviors (\textit{e.g.}, pricing, hiring) have not yet been incorporated. Simulating these agents with LLMs can facilitate a move towards a more realistic macroeconomic system, giving rise to more complex empirical regularities, such as the Beveridge curve and procyclicality/countercyclicality~\cite{dawid2018agent}.

\paragraph{Optimization and Forecasting} Current results are confined to replicating stylized facts~\cite{dawid2018agent}. However, another primary goal of macroeconomic research is policy optimization, along with accurate forecasts of key macroeconomic indicators~\cite{poledna2023economic}. Therefore, EconAgent still requires more realistic behavioral responses to subtle changes in macroeconomic policies. Moreover, constructing a macroeconomic system that closely mirrors the real world necessitates the implementation of EconAgent at the urban scale level, which cannot be achieved without further breakthroughs in LLMs, including enhancements in inference speed and reductions in computational demands.

\section*{Acknowledgement}
This work is supported by the National Natural Science Foundation of China under U23B2030 and 72342032.


\clearpage
\bibliography{bibliography}


\appendix
\input{6.appendix}



\end{document}
