\vspace{-0.8cm}
\section{\label{sec:intro}Introduction}

Neural architecture search (NAS) has been successfully applied to design model architectures for image classification and language models~\citep{nas,nas_module,nas_by_transformation,pnas,hierarchical_nas}. In NAS, an RNN controller is trained in a loop: the controller first samples a candidate architecture, \ie~a \textit{child model}, and then trains it to convergence to measure its performance on the task of desire. The controller then uses the performance as a guiding signal to find more promising architectures. This process is repeated for many iterations. Despite its impressive empirical performance, NAS is computationally expensive and time consuming, \eg~\citet{nas_module} use $450$ GPUs for $3$-$4$ days (\ie~32,400-43,200 GPU hours). Meanwhile, using less resources tends to produce less compelling results~\citep{deep_arc,nas_dqn}. We observe that the computational bottleneck of NAS is the training of each child model to convergence, only to measure its accuracy whilst throwing away all the trained weights.

The main contribution of this work is to improve the efficiency of NAS by \textit{forcing all child models to share weights} to eschew training each child model from scratch to convergence. The idea has apparent complications, as different child models might utilize their weights differently, but was encouraged by previous work on transfer learning and multitask learning, which established that parameters learned for a particular model on a particular task can be used for other models on other tasks, with little to no modifications~\citep{conv_features_transfer,nmt_transfer,multitask_seq2seq}.

We empirically show that not only is sharing parameters among child models possible, but it also allows for very strong performance. Specifically, on CIFAR-10, our method achieves a test error of $2.89\%$, compared to $2.65\%$ by NAS. On Penn Treebank, our method achieves a test perplexity of $55.8$, which significantly outperforms NAS's test perplexity of $62.4$~\citep{nas} and which is a new state-of-the-art among Penn Treebank's approaches that do not utilize post-training processing. Importantly, in all of our experiments, for which we use a single Nvidia GTX 1080Ti GPU, the search for architectures takes less than $16$ hours. Compared to NAS, this is a reduction of GPU-hours by more than 1000x. Due to its efficiency, we name our method \textit{Efficient Neural Architecture Search} (\enas).