\section{Training Details}
\subsection{Policy Training}

\agentname{} was trained using distributed data parallel in PyTorch \citep{pytorch}. During training, segments of 640 timesteps were sampled from the dataset. Due to memory constraints, these segments were further broken up into chunks of 64, which are processed sequentially. Since VPT uses a Transformer-XL \citep{txl}, this sequential processing lets the policy attend to previous batches up to the limit of its context length. We optimized the weights using AdamW \citep{adamw} with a maximum learning rate of 4e-5 and a linear warmup for the first 10M frames followed by a cosine learning rate decay schedule that decays to 10\% of the original learning rate. See \Cref{table:model_hparams} for an exhaustive list of hyperparameters used during training.

During training, we sample data using packed hindsight relabeling (\autoref{fig:relabeling}). This involves sampling a segment of an episode, randomly selecting some timesteps at which to change goals, and then filling in the corresponding goal embeddings for the entire episode with the embeddings from the corresponding goal segments. See \Cref{algo:hindsight} for a detailed explanantion of packed hindsight relabelling.

\renewcommand{\arraystretch}{1.25}
\begin{table}[h]
    \centering
    \begin{minipage}[b]{0.45\textwidth}
        \centering
        % First table starts
        \begin{tabular}{|l|l|}
            \hline
            \textbf{Hyperparameter Name} & \textbf{Value} \\ \hline
            \texttt{trunc\_t} & 64 \\ \hline
            \texttt{T} & 640 \\ \hline
            \texttt{batch\_size} & 12 \\ \hline
            \texttt{num\_workers} & 4 \\ \hline
            \texttt{weight\_decay} & 0.039428 \\ \hline
            \texttt{n\_frames} & 160M \\ \hline
            \texttt{learning\_rate} & 4e-5 \\ \hline
            \texttt{optimizer} & AdamW \citep{adamw} \\ \hline
            \texttt{warmup\_frames} & 10M \\ \hline
            \texttt{p\_uncond} & 0.1 \\ \hline
            \texttt{min\_btwn\_goals} & 15 \\ \hline
            \texttt{max\_btwn\_goals} & 200 \\ \hline
            \texttt{vpt\_architecture} & \texttt{2x} \\ \hline
        \end{tabular}
        \vspace{0.5em}
        \caption{Policy Hyperparameters}
        \label{table:model_hparams}
        % First table ends
    \end{minipage}\hfill
    \begin{minipage}[b]{0.45\textwidth}
        \centering
        % Second table starts
        \begin{tabular}{|l|l|}
            \hline
            \textbf{Hyperparameter Name} & \textbf{Value} \\ \hline
            \texttt{architecture} & MLP \\ \hline
            \texttt{hidden\_dim} & 512 \\ \hline
            \texttt{latent\_dim} & 512 \\ \hline
            \texttt{hidden\_layers} & 2 \\ \hline
            \texttt{batch\_size} & 256 \\ \hline
            \texttt{learning\_rate} & 1e-4 \\ \hline
            $\beta$ & 0.001 \\ \hline
            \texttt{n\_epochs} & 50 \\ \hline
            \texttt{n\_search\_episodes} & 2000 \\ \hline
            \texttt{k} & 5 \\ \hline
            \texttt{offset} & 8 \\ \hline
        \end{tabular}
        \vspace{0.5em}
        \caption{Prior Hyperparameters}
        \label{table:prior_hparams}
        % Second table ends
    \end{minipage}
\end{table}


\SetArgSty{textnormal}
\begin{algorithm}[h!]
\DontPrintSemicolon

\SetKwFunction{sampleEpisodeSegment}{sample\_episode\_segment}
\SetKwProg{myalg}{Function}{}{}

\myalg{\sampleEpisodeSegment{T, min\_btwn\_goals, max\_btwn\_goals}}{

  segment = sampleSegment(episode, T)\;
  curr\_timestep = segment.start\;
  goal\_switching\_indices = []\;

  \While{curr\_timestep < segment.end}{
    curr\_timestep += uniform(min\_btwn\_goals, max\_btwn\_goals)\;
    goal\_switching\_indices.append(curr\_timestep)\;
  }

  relabeled\_goal\_embeds = []\;

  \For{n in range(1, len(goal\_switching\_indices))}{
    relabeled\_goal\_embeds[$i_{n-1}$:$i_n$] = segment.goal\_embeddings[$i_n$]\;
  }

  \KwRet{segment.obs, segment.actions, relabeled\_goal\_embeds}\;

}

\caption{Sampling Episode Segments with \textbf{Packed Hindsight Relabeling}}
\label{algo:hindsight}
\end{algorithm}

\subsection{Prior Training}
\label{sec:prior}
The prior model is a simple CVAE \citep{cvae} that conditions on MineCLIP \citep{fan2022minedojo} text embeddings and models the conditional distribution of visual embeddings given the corresponding text embedding. This model is trained on a combination of around 2,000 hand-labeled trajectory segments and augmented with additional data by automatically searching for text-gameplay pairs from our gameplay dataset. This is done using the following steps:

\begin{enumerate}
    \item Combine the 2,000 text labels with 8,000 additional labels generated by querying \texttt{gpt-3.5-turbo}.
    \item For each of these 10,000 text labels, search through 1,000 episodes sampled from the gameplay dataset to find the top $5$ closest visual MineCLIP embeddings to the text embedding of the text label.
\end{enumerate}

These 50,000 automatically-mined text-video pairs are added to the original 2,000 hand-labeled examples to form the final dataset used for prior training.

We noticed when prompting \agentname{} using visual goals that when the visual goal showed the agent hitting a block but not following through and breaking it that \agentname{} actually avoided breaking blocks. Unfortunately, many of the automatically discovered text-gameplay clips include gameplay of this kind. In order to prevent this issue, we added an offset to the embeddings found in this manner. By selecting embeddings from a timestep \texttt{offset} steps after the originally-selected timestep, the agent is much more likely to follow through with breaking blocks.

We trained our prior model for 50 epochs on this dataset and used early-stopping with a small validation set. An exhaustive list of hyperparameters used for creating the prior model can be found at \Cref{table:prior_hparams}.

\subsection{Training Costs}

The \$60 cost we report corresponds to the cost of renting a 8xA10g node using spot instances on AWS for 12 hours using our instances prices in May 2023.