\documentclass{article}


% if you need to pass options to natbib, use, e.g.:
%     \PassOptionsToPackage{numbers, compress}{natbib}
% before loading neurips_2023


% ready for submission
\PassOptionsToPackage{numbers}{natbib}
\usepackage[final]{neurips_2023}

\input{_macros}


% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
%     \usepackage[preprint]{neurips_2023}


% to compile a camera-ready version, add the [final] option, e.g.:
%     \usepackage[final]{neurips_2023}


% to avoid loading the natbib package, add option nonatbib:
%    \usepackage[nonatbib]{neurips_2023}


\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{dcolumn}
\usepackage{textcomp}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mdframed}
\usepackage[nameinlink]{cleveref}
\newcolumntype{d}[1]{D{.}{.}{#1}}

\definecolor{headerColor}{RGB}{220,220,220}

\let\subsectionautorefname\sectionautorefname
\let\subsubsectionautorefname\sectionautorefname

\title{\agentname{}: A Generative Model for \\Text-to-Behavior in Minecraft}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to break the
% lines. Using \AND forces a line break at that point. So, if LaTeX puts 3 of 4
% authors names on the first line, and the last on the second line, try using
% \AND instead of \And before the third author name.

\newcommand*\samethanks[1][\value{footnote}]{\footnotemark[#1]}
\author{%
  Shalev Lifshitz$^{1,2}\thanks{Equal contribution.}$ \\
  \texttt{shalev.lifshitz@mail.utoronto.ca}
  \And
  Keiran Paster$^{1,2}\samethanks$ \\ \texttt{keirp@cs.toronto.edu} \\
  \AND
  Harris Chan$^{1,2}\thanks{Core contribution.}$ \\
  \texttt{hchan@cs.toronto.edu} \\
  \And
  Jimmy Ba$^{1,2}$ \\
  \texttt{jba@cs.toronto.edu}
  \And
  Sheila McIlraith$^{1,2}$ \\
  \texttt{sheila@cs.toronto.edu}
}


\begin{document}

\newcommand{\agentname}{\textsc{Steve-1}}

\maketitle

\renewcommand*{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}

\begin{center}\small
\vspace{-2em}
$^1$Department of Computer Science, University of Toronto, Toronto, Canada.\newline $^2$Vector Institute for Artificial Intelligence, Toronto, Canada.\quad
\end{center}

\input{macros-admin}

\begin{abstract}
\vspace{-0.5em}
Constructing AI models that respond to text instructions is challenging, especially for sequential decision-making tasks. This work introduces a methodology, inspired by unCLIP, for instruction-tuning generative models of behavior without relying on a large dataset of instruction-labeled trajectories. Using this methodology, we create an instruction-tuned Video Pretraining (VPT) model called \mbox{\agentname{}}, which can follow short-horizon open-ended text and visual instructions in Minecraft\texttrademark . \agentname{} is trained in two steps: adapting the pretrained VPT model to follow commands in MineCLIP's latent space, then training a prior to predict latent codes from text. This allows us to finetune VPT through self-supervised behavioral cloning and hindsight relabeling, reducing the need for costly human text annotations, and all for only \$60 of compute. By leveraging pretrained models like VPT and MineCLIP and employing best practices from text-conditioned image generation, \agentname{} sets a new bar for open-ended instruction-following in Minecraft with low-level controls (mouse and keyboard) and raw pixel inputs, far outperforming previous baselines and robustly completing 12 of 13 tasks in our early-game evaluation suite. We provide experimental evidence highlighting key factors for downstream performance, including pretraining, classifier-free guidance, and data scaling. All resources, including our model weights, training scripts, and evaluation tools are made available for further research.
\end{abstract}

\input{1_introduction.tex}
\input{2_related_work.tex}
\input{3_method.tex}
\input{4_experiment.tex}
\input{5_conclusion.tex}

\newpage
\input{acknowledgement.tex}

\bibliography{steve-1}
\bibliographystyle{plainnat}

\newpage
\appendix
\input{6_broaderimpact.tex}
\input{11_appendix_performance}
\input{7_appendix_ablations.tex}
\input{8_appendix_dataset.tex}
\input{9_appendix_training.tex}
\input{10_appendix_vis.tex}


\end{document}