
\section{Discussion and Future Work}
\label{sec:discussion}


We introduced \method{}, a large transformer-based policy pretrained
on the largest robot manipulation dataset to date,  \ntrajs{} robot trajectories. We demonstrated that \method{} can solve a variety of tasks out-of-the-box and showed how \method's compositional design enables finetuning to new inputs and action spaces, making \method{} a versatile initialization for a wide range of robotic control problems. Apart from the model itself, we have released our full training and finetuning code, alongside tools that make it easier to train on large robot datasets.

While \method{} achieves strong performance in both zero-shot and finetuning evaluations, we find that the current model still has several short-comings, which we attribute in large parts to characteristics of the training data.
First, we found that the current \method{} model struggles with adequately processing wrist camera information. Often finetuning results were stronger when using only a third person camera instead of combining third person and wrist camera. Additionally, we notice a large difference between language-conditioned policy performance and goal-conditioned policy performance. In both cases, a lack of the respective modalities in the training data is the likely reason: only 27\% of the data contains wrist camera information and only 56\% of the pretraining data contains language annotations.

Expanding the data used to train \method{} is a natural avenue of improvement. Since the Open X-Embodiment dataset is comprised of optimal robot demonstrations, the current model trains via imitation; future work may consider learning from sub-optimal or online interaction data that require alternative objectives. Further, while we trained and evaluated \method{} exclusively on single and dual-arm manipulators; expanding to a wider set of robots that perform navigation or mobile manipulation would be an direction of high opportunity. 

While \method{} represents a step towards building generalist robot policies that work out-of-the-box on diverse robot setups, there remains work to improve the model, including better language conditioning, improved support for wrist cameras, and incorporating data beyond optimal demonstrations. We hope that \method{} offers a simple launchpad for researchers and practitioners to access larger robotic datasets and leverage pretrained robotics models for efficient learning of new tasks and broad generalization.

