

\vspace{-0.5em}
\section{Related Work}
\label{sec:related-work}




\paragraph{Status and Limits of Current LLMs at Social Tasks.}
\label{subsec:status-and-limits-of-current-llms-at-social-tasks}
Recent benchmarks show steady progress in LLMs' social reasoning abilities. 
False belief tests \citep{kim-etal-2023-fantom, wu-etal-2023-hi} evaluate mental state tracking, while social commonsense and norm adherence tasks \citep{sap2019socialiqacommonsensereasoningsocial, zhou2023cobraframescontextualreasoning} probe broader social understanding. 
These benchmarks adopt an \textit{third-person observer} setup, where LLMs see the full context and reason from an outsider’s perspective. In contrast, tasks like SOTOPIA \citep{zhou2024sotopia} and NegotiationArena \citep{bianchi2024llmsnegotiatenegotiationarenaplatform} embed LLMs as interactive agents navigating social goals from a interactive, \textit{first-person} view. 
Both settings have exposed persistent gaps in AI's ability for long-term theory of mind, and safe social behavior.

\paragraph{Algorithms to Improve LLMs' Social Abilities.}
\label{subsec:algorithms-to-improve-llms-social-abilities}
A range of methods, including training-based, neuro-symbolic, and prompt-based methods, have been proposed to improve the social reasoning of LLMs.  Training-based approaches (e.g., SODA \citep{kim2023sodamillionscaledialoguedistillation}, SOTOPIA-$\pi$ \citep{wang2024sotopiapiinteractivelearningsocially}) distill social knowledge from large-scale interactions but struggle with generalization. 
Neuro-symbolic models (e.g., belief trackers \citep{sclar2023mindinglanguagemodelslack} and AutoToM \citep{zhang2025autotomautomatedbayesianinverse}) offer structure for reasoning but don’t scale well. 
Prompt-based methods (e.g., SIMTOM \citep{wilf2023thinktwiceperspectivetakingimproves}) focus narrowly on individual agents, risking the omission of broader social context.
Altogether, these methods capture only fragments of social reasoning, revealing the need for structured, general-purpose representations of the full social world state.

\paragraph{(Social) World Models.}
\label{subsec:social-world-models}
Recent advances in LLMs have enabled the development of general-purpose generative world models.
However, these world models have primarily focused on representing the physical state of the world \citep{xiang2024pandorageneralworldmodel, huang2022innermonologueembodiedreasoning, ding2024understandingworldpredictingfuture, liu2025worldmodelmillionlengthvideo}. 
Cognitive science research has shown that humans maintain sophisticated models of other agents' mental states \citep{sap2023neuraltheoryofmindlimitssocial, jara-ettinger2024traces}. 
This insight has inspired the theoretical discussion of mental social world \citep{hinsz1995mental, ding2024understandingworldpredictingfuture}. 
As shown in Figure \ref{fig:social-world-model}, a social world model extends traditional world models to include representations of other agents' beliefs, intentions, and potential actions.
Recent efforts to model social worlds have integrated symbolic representations with neural methods \citep{Dong2023CoRRPUS,martin2021thesis,zhang2025autotomautomatedbayesianinverse} or developed social simulation systems \citep{park2023generativeagentsinteractivesimulacra, 10.1145/3526113.3545616}. 
However, these approaches are often constrained to specific domains.




