\section*{Impact Statement}
Our work advances the understanding of social reasoning in AI systems, which has the potential to improve human--AI interaction and enable more socially-aware technologies. At the same time, it is important to consider both societal impacts and reproducibility.

\paragraph{Ethical Considerations, Risks, and Mitigation.}
Enhanced social reasoning capabilities could potentially be misused for manipulation or deception. We therefore emphasize transparent development and responsible deployment. Our framework is intended as a research tool to advance scientific understanding rather than for direct deployment in high-stakes applications.

\paragraph{Privacy and Data Considerations.}
Our experiments use publicly available datasets and benchmarks. We do not collect new human-subject data, and our experimental protocols follow established ethical guidelines for AI research. We aim to respect privacy and reduce the risk of encoding harmful biases; broader impact considerations are discussed in Appendix~\ref{app:limitations}.

\paragraph{Reproducibility and Resources.}
Complete experimental settings are documented in \S\ref{sec:social_understanding} for third-person reasoning tasks and \S\ref{subsec:sotopia_experiment_setup} for first-person interactive tasks, including data splits, prompts, and key hyperparameters. Additional implementation details are provided in the appendix. We will release our codebase in the supplemental material, including scripts for data preprocessing and evaluation, along with documentation and usage instructions. Compute resource requirements (hardware specifications and runtime estimates) are reported in Appendix~\ref{app:compute_resource}.

\paragraph{Transparency of Claims.}
All theoretical results in \S\ref{sec:protocol} are accompanied by explicit assumptions and proofs, with detailed derivations in Appendix~\ref{app:proof_of_social_world_state}. Where applicable, we report uncertainty (e.g., error bars) for experiments supporting our main claims (e.g., Figure~\ref{fig:model_performance_comparison}).

