\section{Conclusion and future work}
In this paper, we propose an interactive learning method \model to study how to use LLM ratings as a learning signal to improve the social intelligence of language agents. We first find that through optimizing the goal completion score, the general performance on \sotopia \citep{sotopia}, a social intelligence benchmark is improved. However, we find that the gap between LLM ratings and human judgment is enlarged through this process. We also find that the \model improves social intelligence without a loss of general QA ability and with an improvement in safety. 

Although \model demonstrates strong capabilities of improving social intelligence, several directions will improve our method further. (1) Online reinforcement learning: \model is an offline training method that cannot improve iteratively. Future work could study how online methods like PPO \cite{schulman2017proximal} can be applied without the high cost of LLM ratings.  (2) Learning from humans: as mentioned in \S\ref{sec:background}, we use GPT-4 as the expert due to the challenge of collecting human interaction data. Future work could explore using existing data including forum conversations, movies, and dialog datasets as offline data for training agents. (3) In \S\ref{sec:safety-section}, we only evaluate one social task, which allows us to dig deep into the task and create customized metrics. Also, how to derive safety metrics for all social tasks is an interesting future direction. (4) As demonstrated in \S\ref{automatic-eval-results}, the gap between GPT-4 and human evaluation increases as the model optimizes GPT-4 scores. Future research could consider more robust evaluation and learning signals for social intelligence tasks. 
