\section*{Ethical Statement}
Our goal for the \model project is to enhance the social intelligence of AI agents, as evaluated by \eval. Similar to \citet{sotopia}, we also focus on creating more realistic conversations, fostering better relationships, providing knowledgeable conversation, maintaining secrecy, following social rules, improving agents' abilities to achieve financial and material gains, and completing social goals. It is important to note that our objective is not to create AI systems that are indistinguishable from humans or create potential global risks~\citep{yudkowsky2008artificial}. Instead, our target is to study the development and learning processes of human social intelligence. Moreover, this research provides insights into social behavior under various circumstances without the costly need for data collection involving human participants. Because building AI systems based on large language models, particularly those designed for strategic social interactions, can lead to unexpected outcomes and potentially negative social impacts ~\citep{si2022toxic}, we approach the experiments cautiously. Specifically, the role-playing abilities of large language models may lead to anthropomorphism, as described by ~\citet{shanahan2023role}, where the AI system is perceived to exhibit human-like personalities. Our research aims to understand and responsibly navigate these challenges, potentially referring to the framework by \citet{zhang2023ethical}. 

We acknowledge that using any LLM including GPT-4 to evaluate our system, \eval, could introduce biases~\citep{wang2023large, gallegos2023bias}. Our future research will focus on identifying, understanding, and mitigating social and cultural biases~\citep{tao2023auditing}. It is essential for us to enhance our model's social intelligence without incorporating any biases. This step is also crucial in the development of responsible and unbiased AI agents. Furthermore, our study has observed that instances of unsafe behavior, such as generation of toxic language or harmful suggestions, can emerge during our model's training. These behaviors present significant social risks and safety risks \citep{hendrycks2023overview, wang2023decodingtrust}. Addressing these issues is vital for ensuring the safe and ethical use of AI in society and is particularly important during the development of AI systems.


In our human evaluation studies, we ensure that all our annotators are based in either the United Kingdom or the United States. In the United States, annotators are compensated at a rate of \$1.5 for each task they complete, with the expectation that each task will take no more than 10 minutes. This setup allows them to potentially earn over \$9 per hour, surpassing the minimum wage in the U.S. Meanwhile, in the United Kingdom, we offer additional bonuses to ensure that annotators' average earnings exceed \$14.5 per hour, aligning with minimum wage standards in United Kingdom. All human-subject experiments are approved by the Institutional Review Board (IRB) at the authors’ institution.