\section{Ethics Statement}
\label{sec:ethics-statement}

\benchmark{} is collected entirely from public repositories with licenses that permit software usage that our contributions are in accordance with.
Details of the licenses are included in Table~\ref{table:repo-summaries}.
During the collection or evaluation processes, we do not collect information about GitHub users, and the \benchmark{} task instances do not use GitHub data beyond what is offered via the public API and website.
Our contributions do not involve any human subject participation; we do not perform crowdsourcing or recruit human task workers for any part of \benchmark{}, including its collection and evaluation procedures along with the experiments.
\benchmark{}'s filtering criteria for GitHub repositories based on popularity does not implicitly or explicitly rely on any discriminative or biased heuristics for repository selection.
For the dataset release, we plan to open source the \benchmark{} task instances, the collection and evaluation infrastructure, the experimental results, the training data used for fine-tuning \swellama{} models, and the \swellama{} model weights.
Following best practice precedents, we will also put forth ample documentation to describe each component and its use, and we will also put in place convenient communication channels for soliciting feedback to improve \benchmark{}.
\benchmark{} does not put forth any immediately harmful insights.
We briefly discuss the potential impact of \benchmark{}'s usage in Section~\ref{appx:societal-impact}.

\section{Reproducibility Statement}
\label{sec:reproducibility-statement}
For our submission, we have uploaded the entirety of the source code as a zipped file that has been properly anonymized.
We have organized the codebase such that separate directories correspond to different contributions within the main paper (i.e. dataset collection, evaluation, open source model inference, \swellama{} training, etc.).
The source code contains inline documentation that details purpose and usage of different parts of the codebase.
In addition, we also include the full set of 2294 \benchmark{} task instances that contains all the components discussed in the main paper.
Beyond the documentation in the source code, we include thorough technical details for the collection pipeline and evaluation procedures in Section~\ref{appx:benchmark:construction} and Section~\ref{appx:benchmark:eval-procedure} that complements the original details in Section~\ref{sec:benchmark} of the main paper.
These sections fully cover the logic presented in the code and can be helpful for understanding it.
Moving forward, as discussed in the ethics statement, we plan to more formally release \benchmark{} to the public as an open source repository with thorough details that describes the benchmark, outlines the code, and details its usage.
A major component of \benchmark{} is the collection framework, which will be part of the open sourced code.
Because of its easily maintainable design, as discussed in the main paper, our hope and belief is that \benchmark{} should be highly reproducible.
