\begin{abstract}
  %v1
  %Developing state-of-the-art image classification models requires significant engineering efforts in tuning network architectures. In this paper, our focus is to learn a modular architecture which can be transferred from a small dataset to a large dataset. Key to our method is to reduce the problem of learning best convolutional architectures to the problem of learning a small convolutional cell. The cell can then be stacked in series to handle larger images and more complex datasets. This approach is therefore akin to learning an LSTM cell within a recurrent network.  In our experiments, the cell is learned on the CIFAR-10 dataset and then transferred to the ImageNet dataset. Although its structure was not learned directly on ImageNet, the cell shows excellent transferability. An architecture constructed from the best cell achieves state-of-the-art accuracy of 82.3\% top-1 and 96.0\% top-5 on ImageNet, which
  %is 0.8\% better in top-1 accuracy than best human-invented architectures while having 9 billion less flops. A smaller network constructed from the best cell also achieves 74\% top-1 accuracy, which is 3.1\% better than the state-of-the-art, ShuffleNet.
 
 %v2
 %Developing state-of-the-art image classification models often requires significant architecture engineering and tuning.  In this paper, we attempt to reduce the amount of architecture engineering by using Neural Architecture Search to learn an architectural building block on a small dataset that can be transferred to a large dataset.  This building block, a convolutional cell, can then be stacked in series to handle larger images and more complex datasets. This approach is similar to learning the structure of a recurrent cell within a recurrent network.  In our experiments, we search for the cell on the CIFAR-10 dataset and then apply the best cell to the ImageNet dataset. Although the cell is not learned directly on ImageNet, an architecture constructed from the best cell achieves state-of-the-art accuracy of 82.3\% top-1 and 96.0\% top-5 on ImageNet, which is 0.8\% better in top-1 accuracy than the best human-invented architectures while having 9 billion less flops. A smaller network constructed from the best cell also achieves 74\% top-1 accuracy, which is 3.1\% better than the equivalently-sized state-of-the-art model, ShuffleNet.
 
 Developing neural network image classification models often requires significant architecture engineering.  In this paper, we study a method to learn the model architectures directly on the dataset of interest. As this approach is expensive when the dataset is large, we propose to search for an architectural building block on a small dataset and then transfer the block to a larger dataset. The key contribution of this work is the design of a new search space (which we call the ``NASNet search space") which enables transferability.
 In our experiments, we search for the best convolutional layer (or ``cell") on the CIFAR-10 dataset and then apply this cell to the ImageNet dataset by stacking together more copies of this cell, each with their own parameters to design a convolutional architecture, which we name a ``NASNet architecture". We also introduce a new regularization technique called ScheduledDropPath that significantly improves generalization in the NASNet models. On CIFAR-10 itself, a NASNet found by our method achieves 2.4\% error rate, which is state-of-the-art. Although the cell is not searched for directly on ImageNet, a NASNet constructed from the best cell achieves, among the published works, state-of-the-art accuracy of 82.7\% top-1 and 96.2\% top-5 on ImageNet. Our model is 1.2\% better in top-1 accuracy than the best human-invented architectures while having 9 billion fewer FLOPS -- a reduction of 28\% in computational demand from the previous state-of-the-art model.  When evaluated at different levels of computational cost, accuracies of NASNets exceed those of the state-of-the-art human-designed models. For instance, a small version of NASNet also achieves 74\% top-1 accuracy, which is 3.1\% better than equivalently-sized, state-of-the-art models for mobile platforms.
 Finally, the image features learned from image classification are generically useful and can be transferred to other computer vision problems. On the task of object detection, the learned features by NASNet used with the Faster-RCNN framework surpass state-of-the-art by 4.0\% achieving 43.1\% mAP on the COCO dataset.
  
  %The learned architecture is computationally efficient achieving state-of-the-art accuracy with a few number of parameters and floating point operations.
  %Additionally, the learned architecture may be flexibly scaled in terms of computational demand and model size. Across a range of computational budgets, with almost 2 orders of magnitude, we find that the family of models derived from the learned architecture outperforms previous human-invented models achieving superior performance at equivalent or lesser computational demands. Notably, the smallest version of the learned model outperforms streamlined architectures targeted towards mobile and embedded vision tasks.
  %Finally, we show preliminary result demonstrating that the features of the learned architecture may be employed to improve object detection systems.
  \end{abstract}
