\section{Introduction}

Developing neural network image classification models often requires significant \emph{architecture engineering}. Starting from the seminal work of~\cite{krizhevsky2012imagenet} on using convolutional architectures \cite{fukushima1982neocognitron,lecun1998gradient} for ImageNet~\cite{deng2009imagenet} classification, successive advancements through architecture engineering have achieved impressive results~\cite{simonyan2014very,szegedy2015going,he2015deep,szegedy2016rethinking,szegedy2016inception,xie2016aggregated}. 

%In addition to being an difficult and important benchmark in computer vision, features derived from ImageNet classifiers are of great importance to many other computer vision tasks.
%We focus on ImageNet classification because the features derived from this network are of great importance in computer vision. 
%For example, features from networks that perform well on ImageNet classification
%provide state-of-the-art performance when transferred to other computer vision tasks where
%labeled data is limited %\cite{donahue2014decaf}.
%Furthermore, advances in convolutional architecture design may be applied to tasks outside of the image domain \cite{wavenet,KalchbrennerESO16}.

In this paper, we study a new paradigm of designing convolutional architectures and describe a scalable method to optimize convolutional architectures on a dataset of interest, for instance the ImageNet classification dataset. 
Our approach is inspired by the recently proposed Neural Architecture Search (NAS) framework~\cite{zoph2017neural}, which uses a reinforcement learning search method to optimize architecture configurations. Applying NAS, or any other search methods, directly to a large dataset, such as the ImageNet dataset, is however computationally expensive. We therefore propose to search for a good architecture on a proxy dataset, for example the smaller CIFAR-10 dataset, and then transfer the learned architecture to ImageNet. We achieve this transferrability by designing a search space (which we call ``the NASNet search space") so that the complexity of the architecture is independent of the depth of the network and the size of input images. More concretely, all convolutional networks in our search space are composed of convolutional layers (or ``cells") with identical structure but different weights. Searching for the best convolutional architectures is therefore reduced to searching for the best cell structure. Searching for the best cell structure has two main benefits: it is much faster than searching for an entire network architecture and the cell itself is more likely to generalize to other problems. 
In our experiments, this approach significantly accelerates the search for the best architectures using CIFAR-10 by a factor of $7\times$ and learns architectures that successfully transfer to ImageNet.


Our main result is that the best architecture found on CIFAR-10, called NASNet,
achieves state-of-the-art accuracy when transferred to ImageNet classification without much modification. On ImageNet, NASNet achieves, among the published works, state-of-the-art accuracy of 82.7\% top-1 and 96.2\% top-5. This result amounts to a 1.2\% improvement in top-1 accuracy than the best human-invented architectures while having 9 billion fewer FLOPS. On CIFAR-10 itself, NASNet achieves 2.4\% error rate, which is also state-of-the-art.

%while having fewer parameters than models with comparable performance. A small version of the state-of-the-art Shake-Shake model~\cite{gastaldi17shakeshake} with 2.9M parameters achieves 96.45\% accuracy, while our 3.3M parameters model achieves a 96.59\% accuracy. Not only does our model have a better accuracy, it also needs only 600 epochs to train, which is one third of the number of epochs for the Shake-Shake model.

%Additionally, we only train our model for 600 epochs compared to 1800 epochs for the Shake-Shake model.

  Additionally, by simply varying the number of the convolutional cells and number of filters in the convolutional cells, we can create different versions of NASNets with different computational demands. Thanks to this property of the cells, we can generate a family of models that achieve accuracies superior to all human-invented models at equivalent or smaller computational budgets \cite{szegedy2016rethinking,BatchNorm}. Notably, the smallest version of NASNet achieves 74.0\% top-1 accuracy on ImageNet, which is 3.1\% better than previously engineered architectures targeted towards mobile and embedded vision tasks \cite{howard2017mobilenets,shufflenet}.

Finally, we show that the image features learned by NASNets are generically useful and transfer to other computer vision problems. In our experiments, the features learned by NASNets from ImageNet classification can be combined with the Faster-RCNN framework~\cite{faster_rcnn} to achieve state-of-the-art on COCO object detection task for both the largest as well as mobile-optimized models. Our largest NASNet model achieves 43.1\% mAP, which is 4\% better than previous state-of-the-art. %Table~\ref{tab:intro} summarizes our main results.

%\footnote{Open-source code for performing inference on models pretrained on ImageNet is available at the {\it Slim} repository within the {\it TensorFlow} repository at \texttt{http://github.com/tensorflow/models/}}







%In terms of training time, the new search space gives a factor of 6 to 7 times speedup from the initial results by~\cite{zoph2017neural}. In particular, the search process on CIFAR-10 takes only 4 days compared to 3-4 weeks.
