\pdfoutput=1
\documentclass[11pt]{article}

% Change "review" to "final" or"preprint".
\usepackage[final]{acl}
\usepackage{times}
\usepackage{latexsym}
% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

\usepackage{microtype}

\usepackage{inconsolata}
\usepackage{graphicx}
\usepackage{amssymb, algorithm, algpseudocode, algorithmicx, lipsum, xspace,multirow,booktabs,array,colortbl,multicol}
\definecolor{mydarkblue}{rgb}{0, 0, 0.5}
% \usepackage{hyperref}
\usepackage{url}
\usepackage{tabularx}   % For tables with adjustable-width X columns
\usepackage{ragged2e}   % For \RaggedRight in X columns
%\usepackage[colorlinks,citecolor=mydarkblue]{hyperref}
\usepackage{listings}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tcolorbox}
\usepackage{array}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{graphicx}
\input{cmd.tex}

\title{\framework{}: A Self-Referential Agent Framework for Recursively Self-Improvement}

\author{ 
 Xunjian Yin$^{\spadesuit}$\hspace{0.5mm},
 Xinyi Wang$^{\clubsuit}$\hspace{0.5mm},
 Liangming Pan$^{\diamondsuit}$\hspace{0.5mm}, 
 Li Lin$^{\spadesuit}$\hspace{0.5mm}
 \\
 \bf{Xiaojun Wan$^\spadesuit$\hspace{0.5mm},
 William Yang Wang$^\clubsuit$}
\hspace{0.2mm}\hspace{1.5mm} \\
$^\spadesuit$ Peking University \quad$^\clubsuit$University of California, Santa Barbara  \quad $^\diamondsuit$ University of Arizona \\
 \texttt{\{xjyin,wanxiaojun\}@pku.edu.cn} \quad \texttt{william@cs.ucsb.edu} 
}


\begin{document}
\maketitle

\begin{abstract}
The rapid advancement of large language models (LLMs) has significantly enhanced the capabilities of agents across various tasks. However, existing agentic systems, whether based on fixed pipeline algorithms or pre-defined meta-learning frameworks, cannot search the whole agent design space due to the restriction of human-designed components, and thus might miss the more optimal agent design. In this paper, we introduce \framework, a self-evolving framework inspired by the \godel machine, enabling agents to recursively improve themselves without relying on predefined routines or fixed optimization algorithms. \framework leverages LLMs to dynamically modify its own logic and behavior, guided solely by high-level objectives through prompting. Experimental results on multiple domains demonstrate that implementation of \framework can achieve continuous self-improvement, surpassing manually crafted agents in performance, efficiency, and generalizability. 
% While \method showcases the feasibility, challenges remain in achieving stable and scalable recursive optimization, which requires the collective effort of the entire research community. 
\end{abstract}

\section{Introduction}
\input{sections/1-introduction}

\section{Related Work}
\input{sections/7-Related_Work}

\section{Self-Referential \framework{}}
\input{sections/2-Godel}

\section{\framework Implementation}
\input{sections/3-Roz}

\section{Experiments}
\input{sections/4-Experiment}

\section{Analysis}
\input{sections/5-Analysis}


\section{Discussions and Future Directions}
\input{sections/6-Discussions}


\section{Conclusion}
\input{sections/8-Conclusion}

\section*{Limitations}
\input{sections/9-Limitations}

\section*{Ethics Statement}
\framework{}, capable of reading and modifying its own code, offers significant potential for advancing AI autonomy and innovation. However, this capability raises ethical and safety concerns that must be addressed to prevent harmful outcomes.

Self-modification may lead to unpredictable behavior, such as errors or unintended outputs that could violate ethical principles or produce harmful results. To mitigate these risks while preserving innovation, we propose:
(1) \textbf{Sandboxed Environment}: Modifications should occur in an isolated sandbox to prevent unintended impacts and allow safe testing.
(2) \textbf{Constrained Modifications}: Clear rules should limit the scope of changes to ensure safety without stifling creativity.

Further research is needed to balance safety and innovation, ensuring self-modifying agents operate within ethical boundaries. Sandboxed execution and ongoing scrutiny will help maximize benefits while minimizing risks.



% \section*{Acknowledgments}
% \input{sections/z2-Acknowledgements}
% \bibliographystyle{acl_natbib}
\bibliography{custom}
\newpage
\appendix

\section{Goal Prompt of \framework}
\input{sections/z1-App}

\section{Experiment Details}
\input{sections/z2-App}

\section{Representative Policies Improved by \framework}
\input{sections/z3-App}

\section{Cost of Experiments}
\input{sections/z4-App}

% \section{Discussions and Future Directions}
% \label{app:future}
% \input{sections/6-Discussions}


\section{Additional Novel Policies Designed by \framework}
\input{sections/z5-App}

\end{document}
