\input{figs/dataset}
\section{Internet-scale Knowledge Base}
\label{sec:dataset}


Two commonly used approaches~\cite{silver2017mastering, vinyals2019alphastar, openai2019dota, DBLP:journals/ral/FuchsSKSD21} to train embodied agents include training agents from scratch using RL with well-tuned reward functions for each task, or using a large amount of human-demonstrations to bootstrap agent learning. However, crafting well-tuned reward functions is challenging or infeasible for our task suite (Sec. \ref{sec:benchmark-creative}), and employing expert gamers to provide large amounts of demonstration data would also be costly and infeasible~\cite{vinyals2019alphastar}.

Instead, we turn to the open web as an ever-growing, virtually unlimited source of learning material for embodied agents. The internet provides a vast amount of domain knowledge about Minecraft, which we harvest by extensive web scraping and filtering. We collect 33 years worth of YouTube videos, 6K+ Wiki pages, and millions of Reddit comment threads.  
Instead of hiring a handful of human demonstrators, we capture the collective wisdom of millions of Minecraft gamers around the world. Furthermore, language is a key and pervasive component of our database that takes the form of YouTube transcripts, textual descriptions in Wiki, and Reddit discussions. Language facilitates open-vocabulary understanding, provides grounding for image and video modalities, and unlocks the power of large language models \cite{devlin2018bert,shoeybi2019megatron,brown2020gpt3} for embodied agents. To ensure socially responsible model development, we take special measures to filter out low-quality and toxic contents \cite{bommasani2021foundation,detoxify} from our databases, detailed in the Appendix (Sec.~\ref{supp:sec:dataset}).

\para{YouTube Videos and Transcripts.} 
Minecraft is among the most streamed games on YouTube~\cite{gerblick_2021}. Human players have demonstrated a stunning range of creative activities and sophisticated missions that take hours to complete (examples in Fig. \ref{fig:dataset}). We collect 730K+ narrated Minecraft videos, which add up to 33 years of duration and 2.2B words in English transcripts. 
In comparison, HowTo100M~\cite{miech2019howto100m} is a large-scale human instructional video dataset that includes 15 years of experience in total -- about half of our volume. The time-aligned transcripts enable the agent to ground free-form natural language in video pixels and learn the semantics of diverse activities without laborious human labeling. We operationalize this insight in our pre-trained video-language model (Sec. \ref{sec:method-mineclip-pretraining}). 

\para{Minecraft Wiki.}
The Wiki pages cover almost every aspect of the game mechanics, and supply a rich source of unstructured knowledge in multimodal tables, recipes, illustrations, and step-by-step tutorials. We use Selenium~\cite{selenium} to scrape 6,735 pages that interleave text, images, tables, and diagrams. The pages are highly unstructured and do not share any common schema, as the Wiki is meant for human consumption rather than AI training. To preserve the layout information, we additionally save the screenshots of entire pages and extract 2.2M bounding boxes of the visual elements \Rebuttal{(visualization in Fig.~\ref{supp:fig:wiki_supp} and \mbox{\ref{supp:fig:wiki_bbox}}). We do not use Wiki data in our current experiments. Since the Wiki contains detailed recipes for all crafted objects, they could be provided as input or training data for hierarchical planning methods and policy sketches~\mbox{\cite{andreas2017sketch}}.} Another promising future direction is to apply document understanding models such as LayoutLM~\cite{xu2019layoutlm, xu2020layoutlmv2} and DocFormer~\cite{appalaraju2021docformer} to learn actionable knowledge from these unstructured Wiki data.

\para{Reddit.}
We scrape 340K+ posts along with 6.6M comments under the ``r/Minecraft'' subreddit. These posts ask questions on how to solve certain tasks, showcase cool architectures and achievements in image/video snippets, and discuss general tips and tricks for players of all expertise levels.
\Rebuttal{We do not use Reddit data for training in Sec.~\ref{sec:experiments}, but a potential idea is to finetune large language models \mbox{\cite{devlin2018bert,radford2019gpt2}} on our Reddit corpus to generate instructions and execution plans that are better grounded in the Minecraft domain. Concurrent works~\mbox{\cite{ahn2022saycan, huang2022inner, zeng2022socratic}} have explored similar ideas and showed excellent results on robot learning, which is encouraging for more future research in \mbox{\minedojo}. }