\section{Introduction}
\label{introduction}

\afterpage{\input{figures/domains/figure}}

Planning is a natural and powerful approach to decision making problems with known dynamics, such as game playing and simulated robot control \citep{tassa2012mpc,silver2017alphago,moravvcik2017deepstack}. To plan in unknown environments, the agent needs to learn the dynamics from experience. Learning dynamics models that are accurate enough for planning has been a long-standing challenge. 
Key difficulties include model inaccuracies, accumulating errors of multi-step predictions, failure to capture multiple possible futures, and overconfident predictions outside of the training distribution.

Planning using learned models offers several benefits over model-free reinforcement learning. First, model-based planning can be more data efficient because it leverages a richer training signal and does not require propagating rewards through Bellman backups. Moreover, planning carries the promise of increasing performance just by increasing the computational budget for searching for actions, as shown by \citet{silver2017alphago}. Finally, learned dynamics can be independent of any specific task and thus have the potential to transfer well to other tasks in the environment.

Recent work has shown promise in learning the dynamics of simple low-dimensional environments \citep{deisenroth2011pilco,gal2016deeppilco,amos2018awareness,chua2018pets,henaff2018planbybackprop}. However, these approaches typically assume access to the underlying state of the world and the reward function, which may not be available in practice. In high-dimensional environments, we would like to learn the dynamics in a compact latent space to enable fast planning. The success of such latent models has previously been limited to simple tasks such as balancing cartpoles and controlling 2-link arms from dense rewards \citep{watter2015e2c,banijamali2017rce}.

In this paper, we propose the \fullmethod (\method), a model-based agent that learns the environment dynamics from pixels and chooses actions through online planning in a compact latent space. To learn the dynamics, we use a transition model with both stochastic and deterministic components. Moreover, we experiment with a novel generalized variational objective that encourages multi-step predictions. \method solves continuous control tasks from pixels that are more difficult than those previously solved by planning with learned models.

Key contributions of this work are summarized as follows:
\begin{itemize}
\paritem{Planning in latent spaces}
We solve a variety of tasks from the DeepMind control suite, shown in \cref{fig:domains}, by learning a dynamics model and efficiently planning in its latent space. Our agent substantially outperforms the model-free A3C and in some cases D4PG algorithm in final performance, with on average $200\times$ less environment interaction and similar computation time.
\paritem{Recurrent state space model} We design a latent dynamics model with both deterministic and stochastic components \citep{buesing2018dssm,chung2015vrnn}. Our experiments indicate having both components to be crucial for high planning performance.
\paritem{Latent overshooting}
We generalize the standard variational bound to include multi-step predictions. Using only terms in latent space results in a fast regularizer that can improve long-term predictions and is compatible with any latent sequence model.
\end{itemize}
