    

\section{Introduction}

Most real-world tasks require teams to collaboratively solve problems, and assistive AI agents promise to further augment human capabilities in problem solving.
AI development has long focused on optimizing agents to achieve or surpass ``human-levels'' of accuracy on a given set of tasks, often learning by {\it mimicking} how other agents perform.
Rather than supplementing other agents, such objectives suggest that each newly trained agent is a means to replace another, thus diminishing team potential.
We argue for a need to create agents that are optimized to {\it collaborate} with other agents---human or AI---to complement their problem solving abilities and parallelize task execution. 

Creating such collaborative AI agents requires ensuring their ability to efficiently and effectively communicate with collaborators and continuously learn and adapt throughout this process in real-world embodied tasks. 
Meeting these goals depends on overcoming challenges pertaining to: (1) \textit{embodiment}, our primary form of interaction with the real-world; and (2) \textit{natural language}, our defacto form of \textit{communication} and simultaneously an incredibly computationally complex search space for computers.

Successful (singular LLM-based) embodied agents must be able to ground their existing knowledge of how to perform a task to the affordances of their environment, i.e. the actions that can be performed in a given state.
The longer the horizon of such a sequential decision making task, the more difficult modern agents find it to \textit{reason} about the complexities of the task and to learn from environmental feedback to correct their course of action.
Performing such tasks in tandem with other agents adds whole layers of complexity on top as agents must rapidly share critical information, coordinate plans, and efficiently manage limited resources and time \cite{cemri2025multi, guo2024large}.

To facilitate research in this area of multi-agent collaboration for embodied reasoning, we introduce \mindcraft{}, a simulation platform for studying multi-agent collaboration through natural language in rich, embodied scenarios. 
\mindcraft{} uniquely brings together the ability to test agents' abilities to collaborate, communicate, and more efficiently perform embodied reasoning~(\Cref{tab:simulator_differences}).
We further create MineCollab, a benchmark comprising three practical tasks: cooking, which involves preparing a meal while coordinating ingredient collection; crafting, where agents assemble a pickaxe from mined materials; and construction, which requires building houses from detailed blueprints as can be seen in ~\Cref{fig: motivation}.
Using our platform,  we generate a dataset of 2,000 trials with LLaMA-70B-3.3-Instruct, including around 200 successful runs, resulting in 16,000 total examples. 
Additional data can be easily produced, as a large number of variations of the task can be quickly created via procedural generation---e.g. by changing attributes such as the complexity of the types of recipes an agent would have to cook, the complexity of the blueprint, etc.

We systematically evaluate state-of-the-art LLM agents on these three task suites, testing their collaborative and embodied reasoning abilities. 
Overall, even the most advanced LLMs such as Claude 3.5 Sonnet struggle to place more than 40\% of the total blocks in our construction task - and all LLMs struggle in more complicated tasks involving four or five collaborating agents.
We find that one of the major bottlenecks is that most existing LLMs are not well optimized to communicate information with other agents via natural language, a key aspect of multi-agent collaboration.
Our experiments reveal that task success is highly sensitive to communication quality, with performance dropping by over 15\% when agents must explicitly communicate detailed plans. 
These findings underscore the limitations of standard techniques such as prompting and fine-tuning, and point to the need for more advanced methods—opening new directions for future research.



























