\section{Related Work}

\input{sections/tables/platform_comparison}

\textbf{Minecraft as a Tool for AI Research.} 
Minecraft is a vast open-ended embodied world with complex dynamics and sparse rewards.
For these reasons, it has been a popular tool for researchers for studying world models \citep{hafner2025mastering}, planning \citep{wangvoyager, nottingham2023embodied}, and simple collaboration \citep{bara-etal-2021-mindcraft, yu2024mineland}.
We chose Minecraft for similar reasons, the expressivity of the simulator allows for a large range of tasks to be designed.




\textbf{Platforms for Multi-Agent and Human-AI Collaboration.} 
Overcooked AI \citep{carroll2019utility} is a popular framework for studying the capabilities of AI agents to collaborate with one another. 
Similarly, CerealBar \citep{suhr-etal-2019-executing} and GovSim \citep{piatti2024cooperate} test collaborative abilities of LLM agents but through a different lens. 
Other works such as \citep{bohus2024towards, wan2024infer, haduong2024cps}, study fine-grained collaboration between people. 
We use these simulators as inspiration and build on them in the following ways: 1) in addition to cooking themed tasks, we include a greater variety of tasks such as crafting and construction tasks, 2) create an environment that is controllable in language, 3) study both the peer-to-peer and leader/follower interactions of our agents.
\Cref{tab:simulator_differences} outlines the differences between our platform and others. %


\textbf{Embodied AI and Robotics for Collaboration.} 
Single agent embodied scenarios in home cooking environments are the most common type of task previously studied~\citep{li2024embodied, procthor, savva2019habitat}. 
Habitat AI and the corresponding dataset of instructions PARTNR \cite{chang2024partnr} creates a large dataset of human-AI collaborative tasks. 
Similarly, \cite{zhangbuilding} studies how agents can collaborate in a kitchen. 

\textbf{Multi-agent Methods for LLMs.} 
Frameworks like Teach \citep{padmakumar2022teach} and Optima \citep{chen2024optima} add dimensions of real-time coordination and optimized efficiency in multi-agent systems. 
In \cite{zhangbuilding} and \cite{yu2024mineland}, the authors focus on creating a modular and iterative prompting method. 
Alternatively, \cite{motwani2024malt} and \cite{chen2024magdi} propose new finetuning approaches for improving multi-agent interaction in language models.
One objective of \mindcraft{} is to promote research into these methods by providing complex embodied environments to study multi-agent communication. 

