\paragraph{Social Goal}
As mentioned in Section~\ref{sec:data_analysis}, valid social goals should be both achievable and clear enough to evaluate.
In the data validation annotation task, annotators need to check all social goals appeared in each scenario to see if it is valid with or without rewriting.
Available tags include:

\begin{itemize}
    \item 0 (invalid): At least one character has no valid social goals.
    \item 1 (valid): All social goals are valid.
    \item 2 (need fix): Some social goals are invalid, but every character has at least one valid goal.
\end{itemize}

\paragraph{Private Information}
We define a private information set to be valid as being sufficient to answer the corresponding question by the agent who owns it.
Available tags in the data validation annotation task include:

\begin{itemize}
    \item 0: Invalid
    \item 1: Valid, but private info needs to be combined with the information from the goal to be complete.
    \item 2: Valid, private info is complete on its own.
    \item 3: Valid, but private info needs to be combined with the correct answer from the info reason question column to be complete.
\end{itemize}

\paragraph{Annotation Statistics}
The kappa consistency for the first and second groups of annotators is 0.79 and 0.61, respectively.
After majority voting, there are still 37 templates that need to review;
the corresponding data was handed over to another group of annotators for review. We pay the annotators according to the graduate wage standards of their respective countries.