
\section{Discussions and limitations}\label{sec: discussions and limitations}

\paragraph{When to use \our{} as an LHH.}
Our experiments limit the number of heuristic evaluations to 100 shots and the results do not necessarily scale up. \our{} is designed for scenarios where sample efficiency is crucial, such as real-world applications where heuristic evaluation can be costly. Allowing a large number of heuristic evaluations could obscure the impact of reflection or other prompting techniques, as reported by \citet{zhang2024understanding}.

\paragraph{When to use \our{} as an (alternative to) NCO/ML4CO method.}

LHH can be categorized as an NCO/ML4CO method. However, to facilitate our discussion, we differentiate LHHs from "traditional" NCO methods that usually train NN-parameterized heuristics via parameter adjustment.
In \cref{sec: heuristic generation}, we demonstrate that \our{} can either outperform or enhance NCO methods. Below, we explore the complementary nature of LHH and NCO methods.

\begin{itemize}[left=10pt]

\item \textbf{Rule-based v.s. NN-parameterized policies.}
LHHs generate interpretable and rule-based heuristics (code snippets), while NCO generates black-box NN-parameterized policies. Interpretable heuristics offer insights for human designers and can be more reliable in practice when faced with dynamic environments, limited data, distributional shifts, or adversarial attacks. However, they may not be as expressive as neural networks and may underfit in complex environments.

\item \textbf{Evolution and training.} 
LHHs require only less than 100 heuristic evaluations and about 5 minutes to evolve a strong heuristic, while many NCO methods usually require millions of samples and days of training. LHHs are more practical when solution evaluation is expensive.

\item \textbf{Inference.}
LHHs generate heuristics that are less demanding in terms of computational resources, as they do not require GPU during deployment. NCO methods require GPU for training and deployment, but they can also leverage the parallelism of GPU to potentially speed up inference.


\item \textbf{Engineering efforts and inductive biases.}
LHHs only need some text-based (and even black-box) explanations to guide the search. NCO requires the development of NN architectures, hyperparameters, and training strategies, where informed inductive biases and manual tuning are crucial to guarantee performance.
\end{itemize}

\paragraph{The choice of LLMs for \our{}.}
Reflection is more effective when using capable LLMs, such as GPT-3.5 Turbo and its successors, as discussed by \citet{shinn2023reflexion}. Currently, many open-source LLMs are not capable enough to guarantee statistically significant improvement of reflections \cite{zhang2024understanding}. However, as LLM capabilities improve, we only expect this paradigm to get better over time \cite{shinn2023reflexion}. One can refer to \cite{zhang2024understanding} for extended evaluations based on more LLMs and problem settings.

\paragraph{Benchmarking LHHs based on heuristic evaluations.}
We argue that benchmarking LHHs should prioritize the number of heuristic evaluations rather than LLM query budgets \cite{zhang2024understanding} due to the following reasons. 
\begin{itemize}[left=10pt]
    \item Prioritizing scenarios where heuristic evaluations are costly leads to meaningful comparisons between LHHs. The performance of different LHH methods becomes nearly indistinguishable when a large number of heuristic evaluations are allowed \cite{zhang2024understanding}.
    
    \item The overhead of LLM queries is negligible compared to real-world heuristic evaluations. LLM inference—whether via local models or commercial APIs—is highly cost-effective nowadays, with expenses averaging around \$0.0003 per call in \our{} using GPT-3.5-turbo, and response times of under one second on average for asynchronous API calls or batched inference. These costs are negligible compared to real-world heuristic evaluations, which, taking the toy EDA problem in this paper as an example, exceeds 20 minutes per evaluation.

    \item Benchmarking LHHs based on LLM inference costs presents additional challenges. Costs and processing time are driven by token usage rather than the number of queries, complicating the benchmarking process. For instance, EoH \cite{liu2024_llm_gls} requires heuristic descriptions before code generation, resulting in higher token usage. In contrast, although \our{} involves more queries for reflections, it is more token-efficient when generating heuristics.
\end{itemize}



\section{Conclusion}\label{sec: conclusion and limitation}

This paper presents Language Hyper-Heuristics (LHHs), a rising variant of HHs, alongside Reflective Evolution (\our{}), an evolutionary framework to elicit the power of LHHs. Applying \our{} across five heterogeneous algorithmic types, six different COPs, and both white-box and black-box views of COPs, we yield state-of-the-art and competitive meta-heuristics, evolutionary algorithms, heuristics, and neural solvers. Comparing against SOTA LHH \cite{liu2024_llm_gls}, \our{} demonstrates superior sample efficiency. The development of LHHs is still at its emerging stage. It is promising to explore their broader applications, better dual-level optimization architectures, and theoretical foundations. We also expect \our{} to enrich the landscape of evolutionary computation, by showing that genetic cues can be interpreted and verbalized using LLMs.

\clearpage