\section{Methods}
\label{sec:methods}

The main running loop of \acr{SICA} resembles the
\acr{ADAS} loop \citet{huAutomatedDesignAgentic2024} and is illustrated in
Figure~\ref{fig:agent_loop}.
In particular, both \acr{SICA}, and \acr{ADAS} keep an archive of previous agents and their benchmark results.
In the first step, \acr{SICA} takes the best performing agent from the archive up until this point as the meta-agent, which is instructed to
look through the archive, identify an improvement, and implement it. The
high-level scheme is illustrated in Algorithm~\ref{algo:adas}.
Note that this is different from \acr{ADAS}, in that \acr{ADAS} has a fixed meta-agent, so does not select the meta-agent from the archive (the archive in \acr{ADAS} is an archive of target-agents, not meta-agents).
Second, both \acr{ADAS} and \acr{SICA} evaluate the new agent on a set of evaluation benchmarks and store the results.

We define the `best' performing agent by a utility
function, which incorporates common desiderata for a good agent; the normalised
benchmark performance score $p_{\text{score}} \in [0, 1]$, the wall-clock time
in seconds $p_{\text{time}}$, as well as the dollar cost $p_{\text{cost}}$. The
base utility is calculated as
\begin{equation}
\label{eq:base_utility}
U = w_{\text{score}} p_{\text{score}} + w_{\text{cost}} (1 - \min(1, p_{\text{cost}} / \$ 10)) + w_{\text{time}} (1 - \min(1, p_{\text{time}} / 300 \text{ s}))
\end{equation}
where we set the coefficients to $w_{\text{score}} = 0.5$,
$w_{\text{cost}} = 0.25$ and $w_{\text{time}} = 0.25$.
We cap the worst cost at
\$10 per problem, and impose a timeout of 300 s after which we cancel the agent.
To give partial credit for work done before the timeout, we calculate the final
utility as follows, with a timeout penalty of $\tau = 0.5$:
\begin{equation}
U_{\text{final}} =
\begin{cases}
    U (1 - \tau), & \text{if timed out} \\
    U, & \text{otherwise}
\end{cases}
\end{equation}

Note that since we are not performing any weight updates, this numerical score
is only used to pick the next meta agent, as well as the base agent for the next
iteration.

We begin by describing the initial coding agent.
We then go on to describe the benchmark runner framework, and how this framework
naturally allows us to create a self-referential task (that of improving the
coding agent).

\begin{wrapfigure}{R}{0.35\textwidth}
\begin{tikzpicture}[
    box/.style={
        draw,
        rectangle,
        minimum width=5cm,    % Reduced from 12cm
        align=left,
        rounded corners=2pt,
        fill=white
    },
    section/.style={
        draw,
        rectangle,
        minimum width=4cm,    % Reduced from 11cm
        align=left,
        rounded corners=2pt,
        fill=b4!20
    },
    component/.style={
        rectangle,
        align=left,
        text width=4cm       % Reduced from 10cm
    }
]

% System Prompt Section
\node[section] (system) at (0,0) {System Prompt};
\node[component, below=0.55cm of system.north] (system_comp) {
    \textbullet~Agent definition and goals\\
    \textbullet~Tool documentation\\
    \textbullet~Sub-agent documentation\\
    \textbullet~System instructions
};

% Core Prompt Section
\node[section, below=2cm of system] (core) {Core Prompt};
\node[component, below=0.55cm of core.north] (core_comp) {
    \textbullet~Problem statement or instruction\\
    \textbullet~Open files\\
    \textbullet~Directory tree
};

% Assistant Messages Section
\node[section, below=1.7cm of core] (assistant) {Assistant Messages};
\node[component, below=0.55cm of assistant.north] (assistant_comp) {
    \textbullet~CoT reasoning\\
    \textbullet~Tool calls and results\\
    \textbullet~Sub-agent calls and results\\
    \textbullet~Overseer notifications
};


% Background container - now includes the component nodes
\begin{scope}[on background layer]
    \node[box,fit={(system) (system_comp) (core) (core_comp) (assistant) (assistant_comp)},inner sep=0.5cm] (container) {};
\end{scope}

% Labels for major sections
\node[rotate=90,anchor=south] at (container.west) {LLM Context Window};

\end{tikzpicture}
\label{fig:context_window}
\caption{LLM context window structure.}
\end{wrapfigure}


\subsection{Initial agent}%
\label{subsec:tools}

We were interested in useful, practically relevant coding agents capable of self-improvement.
To that end, we started with a sophisticated coding agent, with a number of tools, sub-agents and oversight mechanisms.
Of course, the tools, sub-agents and oversight mechanisms were all amenable to self-improvement; but here we simply describe the starting point.

We designed a set of tools to open (i.e.~add to the context) and close files, overwrite files, execute a shell command and a simple calculator tool. We also include basic tools to submit a final answer to a benchmark problem, return a result from a sub-agent call to its caller, as well as exiting early from a sub-agent call. Finally, we provide an `archive analysis' tool, which facilitates extracting high-level summary statistics about each agent iteration in the archive.
We describe the tool calling mechanism in more detail in Appendix~\ref{sec:function_calling}.

Next, we included several \emph{sub-agents}. These are merely agents invoked by
an existing agent, much like a tool call, by accepting input arguments and
returning a string value.
Introducing this abstraction serves two purposes.
The first is to ensure the benchmark tasks can run entirely autonomously, without human direction and guidance.
We provide the problem statement to the main entrypoint agent, (the full prompt for which is given in Appendix~\ref{subsec:prompts})
which then decomposes the task, delegating and asking questions to sub-agents.
% The  sub-agents allow the main agent to provide the guidance that would otherwise be provided by a human.
The second is to manage the context length for extended agent runs. The meta-improvement task is challenging, and the main agent may take on the order of one hour to finish one meta-improvement iteration. The sub-agent calls allow the context used for a sub-task to be naturally discarded when the agent returns, with the value returned by the sub-agent providing a summary of that sub-task in the main agent's context.
% During a run, an initial sub-agent may explore the codebase, another
% might implement some functionality, and another may test this functionality---at
% the end of each step the sub-agents' contexts are discarded, and with it the
% open file content, chain-of-thought reasoning, tool calls and so forth used to
% perform the sub-task, hence saving context.
Initially, we included three agents: a coding agent, a problem-solver agent and a reasoning agent.
The full prompts for these agents are given in Appendix~\ref{subsec:sub_agent_prompts}.

% \subsection{Oversight Mechanism}%
% \label{subsec:oversight}

Finally, one important component we provide in the initial agent that enables
extended, autonomous operation while remaining on-task, avoiding loops or other
behaviours that frustrate progress is the asynchronous overseer. This is an
\acr{LLM}, running periodically in a concurrent thread, which is prompted to
judge whether there are any pathological behaviours or deviations from the
original task, and which may intervene by notifying the currently running agent
(or any of its parents) by means of a message in-lined into the assistant
context, or in serious cases to cancel the execution of an agent if it has
deviated too far or appears stuck. The overseer is called every 30s by default,
or on key events.

This overseer is provided with a comprehensive textual representation of the
state of the system (a truncated example of which is provided in
Appendix~\ref{subsec:traces}) with verbose content truncated to limit context.
This consists of the `callgraph' of agent and sub-agent execution, in addition
to the event stream of \acr{LLM} messages, tool calls and responses, and
sub-agent calls and responses associated with each agent call.  This broad
representation of the system's behaviour, allows the overseer to to pick out
patterns, as well as detect repeated work completed by previous agent calls. The
full Overseer prompt is given in Appendix~\ref{subsec:overseer_prompt}.

The structure of the agent's contexts, which contains e.g.\ open file contents, rather than just the prompt is critical.  In the initial coding agent, the context is structured as Figure~\ref{fig:context_window}.
The system prompt with the agent definition (from Appendix~\ref{subsec:prompts}) is presented first, listing the
definitions of the tools that the agent has available and
the sub-agents it has available to call too. The system prompt concludes with system
information, such as instructions for how to break out of the agent loop and
return to the calling process.

Next comes the `core prompt', which is set as the first user message in the
chat template format\footnote{We use the user message role in the chat template
for the core prompt not by design, but owing to the fact that we are using chat
endpoints from model provider APIs. If fine-tuning the \acr{LLM} specifically
for agentic applications, one might choose a more appropriately named section
delimiter such as \texttt{<core>}.}, and contains the caller-specified problem
statement to work on (the caller might be the user invoking the agent, or an
agent calling a sub-agent). This is also where we insert a view of the files the
agent has open, as well as a representation of the current working directory.

Finally, the remainder of the \acr{LLM} agent's context is the running assistant
message. This contains periods of chain-of-thought reasoning about the problem,
punctuated by tool calls and their responses, sub-agent calls and their
responses, as well as any notifications or comments from the asynchronous
overseer system.

The \acr{LLM} context is laid out in this way to allow new content to be
appended, hence preserving the \acr{KV} cache to the benefit of latency between
tool calls and cost. For the base agent, we adopt a simple scheme where file
edits are appended as diffs, and these are periodically re-consolidated into the
stale file view after a certain number accumulate. More sophisticated \acr{KV}
cache preservation schemes may be written by the agent to drive down cost.

\begin{algorithm}[t]
  \KwIn{Evaluation benchmarks $B = \{b_{j} : j = 1, \ldots, m\} $, iteration count $n \in \mathbb{N}$}
  \KwOut{Improved agent system $A_{n}$}
  Initialise agent $A_{0}$\;
  \For {$i = 0, 1, \ldots, n-1$} {
    Evaluate $A_{i}$ on benchmarks $B$ and store in $p_{i}$\;
    Run $A_{\hat{i}}$ to generate $A_{i+1}$, using the archive of $A_{\le i}$
    and $p_{\le i}$, where $\hat{i} = \argmax_{j \in \{0, \ldots, i\}}p_{j}$\;
  }
  \Return $A_{n}$\;
  \caption{\label{algo:adas}Self-Referential Agent Improvement.}
\end{algorithm}
