\section{Related Works}\label{sec:related_work}
\paragraph{Self Improving LLM.} Previous works \citep{zelikman2022star, wang-etal-2023-self-instruct, huang-etal-2023-large, madaan2023self,10.5555/3692070.3692326, gulcehre2023reinforcedselftrainingrestlanguage, singh2024beyond, DBLP:conf/iclr/NiIWPMRG23, DBLP:conf/emnlp/HwangKKYS24, havrilla2024glorewhenwhereimprove, pang2024language} have demonstrated the feasibility of LLMs' self-improvement over their previous iteration by training on data distilled by the previous instances of the model. Most of these approaches usually have data filtering/reranking step in the pipeline, which is often performed by the model itself \citep{wu2025metarewarding} or by training another \citep{hosseini2024vstar} verifier model.  Particularly, \citep{huang-etal-2023-large, wang2023selfconsistency,prasad2024selfconsistencypreferenceoptimization} demonstrated the feasibility of using majority voting and self-consistency to filter chain-of-thought traces that, when used as SFT training data, improve the LLM performance on downsteaming tasks. A concurrent work, \citep{zhao2025absolutezeroreinforcedselfplay}, proposes a self-evolution, self-play pipeline where an LLM generates coding problems of appropriate difficulty, solves and trains on them using RLVR. The model-generated solutions are validated by a code executor in the loop. 
Previous works have studied self-improvement by generating labels through majority voting ~\citep{prasad2024selfconsistencypreferenceoptimization, huang-etal-2023-large}, but these works are typically confined to one or a few rounds of SFT or DPO~\citep{rafailov2024directpreferenceoptimizationlanguage}. This essentially involves distilling majority voting labels from a fixed policy into the current policy over each round of training. In contrast, we explore \textit{online RLVR's} potential in self-improving LLMs where the label generating policy evolves after every gradient step. A few concurrent works~\citep{chen2025selfquestioninglanguagemodels,prabhudesai2025maximizingconfidenceimprovesreasoning,zhao2025learningreasonexternalrewards,shao2025spuriousrewardsrethinkingtraining} have also explored various forms of self-rewarding mechanisms through majority voting or a similar metric of self-consistency (e.g., token/sequence level entropy) in Online RLVR. 
Finally, in a recent work, \citep{song2025mind} formalized a generation verification gap as central to the model's ability to self-improve. Similarly, \citep{huang2025selfimprovement} proposed a ``sharpening" mechanism as the key to self-improvement. Our \algo{} pipeline builds on top of both of these intuitions. We refer the interested reader to~\citet{gao2025surveyselfevolvingagentspath} for a survey of other works associated with self-evolving LLM agents.

\paragraph{Online RLVR and Easy to Hard Generalization.} Online reinforcement learning with verifiable reward (RLVR) \citep{lambert2025tulu3pushingfrontiers} has emerged as a new paradigm of LLM post-training especially for enhancing math, coding and reasoning performances \citep{openai2024openaio1card, deepseekai2025deepseekr1incentivizingreasoningcapability, kimiteam2025kimik15scalingreinforcement, lambert2025tulu3pushingfrontiers}. Despite the success of the reasoning models, it is still unclear to what extent they can generalize beyond the difficulty of their training data distribution, a problem termed easy to hard generalization \citep{sun2024easytohard}. \citep{sun2024easytohard} shows that models can be trained to solve level 4-5 MATH\citep{hendrycks2021measuring} problems after training using a process reward model trained on MATH level 1-3 dataset. Another work \citep{lee2025selfimprovingtransformersovercomeeasytohard} explores this question and finds that transformers are capable of easy-to-hard generalization by utilizing \textit{transcendence} phenomenon \citep{zhang2024transcendence} in the context of simple addition, string copying, and maze solving using small language models. 

\paragraph{Model Collapse and Reward Hacking.} Model collapse is a well-known phenomenon in training on self-generated training data \citep{alemohammad2024selfconsuming, DBLP:journals/nature/ShumailovSZPAG24, shumailov2024curserecursiontraininggenerated, bertrand2024on, briesch2025large}, and multiple approaches related to data mixing, reliable verification, training using contrastive loss using negative samples and curriculum learning have been proposed \citep{gerstgrasser2024is, feng2025beyond, briesch2025large, song2025mind, gillman2024selfcorrectingselfconsumingloopsgenerative, setlur2024rl} to prevent models from collapsing, which previous work on LLM's easy to hard generalization \citep{lee2025selfimprovingtransformersovercomeeasytohard} also utilize. 
However, in RL paradigm, we do not directly do supervised fine-tuning on model-generated data, and it remains an open question to what extent the previous findings of model collapse apply to our RLVR setting. In our work, we show that models trained using RL on self-labeled data often suffer from actor collapsing due to reward hacking \citep{amodei2016concreteproblemsaisafety, denison2024sycophancysubterfugeinvestigatingrewardtampering} and propose a few strategies to mitigate it. Finally, a concurrent and complementary work,~\citet{zhang2025freelunchrethinkinginternal}, has also demonstrated the failure of various self-reward mechanisms to sustain self-improvement under prolonged training, which further validates the observations in this work.


\paragraph{Data Efficient RLVR.} Several concurrent works look into the data efficiency of the RLVR pipeline. Notably, \citep{wang2025reinforcementlearningreasoninglarge} shows that by just training on one example, the model can achieve performance equivalent to training on 1.2k examples from the DeepScaleR dataset \citep{deepscaler2025}. Similarly, TTRL \citep{zuo2025ttrl}, also proposes a label-free online RLVR paradigm in a test-time setting, similar to \algo{}. Our work also explores this paradigm in Section \ref{sec4.test.time.self.improvement} as an extension of SRT.
