\section{Conclusion}\label{sec:conclusion}


We use Large Language Models as the commonsense world model and the heuristic policy within Monte Carlo Tree Search to achieve better-reasoned decision-making for daily tasks. MCTS enables LLM to leverage its world modelling knowledge for informed reasoning and explore new combinations of actions to tackle novel tasks. LLM helps MCTS through the biased sampling of states and actions, improving its efficiency in resolving complex task-planning problems. 
{
% \color{blue}
Our analysis and empirical evidence suggest that, for certain real-world domains, if the description length of the world is substantially shorter than policy, using LLM as a model in a model-based approach is a better option than using LLM as policy. 
%However, this rule only applies for moderately complex reasoning problems, or external information is available to rectify the LLM's model error, like LLM-MCTS. Otherwise, both approaches should work equally well or have near-zero performance. 

\textbf{Limitations.} The runtime of LLM-MCTS is currently hindered by multiple LLM calls. The details of runtime performance are in Appendix \ref{app-sec:runtime}. %However, our study aims to identify this possibility and highlight the trade-off between accuracy and computational efficiency. 
While our method requires multiple LLM calls, it provides substantially improved results. There are also various ways to enhance runtime performance like using smaller LLMs like Llama \cite{touvron2023llama, touvron2023llama2} or distilling LLM's knowledge into a smaller model \cite{shridhar2023distilling, hsieh-etal-2023-distilling, liang2023less}. Those are interesting avenues for future research.

\textbf{Broader impact.} There might be concerns about the inherent biases of LLMs that may lead to unfair or risky decisions in some domains. Further study about the fairness and bias of LLMs' knowledge would be beneficial.  
}


% \paragraph{Boarder impact}

%%% Local Variables:
%%% TeX-master: "./main"
%%% End: