\section{Evaluation}
\label{sec:evaluation}

The rapid emergence of autonomous LLM-based agents has underscored the need for rigorous, multidimensional evaluation frameworks. As these agents are deployed across increasingly diverse tasks and environments, recent research has introduced a range of benchmarks and methodologies to assess not only task completion but also reasoning quality, generalisation ability, and compliance with safety and alignment standards. Evaluation is no longer viewed as a static endpoint but as a dynamic feedback mechanism: fine-grained performance signals are now used to guide agent optimisation, prompt refinement, and dataset augmentation, enabling self-evolving systems that continuously acquire new capabilities and address failure cases. Current evaluation paradigms encompass structured benchmark tasks with standardised metrics, safety- and alignment-oriented audits, and LLM-as-a-judge approaches that leverage large models as flexible, scalable evaluators. 

\subsection{Benchmark-based Evaluation}

\subsubsection{Tool and API-Driven Agents}
Tool-augmented agents are evaluated based on their ability to invoke external APIs and functions to solve problems that exceed the scope of their intrinsic knowledge. Benchmarks such as ToolBench~\citep{xu2023tool}, API-Bank~\citep{li2023api}, MetaTool~\citep{huang2023metatool}, and ToolQA~\citep{zhuang2023toolqa} define tasks that require tool usage and assess both the correctness and efficiency of API calls. Many of these evaluations employ simulated APIs or sandboxed environments, measuring task success alongside interaction efficiency. Early studies have shown that agents often overfit to specific tool schemas, exhibiting limited generalisation to previously unseen APIs. To address this limitation, recent benchmarks such as GTA~\citep{wang2024gta} and AppWorld~\citep{trivedi2024appworld} introduce more realistic, multi-step tasks that require planning and coordination across multiple tools, while placing greater emphasis on process-oriented evaluation metrics. This trend reflects a broader shift towards richer, reasoning-aware evaluations that assess not only final outcomes but also the quality of the decision-making process.

\subsubsection{Web Navigation and Browsing Agents}
Web agents are evaluated on their ability to interact with websites, extract information, and complete real-world online tasks. Benchmarks such as BrowseComp~\citep{wei2025browsecomp}, MM-BrosweComp~\citep{li2025mm}, WebArena~\citep{zhou2023webarena}, VisualWebArena~\citep{koh2024visualwebarena}, WebCanvas~\citep{pan2024webcanvas}, WebWalker~\citep{wu2025webwalker}, and AgentBench~\citep{liu2023agentbench} have progressively increased the realism and diversity of web-based evaluations, spanning simulated and live environments. These benchmarks test navigation skills, adaptability to interface changes, and the integration of textual and visual information. Recent work incorporates intermediate metrics (e.g., sub-goal completion) and robustness assessments, though reproducibility and generalisation remain challenging due to the dynamic nature of the web.

\subsubsection{Multi-Agent Collaboration and Generalists}
As agents become more general-purpose, new benchmarks target multi-agent coordination and cross-domain competence. MultiAgentBench~\citep{zhu2025multiagentbench} and SwarmBench~\citep{ruan2025benchmarking} evaluate collaboration, competition, and decentralised coordination among LLM agents, assessing both task completion and the quality of communication and strategy. Generalist benchmarks such as GAIA~\citep{mialon2023gaia} and AgentBench~\citep{liu2023agentbench} test adaptability across diverse environments, from web navigation to coding and database queries. Recent work, \cite{wang2025efficientagentsbuildingeffective} further explores the GAIA benchmark to analyse the efficiency–effectiveness trade-off in agentic systems, proposing \textsc{Efficient Agents}, a framework that achieves competitive performance with significantly reduced operational costs. These evaluations highlight challenges in aggregating metrics across heterogeneous tasks, risks of overfitting to narrow scenarios, and the need for unified, holistic leaderboards.

\subsubsection{GUI and Multimodal Environment Agents}
GUI and multimodal benchmarks challenge agents to operate in rich, interactive environments that combine textual and visual inputs. Mobile-Bench~\citep{deng2024mobile}, AndroidWorld~\citep{rawles2024androidworld}, CRAB~\citep{xu2024crab}, GUI-World~\citep{chen2024gui}, and OSWorld~\citep{xie2024osworld} simulate realistic apps and operating systems, requiring complex action sequences. Tasks often combine natural language understanding, visual perception, and API invocation. Evaluations measure task success, state management, perception accuracy, and adaptability to GUI changes. However, the diversity of GUI environments makes standardisation and reproducibility difficult, and agents remain brittle when faced with interface variability.


\subsubsection{Domain-Specific Task Agents}
Domain-focused benchmarks in coding (SWE-bench~\citep{jimenez2023swe}), data science (DataSciBench~\citep{zhang2025datascibench}, MLGym~\citep{nathani2025mlgym}), enterprise productivity (WorkBench~\citep{styles2024workbench}), and scientific research (OpenAGI~\citep{ge2023openagi}, SUPER~\citep{bogin2024super}) assess specialised competencies that integrate planning, tool use, and adherence to domain norms. SWE-bench, for example, evaluates code-editing agents on real GitHub repositories, while AgentClinic~\citep{schmidgall2024agentclinic} and MMedAgent~\citep{li2024mmedagent} test multimodal reasoning in clinical settings. 
Evaluation criteria have expanded from binary success measures to encompass metrics such as test pass rates, policy adherence, and conformity to domain-specific constraints. Despite these advances, inconsistencies in metric definitions and persistent gaps in generalisation remain significant challenges.



\subsection{LLM-based Evaluation}

\subsubsection{LLM-as-a-Judge}
The LLM-as-a-Judge paradigm refers to employing large language models to assess the quality of outputs generated by AI systems, such as text, code, or conversational responses, via structured prompts~\citep{arabzadeh2024towards,li2024llms,qian2025enhancing}. This approach has attracted attention as a scalable and cost-effective alternative to conventional evaluation methods, including human judgment and automatic metrics (e.g., BLEU, ROUGE), which often fail to capture semantic depth or coherence~\citep{arabzadeh2024towards}. LLM judges typically operate in two modes: \textit{pointwise} evaluation~\citep{ruan2024liveideabench}, where outputs are scored directly against criteria such as factuality and helpfulness, and \textit{pairwise} comparison, where two outputs are compared and the preferred one is selected with justification~\citep{li2024llms,zhao2024auto}.

Recent studies demonstrate that LLM-based evaluations can correlate with human judgments, in some cases reaching parity with inter-annotator agreement levels~\citep{arabzadeh2024towards}. However, these methods are sensitive to prompt design and susceptible to biases introduced by subtle instructional variations~\citep{arabzadeh2024towards,zhao2024auto}. Furthermore, single-step, output-focused evaluations may overlook the reasoning depth in multi-step processes~\citep{zhuge2024agent,wang2025dynamically}. To address these limitations, enhancements have been proposed, including multi-agent deliberation frameworks such as CollabEval~\citep{qian2025enhancing} and structured meta-evaluation benchmarks to calibrate and improve the reliability of LLM judges~\citep{li2024llms,zhao2024auto}.

\subsubsection{Agent-as-a-Judge}
The Agent-as-a-Judge framework extends LLM-based evaluation by employing full-fledged agentic systems capable of multi-step reasoning, state management, and tool use to critique other AI agents~\citep{zhuge2024agent,zhao2024auto,qian2025enhancing}. Different from traditional LLM judges, which focus solely on final outputs, agent judges evaluate the entire reasoning trajectory, capturing decision-making processes and intermediate actions~\citep{zhuge2024agent}. For example, \cite{zhuge2024agent} applied an agent judge to the DevAI benchmark for code-generation agents. The framework incorporated specialised modules to analyse intermediate artefacts, construct reasoning graphs, and validate hierarchical requirements, resulting in evaluations that aligned more closely with human expert judgments than traditional LLM-based approaches. Agent judges also delivered substantial efficiency gains, reducing evaluation time and cost relative to manual review~\citep{zhuge2024agent,zhao2024auto}.

Nevertheless, implementing the Agent-as-a-Judge methodology introduces additional complexity and raises challenges for generalisation to domains other than code generation. Current research seeks to improve adaptability and simplify deployment across a broader range of AI tasks~\citep{zhao2024auto,qian2025enhancing}.


\subsection{Safety, Alignment, and Robustness in Lifelong Self-Evolving Agents}
In the context of the \ThreeLaws{}, \textbf{Endure}, the maintenance of safety and stability during any modification, forms the primary constraint on all other forms of adaptation. For lifelong, self-evolving agentic systems, safety is not a one-off certification but an ongoing requirement: every evolution step, from prompt updates to topology changes, must be assessed for unintended or malicious behaviours. This necessitates evaluation protocols that are \emph{continuous}, \emph{granular}, and \emph{scalable}, ensuring that agents can remain aligned while adapting over extended lifetimes.

Recent work has introduced diverse evaluation paradigms. Risk-focused benchmarks such as \textsc{AgentHarm}~\citep{andriushchenko2024agentharm} measure an agent’s propensity to comply with explicitly malicious multi-step requests—requiring coherent tool use to execute harmful objectives such as fraud or cybercrime, revealing that even leading LLMs can be coaxed into complex unsafe behaviours with minimal prompting. Domain-specific probes such as \textsc{RedCode}~\citep{guo2024redcode} (code security) and \textsc{MobileSafetyBench}~\citep{lee2024mobilesafetybench} (mobile control) stress-test agents in realistic, sandboxed environments. Behavioural probes like \textsc{MACHIAVELLI}~\citep{pan2023rewards} explore whether agents develop unethical, power-seeking strategies under reward optimisation, highlighting the interplay between \textbf{Endure} and \textbf{Excel}, safe adaptation must not degrade core task competence.

Meta-evaluation approaches, e.g., \textsc{Agent-as-a-Judge}~\citep{zhuge2024agent}, \textsc{AgentEval}~\citep{arabzadeh2024towards}, and \textsc{R-Judge}~\citep{yuan2024r} -- position LLM agents themselves as evaluators or safety monitors, offering scalable oversight but also exposing the limitations of current “risk awareness.” These studies underline the multi-dimensional nature of safety, where accuracy alone is insufficient; over-reliance on correctness metrics can conceal epistemic risks and systemic biases~\citep{li2025accuracy}. Legal alignment tests such as \textsc{SafeLawBench}~\citep{cao_safelawbench_2025} further show that even state-of-the-art models struggle to satisfy established legal principles, reflecting the difficulty of codifying alignment in domains with open-textured norms.

Despite these advances, most current evaluations are \textit{snapshot-based}, assessing agents at a single point in time. For MASE systems, safety evaluation must itself become dynamic -- continuously monitoring, diagnosing, and correcting behaviours as the system evolves. Developing longitudinal, evolution-aware benchmarks that track safety, alignment, and robustness across the full lifecycle of an agent ecosystem remains an open and urgent challenge.