\section{A DSL for Causal Trajectories}
\label{sec:dsl}

Final-answer accuracy cannot distinguish guessing from transferable mechanism discovery. We therefore introduce a domain-specific language (DSL) that records per-step causal commitments and converts hypotheses into SCM artifacts for trajectory-level scoring.

At each interaction step \(t\), the agent emits a compact DSL record with five
fields: \emph{Memory} \(M_t\), the persistent episode notes; \emph{Thought}
\(T_t\), a short interpretation of the current evidence; \emph{Past data}
\(\mathcal{D}_{\le t}\), the accumulated observations and intervention
outcomes; \emph{Hypothesis} \(H_t\), the current causal claim; and
\emph{Experiment} \(E_t\), the next planned intervention and its rationale.
Only \(H_t\) is used as a scored causal artifact: it states hypothesized edges,
the structural equation for \texttt{frequency}, and the associated
coefficients. Appendix Figure~\ref{fig:causal_visualization} shows how parsed
hypotheses are rendered as candidate graphs and recovery metrics over time.
Prompting and repair details appear in Appendix~\ref{app:dsl_implementation}.

\paragraph{Making the hypothesis parsable.}
We make \(H_t\) a scored object by requiring a fixed schema rather than
free-form prose. The schema contains three typed parts: directed edges as
\texttt{(parent, child)} pairs over episode variables, a \texttt{frequency}
structural equation in the declared functional family, and numeric coefficients
for the equation terms. A deterministic parser converts each valid hypothesis
into a candidate graph \(G_t\) and target mechanism \(\hat f_t\), producing a
trajectory \(\{(G_t,\hat f_t)\}_{t=1}^{T}\). This lets the benchmark score the
mechanism the agent commits to at each step using the same graph, root, and
coefficient metrics used for final evaluation, rather than relying only on the
final numeric answer.

