\section{The Construction of CausaLab}
\label{sec:benchmark}

This section first defines the episode-level task and what the agent must
infer, then specifies the SCM in \S\ref{sec:scm-construction}, the observation
and intervention protocol in \S\ref{sec:obs-int}, and the evaluation targets in
\S\ref{sec:eval-targets}. Artifact, licensing, and implementation details
are provided in Appendix~\ref{app:artifact_implementation}.
Throughout the section, Figure~\ref{fig:causal_main} serves as a running
example: the agent first observes prior crystal records, then intervenes on a
controllable property of the manipulator crystal, and finally predicts the
reactor crystal's hidden \texttt{frequency}.

\paragraph{Design principles.}
The benchmark is designed around three goals. First, can a model infer a
causal mechanism that transfers to a new instance, rather than fitting an
isolated value pattern? Second, can it choose informative interventions rather
than passively consume a fixed dataset? Third, how do these abilities scale
with graph size, topology, functional form, intervention budget, and hidden
disturbances? The corresponding design choices that realize these goals are
shared-mechanism transfer between two crystals, online intervention choice,
and synthetically controlled SCM generation with known ground truth.

\paragraph{Task formulation.}
A \projectname{} episode is a transfer problem under a hidden SCM: the causal
graph, structural equations, and coefficients are all hidden, and the agent is
given only prior measurement records plus a finite budget for interventions
(Figure~\ref{fig:causal_main}). The episode also contains two crystals
generated by the same SCM: a manipulator crystal on which the agent may
intervene, and a reactor crystal whose \texttt{frequency} is held out. The
initial records contain physical properties and resulting \texttt{frequency}
values from earlier measurements under the same SCM. The agent then spends its interaction budget on
interventions over controllable non-\texttt{frequency} properties of the
manipulator crystal and observes the resulting measurements. After collecting
this evidence, the agent predicts the hidden \texttt{frequency} of the reactor
crystal. The records, manipulator crystal, and reactor crystal share the same
SCM but have different property values, so the agent cannot solve the task by
copying an observed frequency; it must infer a mechanism that transfers.

The agent is told the property names and functional family but receives
interventions only on a configured subset \(C\subseteq O\) of controllable
observable non-\texttt{frequency} variables; variables outside \(C\)
(including \(Y\) and any non-controllable property) are observable but not
intervenable. The reactor crystal exposes only its non-\texttt{frequency}
variables; Appendix Table~\ref{tab:variable_access} summarizes which variables
are observable, intervenable, and hidden/exogenous in the episode. At each step
the agent also emits a DSL
hypothesis that we parse into a directed graph, \texttt{frequency} equation,
and coefficients. Solving an episode therefore requires both a correct
reactor prediction and a causal hypothesis that matches the hidden SCM under
the metrics of \S\ref{sec:eval-targets}.

\subsection{Structural Causal Models}
\label{sec:scm-construction}

Each episode instantiates an SCM
\(\mathcal{M}=(\mathbf{U},\mathbf{V},F,P(\mathbf{U}))\) \citep{Pearl_2009}.
Here \(\mathbf{U}\) are exogenous source terms, \(\mathbf{V}\) are endogenous
variables, \(F\) is the set of structural equations, and \(P(\mathbf{U})\) is
the exogenous distribution. In \projectname{}, the endogenous variables are
observable properties \(O\) plus the target \(Y=\texttt{frequency}\). Root
variables are endogenous nodes whose values are generated from exogenous source
terms, and optional hidden-noise terms are also exogenous. We sample a DAG
\(G\) over \(\mathbf{V}=O\cup\{Y\}\), assign root nodes from their exogenous
sources, then compute non-root variables in topological order. We use exactly
two structural-equation families: linear and quadratic. In the linear family,
\[
X = b + \sum_{p \in \mathrm{pa}(X)} w_p p,
\]
and in the quadratic family,
\[
X = b + \sum_{p \in \mathrm{pa}(X)} (u_p p^2 + w_p p).
\]
The sampled graph, equations, and coefficients, including the base value of
\texttt{frequency}, are shared across the prior records, manipulator crystal,
and reactor crystal; controllable-property base values differ across these
instances. This hidden
SCM corresponds to the causal graph in Figure~\ref{fig:causal_main}, serves as the common mechanism behind the prior records, the manipulator crystal,
and the reactor crystal. This asymmetry is what forces the agent to infer how variables are
connected and then apply that mechanism to the reactor's property values.

Some graph families also include an unobserved exogenous disturbance \(H\)
that perturbs the system as follows. After every intervention, \(H\) is
resampled and added as a fixed-weight shift to a designated subset of
observable endogenous variables; those shifted values then propagate
downstream through \(F\). \(H\) itself is not in \(\mathbf{V}\), is not named
to the agent, and cannot be observed or set directly --- the agent sees only
its downstream effects on the returned variable values. These settings test
whether an agent can distinguish a stable causal mechanism from
post-intervention noise. Additional distributions and coefficient ranges
appear in Appendix~\ref{app:appendix}; formal SCM and hidden-disturbance
details appear in Appendix~\ref{app:scm_details}.
\subsection{Interaction and Outputs}
\label{sec:obs-int}

Each episode proceeds through a repeated hypothesis--experiment loop. The
agent receives an initial batch of measurement records, including
non-\texttt{frequency} properties and the resulting \texttt{frequency}. It may
then intervene by setting one controllable non-\texttt{frequency} property on
the manipulator crystal; the environment recomputes that crystal's resulting
measurement under the hidden SCM and returns it to the agent. The reactor
crystal is observed but not intervened on: its non-\texttt{frequency}
properties are visible, and its
\texttt{frequency} remains hidden until the agent submits a final value.

Concretely, the loop begins with the initial observation batch and then
alternates between interventions and observations:
\emph{choose an intervention on one controllable manipulator-crystal property}
\(\rightarrow\) \emph{observe the resulting manipulator-crystal measurement}
\(\rightarrow\) \emph{revise the DSL hypothesis and choose the next
intervention}. For example, after seeing several prior measurement records, an
agent may set the manipulator crystal's \texttt{radiation} to a
chosen value, see how \texttt{temperature}, \texttt{conductivity}, and
\texttt{frequency} change, and then decide whether the evidence supports a
direct edge into \texttt{frequency} or an indirect path through another
property. This is the interaction that Figure~\ref{fig:causal_main} depicts at
the task level and Appendix Figure~\ref{fig:causal_visualization} exposes at the
trajectory level.

The intervention semantics are shift-style rather than hard
\(\mathrm{do}(X{=}v)\) \citep{backshift2015}, and we specify them here because
they determine what the agent's returned observations mean.
This models a laboratory control that shifts a controllable baseline while preserving upstream dependencies across sequential interventions.

For a controllable
variable \(X\in C\), an intervention request with value \(v\) replaces the
base term in that variable's structural equation for the next environment
update:
\[
X \leftarrow v + \sum_{p \in \mathrm{pa}(X)} w_p p
\]
in the linear family, and analogously
\[
X \leftarrow v + \sum_{p \in \mathrm{pa}(X)} (u_p p^2 + w_p p)
\]
in the quadratic family. Incoming parent contributions are therefore retained;
only the intercept/base component is shifted. A hard intervention would instead
force \(X=v\) and sever incoming causal influence.

At the end of the episode, the agent submits a numeric prediction for the
reactor \texttt{frequency} and a final DSL hypothesis specifying causal edges,
the proposed structural equation for \texttt{frequency}, and coefficients. The
same DSL can be emitted at intermediate steps, giving a trajectory of evolving
hypotheses.

\subsection{Evaluation}
\label{sec:eval-targets}

We evaluate whether the model both solves the held-out task and recovers the
mechanism needed to solve it causally. Task success is frequency accuracy on
the reactor crystal, corresponding to the final reactor prediction in
Figure~\ref{fig:causal_main}.
Mechanism recovery compares the parsed structured hypothesis log
against the ground-truth SCM: graph precision, recall, and \(F_1\) measure
recovered causal edges; structural Hamming distance (SHD) counts missing,
extra, and reversed directed edges, with lower values indicating closer graph
recovery; coefficient \(F_1\) measures whether the quantitative
\texttt{frequency} mechanism is correct; and root-node identification measures
whether the agent distinguishes exogenous/root variables from mediated
variables. This separation is essential: an agent may predict the held-out
\texttt{frequency} without recovering the SCM, or recover the qualitative graph
while missing the coefficients needed for reliable transfer.
A correct solution therefore requires three linked behaviors: collect useful
observational/interventional evidence, infer a graph and target equation that
explain the prior records and manipulator-crystal measurements, and apply that mechanism to the reactor
crystal's observed properties.
