\pdfoutput=1
\documentclass{article} %
\usepackage[dvipsnames]{xcolor}
\usepackage{colm2024_conference_arxiv}

\usepackage{microtype}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{epigraph} 
\usepackage{tabularx}

\usepackage{xcolor}
\lstset{language=Python, basicstyle=\ttfamily\small, breaklines=true}

\input{math_commands}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}
\renewcommand{\R}{\mathbb R}

\newcommand{\rylan}[1]{\textcolor{red}{rylan: #1}}
\newcommand{\dhruv}[1]{\textcolor{blue}{dhruv: #1}}
\newcommand{\apratim}[1]{\textcolor{magenta}{apratim: #1}}
\newcommand{\DR}[1]{\textcolor{red}{Dan: #1}}
\newcommand{\mg}[1]{\textcolor{green!80!black}{matthias: #1}}
\newcommand{\DLD}[1]{\textcolor{cyan}{daviddonoho: #1}}
\newcommand{\replace}[1]{#1}
\newcommand{\replacemultiple}[1]{#1}
\newcommand{\accumulate}[1]{#1}



\title{Is Model Collapse Inevitable? Breaking the Curse of\\ Recursion by Accumulating Real and Synthetic Data}


\author{Matthias Gerstgrasser\thanks{Denotes equal authorship.}\, \thanks{Harvard \& Stanford University.} \,, Rylan Schaeffer$^*$, Apratim Dey$^*$, Rafael Rafailov$^*$, Dhruv Pai \\
Stanford University \\
\texttt{\{mgerst,rschaef,apd1995,rafailov,dhruvpai\}@stanford.edu} \\
\AND
Henry Sleight\thanks{Denotes equal contribution.}\,, John Hughes$^{\ddag}$, Tomasz Korbak$^{\ddag}$, Rajashree Agrawal$^{\ddag}$\\
Constellation \\
\AND
Andrey Gromov\\
University of Maryland, College Park \\
\AND
Daniel A. Roberts\\
MIT \& Sequoia Capital\\
\AND
Diyi Yang, David Donoho \& Sanmi Koyejo\\
Stanford University\\
\texttt{\{diyiy,donoho,sanmi\}@stanford.edu} \\
}


\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\colmfinalcopy %
\begin{document}


\maketitle

\begin{abstract}
The proliferation of generative models, combined with pretraining on web-scale data, raises a timely question: what happens when these models are trained on their own generated outputs? Recent investigations into model-data feedback loops proposed that such loops would lead to a phenomenon termed \textit{model collapse}, under which performance progressively degrades with each model-data feedback iteration until fitted models become useless. However, those studies largely assumed that new data \textit{\replace{replace}} old data over time, where an arguably more realistic assumption is that data \textit{\accumulate{accumulate}} over time. In this paper, we ask: what effect does accumulating data have on model collapse? 
We empirically study this question by pretraining sequences of language models on text corpora. We confirm that \replace{replacing the original real data by each generation's synthetic data does indeed tend towards model collapse}, then demonstrate that \accumulate{accumulating the successive generations of synthetic data alongside the original real data avoids model collapse}; these results hold across a range of model sizes, architectures, and hyperparameters. We obtain similar results for deep generative models on other types of real data: diffusion models for molecule conformation generation and variational autoencoders for image generation. To understand why accumulating data can avoid model collapse, we use an analytically tractable framework introduced by prior work in which a sequence of linear models are fit to the previous models' outputs. Previous work used this framework to show that \replace{if data are replaced, the test error increases with the number of model-fitting iterations}; we extend this argument to prove that \accumulate{if data instead accumulate}, the test error has a finite upper bound independent of the number of iterations, meaning \accumulate{model collapse no longer occurs}. 
Our work provides consistent empirical and theoretical evidence that \accumulate{data accumulation avoids model collapse}.
\end{abstract}

\input{01_introduction}
\input{03_real_generative_models}
\input{02_linear_regression}
\input{04_discussion}

\clearpage

\bibliography{colm2024_conference}
\bibliographystyle{colm2024_conference}

\clearpage
\appendix
\input{99_appendix}


\end{document}
