\begin{abstract}
Current Large Language Models (LLMs) often undergo supervised fine-tuning (SFT) to acquire tool use capabilities. However, SFT struggles to generalize to unfamiliar or complex tool use scenarios. Recent advancements in reinforcement learning (RL), particularly with R1-like models, have demonstrated promising reasoning and generalization abilities. Yet, reward design for tool use presents unique challenges: multiple tools may be invoked with diverse parameters, and coarse-grained reward signals, such as answer matching, fail to offer the finegrained feedback required for effective learning.
In this work, we present the first comprehensive study on reward design for tool selection and application tasks within the RL paradigm. We systematically explore a wide range of reward strategies, analyzing their types, scales, granularity, and temporal dynamics. Building on these insights, we propose a principled reward design tailored for tool use tasks and apply it to train LLMs using Group Relative Policy Optimization (GRPO).
Empirical evaluations across diverse benchmarks demonstrate that our approach yields robust, scalable, and stable training, achieving a 17\% improvement over base models and a 15\% gain over SFT models. These results highlight the critical role of thoughtful reward design in enhancing the tool use capabilities and generalization performance of LLMs. All the code are released to facilitate future research.\footnote{\ Data and codes released at \url{https://github.com/qiancheng0/ToolRL}}
\end{abstract}

% \emre{we are showing both ppo and grpo, my bet is not to overfit grpo in motivations; we can say like "we got best with grpo or etc.'}
% \emre{here can we say: our results improve base model delta-X and outperform sft baselines delta-Y?}
% \xiusi{This should be more accurate: models trained with RL has shown strong reasoning and generalization capabilities.}
% \heng{add why it requires to design new and more reward strategies?}

% Current large language models (LLMs) often undergo supervised fine-tuning (SFT) to acquire tool use capabilities. However, SFT tends to fall short in generalizing to unfamiliar tool use scenarios.
% With the emergence of R1-like models, these models trained with RL has shown strong reasoning and generalization capabilities. However, reward design for tool use poses unique challenges: multiple tools may be invoked, each with diverse parameters, making coarse answer matching fails to provide finegrained feedback.
% Furthermore, the challenge of designing optimal and effective reward functions for tool learning remains largely unexplored.
% In this work, we present the first in-depth study of reward design for tool selection and application tasks within the RL framework, and empirically shows its significant effectiveness especially under Group Relative Policy Optimization (GRPO) training.
% We systematically explore a variety of reward strategies, examining their types, scale, granularity, and temporal dynamics. With these insights, we develop a principled reward design specifically for tool learning and use it to train our models through RL.
% Empirical results show that our reward design leads to robust, scalable, and stable training outcomes, with performance improvements of 17\% over base models and 15\% over SFT models across benchmarks. This proves our  design's effectiveness in enhancing the tool use capabilities and generalizability of LLMs.
% All the code are released to facilitate future research.\footnote{\ Data and codes released at \url{https://github.com/qiancheng0/ToolRL}}