
\documentclass{article} % For LaTeX2e
\usepackage[preprint]{colm2026_conference}

\usepackage{microtype}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}

% NOTE: including geometry package
% The geometery package modifies some page properties when used. This can dramatically change the page margins, leading to severe template violation, and potential desk rejection. If the package is required, it can be used with the "pass" flag to skip the default page modifications, as in the following line:
% \usepackage[pass]{geometry}

\usepackage{lineno}

\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}


% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{CJKutf8}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{floatflt}
\usepackage{wrapfig}

\usepackage{fix-cm}

\usepackage{lipsum}
\usepackage{makecell}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode} 
\usepackage{pifont}   
\usepackage{subcaption} 
\usepackage{diagbox}
\usepackage{tabu}
\sisetup{detect-all, table-format = 3.1}   
\newcolumntype{d}{S}          
\usepackage{caption}
\usepackage{xparse}
\usepackage{stackengine} 

% \usepackage{siunitx,makecell}
% \sisetup{
%   detect-weight=true, detect-family=true,
%   table-number-alignment = center,   % 关键：数字居中而不是按小数点对齐
%   table-format = 2.1                 % 本表最大到 99.9，可按需调到 3.1
% }
% \newcolumntype{d}{S}        

\sisetup{
  detect-weight = true,      
  detect-family = true, 
  table-number-alignment = center,
  table-format  = 3.1        
}

\usepackage{xcolor,colortbl,booktabs,tabularx,makecell,graphicx}


\newcommand{\rot}[1]{\rotatebox{60}{#1}}
\newcommand{\rott}[2][15]{
  \smash{\rotatebox[origin=c]{#1}{\parbox{1.415cm}{\centering #2}}}%
  \rule{0pt}{1.5em}
}

\usepackage{adjustbox}



\newcolumntype{R}{>{\raggedright\arraybackslash}p{3.6cm}}
\usepackage{amssymb} 
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage{amsmath, amssymb}  



\algnewcommand{\LeftComment}[1]{\Statex \(\triangleright\) #1}


\usepackage{array}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{arydshln}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{adjustbox} 
\usepackage{xr}
\usepackage{listings}
\usepackage{bbm}

\usepackage[utf8]{inputenc}        
\usepackage[english]{babel} 




\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% \usepackage[textsize=tiny]{todonotes}
\newcommand{\ie}{\textit{i.e.}}
\newcommand{\eg}{\textit{e.g.}}

\definecolor{nred}{RGB}{196, 38, 11}
\definecolor{ngreen}{RGB}{18, 141, 21}
\definecolor{nblue}{RGB}{41, 52, 190}
\definecolor{hzw}{RGB}{223, 97, 76}
\definecolor{lt}{RGB}{54, 89, 170}

\definecolor{TableGreen}{RGB}{0, 196, 0 }
\newcommand{\tc}[1]{\textcolor{TableGreen}{#1}}

\definecolor{LightGreen}{RGB}{243,247,240}
\renewcommand{\tt}[1]{\textcolor{LightGreen}{#1}}

\newcommand{\revise}[1]{\textcolor{blue}{#1}}


\newcommand{\ignore}[1]{}
\newcommand{\model}{\textbf{Ours}}
\newcommand{\outline}[1]{\textbf{#1}}


% \sisetup{
%   table-number-alignment = center,
%   table-figures-integer = 2,
%   table-figures-decimal = 1,
%   table-figures-uncertainty = 1,
% }

\newcommand{\starcell}[1]{#1\rlap{${}^*$}}

\title{One Token to Fool LLM-as-a-Judge}

\author{Yulai Zhao\thanks{Equal Contribution. The work was done during YL and HL's internship at Tencent AI Lab.}~~$^{,1}$, Haolin Liu$^{*,2}$, Dian Yu$^{3}$, S.Y. Kung$^{1}$, Meijia Chen$^{4}$,  Haitao Mi$^{3}$, Dong Yu$^{3}$ \\
$^1$ Princeton University, $^2$ University of Virginia, $^3$ Tencent AI Lab,  $^4$ Rutgers University
}

% \affil[1]{Tencent AI Lab}
% \affil[2]{Princeton University}
% \affil[3]{University of Virginia}

% \author[ ]{Yulai Zhao\thanks{Equal Contribution. The work was done during YL and HL's internship at Tencent AI Lab.}~~$^{,1,2}$}
% \author[ ]{Haolin Liu$^{*,1,3}$}
% \author[ ]{Dian Yu$^{1}$}
% \author[ ]{S.Y. Kung$^{2}$} 
% \author[ ]{\mbox{Haitao Mi}$^{1}$}
% \author[ ]{Dong Yu$^{1}$}

% \affil[1]{Tencent AI Lab}
% \affil[2]{Princeton University}
% \affil[3]{University of Virginia}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\begin{document}

\ifcolmsubmission
\linenumbers
\fi

\maketitle

% \input{abstract}
\input{abstract_draft}

% \input{intro}
\input{intro_draft_colm}


\section{Methodology}
\label{sec:pre}
\input{method}


\input{experiments_colm}
\input{conclusions}

\newpage
% \section*{Limitations}
% This study has several limitations. Our evaluation focuses on reasoning openers and superficial symbols, leaving other adversarial patterns, such as reflection or backtracking cues, for later investigation. The non-monotonic scaling behavior we observed across model sizes is based on a preliminary hypothesis. Fully elucidating these underlying mechanisms remains an open challenge. Additionally, removing questions from prompts is highly effective for mathematical reasoning, but its applicability to open-ended general reasoning is limited because the question context is often essential for determining semantic equivalence.

\section*{Ethics Statement}
\paragraph{Responsible Disclosure of Vulnerabilities.} Our research identifies ``master key'' adversarial patterns that trigger false positive rewards in generative reward models. While disclosing these patterns carries risks of misuse, identifying systematic flaws is a prerequisite for developing robust and transparent AI alignment mechanisms. By proposing the Master-RM strategy and targeted data augmentation, we provide the community with proactive tools to secure RLVR pipelines.

\paragraph{Human Annotation and Expertise.} This study utilizes human agreement analysis to validate automated judgments. Annotations were performed internally by the authors, all of whom possess a PhD-level background in computer science or statistics. This technical expertise enabled the rigorous evaluation of complex mathematical and scientific reasoning trajectories. No external subjects were recruited, no compensation was involved, and no participants faced psychological or physical risks. Final labels were established through a rigorous majority voting process to minimize subjective bias.

\paragraph{Use of Data and Models.} We conducted our evaluations using established, peer-reviewed benchmarks and public language models. Committed to open science, we will release our Master-RM models and the augmented $180k$-instance training dataset upon publication. These artifacts contain no personally identifiable information (PII) or offensive content, as they are derived from standard mathematical and general-domain reasoning tasks.

\bibliography{references}
\bibliographystyle{colm2026_conference}

\newpage
\appendix

\input{appendix}

\end{document}
