\section{Discussion and Conclusion}
This paper introduces QDAIF, a quality-diversity method that aims to discover diverse and high-quality solutions in qualitative domains, by leveraging advances in foundation models to evaluate the quality and diversity of generated individuals. QDAIF outperforms baseline methods in returning more diverse, high-quality solutions in creative writing domains (\textbf{Opinions}, \textbf{Stories}, \textbf{Poetry}), that benefit greatly from accurate AI feedback measures. The paper's results highlight that QDAIF can succeed at its aims, generating solutions that align with human perception of quality and diversity. 

We note limitations with QDAIF that motivate future work. Firstly, we suspect reward hacking happening when using LMs to generate feedback. Our human evaluation investigation shows that while the LM's evaluation of quality mostly aligns with human perception, the correlation drops when the evaluated quality is in the range 0.995 to 1 (cf.~\cref{fig:quality_vs_fitness}). The text generation might have exploited certain attributes or phrasings that allow an LM to give a high-quality estimate, but not what humans would agree is good. This is a common issue highlighted by other works when using AI models as classifiers or evaluators \citep{nguyen2015deep}, highlighting risks of open-ended search to be tackled \citep{ecoffet2020open}. One method to address this limitation could be to use RLHF finetuning \citep{ouyang2022training} to produce LMs that can detect and mitigate adversarially generated texts. Another possible approach could be to use an ensemble of different AI models to evaluate solutions, rather than relying only on one; the hope would be that robustness would result from models having uncorrelated blind spots.

Furthermore, although QDAIF makes it easy to specify qualitative aspects of diversity through natural language prompts, it still requires specified definitions of diversity axes. For example, if we applied QDAIF to generate short stories of different genres (e.g. comparing horror vs. romance), it would not autonomously explore other important attributes that a writer might care about (e.g. first-person vs. third-person perspective) unless explicitly specified. When we tested different diversity measures in the Stories domain, such pathologies were observed (\cref{app:diff-diversity-measures}). For example, when using "hero spy vs. hero politician" as the diversity measure, many of the solutions generated tend to neglect the interaction between the spy and the politician, focusing solely on the character that is meant to be the hero. However, someone writing a short story about a spy and a politician would naturally care about how the characters interact with one another. One possible way to automatically determine interesting diversity measures is to utilize the human notions of interestingness distilled into foundation models \citep{zhang2023omni}. That is, we could ask LMs to suggest interesting diversity measures that a human would typically care about in the domain, thereby enabling a more autonomous creative search (see \cref{app:expanding_dim} for findings on the potential of this method).

In conclusion, we show that QDAIF is a promising approach to open-ended search that can reveal unexplored creative writing spaces, surpassing alternative text generation methods in generating diverse high-quality natural language text. AI feedback, Evolution through Large Models (ELM), and quality-diversity search (QD) were found to be essential ingredients for enhanced AI systems that can innovate in subjective spaces, similar to past research on Innovation Engines \citep{nguyen2016understanding, nguyen2015innovation}. In fact, we see AI feedback as a general ingredient for open-ended search for solutions in multimodal domains, capable of following instructions beyond text \citep{liu2023visual}. QDAIF can be easily extended to multi-modal domains (e.g. vision-language) for synthetic data generation and evaluation, building on top of recent advances in the field \citep{eichenberg2021magma,alayrac2022flamingo,bellagente2023multifusion,driess2023palm,bhatt2023surrogate,sudhakaran2023mariogpt,todd2023level}. We see many possibilities from QDAIF to build creative search systems with evaluation, diversification, and improvement capabilities, bringing us closer to AI that can support and extend human innovation.

\section*{Ethics Statement}
Human evaluations were performed by the co-authors of this paper and select colleagues. All human evaluators provided informed consent, and their feedback and assessments were obtained without coercion or bias. We took action to prevent bias by presenting evaluators with texts to evaluate in a blind setting, with only the instructions for the study annotation task presented (to carefully read through the presented texts, then give a quality score and a label of the characteristic that best matches the texts). We show a detailed setup for the human study in \cref{app:human_study_setup}.

For transparency, we provide the full set of results with caption descriptions from our human evaluation. In the \textbf{Opinions} domain, \crefrange{app:table_eval_opinions_b1}{app:table_eval_opinions_b4} contain the human evaluation results for sets from baseline methods, \crefrange{app:table_eval_opinions_aif_near_seeded}{app:table_eval_opinions_aif_replace_zero} contain the human evaluation results for sets from QDAIF methods, and \crefrange{app:table_eval_opinions_ef_near_seeded}{app:table_eval_opinions_ef_replace_zero} contain the human evaluation results for sets from embedding feedback QD methods. In the \textbf{Stories - Genre} domain, \crefrange{app:table_eval_stories_genre_b1}{app:table_eval_stories_genre_b4} contain the human evaluation results for sets from baseline methods, and \crefrange{app:table_eval_stories_genre_aif_near_seeded}{app:table_eval_stories_genre_aif_replace_zero} contain the human evaluation results for sets from QDAIF methods. For the \textbf{Stories - Ending} domain, \crefrange{app:table_eval_stories_ending_b1}{app:table_eval_stories_ending_b4} contain the human evaluation results for sets from baseline methods, and \crefrange{app:table_eval_stories_ending_aif_near_seeded}{app:table_eval_stories_ending_aif_replace_zero} contain the human evaluation results for sets from QDAIF methods. 


\section*{Author Contributions}\label{sec:contrib}
Herbie developed the setup and framework for the Poetry domain experiments and base library for research. Andrew developed the setup and experiments for the Opinions and Stories domains, and contributed to extended studies, visualization, and analysis across experiments in the paper. Hannah contributed additional experimentation in the Stories domain, in addition to coordinating part of human evaluation studies. Jenny contributed qualitative analysis across studied domains. Koen developed visualization scripts used in Opinions and Stories domain experiments. Marco contributed to part of the technical implementation and ideation. Andrew conducted the blind human evaluation study, and Gr\'egory advised on the conduct and analysis of the human study. Joel, Jeff, and Ken initiated early ideation for this work. Joel, Gr\'egory, Jeff, and Ken advised and guided. Andrew, Jenny, Herbie, and Joel wrote the manuscript with edits and feedback from all authors.

\section*{Acknowledgements}
We thank Robert Baldock, Samuel Weinbach, Souradeep Nanda, Jan Zierstek, and Andres Felipe Cruz Salinas for insightful discussions and feedback within the lab at Aleph Alpha. We also thank Katherine Hardgrave, David Nugent, Daniel Flood, and Formula Trinity Autonomous for the inspiration that seeded the momentum leading up to this work.