%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{intro_sec}

In recent years, neural networks have reached remarkable performance on key tasks and seen a fast increase in their popularity \citewithcomments{\eg }{he2015delving,silver2016mastering,wu2016google}{}. This success was only possible due to decades of machine learning (ML) research into many aspects of the field, ranging from learning strategies to new architectures \citewithcomments{}{rumelhart1986learning,lecun1995convolutional,hochreiter1997long}{, among many others}. The length and difficulty of ML research prompted a new field, named \textit{\aml}, that aims to automate such progress by spending machine compute time instead of human research time \cite{fahlman1990cascade,hutter2011sequential,finn2017model}. This endeavor has been fruitful but, so far, modern studies have only employed constrained search spaces heavily reliant on human design. A common example is \textit{architecture search}, which typically constrains the space by only employing sophisticated expert-designed layers as building blocks and by respecting the rules of backpropagation \cite{zoph2016neural,real2017large,tan2019mnasnet}. Other \aml studies similarly have found ways to constrain their search spaces to isolated algorithmic aspects, such as the learning rule used during backpropagation \cite{andrychowicz2016learning,ravi2016optimization}, the data augmentation \cite{cubuk2018autoaugment,park2019specaugment} or the intrinsic curiosity reward in reinforcement learning~\cite{alet2019meta}; in these works, all other algorithmic aspects remain hand-designed. This approach may save compute time but has two drawbacks. First, human-designed components bias the search results in favor of human-designed algorithms, possibly reducing the innovation potential of \aml. Innovation is also limited by having fewer options \cite{elsken2019neural}. Indeed, dominant aspects of performance are often left out \cite{yang2019evaluation}. Second, constrained search spaces need to be carefully composed \cite{zoph2017learning,So2019TheET,negrinho2019towards}, thus creating a new burden on researchers and undermining the purported objective of saving their time.

To address this, we propose to automatically search for \textit{whole} ML algorithms using \textit{little} restriction on form and \textit{only} simple mathematical operations as building blocks. We call this approach \textit{\amlz}, following the spirit of previous work which aims to learn with minimal human participation \citewithcomments{\eg }{silver2017mastering}{}. In other words, \amlz aims to search a fine-grained space simultaneously for the model, optimization procedure, initialization, and so on, permitting much less human-design and even allowing the discovery of \mbox{non-neural} network algorithms. To demonstrate that this is possible today, we present an initial solution to this challenge that creates algorithms competitive with backpropagation-trained neural networks.

The genericity of the \amlz space makes it more difficult to search than existing \aml counterparts. Existing \aml search spaces have been constructed to be dense with good solutions, thus deemphasizing the search method itself. For example, comparisons on the same space found that advanced techniques are often only marginally superior to simple random search (RS) \cite{li2019RS,elsken2019neural,negrinho2019towards}. \amlz is different: the space is so generic that it ends up being quite sparse. The framework we propose represents ML algorithms as computer programs comprised of three \emph{component functions}, \setup, \predict, and \learn, that performs initialization, prediction and learning. The instructions in these functions apply basic mathematical operations on a small memory. The operation and memory addresses used by each instruction are free parameters in the search space, as is the size of the component functions. While this reduces expert design, the consequent sparsity means that RS cannot make enough progress; \eg good algorithms to learn even a trivial task can be as rare as $1$ in $10^{12}$. To overcome this difficulty, we use small proxy tasks and migration techniques to build highly-optimized open-source infrastructure capable of searching through 10,000 models/second/cpu core. In particular, we present a variant of functional equivalence checking that applies to ML algorithms. It prevents re-evaluating algorithms that have already been seen, even if they have different implementations, and results in a 4x speedup. More importantly, for better efficiency, we move away from RS.\footnote{\label{open_source_fn}We open-source our code at \url{https://github.com/google-research/google-research/tree/master/automl_zero\#automl-zero}}

Perhaps surprisingly, evolutionary methods can find solutions in the \amlz search space despite its enormous size and sparsity. By randomly modifying the programs and periodically selecting the best performing ones on given tasks/datasets, we discover reasonable algorithms. We will first show that starting from empty programs and using data labeled by ``teacher'' neural networks with random weights, evolution can discover neural networks trained by gradient descent (Section~\ref{difficulty_sec}). Next, we will minimize bias toward known algorithms by switching to binary classification tasks extracted from CIFAR-10 and allowing a larger set of possible operations. The result is evolved models that surpass the performance of a neural network trained with gradient descent by discovering interesting techniques like multiplicative interactions, normalized gradient and weight averaging (Section~\ref{main_result_sec}). Having shown that these ML algorithms are attainable from scratch, we will finally demonstrate that it is also possible to improve an existing algorithm by initializing the population with it. This way, evolution adapts the algorithm to the type of task provided. For example, dropout-like operations emerge when the task needs regularization and learning rate decay appears when the task requires faster convergence (Section~\ref{zoo_sec}). Additionally, we present ablation studies dissecting our method (Section~\ref{discussion_sec}) and baselines at various compute scales for comparisons by future work (Suppl.\ Section~\ref{baselines_sec}).

\renewcommand\labelitemi{\raisebox{1.5pt}{\fontsize{8}{8}$\bullet$}}

In summary, our contributions are:
\begin{itemize}[noitemsep,topsep=-5pt,leftmargin=*,labelsep=4pt]
    \item \amlz, the proposal to automatically search for ML algorithms from scratch with minimal human design;
    \item A novel framework with open-sourced code\footnotemark[\getrefnumber{open_source_fn}] and a search space that combines only basic mathematical operations;
    \item Detailed results to show potential through the discovery of nuanced ML algorithms using evolutionary search.
\end{itemize}
