\paragraph{Data Source}
We collect scripts from the Internet Movie Script Database (IMSDb\footnote{https://imsdb.com/}), an online repository of open-source screenplays for movies and television shows.
We use GPT-4o to divide each script into episodes according to discernible shifts in temporal settings, spatial locations, character dynamics, and narrative progressions. Each episode is further divided into scenes based on the variations in the dialogue content, with the prompts detailed in Appendix~\ref{app:data_source}.
We filter out scenes with fewer than 10 dialogues or those featuring only characters speaking for multiple turns to ensure active interaction between at least two characters. After processing, we have 1,300 scenes, 12,401 rounds of conversations, and 114,834 tokens.
The detailed statistics of scripts are provided in Appendix~\ref{app:detailed_data_info}.

\paragraph{Data Validation}
We conduct human validation on the generated templates from the automatic pipeline to ensure the quality of our benchmark.
For social goals, we mainly consider: (1) whether the goal is achievable by the character, and (2) whether the goal is clear enough to evaluate.
For private information, we focus on: (1) awareness by other characters and background information leakage, and (2) sufficiency of information for the character to answer questions.

The validation involves 6 graduate students in two groups, with each record annotated by 3 annotators.
We take the majority vote as the final result when at least two annotators agree.
For scenarios where all annotations diverged or were marked as invalid, we assign it to the other three annotators to review it.
Details can be found in Appendix~\ref{app:data_val_annotation}.

\paragraph{Data Analysis}
Based on the scripts, we develop 245 effective templates by constructing scenarios.
Each template is diversified with five scenarios, featuring characters tailored to fit specific scenario constraints.
This results in a total of 1,225 scenarios that cover a wide range of social situations and objectives, with 363 of these scenarios containing roles that involve private information.
Recognizing the inseparable connection between social interaction and space \cite{1991The}, we categorize these scenarios into three types: personal domain, small society, and large society.
A detailed introduction to the classification is shown in Appendix~\ref{app:social scenario}.
In our dataset, 54\% of scenarios are in the personal domain, 37\% in small society, and 9\% in large society.

For social goals, we apply the ERG theory \cite{ALDERFER1969142} to categorize these goals into three hierarchical needs: Existence, Relatedness, and Growth. Based on these needs, we identify eight key social goals(e.g., Information Acquisition, Relationship Building, Competition), detailed in Appendix~\ref{app:social_goal}.
Our dataset includes all these social goals, with the number of scenarios for each shown in Figure~\ref{fig:merge} (a). Generally, higher-level social goals are less frequent, reflecting real-life patterns.

The final dataset contains a diverse collection of 859 individual profiles with 366 types of occupations. The characters exhibit a wide range of attributes, emphasizing the great diversity in terms of gender, age, occupation, big five, moral values, personality, and decision-making styles, as shown in Figure~\ref{fig:merge} (b) and Figure~\ref{fig:merge} (c). For instance, in terms of gender, there are individuals identified as male, female, non-binary, genderqueer, and so on. Ages vary from childhood to old age, providing a spread across different life stages.
