\section*{Author information}
\label{sec:authors}

These authors contributed equally: Alexander Novikov, Ngân Vũ, Marvin Eisenberger, Emilien Dupont, Po-Sen Huang, Adam Zsolt Wagner, Sergey Shirobokov, Borislav Kozlovskii, and Matej Balog.

\paragraph{Contributions.}
A.N. and M.B. designed and implemented the initial version of \method.
\;
M.B., A.N., N.V. and P.K. developed project vision and scoped problems.
\;
N.V. and P.-S.H. oversaw the practical applications.
\;
E.D. and M.E. implemented the first benchmark problem used for iterating on \method, with input from F.J.R.R. and M.B.
\;
A.N. and M.E. developed the final version of \method, with contributions from S.S., P.-S.H., and input from M.B., E.D., A.Z.W. and N.V.
\;
A.N., S.S., P.-S.H. and M.E. maintained the infrastructure underlying \method.
\;
M.E. and E.D. used \method to discover new algorithms for matrix multiplication, with input from F.J.R.R.
\;
A.Z.W. worked on the applications to open mathematical problems, with help from A.M., M.E., and A.N.
\;
A.N. contributed to the Borg scheduling application.
\;
P.-S.H. and N.V. worked on the application to Gemini kernel engineering.
\;
P.-S.H. and A.N. contributed to the TPU circuit design application.
\;
B.K. and S.S. worked on applying \method to directly optimize compiler-generated code.
\;
M.E. performed the ablation experiments.
\;
M.B., A.N., M.E., S.S. and P.-S. H. performed the majority of code reviews.
\;
M.B., E.D., S.C., N.V., A.Z.W., F.J.R.R., M.E., A.N., B.K., S.S., A.M., and M.P.K. wrote the paper, with input from A.S.,  P.-S.H and P.K.
\;
N.V., E.D., M.E., S.C., A.N., and A.Z.W. created the figures.
\;
F.J.R.R., A.M., and A.Z.W. assembled the accompanying Google Colab.
\;
S.N., A.D. and P.K. advised and enabled multiple strands of this work.
\;
M.B., A.N., N.V. and G.H. coordinated the team. 
\;
P.K. supervised and coordinated the research program. 

\paragraph{Corresponding authors.}
Matej Balog, Alexander Novikov and Pushmeet Kohli.