\PassOptionsToPackage{usenames,dvipsnames,table}{xcolor}
\documentclass[logo,copyright,12pt]{googledeepmind}

\input{preamble}

\title{\method: A coding agent for scientific and algorithmic discovery}

\author[*]{Alexander Novikov}
\author[*]{Ngân Vũ}
\author[*]{Marvin Eisenberger}
\author[*]{Emilien Dupont}
\author[*]{Po-Sen Huang}
\author[*]{Adam Zsolt Wagner}
\author[*]{Sergey Shirobokov}
\author[*]{Borislav Kozlovskii}
\author[ \hspace{-0.2em}]{Francisco J. R. Ruiz}
\author[ \hspace{-0.2em}]{Abbas Mehrabian}
\author[ \hspace{-0.2em}]{M. Pawan Kumar}
\author[ \hspace{-0.2em}]{Abigail See}
\author[ \hspace{-0.2em}]{Swarat Chaudhuri}
\author[ \hspace{-0.2em}]{George Holland}
\author[ \hspace{-0.2em}]{Alex Davies}
\author[ \hspace{-0.2em}]{Sebastian Nowozin}
\author[ \hspace{-0.2em}]{Pushmeet Kohli}
\author[*]{Matej Balog}
\affil[ \hspace{-0.2em}]{Google DeepMind\footnote{See Acknowledgments and Author information section. $^*$Equal contributions.}}


\begin{abstract}
In this white paper, we present \method, an evolutionary coding agent that substantially enhances capabilities of state-of-the-art LLMs on highly challenging tasks such as tackling open scientific problems or optimizing critical pieces of computational infrastructure.
\method orchestrates an autonomous pipeline of LLMs, whose task is to improve an algorithm by making direct changes to the code. Using an evolutionary approach, continuously receiving feedback from one or more evaluators, \method iteratively improves the algorithm, potentially leading to new scientific and practical discoveries.
We demonstrate the broad applicability of this approach by applying it to a number of important computational problems. When applied to optimizing critical components of large-scale computational stacks at Google, \method developed a more efficient scheduling algorithm for data centers, found a functionally equivalent simplification in the circuit design of hardware accelerators, and accelerated the training of the LLM underpinning \method itself.
Furthermore, \method discovered novel, provably correct algorithms that surpass state-of-the-art solutions on a spectrum of problems in mathematics and computer science, significantly expanding the scope of prior automated discovery methods~\authoryearcite{paredes2023mathematical}.
Notably, \method developed a search algorithm that found a procedure to multiply two $4 \times 4$ complex-valued matrices using $48$ scalar multiplications; offering the first improvement, after 56 years, over Strassen's algorithm in this setting. We believe \method and coding agents like it can have a significant impact in improving solutions of  problems across many areas of science and computation.
\end{abstract}

\begin{document}

\maketitle

\input{introduction.tex}

\input{methods.tex}

\input{results.tex}

\input{ablations.tex}

\input{related_work.tex}

\input{discussion.tex}

\input{acknowledgement.tex}
\input{authors.tex}

\bibliographystyle{abbrvnat}
\bibliography{literature}

\clearpage
\appendix

\input{appendix.tex}

\end{document}
