\section{Iterative Retraining  Converges to the Verifier's Knowledge Center}


\textcolor{black}{
Having established that a single round of verifier-based retraining can improve estimation through a bias--variance trade-off, a natural question arises:
\emph{can this improvement be sustained over multiple rounds, and what is the eventual outcome?}
To contextualize our long-term analysis within the broader literature on model collapse, we first formalize these widely discussed empirical phenomena within our linear regression setting.
Specifically, we define \textbf{Model Degradation/Collapse} as $\limsup_{k \to \infty} \text{MSE}(\hat{\theta}^k)> \text{MSE}(\hat{\theta}^0)$,
and \textbf{Model Improvement} as $\limsup_{k \to \infty} \text{MSE}(\hat{\theta}^k) < \text{MSE}(\hat{\theta}^0)$.
}


Our key finding is that both behaviors can occur in long-term iterative retraining. 
The outcome depends critically on three factors: the growth rate of synthetic data, the verifier's bias, and the verifier's capability (i.e., its ability to reduce variance). 
Over time, iterative retraining injects increasingly more verifier knowledge into the estimator, while the contribution from the original data gradually decays. 
As a result, the verifier and the generative model family eventually dominate the limit behavior, driving the estimator $\hat{\theta}^k$ toward a fixed point, which corresponds to the verifier's knowledge center $\theta_c$. 

This dynamic gives rise to three distinct phases of long-term behavior: \textbf{(1) Unbiased verifier:} If the verifier is unbiased (i.e., $\theta_c= \theta^\star$), iterative retraining yields continuous improvement and the estimator converges to the true parameter.
\textbf{(2) Mildly biased verifier:} With small bias, iterative retraining can improve performance in the short term by reducing variance, but performance eventually plateaus or deteriorates as verifier bias accumulates.
\textbf{(3) Strongly biased verifier:} With large bias, iterative retraining leads to degradation and may even cause collapse in the limit.
\textcolor{black}{Among these, the mildly biased case is the most practically relevant.
It highlights a cautionary message:
while synthetic retraining can initially boost accuracy, a perfectly unbiased verifier is unrealistic; consequently, this inherent bias will ultimately prevent sustained improvement.}

Formally, the following theorem characterizes the long-term behavior of the estimator $\hat{\theta}^k$ in linear regression under   verifier-based synthetic retraining.

\begin{theorem}\label{thm:linear:long_term}  
% Assume $X^0$ satisfies the same conditions as in Theorem~\ref{thm:linear:one_step}.
There exist synthetic retraining processes (e.g., Algorithm~\ref{alg:linear_retraining}) and a constant $0<\rho < 1$ such that:
\vspace{-3mm}
\begin{align}
\mathbb{E} \|\hat{\theta}^k-\theta_c\|^2 \leq \rho^{2k} \mathbb{E}\|\hat{\theta}^0-\theta_c\|^2 + p\sigma^2\sum_{j=0}^{k-1}\frac{\rho^{2(k-j)-1}}{n_j}. \label{equ:linear:mse_long_term}
\end{align}

where $n_1 \leq n_2 \leq \cdots \leq n_k \cdots$ denote the number of verified synthetic samples per direction at each iteration.
In particular, if $\lim_{k \to \infty} n_k = \infty$, then $\lim_{k \to \infty} \mathbb{E}\|\hat{\theta}^k - \theta_c\|^2 = 0$.
\end{theorem}



The proof of Theorem~\ref{thm:linear:long_term} is provided in Appendix~\ref{app:linear}, utilizing concentration bounds and supermartingale inequalities to establish convergence.
Here we focus on the main intuition and highlight the key novelty of our analysis.  

The central observation to establish Theorem~\ref{thm:linear:long_term} is that the iterative retraining procedure (see Figure~\ref{fig:pipeline}) induces a \emph{Markov process}: the next state $\hat{\theta}^{k+1}$ depends only on the current state $\hat{\theta}^k$.  
Formally, the update can be expressed as
\begin{align}
\hat{\theta}^{k+1} = T(\hat{\theta}^k) + \eta_{k+1}, \label{equ:linear:intuition}
\end{align}
where $T(\cdot)$ is a deterministic mapping determined by verifier filtering, and $\eta_{k+1}$ is a sub-Gaussian noise term due to the randomness of synthetic samples at iteration $k+1$.  
Crucially, we show that $T(\cdot)$ is a \emph{contraction mapping}, and that the variance of the noise decays at the rate $\Var(\eta_{k+1}) \asymp 1/n_{k+1}$. This perspective allows us to view \eqref{equ:linear:intuition} as a discretized stochastic differential equation (SDE).  
As $n_k \to \infty$, the noise term vanishes and the dynamics are dominated by the deterministic contraction $T(\hat{\theta}^k)$, which drives the recursion toward its fixed point---the verifier's knowledge center $\theta_c$.  
The presence of the verifier is therefore \emph{essential}: it is precisely what transforms the update rule into a contraction, guaranteeing convergence.

By contrast, in prior work on model collapse without a verifier (e.g., \citet{gerstgrasser2024model, xu2025probabilistic}), the update reduces to the identity mapping.  
In that case, increasing the synthetic sample size can suppress noise accumulation and ensure bounded error (i.e., $\text{MSE}(\hat{\theta}^k) < \infty$), but there is no contraction and hence no convergence or sustained improvement. 
%The critical difference between $T(\cdot)$ and the identity is exactly the knowledge extracted from the verifier through synthetic data.
\textcolor{black}{The knowledge extracted from the verifier is precisely what elevates $T(\cdot)$ beyond an identity mapping.}
Our analysis is the first to formally show that the verifier fundamentally alters the long-term dynamics: it continuously injects knowledge, iteration by iteration, so that the estimator moves closer to $\theta_c$ over time.  

This contribution also clarifies a common misconception: even with a perfect verifier ($\theta_c = \theta^\star$) and infinitely many synthetic samples in one iteration, convergence cannot occur in a single step.  
As shown in Theorem~\ref{thm:linear:one_step}, while infinite samples remove the synthetic variance term, the verification error term persists.  
Thus, convergence requires the \emph{iterative} action of the verifier, which gradually aligns the estimator with the truth.



