
\section{Discussion}

Our study provides a theoretical and empirical characterization of verifier-guided synthetic retraining.  
We show that the process yields \emph{short-term gains} by reducing variance through verifier filtering, but in the \emph{long run} the estimator converges to the verifier’s knowledge center.  
This explains both the promise and the risk of such methods: a high-quality verifier can inject reliable external knowledge, while a biased verifier inevitably steers the model away from the truth.  
Viewed through the lens of \emph{information elicitation}, our framework formalizes how external signals are incorporated recursively into training and why the outcome reflects the verifier’s information.  

%This insight also sheds light on the empirical success of recent large-scale systems: one may interpret iterative pipelines such as \emph{DeepSeek} or the use of \emph{ChatGPT as a verifier} as practical realizations of verifier-guided retraining.  
%Our theory helps to partially explain why these approaches can initially boost performance, while also cautioning that their eventual convergence point is determined by the verifier’s knowledge and biases.  
%Thus, our findings have direct implications for designing verifier-based training loops in practice, where understanding and controlling verifier bias is critical.  \yw{YOU MIGHT CHANGE TO OTHER EXAMPLES AND NEED TO CITE AND THE KEY IS TO INSPIRE THE READER THE BROADER PICTURE OF THIS THEORETICAL INSIGHTS} \textcolor{red}{The deepseek and ChatGPT is not suitable here. they are data distillation. our method need the model to generate synthetic data itself, not trained on other model's data. Not sure how to write this part.}

Meanwhile, we also acknowledge the limitations of our results.Primarily, our analytical testbed relies on a well-specified parametric setting (linear regression) that assumes the existence of a global, ground-truth optimal parameter $\theta^*$.
This idealized assumption mathematically abstracts the complex, often competing attributes of a "good" generative model---such as sample diversity and generation quality---into a singular distance metric.
In practice, while models like LLMs are parametric, they are approximating a true data-generating process that is unknown and highly likely non-parametric.
For complex domains like natural language, a singular "true model" may not even exist; therefore, defining or evaluating an optimal model remains an open challenge.
While our empirical extensions to VAEs and LLMs validate the theory qualitatively, formal generalization to richer models such as exponential families or simple neural network architectures are interesting future directions.
Other future venues include developing sharper bounds for nonlinear models, exploring effectiveness of alternative synthetic design strategies beyond block orthogonalization, and studying verifier dynamics in large language models (LLMs) and vision models.   
