\vspace{-1em}  % ugh
\section{Introduction}
\label{section:introduction}

Language models (LMs) are rapidly being deployed in commercial products such as chatbots and coding assistants.
At the same time, existing benchmarks have become saturated~\citep{kiela2021dynabench, Ott2022MappingGD} and fail to capture the frontier of what state-of-the-art LMs can and cannot do. 
There is a need for challenging benchmarks that more accurately reflect real-world applications of LMs to help shape their future development and usage~\citep{srivastava2023imitation}.

\input{figures/teaser}

Building a good benchmark is difficult since tasks must be challenging enough to stump existing models, but model predictions must also be easy to verify~\citep{MartnezPlumed2021ResearchCD}.
Coding tasks are appealing as they pose challenging problems to LMs yet generated solutions can be easily verified by running unit tests.
However, existing coding benchmarks, such as HumanEval~\citep{chen2021evaluating}, mostly involve self-contained problems that can be solved in a few lines of code.

In the real world, software engineering is not as simple.
Fixing a bug might involve navigating a large repository, understanding the interplay between functions in different files, or spotting a small error in convoluted code.
Inspired by this, we introduce \benchmark{}, a benchmark that evaluates LMs in a realistic software engineering setting.
As shown in Figure~\ref{fig:teaser}, models are tasked to resolve issues (typically a bug report or a feature request) submitted to popular GitHub repositories.
Each task requires generating a patch describing changes to apply to the existing codebase.
The revised codebase is then evaluated using the repository's testing framework.

\benchmark{} offers several advantages over existing LM programming benchmarks.
These include, a realistic setting that utilizes user-submitted issues and solutions, diverse inputs featuring unique code problems from $12$ repositories, a robust framework for execution-based evaluation, and the ability to continuously update the benchmark with new instances, requiring minimal human intervention.

We evaluate multiple state-of-the-art LMs on \benchmark{} and find that they fail to solve all except the simplest issues.
Using a BM25 retriever, Claude 2 is only able to resolve $1.96\%$ of the issues. 

In addition to \benchmark{} our contributions include the release of a training dataset, \benchmark{}-train, which is essential for advancing open model development in this challenging domain.
This dataset comprises a collection of $\num{19000}$ non-testing task instances derived from $37$ repositories.
Utilizing \benchmark{}-train, we release two fine-tuned models, \swellama{} $7$b and $13$b, based on the CodeLlama~\citep{rozière2023code} model.
We find that in some settings \swellama{} $13$b is competitive with Claude 2 and is capable of processing contexts exceeding $\num{100000}$ tokens.
