\section{Experiments}
\label{sec:experiments}

\noindent \textbf{Tasks.}
% \label{sec:tasks}
We now present results for models pre-trained on \env{}-10K on several navigation and manipulation benchmarks to demonstrate the benefits of large-scale training. We consider ObjectNav (navigation towards a specific object category) in \env{}, \elienv{}, RoboTHOR~\cite{Deitke2020RoboTHORAO}, HM3D~\cite{Ramakrishnan2021HabitatMatterport3D}, and AI2-iTHOR~\cite{kolve2017ai2}. We also consider two manipulation-based tasks: ArmPointNav~\cite{manipulathor} and 1-phase Room Rearrangement~\cite{weihs2021visual}. In ArmPointNav, the agent moves an object using a robotic arm from a source location to a destination location specified in the 3D coordinate frame. In Room Rearrangement, the goal is to move objects or change their state to reach a target scene state.

\noindent \textbf{Models.}
% \label{sec:arch}
Our models for all tasks consist of a CNN to encode visual information and a GRU to capture temporal information. We deliberately use a simple architecture across all tasks to show the benefits of large-scale training. Our ObjectNav and Rearrangement models use the CLIP-based architectures of \cite{khandelwal2021simple}. Our ArmPointNav model uses a simpler visual encoder with 3 convolutional layers; we found this more effective than the CLIP encoder. All models are trained with the AllenAct~\cite{weihs2020allenact} framework, see the Appendix for training details.


\noindent \textbf{Results.}
\label{sec:results}
We present results in two settings: zero-shot and after fine-tuning on the training scenes provided by the downstream benchmark. Zero-shot experiments show us how well models trained on \env generalize to new environments, whereas fine-tuning experiments tell us if representations learned from \env can serve as a good initialization for quick tuning. For all experiments, we use only RGB images (no depth and other modalities is used). 

Zero-shot is particularly challenging since other environments have different appearance statistics, layouts, and object distributions compared to \env{}. \elienv{} and AI2-iTHOR~\cite{kolve2017ai2} are high-fidelity artist-designed scenes with high-quality shadows and lighting. HM3D is constructed from 3D scans of houses which can differ quite a bit from synthetic environments. RoboTHOR~\cite{Deitke2020RoboTHORAO} houses use wall panels and floors with very specific textures.

\noindent \textbf{\emph{Zero-shot transfer results.}} Models trained only on \env and evaluated zero-shot outperform previous SoTA models on 3 benchmarks (refer to \emph{zero-shot} rows of Table~\ref{tab:allresults}). These are very strong results since the models generalize to not only unseen objects and scenes, but also different appearance and layout statistics.

\noindent \textbf{\emph{Fine-tuning results.}} Further fine-tuning of the model using each benchmark's training data, achieves state-of-the-art results on all benchmarks (refer to \emph{fine-tune} rows of Table~\ref{tab:allresults}). Notably, our model is ranked first on three public leaderboards as of 10am PT, June 14th 2022: Habitat 2022 ObjectNav challenge, AI2-THOR Rearrangement 2022 challenge, and RoboTHOR ObjectNav challenge. It should be noted that our model achieves these results using a very simple architecture and only RGB images. Other techniques typically use more complex architectures that include mapping or visual odometry modules and use additional perception sensors such as depth images.

\noindent \textbf{Scale ablation.} To evaluate the effect of scale we train the models on 10, 100, 1,000, and 10,000 houses. For this experiment, we do not use any material augmentations. As shown in Table~\ref{tab:ablation}, the performance improves as we use more houses for training, demonstrating the benefits of large-scale data for Embodied AI tasks.

\input{tables/all_tasks_results}

\input{tables/scale_ablation_results}


