



  \bestofnalg is a simple and natural self-training scheme, and
  converges to a sharpened policy as $n, N\to \infty$. However, using
  a fixed response sample size $N$ may be wasteful for prompts where
  the model is confident. To this end, in this section we introduce
  and analyze, a variant of
  \bestofnalg based on \emph{adaptive sampling}, which adjusts the
  number of sampled responses adaptively.



  \paragraph{Algorithm}
  We present the adaptive \bestofnalg algorithm only for the special case of the
  maximum likelihood sharpening self-reward. Let a \emph{stopping parameter} $\mu>0$ be given. For $x_i\in\cX$,
  and $y_{i,1},y_{i,2}\ldots\sim\piref(\cdot\mid{}x_i)$, define a
  stopping time (e.g., \iftoggle{workshop}{\cite{benjamini1995controlling}}{ \citet{benjamini1995controlling}}) via:
  \begin{align}
    \label{eq:bon_stopping}
    \taumu(x_i) := \inf \left\{k : \frac{1}{\max_{1 \le j \le k} \piref(y_{i,j}\mid{}x_i)} \le \frac{k}{\mu} \right\}.
  \end{align}
  The adaptive \bestofnalg algorithm computes adaptively sampled
  responses $\yada_i$ via
  \[
    \yada_i\sim\argmax\crl*{\log\piref(y_{i,j}\mid{}x_i)\mid{}y_{i,1},\ldots,y_{i,\taumu(x_i)}},
  \]
  then trains the sharpened model through SFT:
  \[
    \pihatada =
    \argmax_{\pi\in\Pi}\sum_{i=1}^{n}\log\pi(\yada_i\mid{}x_i).
  \]
  Critically,
  by using scheme in \cref{eq:bon_stopping}, this algorithm can stop
  sampling responses for the prompt $x_i$ if it becomes clear that the
  confidence is large.

\paragraph{Theoretical guarantee}  

We now show that adaptive \bestofnalg enjoys provable benefits over
its non-adaptive counterpart through the dependence on the accuracy
parameter $\eps>0$.  


  Given $x\in\cX$, and $y_1,y_2\ldots\sim\piref(x)$, let
  $\taumu(x) := \inf \crl[big]{k : \frac{1}{\max_{1 \le i \le k}
      \piref(y_i\mid{}x)} \le k/\mu }$, and define a random variable 
  $\yada(x)\sim\argmax\crl*{\log\piref(y_i\mid{}x)\mid{}y_1,\ldots,y_{\taumu}\sim\piref(x)}$.
Let $\piada(x)$ denote the distribution over $\yada(x)$. We make the
following realizability assumption.
\begin{assumption}\label{ass:ada-realizability}
  The model class $\Pi$ satisfies $\piada\in\Pi$.
\end{assumption}
Compared to \bestofnalg, we require a somewhat stronger coverage
coefficient given by 
  \begin{align}
    \Cstarb = \En_{x\sim\mu}\brk*{\frac{1}{\max_{y\in\cY}\piref(y\mid{}x)}}.
  \end{align}
  This definition coincides with \cref{eq:cstar} when the arg-max
  response is unique, but is larger in general.\loose

Our main theoretical guarantee for adaptive \bestofnalg is as follows.
  \begin{theorem}
    \label{thm:bestofn_adaptive}
    Let $\delta,\rho\in (0,1)$ be given. Set $\mu =
    \ln(2\delta^{-1})$, and assume \cref{ass:ada-realizability}
    holds. Then with probability at least $1-\deltaf$, the adaptive \bestofnalg
    algorithm has
\begin{align}
  \Pr_{x \sim \cdist}[\pihat(\Ystar(x) \mid x) \leq 1 - \delta] \lesssim  \frac{\log(|\Pi|\deltaf^{-1})}{\delta n} ,
\end{align}
and has sample complexity $\En[m] = n\cdot\Cstarb
\log(\delta^{-1})$. Taking $n \gtrsim
\frac{\log(|\Pi|\deltaf^{-1})}{\delta \epsilon} $ ensures that with
probability at least $1-\deltaf$, $\Pr_{x \sim \cdist}[\pihat(\Ystar(x) \mid x) \leq 1 -
  \delta]\leq\eps$, and gives total sample complexity
\begin{align}
  \En\brk*{m} = O\left(\frac{\Cstarb\log(\abs{\Pi}\delfail^{-1})\log(\delta^{-1})}{\delta\eps}\right).
\end{align}
\end{theorem}
Compared to the result for \bestofnalg in \cref{thm:bestofn}, this
shows that adaptive \bestofnalg achieves sample complexity scaling
with $\frac{1}{\eps}$ instead of $\frac{1}{\eps^2}$. We believe the dependence on $\Cstarb$ for this algorithm
is tight, as the adaptive stopping rule used in the algorithm can be
overly conservative when $\abs{\Ystar(x)}$ is large.
\loose

\paragraph{A matching lower bound}
We now prove a complementary lower bound, which shows that the
$\eps$-dependence in \cref{thm:bestofn_adaptive} is tight. To do so,
we consider the following adaptive variant of the \framework framework.
\begin{definition}[Adaptive sample-and-evaluate framework]
  In the \textbf{Adaptive Sample-and-Evaluate} framework, the
  learner is allowed to sample $n$ prompts $x \sim \cdist$, and sample an
  arbitrary, adaptively chosen number of samples
  $y_1,y_2,\dots \sim \piref(\cdot \mid x)$ before sampling a new
  prompt $x' \sim \cdist$. In this framework we define sample
  complexity $m$ as the total number of pairs $(x,y)$ sampled by the
  algorithm, which is a random variable.
\end{definition}
Our main lower bound is as follows.
\begin{theorem}[Lower bound for sharpening under adaptive sampling]
  \label{thm:lower_adaptive}
  Fix an integer $d \ge 1$ and parameters $\epsilon \in (0,1)$ and $C
  \ge 1$. There exists a class of models $\Pi$ such that (i) $\log |\Pi|
  \eqsim d (1+\log(C \epsilon^{-1}))$, (ii) $\sup_{\pi \in \Pi}
  \Cstar(\pi) \lesssim C$, and (iii) $\Ypi(x)$ is a singleton for all
  $\pi\in\Pi$, for which any sharpening algorithm $\pihat$ in the
  adaptive \framework framework that
  achieves $\En\brk*{\Pr_{x \sim \cdist}[\pihat(\Ypi[\piref](x)\mid{}x) > 1/2]}  \ge 1
  - \epsilon$ for all $\piref \in \Pi$ must collect a total number of samples $m = n\cdot{}N$ at least
\begin{align}
  \En\brk{m}
  \gtrsim 
        \frac{ C\log |\Pi|}{\epsilon\cdot{}(1+\log(C
  \epsilon^{-1}))}.
\end{align}
\end{theorem}
\cref{thm:lower_adaptive} is a special case of a more general theorem, \cref{thm:lower_general}, which is stated and proven in \cref{sec:proofs_lower}.



