
\dfc{
\begin{itemize}
\item Do we want to try to say anything about inference-time algos
  like MCTS in this paper?
\end{itemize}
}

\dfc{Questions:
  \begin{itemize}
  \item Criticisms:
    \begin{itemize}
    \item It's also reasonable/practical to consider forms of
      self-improvement that leverage external signal (e.g., XPO), and this
      may be more useful in many settings.
      \begin{itemize}
      \item We can argue that this is complementary, since any method
        that uses external feedback can potentially be pushed a little
        further by pure self-improvement.
      \end{itemize}
    \item 
    \end{itemize}
  \item What is the distinction between self-training and
    self-improvement?
    \begin{itemize}
    \item Self-training: Any time we train a model on its own outputs
    \item Self-improvement: Broader problem. A tentative proposal: We
      have some task/objective/metric in mind, but we want to improve
      the performance of our model on this task without giving it any
      explicit feedback
      \item Another term we can use: ``Training-time
        self-improvement'' (to contrast with inference-time self-improvement).
    \end{itemize}
  \item 
    Positioning our work:
  \begin{itemize}
  \item How to distinguish from, e.g, \bestofn with a reward model?
    \begin{itemize}
    \item We are explicitly considering \emph{self-supervised}
      algorithms that do not require external feedback?
    \end{itemize}
  \end{itemize}
  \item Formal definition of \emph{sharpening}?
    \begin{itemize}
    \item Tilting policy $\pi$ towards its argmax?
    \end{itemize}
  \end{itemize}
  }
  \subsection*{Notation}
  \dfc{
 \begin{itemize}
 \item Base policy: $\piref$, other options include
   $\pi_{\texttt{base}}$ or $\pi_{\texttt{init}}$
   \begin{itemize}
   \item $\pi_{\texttt{base}}$ 
   \item Don't introduce $\pistar$ in general notation.
   \end{itemize}
 \item Use superscript for $\star$ ala $\ystar$, $\Cstar$
   \begin{itemize}
   \item Superscript
   \end{itemize}
 \item Examples: $x\ind{i}$ or $x_i$?
   \begin{itemize}
   \item Subscript
   \end{itemize}
 \item Responses are $y\in\cY$, autoregressive is special case where
   $\cY=\cV^{H}$ (vocabulary), $y=y_{1:H}$.
 \item Language modeling lingo:
   \begin{itemize}
   \item $\pi$ is a model
   \item $x$: prompt
   \item $y$: response
   \end{itemize}
 \item Notation: $(\eps,\delta,\gamma)$-sharpened policy:
 \[
         \bbP_{x\sim\rho}\brk*{\pihat\prn*{\Ygamma(x)}\geq{}1-\delta} \geq{} 1-\eps.
 \]
 Or do we want to do the version where $\eps$ and $\delta$ are pooled together?
 \item Failure probability: $\deltaf$. Or should we swap this w/
   $\delta$?
   \begin{itemize}
   \item Change context distribution to $\mu$, use $\rho$ for failure probability
   \end{itemize}
 \item $N$ as symbol for \bestofn / number of samples per context
 \item $n$ as number of contexts
   \item $m = n\cdot{}N$?
 \item $\Ygamma(x)=\crl*{y\mid{}
     \piref(y\mid{}x)\geq{}(1-\gamma)\piref(\ystar(x)\mid x)}$
 \item $\Ystar(x)=\Ygamma[0](x)$. Use this in place of $\ystar(x)$
   whenever we can (i.e., whenever a result does not require
   $\ystar(x)$) to be unique.
   \begin{itemize}
   \item Idea: Use $\mb{y}^{\star}_{\gamma}(x)$ and $\mb{y}^{\star}(x)$.
   \end{itemize}
 \item $\Cstar$ for $\En\brk*{\frac{1}{\piref(\Ystar(x)\mid{}x)}}$,
   $\Cstarg$ for $\En\brk*{\frac{1}{\piref(\Ygamma(x)\mid{}x)}}$
   \begin{itemize}
   \item $C_{\texttt{cov}}$, $C_{\texttt{cov},\gamma}$ (do this for
     now but macro it and see how the other looks once theorems are in place)
   \item $\texttt{Cov}$, $\texttt{Cov}_{\gamma}$
   \end{itemize}
 \item Conventions:
   \begin{itemize}
   \item Present main results with $\Ygamma$ if possible.
   \item Use $\Ystar(x)$ instead of $\ystar(x)$ is possible.
   \end{itemize}
 \end{itemize}
}

