\section{Related Work}

\subsection{From Symbolic Agents to Neural Language Models}
Social simulation has evolved from symbolic \cite{o1998fipa}, rule-based agents to data-driven neural approaches. Traditional multi-agent systems \cite{weiss1999multiagent} employed explicit cognitive models with deductive reasoning, while game-theoretic frameworks relied on rational choice assumptions. These approaches prioritized theoretical interpretability and control over predictive accuracy, a reasonable trade-off when modeling capabilities were limited.

Our work diverges fundamentally from this tradition. Rather than constructing agents from theoretical principles, we aim to replicate observed communication patterns as precisely as possible. This shifts the goal from explanation to imitation, and from symbolic representations to natural language generation. The question is not whether agents follow theoretically motivated rules, but whether they produce outputs statistically indistinguishable from real users.

\subsection{LLMs as Human Simulacra: Promise and Limitations}
The use of LLMs as human surrogates began with believable non-player characters in game environments \cite{park2023generative}, demonstrating superficially authentic behavior. This success sparked broader interest in using LLMs as synthetic participants across social sciences \cite{argyle2023out, chuang2024simulating, papachristou2024network}. Proponents argue that appropriate prompting enables models to accurately emulate response distributions from diverse demographic subgroups \cite{argyle2023out, chang2025llms}.

However, growing evidence challenges these optimistic claims. LLM-generated synthetic opinions reveal fundamental limitations of prompting-based alignment. While persona prompting approximates US opinion distributions, performance degrades substantially for non-English populations \cite{argyle2023out, ma2024algorithmic, munker2025political, munker2025cultural}. This suggests prompting privileges cultural contexts embedded in training data rather than reliably grounding outputs in external reality.

Moreover, prompting produces unstable representations. Minor prompt variations dramatically affect behavioral outputs \cite{ma2024algorithmic}, and RLHF training compounds this instability \cite{tjuatja2024llms}. These findings indicate that prompting inadequately controls model behavior, failing to consistently activate intended knowledge representations.

\subsection{Methodological and Ethical Concerns}

Beyond technical limitations, using LLMs as human proxies raises serious methodological questions. Training data biases can systematically misrepresent marginalized groups \cite{abid2021persistent, hutchinson2020social}. The disembodied nature of LLMs means they lack grounding in physical reality, cultural contexts, physical environments, and interpersonal relationships—that fundamentally shapes human cognition and decision-making \cite{hussein2012sapir, argyle2023out}.

Ethically, deploying LLMs as participant replacements raises concerns about informed consent, potential misuse, and oversimplification of complex human behaviors. These concerns intensify when researchers make causal claims based on simulated data without validating empirical realism.

\paragraph{Our Position} We argue that LLM-based simulation can contribute meaningfully to social science, but only when coupled with rigorous validation against real-world data. Claims about simulation validity must be empirically demonstrated, not assumed. This paper provides a framework for such validation.