\section{Experiments on Creative Writing Domain}
\subsection{Setup: Opinion Writing, Short Stories}\label{main:setup}

To demonstrate the versatility of QDAIF in different applications of creative text evolution, we evaluated QDAIF on these domains: \textbf{Opinions}, and \textbf{Stories}. The \textbf{Opinions} domain is focused on generating diverse, realistic pieces about one's opinions on eating vegetables and plant-based foods - the diversity measure is based on the sentiment of opinions on this topic (e.g. shown in example texts in the \cref{fig:architecture} overview). For the \textbf{Stories} domain, the topic is about a short story, containing two characters: a spy, and a politician. The diversity of stories is evaluated using a variety of measures based on AI Feedback, with the main ones being: \textbf{Stories - Genre} (Romance vs Horror) (1D archive), \textbf{Stories - Ending} (Happy vs Tragic) (1D archive), and \textbf{Stories - Genre and Ending} (2D archive). These domains capture the strengths and limitations of all methods, ranging from simple (\textbf{Opinions}) to challenging (\textbf{Stories - Genre and Ending}). We show in \cref{fig:overview} that the 2D domain is challenging, yet QDAIF still outperforms the baseline in filling the archive with diverse, high-quality stories. The AI feedback prompts are outlined in \cref{app:aif_prompts_lmx}.

\textbf{Evaluation.}
To assess the performance of methods in creative writing generation, we compute QD scores \citep{pugh2016quality}, a standard metric used to measure the quality-diversity of the discovered corpus of texts. A QD score is defined as the sum of the highest quality values found in each bin. To understand the alignment between AI and human feedback for practical applications in QDAIF, we conducted a human evaluation study on selected elite samples from each method (chosen from the median QD score run out of 5 random seed runs). Using a Likert scale \citep{allen2007likert} for quality assessment, we evaluate the capability of each method to produce a collection of diverse, high-quality texts. To do so we calculate a  ``human'' QD score, defined as the sum of quality scores given for all diversity categories identified by the annotator within the set. Furthermore, to understand how closely AI feedback aligns with human perspectives on subjective evaluation, we measured the agreement rates between human annotators and AI and between two human annotators. Details of the human study are specified in \cref{app:human_study_setup}, demonstrating the validity and advantages of AI feedback in generating human-like feedback on subjective quality and diversity measures.
