\subsection{Formulation}

\benchmark evaluates persona (induced) agents by generating questions that evaluate the persona on the five evaluation tasks introduced in Section~\ref{sec:tasks} while contextualizing the agents in environments they are commonly expected to interact with. Denote the persona description by $p$ and the LLM to which persona $p$ is assigned by $M_p$.
We define environments as settings and external scenarios or conditions in which agents exist and operate. From a diverse set of environments $\mathcal{E}$, an environment selection mechanism $\Xi_e$ selects a subset of the environments $\mathcal{E}_{p}$ to seed the persona agent in, i.e., $\Xi_e: \mathcal{E} \times p \to \mathcal{E}_p$. Once the environments $\mathcal{E}_p$ are selected, the relevant questions to $\mathcal{E}_p$ for each evaluation task are generated using a question generator $\Xi_q: \mathcal{E}_p \times p \times t \to \mathcal{Q}_t$ for $t \in \mathcal{T}$ where $\mathcal{T}$ is the set of evaluation tasks in \benchmark (see Section~\ref{sec:tasks}.) $\mathcal{Q}_t \subset \mathcal{Q}$ for all $t \in \mathcal{T}$ where $\mathcal{Q}$ is the full set of evaluation questions for a given persona agent.

The persona agent $M_p$'s response to $\mathcal{Q}_t$ is denoted by $\mathcal{O}_t$, $\mathcal{O}_t = M_p(\mathcal{Q}_t)$. $\mathcal{O}_t \subset \mathcal{O}$ for all $t \in \mathcal{T}$ where $\mathcal{O}$ is the full set of persona agent responses to $\mathcal{Q}$.

The level of faithfulness of the persona agent's responses in $\mathcal{O}$ to each of the tasks is then evaluated by ensembling the evaluation from $n$ strong LLM evaluator models where we define $E = [E_1,..,E_n]$ as the list of evaluator models. Evaluations are done using comprehensive task-specific rubrics unique to each question in the task $\mathfrak{R}_{t,q}$ that include the following components:
\begin{itemize}
    \item \textit{The task description for the evaluation task}. Each of the five evaluation tasks has a human-curated description that clearly outlines the components of the task. For example, the task description for the Expected Action task is "The persona takes actions within its response to the question that is logically expected of the persona in the setting of the question."
    \item \textit{The scoring guidelines}. Our rubrics have possible scores of 1 - 5, and for each discrete score in this range, we provide human-curated requirements that responses should meet to elicit the score for the task. 
    \item \textit{Custom examples for each possible score}. In order to guide the evaluator models $E$ in evaluating $\mathcal{O}$, we augment the evaluation rubrics with an example of a response that meets the scoring guideline for each discrete score in the rubric. The example for each discrete score is tailored for every persona agent and question pair. We define an examples generator  $\Xi_{\mathfrak{r}}$ as an LLM reasoner such that $\Xi_{\mathfrak{r}}: \mathcal{R}_t \times p \times q \to \mathrm{e}_{p,q}$ for all $q \in \mathcal{Q}$. Here $\mathcal{R}_t$ is the rubric outline for task $t$ that includes only the task description and scoring guidelines. $\mathcal{\mathrm{e}}_{p,q}$ is the set of examples for each score for the given persona description and task-specific question. For each question, $\mathcal{R}_t$ is augmented with $\mathcal{\mathrm{e}}_{p,q}$ to produce $\mathfrak{R}_{t,q}$ which is the final unique rubric for question $q$ in task $t$. Note $\mathfrak{R}_{t,q} \subset \mathfrak{R}_{t}$ where $\mathfrak{R}_{t}$ is the set of completed rubrics for all questions in task $t \in \mathcal{T}$
\end{itemize}
The rubrics additionally include the persona description $p$, the posed question $q$ (where $q \in \mathcal{Q}$) as well as the agent's response to the question $o$ where, where $q \in \mathcal{Q}$). For a given $E_k$ where $k \in \{n\}$, $E_k$ evaluate $\mathcal{O}_t$ using $\mathfrak{R}_t$ i.e. $E_k: \mathfrak{R}_t \to \mathcal{S}_{k,t}$. Here $\mathcal{S}_{k,t}$ is the score matrix generated by evaluator model $E_k$ for all questions for task $t \in \mathcal{T}$ The final score matrix for task $t$ is therefore $S_t = \frac{1}{n}\sum_{k=1}^n S_{k,t}$. $S_t \subset S$ where S is the full score matrix for the persona agent. We include a listing of the notation used and their descriptions in Table~\ref{tab:formulation}

\subsection{Method}
\benchmark is a dynamic persona agent evaluation framework that assesses agents in relevant environments across five tasks (Figure~\ref{fig:main}). The framework comprises several key components:

\paragraph{Dynamic Environment Selection} An LLM reasoner selects pertinent environments from a diverse pool of 150 options based on the agent's persona description. The environment distribution is illustrated in Figure~\ref{fig:environments_big}, with selection prompts detailed in Appendix~\ref{appendix:env}.
% the Appendix~\ref{env}.

\paragraph{Question Generation} For each evaluation task, an LLM reasoner generates 10 task-specific questions per selected environment for a given agent. These questions are designed to assess the agent's ability to respond in a manner aligned with what is expected of the persona of the agent for the given task. Prompts and additional details are provided in Appendix~\ref{appendix:question}.
% Appendix~\ref{appendix:question}.

\paragraph{Persona Agent Response Generation} The agent LLM assumes the given persona using the system prompt, ``You are \texttt{[persona]}. Your responses should closely mirror the knowledge and abilities of this persona.'' as is done in \cite{gupta2024bias}. The persona agent then responds to each of the generated task questions. The complete template is available in Appendix~\ref{appendix:response}.
% Appendix~\ref{appendix:response}.

\paragraph{Reasoning Exemplars} To guide LLM evaluation, the evaluation rubrics are augmented with example responses for each possible score (1-5). An LLM reasoner is given the persona description of the agent, the posed question, and the scoring guidelines for the particular task in order to generate examples of responses to the question that would elicit each of the possible scores in the rubric. These examples are tailored to each persona agent's persona and are generated once for each question. The prompt template, rubric outline, and a sample are included in Appendix~\ref{appendix:example}.
% Appendix~\ref{appendix:example}.

\paragraph{Ensembled Evaluation} Two state-of-the-art LLM evaluator models assess each agent response. They are provided with a comprehensive rubric including task details, scoring criteria, agent-specific examples, persona descriptions, questions, and responses. Evaluators generate a score (1-5) with justification. The final score is the average across both models. While LLM evaluation may introduce bias, we mitigate this through detailed rubrics with clear criteria (provided in Appendix~\ref{appendix:example}), following \cite{liu-etal-2023-g}. We validate the efficacy of LLM evaluations through human evaluation and use ensemble methods to reduce potential variances.