\paragraph{Human Experimental Settings}
To test the alignment of \score with Human Judgment, we conducted a human study on a subsample of 100 personas across three models (\textsc{GPT-3.5}, \textsc{LLaMA-2-13b}, and \textsc{LLaMA-2-70b}) in our experiments, totaling 1500 model responses. The annotators were five experts with university-level English proficiency and substantial world knowledge of different personas and their expected characteristics. The annotators were informed that they annotations would be used only to gauge overall alignment with model generated scores and they were \textbf{provided the same rubric as the evaluator models} (see Appendix~\ref{box:rubrics}) and asked to indicate their assigned score. 

\paragraph{\score is Highly Correlated with Human Judgment} Table~\ref{tab:correlations} show strong correlations between Spearman and Kendall-Tau correlation scores between \score and human evaluations. 
The highest task-level Spearman score reached 84.8\% for Expected Action using \textsc{LLaMA-2-70b}, while the peak Kendall-Tau score was 77.2\%, observed for Linguistic Habits with \textsc{LLaMA-2-70b} and Linguistic Habits with \textsc{LLaMA-2-13b}. Overall \score correlations averaged 75.1\% (Spearman) and 62.73\% (Kendall-Tau) across the three models. 
Importantly, we witness strong inter-annotator agreement, with a Fleiss' Kappa score of $\mathbf{0.71}$ across all annotators.

\textbf{These strong correlations validate \benchmark's potential for large-scale automated evaluation of persona agents, demonstrating its alignment with human judgment.} Interestingly, \textsc{LLaMA-2-13b} demonstrates higher correlations with human evaluations compared to \textsc{GPT-3.5} and \textsc{LLaMA-2-70b} in several key tasks, particularly excelling in Persona Consistency. This unexpected performance suggests potential ambiguities in responses from larger models, evident in \textsc{LLaMA-2-70b}'s lower Spearman correlation scores for Persona Consistency and Linguistic Habits. Further experiments showing the efficacy of our human evaluation is present in Appendix~\ref{appendix:rebuttal}

\paragraph{Model-Human Agreement Case}
Appendix~\ref{appendix: qualitative} illustrates strong alignment between \benchmark and human evaluations across different LLMs. For the 36-year-old Australian environmental lawyer persona, all models adapted their linguistic style to the courtroom context. \textsc{LLaMA-2-13b} received the highest score (4.5) from both evaluation methods, likely due to its specific references to indigenous peoples and Australian colloquialisms that aligned with the persona. \textsc{GPT-3.5} and \textsc{LLaMA-2-70b} scored 4.0, indicating competent but less tailored performances. This case demonstrates \benchmark's capacity to assess context-aware linguistic patterns.

\paragraph{Model-Human Disagreement Case}
Appendix~\ref{appendix: qualitative} also presents an evaluation discrepancy case. For a 22-year-old London writer persona, \benchmark assigned high scores (4.5, 4.5, 4.0) while human evaluators gave substantially lower scores (2.0, 2.0, 3.0). Only \textsc{LLaMA-2-70b} incorporated British vernacular, and all responses lacked the sophisticated language expected from a writer describing artwork. This disparity highlights an opportunity to improve \benchmark's ability to penalize responses that fail to establish and maintain expected linguistic characteristics of a given persona.

% \paragraph{Model-Human Agreement Case}
% In Appendix~\ref{appendix: qualitative} we present an example that demonstrates strong alignment between the \benchmark framework and human evaluations across different LLMs for the given persona and task. The persona of a 36-year-old Australian environmental lawyer is consistently represented in the responses, with each model adapting its linguistic style to fit the courtroom setting and the lawyer's role. Notably, the LLaMA-2-13b model received the highest score (4.5) from both \benchmark and human evaluators, likely due to its specific mention of indigenous peoples (the Wakka Wakka People) and its use of Australian colloquialisms ("G'day"), which align closely with the given persona. The GPT 3.5 and LLaMA-2-70b models both received scores of 4.0, suggesting competent but slightly less tailored performances. All models maintained appropriate courtroom language, demonstrating \benchmark's ability to assess context-aware linguistic patterns.

% \paragraph{Model-Human Disagreement Case}
% Appendix~\ref{appendix: qualitative} also presents a case highlighting evaluation discrepancies. For a 22-year-old London writer persona, \benchmark assigned high scores (4.5, 4.5, 4.0) while human evaluators gave significantly lower scores (2.0, 2.0, 3.0). Only LLaMA-2-70b incorporated British vernacular, and responses lacked the sophisticated language expected from a writer. Furthermore, none of the responses demonstrated the more sophisticated or analytical language one might expect from a writer describing artwork. This disparity suggests that \benchmark has an improvement opportunity in penalizing agent responses for not establishing and maintaining the expected linguistic habits of a given persona.


