\section{Conclusion and Future Work}
\vspace{-0.15em}

\textbf{Conclusion.} We present SILVR, a self-improvement loop for solving novel robotic tasks via visual planning.  Initialized from an in-domain video model pretrained on a small general set of demonstrations, SILVR iteratively updates the visual planner for a novel task of interest through self-collected online experience.  Compared to equivalent behavior cloning setups, or utilizing online experience through reinforcement learning finetuning, we find that SILVR achieves superior self-improvement capabilities and demonstrates sample efficiency.  %
We successfully apply SILVR as a self-improving visual planner not only for synthetic environments, but also on robot arms deployed in the real world.

\textbf{Limitations and Future Work.} SILVR implicitly assumes that the initial in-domain model, optionally adapted with an internet-pretrained video model, achieves a reasonable success rate to collect online experience and achieve self-improvement. This assumption may not hold when the novel task is too challenging. Additionally, the choice of internet-pretrained video model can pose a trade-off on between video quality and computation cost. Whereas in this work we choose AnimateDiff~\citep{guo2023animatediff} as a large-scale pretrained video model with both reasonable generation quality as well as computational efficiency, more recent video generative models with enhanced visual quality can be further explored for improved visual planning performance on downstream robotic tasks.

Whereas SILVR achieves the best self-improvement performance with some initial success rate on the novel task, the cold start problem may pose challenges.  Just as exploration can help address the cold start problem for standard reinforcement learning, we believe that investigating how to improve exploration for the visual planning framework in a principled manner is a promising future direction.

\textbf{Acknowledgments.} This work is partially supported by Samsung and the U.S. National Science Foundation under Cooperative Agreement No. 2433429. Our research was conducted using computational resources at the Center for Computation and Visualization at Brown University. We would like to thank Professors George Konidaris and Stefanie Tellex for their generous support for our real-robot experiments. We would also like to thank Shijie Wang and Zitian Tang for their help with the experiments. Calvin would like to thank Dennis Lee and Ally Koo, as well as Kayan Shih and her family, for all their kindness and hospitality during the paper writing process.


\section{Reproducibility Statement}
 To support reproducibility, all codebases utilized in this paper were modified versions of publicly available repositories.  Furthermore, we provide extensive details of hyperparameters and settings both in the main body of the text as well as in the Appendix.





