We discuss this experiment in Section~\ref{subsec:profile analysis}.
A Chi-square test is employed to identify the abnormal templates with the p-value=0.05.
Typically, Chi-square distribution is formulated as follows:
\begin{equation}
    \chi^2=\frac{(n-1) s^2}{\sigma_0^2}
\end{equation}
where \(n\) denotes number of samples, \(s^2\) denotes the sample variance, and \(\sigma^2\) denotes the population variance.

The Chi-square test has two hypotheses:
\begin{itemize}
    \item Null hypothesis \(H_0\): the sample variance does not have a significant difference with the population variance.
    \item Alternative hypothesis \(H_1\): the sample variance has a significant difference with the population variance.
\end{itemize}
If $\chi^2>p$, then we accept the null hypothesis \(H_0\). On the contrary, we reject \(H_0\) and accept the alternative hypothesis \(H_1\).

In our experiment, we first calculate the variance of all scenarios as the population variance.
Then, the variance of scenarios derived from the same template is calculated as the sample variance.
As we enlarge each template into five scenarios, the sample number is fixed to be 5.
We apply the Chi-square test to all 11 models tested in our main experiments.
For each template, Chi-square test rejecting over \textbf{5} models' results means that there's a significant difference between sample performance and overall performance on the majority of models.
In this case, the template is marked as an abnormal one during the profile enrichment, eventually resulting in \textbf{18} abnormal templates.