%\medbreak
%this section should mention major baselines such as procthor and (ideally) links back to the previous two related work sections
\medbreak
\noindent \textbf{Embodied AI Environments.} Previous work mainly relies on 3D artists to design the environments \cite{ai2thor, li2023behavior, puig2018virtualhome, xia2018gibson, deitke2020robothor, gan2020threedworld, khanna2023hssd}, which is hard to scale up or construct scenes from 3D scans \cite{savva2019habitat, szot2021habitat, ramakrishnan2021hm3d} to reduce human labor, but scenes are less interactive.
The procedural generation framework \procthor~\cite{procthor} showcases its potential to generate large-scale interactive environments for training embodied agents. Phone2Proc \cite{phone2proc} uses a phone scan to create training scenes that are semantically similar to the desired real-world scene. A concurrent work, RoboGen~\cite{wang2023robogen}, proposes to train robots by generating diversified tasks and scenes. These works parallel our concept, \holodeck, which aims to train generalizable embodied agents and presents an avenue for further exploration in text-driven 3D interactive scene generation.
%extends the ability of \proecthor by integrating commonsense priors and spatial knowledge inherent in large language models. %to generate intricate indoor scenes from text descriptions and demonstrates a leap towards realistic, interactable scene generation for embodied AI applications. By integrating commonsense priors and spatial knowledge inherent in large language models, \holodeck 

\smallbreak
\noindent \textbf{Large Language Model for Scene Design.}
% the old approach learns 3D assets layout with a sequential generation NN, but ext2Scene faces challenges due to the absence of large-scale aligned datasets of text and 3D, limiting its applicability.
%v% Eschewing the use of Generative Adversarial Networks (GANs) that characterize other methods, Text2Scene adopts a sequential generation approach to generate compositional scenes from textual descriptions.
% sceneformer, ATISS 
Many works on scene design either learn spatial knowledge priors from existing 3D scene databases~\cite{chang2017sceneseer,tan2019text2scene,ma2018language,tang2023diffuscene,zhao2023roomdesigner,wang2021sceneformer,wei2023lego} or leverage user input and refine the 3D scene iteratively~\cite{chang2014interactive,cheng2019interactive}. However, having to learn from datasets of limited categories such as 3D-FRONT~\cite{fu20213d} restricts their applicability. Recently, Large Language Models (LLMs) were shown to be useful in generating 3D scene layouts~\cite{feng2023layoutgpt,lin2023towards}.
However, their methods of having LLMs directly output numerical values can yield layouts that defy physical plausibility (e.g., overlapping assets). In contrast, %\holodeck is able to generate more detailed elements like doors, windows, and materials. Furthermore, 
\holodeck uses LLMs to sample spatial relational constraints and a solver to optimize the layout, ensuring physically plausible scene arrangements. 
Our human study shows a preference for \holodeck-generated layouts over those generated end-to-end by LLMs. (see Sec~\ref{sec: layout ablation}).
% summarize early days pursuits in the field --> % early work on 3d generation aim to model the distribtuion of 3d objects from datasets 
% text2shape/CLIP marks the start of text-driven 3d generation 
% diffusion models + NeRF --> but the success is still in object generation not scenes

%Early endeavors on 3D generation, such as 3D-GAN~\cite{wu2016learning} and Pointflow~\cite{yang2019pointflow}, emphasize texture-less geometric shape generation, employing voxel or point cloud representations.
\smallbreak
\noindent\textbf{Text-driven 3D Generation.} Early endeavors in 3D generation focus on learning the distribution of 3D shapes and/or textures from category-specific datasets~\cite{wu2016learning,yang2019pointflow,zhou20213d,henzler2019escaping,nguyen2019hologan}. 
%For example, \cite{wu2016learning,yang2019pointflow,zhou20213d} generate texture-less geometric shapes by employing voxel or point cloud representations. PlatonicGAN~\cite{henzler2019escaping} and HoloGAN~\cite{nguyen2019hologan} generate textured 3D objects or scenes by learning from category-specific natural images. 
%However, these works are incapable of text-driven generative tasks unless given a paired scene-text dataset~\cite{chen2019text2shape}. %. An effort to bridge this gap was seen with Text2shape~\cite{chen2019text2shape}, which learns cross-modal connections between texts and 3D models with a specific paired scene-text dataset.
% and then CLIP came out 
%The advent of large vision-language models like CLIP~\cite{radford2021learning} enables zero-shot generation of 3D objects. For example, CLIPMesh~\cite{mohammad2022clip} combines CLIP with a differentiable renderer to generate. 
Subsequently, the advent of large vision-language models like CLIP~\cite{radford2021learning} enables zero-shot generation of 3D textures and objects \cite{huang2023aladdin,mildenhall2021nerf,poole2022dreamfusion,metzer2023latent,lin2023magic3d,gu2023nerfdiff}.
%Other recent works extract semantic priors from pre-trained text-to-image diffusion models and employ Neural Radiance Fields (NeRF)~\cite{mildenhall2021nerf} as the 3D representation~\cite{poole2022dreamfusion,metzer2023latent,lin2023magic3d,gu2023nerfdiff}.
These works excel at generating 3D objects but struggle to generate complex 3D scenes. % with many objects. 
% Despite these advancements, most if not all of these works focus on 3d object generation --> talk about 3d "Scene" generation
% objects in the scene cannot be clearly disentangled with these neural-based methods
More recently, emerging works generate 3D scenes by combining pre-trained text-to-image models with depth prediction 
algorithms to produce either textured meshes or NeRFs~\cite{fridman2023scenescape,hollein2023text2room,zhang2023text2nerf}. However, these approaches yield 3D representations that lack modular composability and interactive affordances, limiting their use in embodied AI. In contrast, \holodeck utilizes a comprehensive 3D asset database to generate semantically precise, spatially efficient, and interactive 3D environments suitable for training embodied agents.
%\ani{This section of related work feels a bit odd. We arent really comparable to direct text-2-3D methods, and so I would move this paragraph to the end of related work, and tone it down. Perhaps talk about how there has been a lot of progress in text-2-3D, and future work can use this to generate assets for Holodeck systems, but modular composability is needed for interactive environments.}
%More recently, 3D scene generation works leverage pre-trained text-to-image models with depth prediction algorithms to produce unified and textured 3D meshes of indoor scenes\cite{,}. % Text2Room~\cite{hollein2023text2room}.%Additionally, works like Text2NeRF~\cite{} adopt a similar strategy but use NeRF to represent the 3D space. 

%the Many works on 3D scene generation are motivated by generating 3D-consistent videos or perceptual views from a single image~\cite{fridman2023scenescape}. create 3D scenes from
%Text2Room generates complete, textured
%3D room geometry from arbitrary trajectories.
%perpetual view generation [78, 43, 41, 7], synthesizing videos via a render-refine repeat pattern from a single RGB image that depict a scene along a forward-facing camera trajectory. In very recent
%concurrent work, Fridman et al. [18] create 3D scenes from text, but focus on this type of 3D-consistent “zoom-out” video generation. Instead, we generate complete, textured
%3D room geometry from arbitrary trajectories
%SceneScape is proposed to do perpetual view generation from textual descriptions. Text2Room proposed text-to-3D schemes, with the former focusing on , and the latter on generating room-scale textured 3D meshes from text prompts. Moreover, Text2NeRF
