\section{Conclusions and Future Work}
\label{section:conclusion}
GAIA-1 is a generative world model for autonomous driving. The world model uses vector-quantized representations to turn the task of future prediction into a next token prediction task, a technique that has been successfully employed in large language models. GAIA-1 has demonstrated its capability to acquire a comprehensive understanding of the environment, distinguishing between various concepts such as cars, trucks, buses, pedestrians, cyclists, road layouts, buildings, and traffic lights --- all through self-supervision. Further, GAIA-1 harnesses the capabilities of video diffusion models to generate realistic driving scenarios, thereby functioning as an advanced neural simulator. GAIA-1 is a multimodal approach that enables the control of the ego-vehicle's actions and other scene attributes through a combination of textual and action-based instructions.

While our method demonstrated promising results that have the potential to push the boundaries of autonomous driving, it is important to acknowledge current limitations. For instance, the autoregressive generation process, while highly effective, does not yet run at real-time. Nevertheless, it is noteworthy that this process lends itself well to parallelization, allowing for the concurrent generation of multiple samples.

The significance of GAIA-1 extends beyond its generative capabilities. World models represent a crucial step towards achieving autonomous systems that can understand, predict, and adapt to the complexities of the real world. Furthermore, by incorporating world models into driving models, we can enable them to better understand their own decisions and ultimately generalize to more real-world situations. Lastly, GAIA-1 can also serve as a valuable neural simulator, allowing the generation of unlimited data, including adversarial examples, for training and validating autonomous driving systems. 
