\saveSpaceSec
\section{Introduction}
\saveSpaceSec
The advent of Large Language Models (LLMs) such as ChatGPT%\footnote{\url{https://chat.openai.com/chat}}
~\citep{chatgpt} and GPT-4~\citep{openai2023gpt4} has led to increasing influence across various sectors, from education and healthcare to customer service and entertainment. 
These powerful AI systems have demonstrated a remarkable ability to understand and generate human-like responses. Despite the remarkable capabilities of LLMs, a key limitation is their lack of long-term memory, an essential aspect of human-like communication, particularly noticeable in scenarios requiring sustained interactions like personal companionship, psychological counseling, and secretarial tasks.
Long-term memory in AI is vital to maintain contextual understanding, ensure meaningful interactions and understand user behaviors over time. For instance, personal AI companions need to recall past conversations for rapport building. In psychological counseling, an AI can provide more effective support with knowledge of the user's history and past emotional states. Similarly, secretarial AI requires memory for task management and preference recognition. The absence of long-term memory in LLMs hinders their performance and user experience. Therefore, it is essential to develop AI systems with improved memory capabilities for a more seamless and personalized interaction.

Therefore, we introduce \method, a novel mechanism designed to provide LLMs with the ability to retain long-term memory and draw user portraits. \method enables LLMs to recall historical interactions, continually evolve their understanding of context, and adapt to a user's personality based on past interactions, thereby enhancing their performance in long-term interaction scenarios.
Inspired by the Ebbinghaus Forgetting Curve theory, a well-established psychological principle that describes how the strength of memory decreases over time, \method further incorporates a dynamic memory mechanism closely mirroring human cognitive process. This mechanism empowers the AI to remember, selectively forget, and strengthen memories based on time elapsed, offering more natural and engaging user experience. 
Specifically, \method is built on a memory storage with memory retrieval and updating mechanism, and ability to summarize past events and users' personality.

\method is versatile as it can accommodate both closed-source LLMs like ChatGPT and open-source LLMs like ChatGLM~\citep{zeng2022glm} or BELLE~\citep{BELLE}.

To exemplify the practical implications of \method, we develop \chatbot, an LLM-based AI Companion chatbot integrated with this innovative memory mechanism. 
\chatbot is designed to retain and reference past interactions, reinforcing the transformative influence of \method in crafting a more personable AI companion.
A distinctive features of SiliconFriend is its tuning with 38k psychological conversations, collected from various online sources, which enables it to exhibit empathy, carefulness, and provide useful guidance, making it adept at handling emotionally charged dialogues. 
Moreover, one of the standout capabilities of SiliconFriend is to understand a user's personality by summarizing from past interactions, which empowers it to tailor responses to the user's individual traits, thereby enhancing user experience.
Additionally, SiliconFriend supports bilingual functionality, catering to users who communicate in English and Chinese. This multi-language support broadens its accessibility and usability across different user groups. 
SiliconFriend is implemented with two open-source models, ChatGLM and BELLE, along with one closed-source model, ChatGPT, showcasing the versatility of \method in accommodating different LLMs.

To evaluate the effectiveness of \method, we conduct evaluations covering both qualitative and quantitative analyses, where the former involves real-world user dialogs and the latter employs simulated dialogs.
For the quantitative analysis, we create a memory storage consisting of 10 days of conversations encompassing a diverse range of topics. These conversations involve 15 virtual users with diverse personalities, for which ChatGPT plays the role of users and generates dialog contexts according to their personalities. 
Based on this memory storage, we design 194 probing questions to assess whether the model could successfully recall pertinent memories and provide appropriate responses.
Experiment results showcase the capabilities of \chatbot in memory recall, provision of empathetic companionship, and understanding of user portraits. These findings corroborate the potential of \method to significantly improve the performance of LLMs in long-term interaction scenarios.
In this paper, we summarize the key contributions as follows:
\begin{itemize} [topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt,leftmargin=20pt]
    \item We introduce \method, a novel human-like long-term memory mechanism, which enables LLMs to store, recall, update memory, and draw user portrait.
    \item We demonstrate the practical applicability of \method through SiliconFriend, an LLM-based AI companion equipped with \method and tuned with psychological dialogs. 
    It can recall past memories, provide empathetic companionship, and understand user behaviors.

    \item We show the generalizability of \method in three key aspects: (1) Accommodation of both open-source and closed-source LLMs; (2) Bilingual ability in both Chinese and English; (3) Applicability with and without memory forgetting mechanism.
    % It is effective in different languages; and 3) It can be utilized with and without memory forgetting mechanism. This adaptability underscores its potential for broader adoption in the AI field.
\end{itemize}

