\section{Discussion and Future Work}
\label{sec:conclusion} 

In this paper, we introduced \ModelAcronym{}, an efficient action tokenizer for high-frequency robotic control data. \ModelAcronym{} uses the discrete cosine transform (DCT) followed by byte-pair encoding (BPE) to compress action chunks, leading to significantly better compression than existing action tokenizers across a range of robotics domains. Our real-world and simulated VLA experiments show that \ModelAcronym{} leads to dramatically improved performance over the previously used na\"{i}ve action discretization approaches, and outperforms more complex learned tokenization methods based on vector quantization. We also showed that we can train \ModelUniversalAcronym{}, a \emph{universal} action tokenizer, that can serve as a strong default tokenizer for any robot action sequence. Using it, we trained \GeneralistModelAcronym, a dexterous generalist policy that can match performance of state-of-the-art diffusion VLAs, while being significantly more efficient to train. 

There are many exciting directions for future work:

\textbf{Action tokenizers.} While we believe that \ModelAcronym{} is a significant step toward general purpose robot action tokenizers, many questions remain. 
In this work, we tested \ModelAcronym{} on static robot manipulators. Our offline experiments demonstrated promising compression capabilities of \ModelUniversalAcronym{} on other robot morphologies like mobile robots, dexterous hands, and humanoids. Testing actual policy performance on these platforms is an exciting direction for future work. Additionally, exploring alternative compression schemes, and testing the combination of compression-based action encodings with non-autoregressive decoding approaches like diffusion~\citep{black2024pi_0} are interesting directions for future investigation.

\textbf{VLA architectures.} 
Our paper has taken initial steps to explore the trade-offs between two major classes of VLA architectures, autoregressive and diffusion decoding VLAs, but the jury on the best VLA architecture is still out. Future work should carefully explore trade-offs in training speed, language grounding abilities, and expressiveness of either approach. 

\textbf{Inference speed.} While \GeneralistModelAcronym{} matches the overall performance of diffusion $\pi_0$, it is slower at inference time (see \cref{sec:ar_vs_diffusion}). While the slower inference speed was acceptable on the static tasks we evaluated, future work should explore approaches for speeding up inference of autoregressive VLA models to enable them to solve highly dynamic tasks. There is a large literature of inference optimizations for large language models that can be readily applied to autoregressive VLAs.

