\paragraph{Agent Models}
We evaluate various LLM families including Llama-2-7b/13b/70b-Chat~\cite{touvron2023llama}, Llama-3-8b/70b-Instruct~\cite{dubey2024llama}, Mistral-7b-Instruct-v0.3~\cite{jiang2023mistral}, Qwen2.5-7b/14b/72b-Chat~\cite{qwen2.5}, GPT-3.5-Turbo~\cite{ouyang2022training} and GPT-4o~\cite{achiam2023gpt}.
For interactions between different models and further analysis, we involve Llama-3-8b, Qwen2.5-14b, GPT-3.5-turbo, and GPT-4o. 

\paragraph{Judge Models}
To effectively leverage current LLMs for automating the evaluation of social interactions as third-party judges, we conduct a human evaluation and compare it with model-based evaluations.
We randomly sample 100 simulated scenarios, posing a total of 584 social goal evaluation questions, and manually verify whether the communication history shows that the goals were achieved.
Using human annotations as ground-truth labels, we calculate the accuracy of various models acting as judges, as shown in Table~\ref{tab:human_eval}.
Given the results, we select GPT-4o, Qwen2.5-72b, and Llama-3-70b from different model families as our judge models, referred to as Judge-GPT-4o, Qwen2.5, and Llama-3 hereafter.
Additionally, we incorporate a majority voting mechanism across these models to create a mixture-of-experts model as another judge.

\paragraph{Implementation Details}
We use vLLM~\citep{kwon2023efficient} to deploy all open source models: Qwen2.5-72b and Llama-3-70b on NVIDIA A100, and other models on NVIDIA RTX 4090.
We apply AutoGen~\cite{wu2024autogen} to manage interacting and judging threads.
We set max new tokens to 128 for all models.
Temperature is set to 1 for agent models to encourage diversity, and 0 for judge models to ensure the stability of evaluation.