\section{Related Work}

\subsection*{Learning in the imagination of world models}

The idea of training policies in a learnt model of the world was first investigated in tabular environments \citep{sutton}. \citet{worldmodels} showed that simple visual environments could be simulated with autoencoders and recurrent networks. SimPLe \citep{simple} demonstrated that a PPO policy \citep{ppo} trained in a video prediction model outperformed humans in some Atari games. Improving upon Dreamer \citep{dreamerv1}, DreamerV2 \citep{dreamerv2} was the first agent learning in imagination to achieve human-level performance in the Atari 50M benchmark. Its world model combines a convolutional autoencoder with a recurrent state-space model (RSSM) \citep{planet} for latent dynamics learning. More recently, \citet{transdreamer} explored a variant of DreamerV2 where a Transformer replaces the recurrent network in the RSSM and \citet{action_free_pretraining} enhance DreamerV2 in the setting where an offline dataset of videos is available for pretraining.

\subsection*{Reinforcement Learning with Transformers}

Following spectacular advances in natural language processing \citep{manning}, the reinforcement learning community has recently stepped into the realm of Transformers. \citet{parisotto} make the observation that the standard Transformer architecture is difficult to optimize with RL objectives. The authors propose to replace residual connections by gating layers to stabilize the learning procedure. Our world model does not require such modifications, which is most likely due to its self-supervised learning objective. The Trajectory Transformer \citep{trajectory_transformer} and the Decision Transformer \citep{decision_transformer} represent offline trajectories as a static dataset of sequences, and the Online Decision Transformer \citep{online_dt} extends the latter to the online setting. The Trajectory Transformer is trained to predict future returns, states and actions. At inference time, it can thus plan for the optimal action with a reward-driven beam search, yet the approach is limited to low-dimensional states. On the contrary, Decision Transformers can handle image inputs but cannot be easily extended as world models. \citet{vqplanning} introduce an offline variant of MuZero \citep{muzero} capable of handling stochastic environments by performing an hybrid search with a Transformer over both actions and trajectory-level discrete latent variables. 

\subsection*{Video generation with discrete autoencoders and Transformers}

\textsc{vqgan} \citep{vqgan} and \textsc{dall-e} \citep{ramesh} use discrete autoencoders to compress a frame into a small sequence of tokens, that a transformer can then model autoregressively. Other works extend the approach to video generation. GODIVA \citep{wu_godiva} models sequences of frames instead of a single frame for text conditional video generation. VideoGPT \citep{yan_videogpt} introduces video-level discrete autoencoders, and Transformers with spatial and temporal attention patterns, for unconditional and action conditional video generation. 



