\section{Humanoid from Pixels}
\label{seq:humanoid}

\input{figures/hum-video/figure}
\input{figures/hum-score/figure}

While the main experiments of this paper focus on the Atari benchmark with discrete actions, DreamerV2 is also applicable to control tasks with continuous actions. For this, we the actor outputs a truncated normal distribution instead of a categorical distribution. To demonstrate the abilities of DreamerV2 for continuous control, we choose the challenging humanoid environment with only image inputs, shown in \cref{fig:hum-video}. We find that for continuous control tasks, dynamics backpropagation substantially outperforms reinforce gradients and thus set $\rho=0$. We also set $\eta=10^{-5}$ and $\beta=2$ to further accelerate learning. We find that DreamerV2 reliably solves both the stand-up motion required at the beginning of the episode and the subsequent walking. The score is shown in \cref{fig:hum-score}. To the best of our knowledge, this constitutes the first published result of solving the humanoid environment from only pixel inputs.

\clearpage

\section{Montezuma's Revenge}
\label{seq:montezuma}

\input{figures/mon-video/figure}
\input{figures/mon-score/figure}

While our main experiments use the same hyper parameters across all tasks, we find that DreamerV2 achieves higher performance on Montezuma's Revenge by using a lower discount factor of $\gamma=0.99$, possibly to stabilize value learning under sparse rewards. \Cref{fig:mon-score} shows the resulting performance, with all other hyper parameters left at their defaults. DreamerV2 outperforms existing model-free approaches on the hard-exploration game Montezuma's Revenge and matches the performance of the explicit exploration algorithm ICM \citep{pathak2017icm} that was applied on top of Rainbow by \citet{taiga2019benchmark}. This suggests that the world model may help with solving sparse reward tasks, for example due to improved generalization, efficient policy optimization in the compact latent space enabling more actor critic updates, or because the reward predictor generalizes and thus smooths out the sparse rewards.

\clearpage