\section{Applications of machine learning models with rejection}~\label{sec:applications}
In safety-sensitive domains, making the wrong decision can have serious consequences such as fatal accidents with self-driving cars, major breakdowns in industrial settings or incorrect diagnoses in medical applications. In these domains, rejection can be used to make cautious predictions. However, the number of papers discussing machine learning with rejection in practical applications is still limited. In this section, an overview of these papers is given. 

\paragraph{Biomedical applications.} Machine learning with rejection is primarily explored in medical applications due to the potential consequences of incorrect decisions~\citep{Liu2022}. The main focus is on ambiguity rejection for medical diagnosing, specifically the detection and classification of diseases. If the model is confident enough, the detection results are automatically translated into a diagnosis. Otherwise, a medical expert verifies the detection~\citep{Kompa2021}. For instance, vocal pathologies are detected using voice recording data, where a linear classifier is trained and uncertain predictions are rejected based on a threshold of the derived posterior probability~\citep{Kotropoulos2009}. Spine disease diagnosis employs the data-replication method, which predicts only when two biased classifiers agree~\citep{Sousa2009b}. Cancer detection, particularly breast tumor detection, benefits from a reject option implemented with an SVM classifier using confidence-based rejection~\citep{Guan2020}. The rejection thresholds are chosen to limit the rejection rate and reduce manual effort. 

Other biomedical applications have also adopted the use of a reject option. \citet{Lotte2008} conduct an experiment on distinguishing hand movements using brain activity. They employ a separate novelty rejector trained in a supervised manner to discard brain activity associated with other activities. \citet{Lewicke2008} explore sleep stage scoring with both types of rejection, utilizing confidence metrics derived from a Neural Network classifier's neural activities. Another sleep stage scoring application utilizes a separate rejector based on \gls{lof} anomaly scores for novelty rejection, identifying patients who deviate from the training data~\citep{VanderPlas2021}. Some papers compare the performance of multiple models with rejection to determine the optimal approach for specific biomedical applications. For instance, \citet{Kang2017} predict the effectiveness of a diabetes drug for individual patients, while \citet{Tang2014} investigate the classification of body positions using sensors placed in patients' shoes. Lastly, a medical application focuses on the analysis of tissue examples, aiming to classify each pixel of tissue images into categories such as bone, fat, or muscle~\citep{Condessa2013,Condessa2015a}.

\paragraph{Engineering applications.} 
Applications in engineering can also benefit from a reject option. For instance, in the chemical identification of gases, time-series data is processed by two classifiers to classify the observed gas. Classification occurs only when there is agreement between the classifiers, and ambiguous predictions are rejected until consensus is reached~\citep{Hatami2013}. A similar ambiguity rejection technique, rejecting when two classifiers disagree, is employed in defect detection in software applications~\citep{Mesquita2016}. Fault detection in steam generators utilizes a set of one against all SVM classifiers, and rejection is based on the distance to the decision boundary of these classifiers, allowing for both rejection types~\citep{Zou2011}. Finally, \cite{Hendrickx2022} employs a separated novelty rejector for vehicle usage profiling.

\paragraph{Economics applications.} In the domain of economics, two applications of machine learning with rejection have been proposed, both focused on ambiguity rejection and novelty rejection. The first application uses a \gls{lvq} to classify dollar bills by value~\citep{Ahmadi2004}. Confidence metrics are obtained from the classifier for both types of rejection. The second application investigates a few rejection techniques on top of a predictor to decide whether to grant a loan~\citep{Coenen2020}

\paragraph{Image recognition applications.} Reject options are usually available for analyzing text styles and reading handwritten numbers~\citep{Fumera2004}, used for both ambiguity rejection~\citep{Xu1992,Huang1995,RAHMAN1998} and novelty rejection~\citep{Lou1999c,Arlandis2002}. These methods employ a confidence-based dependent rejector. Additionally, there is a paper focused on identifying walkers based on their footprints~\citep{Suutala2004}. Initially, each footprint is individually predicted or rejected, and then the information from three consecutive footprints is combined for the final decision.