\section{Hyper Parameters}
\label{sec:hparams}

We use the convolutional and deconvolutional networks from \citet{ha2018worldmodels}, a GRU \citep{cho2014gru} with $200$ units as deterministic path in the dynamics model, and implement all other functions as two fully connected layers of size $200$ with ReLU activations \citep{nair2010relu}. Distributions in latent space are $30$-dimensional diagonal Gaussians with predicted mean and standard deviation.

We pre-process images by reducing the bit depth to 5 bits as in \citet{kingma2018glow}. The model is trained using the Adam optimizer \citep{kingma2014adam} with a learning rate of $10^{-3}$, $\epsilon=10^{-4}$, and gradient clipping norm of $1000$ on batches of $B=50$ sequence chunks of length $L=50$. We do not scale the KL divergence terms relatively to the reconstruction terms but grant the model $3$ free nats by clipping the divergence loss below this value. In a previous version of the agent, we used latent overshooting and an additional fixed global prior, but we found this to not be necessary.

For planning, we use CEM with horizon length $H=12$, optimization iterations $I=10$, candidate samples $J=1000$, and refitting to the best $K=100$. We start from $S=5$ seed episodes with random actions and collect another episode every $C=100$ update steps under $\epsilon\sim\Normal(0,0.3)$ action noise. The action repeat differs between domains: cartpole ($R=8$), reacher ($R=4$), cheetah ($R=4$), finger ($R=2$), cup ($R=4$), walker ($R=2$). We found important hyper parameters to be the action repeat, the KL-divergence scales $\beta$, and the learning rate.

\section{Planning Algorithm}
\input{algorithms/planning}

\clearpage
\section{Multi-Task Learning}
\label{sec:exp_multi}
\input{figures/score_multi/figure_avg}
\input{figures/score_multi/figure}

\clearpage
\section{Latent Overshooting}
\label{sec:exp_overshooting}
\input{figures/score_overshooting/figure}

\clearpage
\section{Activation Function}
\label{sec:exp_activation}
\input{figures/score_activation/figure}

\clearpage
\section{Bound Derivations}
\label{sec:derivs}

\paragraph{One-step predictive distribution}

The variational bound for latent dynamics models $\p(o_{1:T},s_{1:T}|a_{1:T})=\prod_t\p(s_t|s_{t-1},a_{t-1})\p(o_t|s_t)$ and a variational posterior $\q(s_{1:T}|o_{1:T},a_{1:T})=\prod_t\q(s_t|o_{\leq t},a_{<t})$ follows from importance weighting and Jensen's inequality as shown,
\begin{equation}
\begin{aligned}
\ln\p(o_{1:T}|a_{1:T})
&\triangleq\ln\E[\bigg]{\p(s_{1:T}|a_{1:T})}{\prod_{t=1}^T \p(o_t|s_t)} \\
&=\ln\E[\bigg]{\q(s_{1:T}|o_{1:T},a_{1:T})}{\prod_{t=1}^T \p(o_t|s_t)\p(s_t|s_{t-1},a_{t-1})/\q(s_t|o_{\leq t},a_{<t})} \\
&\geq\E[\bigg]{\q(s_{1:T}|o_{1:T},a_{1:T})}{\sum_{t=1}^T \ln\p(o_t|s_t)+\ln\p(s_t|s_{t-1},a_{t-1})-\ln\q(s_t|o_{\leq t},a_{<t})} \\
&=\sum_{t=1}^T \Big(
  \describe{\Ebelow{\q(s_t|o_{\leq t},a_{<t})}{\ln\p(o_t|s_t)}}{reconstruction}
  -\describe{\Ebelow[\big]{\q(s_{t-1|o_{\leq t-1},a_{<a-1}})}{\KL{\q(s_t|o_{\leq t},a_{<t})}{\p(s_t|s_{t-1},a_{t-1})}}}{complexity} \Big).
\end{aligned}
\label{eq:elbo_deriv}
\end{equation}%

\paragraph{Multi-step predictive distribution}

The variational bound on the $d$-step predictive distribution $\pr[p_d](o_{1:T},s_{1:T}|a_{1:T})=\prod_t\p(s_t|s_{t-d},a_{t-1})\p(o_t|s_t)$ and a variational posterior $\q(s_{1:T}|o_{1:T},a_{1:T})=\prod_t\q(s_t|o_{\leq t},a_{<t})$ follows analogously. The second bound comes from moving the log inside the multi-step priors, which satisfy the recursion $\p(s_t|s_{t-d},a_{t-d-1:t-1})=\E{\p(s_{t-1}|s_{t-d},a_{t-d-1:t-2})}{\p(s_t|s_{t-1},a_{t-1})}$.
\begin{equation}
\begin{aligned}
\ln\pr[p_d](o_{1:T}|a_{1:T})
&\triangleq\ln\E[\bigg]{\pr[p_d](s_{1:T}|a_{1:T})}{\prod_{t=1}^T\p(o_t|s_t)} \\
&=\ln\E[\bigg]{\q(s_{1:T}|o_{1:T},a_{1:T})}{\prod_{t=1}^T \p(o_t|s_t)\p(s_t|s_{t-d},a_{t-d-1:t-1})/\q(s_t|o_{\leq t},a_{<t})} \\
&\geq\E[\bigg]{\q(s_{1:T}|o_{1:T},a_{1:T})}{\sum_{t=1}^T \ln\p(o_t|s_t)+\ln\p(s_t|s_{t-d},a_{t-d-1:t-1})-\ln\q(s_t|o_{\leq t},a_{<t})} \\
&\geq\E[\bigg]{\q(s_{1:T}|o_{1:T},a_{1:T})}{\sum_{t=1}^T \ln\p(o_t|s_t)+\Ebelow{\p(s_{t-1}|s_{t-d},a_{t-d-1:t-2})}{\ln\p(s_t|s_{t-1},a_{t-1})}-\ln\q(s_t|o_{\leq t},a_{<t})} \\
&=\sum_{t=1}^T \Big(
  \describe{\E{\q(s_t|o_{\leq t},a_{<t})}{\ln\p(o_t|s_t)}}{reconstruction}
  -\describe{\Ebelow[\big]{\p(s_{t-1}|s_{t-d},a_{t-d-1:t-2})\q(s_{t-d}|o_{\leq t-d},a_{<t-d})}{\KL{\q(s_t|o_{\leq t},a_{<t})}{\p(s_t|s_{t-1},a_{t-1})}}}{multi-step prediction} \Big).
\end{aligned}
\label{eq:dstep_deriv}
\end{equation}%
Since all expectations are on the outside of the objective, we can easily obtain an unbiased estimator of this bound by changing expectations to sample averages.

\paragraph{Relation between one-step and multi-step predictive distributions}

We conjecture that the multi-step predictive distribution $\pr[p_d](o_{1:T})$ lower bounds the one-step predictive distribution $\p(o_{1:T})$ of the same latent sequence model model in expectation over the data set. Since the latent state sequence is Markovian, for $d\geq 1$ we have the data processing inequality
\begin{gather}
\begin{aligned}
\MI{s_t;s_{t-d}} &\leq \MI{s_t;s_{t-1}} \\
\H{s_t}-\H{s_t|s_{t-d}} &\leq \H{s_t}-\H{s_t|s_{t-1}} \\
\E{}{\ln\p(s_t|s_{t-d})} &\leq \E{}{\ln\p(s_t|s_{t-1})} \\
\E{}{\ln\pr[p_d](o_{1:T})} &\leq \E{}{\ln\p(o_{1:T})}.
\end{aligned}
\label{eq:dataproc_deriv}
\end{gather}
Therefore, any bound on the multi-step predictive distribution, including \cref{eq:dstep_deriv} and \cref{eq:latov}, is also a bound on the one-step predictive distribution.

\clearpage
\section{Additional Related Work}
\label{sec:more_related_work}

\paragraph{Planning in state space}

When low-dimensional states of the environment are available to the agent, it is possible to learn the dynamics directly in state space. In the regime of control tasks with only a few state variables, such as the cart pole and mountain car tasks, PILCO \citep{deisenroth2011pilco} achieves remarkable sample efficiency using Gaussian processes to model the dynamics. Similar approaches using neural networks dynamics models can solve two-link balancing problems \citep{gal2016deeppilco,higuera2018synthesizing} and implement planning via gradients \citep{henaff2018planbybackprop}. \citet{chua2018pets} use ensembles of neural networks, scaling up to the cheetah running task. The limitation of these methods is that they access the low-dimensional Markovian state of the underlying system and sometimes the reward function. \citet{amos2018awareness} train a deterministic model using overshooting in observation space for active exploration with a robotics hand. We move beyond low-dimensional state representations and use a latent dynamics model to solve control tasks from images.

\paragraph{Hybrid agents}

The challenges of model-based RL have motivated the research community to develop hybrid agents that accelerate policy learning by training on imagined experience \citep{kalweit2017blending,nagabandi2017mbmf,kurutach2018modeltrpo,buckman2018steve,ha2018worldmodels}, improving feature representations \citep{wayne2018merlin,igl2018dvrl}, or leveraging the information content of the model directly \citep{weber2017i2a}. \citet{srinivas2018upn} learn a policy network with integrated planning computation using reinforcement learning and without prediction loss, yet require expert demonstrations for training.

\paragraph{Multi-step predictions}

Training sequence models on multi-step predictions has been explored for several years. Scheduled sampling \citep{bengio2015scheduled} changes the rollout distance of the sequence model over the course of training. Hallucinated replay \citep{talvitie2014hallucinated} mixes predictions into the data set to indirectly train multi-step predictions. \citet{venkatraman2015dad} take an imitation learning approach. Recently, \citet{amos2018awareness} train a dynamics model on all multi-step predictions at once. We generalize this idea to latent sequence models trained via variational inference.

\paragraph{Latent sequence models}

Classic work has explored models for non-Markovian observation sequences, including recurrent neural networks (RNNs) with deterministic hidden state and probabilistic state-space models (SSMs). The ideas behind variational autoencoders \citep{kingma2013vae,rezende2014vae} have enabled non-linear SSMs that are trained via variational inference \citep{krishnan2015deepkalman}. The VRNN \citep{chung2015vrnn} combines RNNs and SSMs and is trained via variational inference. In contrast to our RSSM, it feeds generated observations back into the model which makes forward predictions expensive. \citet{karl2016dvbf} address mode collapse to a single future by restricting the transition function, \citep{moerland2017learning} focus on multi-modal transitions, and \citet{doerr2018prssm} stabilize training of purely stochastic models. \citet{buesing2018dssm} propose a model similar to ours but use in a hybrid agent instead for explicit planning.

\paragraph{Video prediction}

Video prediction is an active area of research in deep learning. \citet{oh2015atari} and \citet{chiappa2017recurrent} achieve visually plausible predictions on Atari games using deterministic models. \citet{kalchbrenner2016vpn} introduce an autoregressive video prediction model using gated CNNs and LSTMs. Recent approaches introduce stochasticity to the model to capture multiple futures \citep{babaeizadeh2017sv2p,denton2018stochastic}. To obtain realistic predictions, \citet{mathieu2015deep} and \citet{vondrick2016generating} use adversarial losses. In simulated environments, \citet{gemici2017temporalmemory} augment dynamics models with an external memory to remember long-time contexts. \citet{van2017vq} propose a variational model that avoids sampling using a nearest neighbor look-up, yielding high fidelity image predictions. These models are complimentary to our approach.

\clearpage
\section{Video Predictions}
\label{sec:prediction}
\input{figures/prediction/figure}

\clearpage
\section{State Diagnostics}

\input{figures/diagnostics/figure}

\clearpage
\section{Planning Parameters}

\input{figures/mpc/figure}
