\documentclass[natbib,smallcondensed]{svjour3}
% \documentclass[natbib]{svjour3}
\usepackage[utf8]{inputenc}

\usepackage{subcaption}
\usepackage{graphicx}

% \usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{bbm}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{textcomp}
\newcommand{\numberset}{\mathbb} %
\newcommand{\N}{\numberset{N}}
\newcommand{\Z}{\numberset{Z}}
\newcommand{\Q}{\numberset{Q}}
\newcommand{\R}{\numberset{R}}
\newcommand{\E}{\numberset{E}}
\newcommand{\Pp}{\mathbb{P}}
\newcommand{\Ss}{\mathcal{S}}
\newcommand{\Yy}{\mathcal{Y}}
\newcommand{\Chi}{\mathcal{X}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\One}{\mathbbm{1}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{tikz}
\usepackage{ctable} % for \specialrule command
\usepackage{adjustbox}
\usepackage{bbm}
% \captionsetup[subfigure]{width=0.9\textwidth}
\usepackage[normalem]{ulem}


\usepackage[hidelinks]{hyperref}
\usepackage{mathtools}

% \usepackage{todonotes}
% \newcommand{\dries}[1]{\todo[inline,backgroundcolor=olive!30]{\textbf{Dries:} #1}}
% \newcommand{\driesembed}[1]{\todo[backgroundcolor=olive!30]{\textbf{Dries:} #1}}
% \newcommand{\jesse}[1]{\todo[inline,backgroundcolor=green!30]{\textbf{Jesse:} #1}}
% \newcommand{\jesseembed}[1]{\todo[backgroundcolor=green!30]{\textbf{Jesse:} #1}}
% \newcommand{\jd}[1]{\textcolor{green}{#1}}

% \newcommand{\kilian}[1]{\todo[backgroundcolor=yellow!30]{\textbf{Kilian:} #1}}
% \newcommand{\kilianembed}[1]{\todo[backgroundcolor=yellow!30]{\textbf{Kilian:} #1}}
% \newcommand{\lorenzo}[1]{\todo[inline,backgroundcolor=blue!30]{\textbf{Lorenzo:} #1}}
% \newcommand{\lorenzoembed}[1]{\todo[backgroundcolor=blue!30]{\textbf{Lorenzo:} #1}}
% \newcommand{\wannes}[1]{\todo[inline,backgroundcolor=orange!30]{\textbf{Wannes:} #1}}
% \newcommand{\wannesembed}[1]{\todo[backgroundcolor=orange!30]{\textbf{Wannes:} #1}}

% \newcommand{\ok}[1]{\todo[inline,backgroundcolor=gray!30]{\textbf{Addressed:} #1}}

\newcommand{\changed}[1]{{#1}}
% \newcommand{\change}[1]{\textcolor{green}{#1}}
% \newcommand{\removed}[1]{{\color{red}\sout{#1}}}

\newcommand{\rr}[1]{\text{\textregistered}}

\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
\savestack{\tmpbox}{\stretchto{%
  \scaleto{%
    \scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
    {\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
  }{\textheight}% 
}{0.5ex}}%
\stackon[1pt]{#1}{\tmpbox}%
}

\def\bibsection{\section*{References}}

\usepackage{glossaries}
\newacronym{svdd}{SVDD}{Support Vector Data Descriptor}
\newacronym{svm}{SVM}{Support Vector Machine}
\newacronym{ocsvm}{OCSVM}{One-Class Support Vector Machine}
\newacronym{lof}{LOF}{Local Outlier Factor}
\newacronym{if}{IF}{Isolation Forest}
\newacronym{gmm}{GMM}{Gaussian Mixture Model}
\newacronym{hmm}{HMM}{Hidden Markov Model}
\newacronym{vae}{VAE}{Variational Autoencoders}
\newacronym{knn}{k-NN}{k-Nearest Neighbors}
\newacronym{knno}{k-NNO}{k-Nearest Neighbors Outlier}
\newacronym{som}{SOM}{Self-Organizing Map}
\newacronym{rbfn}{RBFN}{Radial Basis Function Network}
\newacronym{lvq}{LVQ}{Learning Vector Quantization}
\newacronym{smo}{SMO}{Sequential Minimal Optimization}
\newacronym{sgd}{SGD}{Stochastic Gradient Descent}
\newacronym{gpd}{GPD}{Generalized Probabilistic Descent}




\newacronym{roc}{ROC}{Receiver Operating Characteristic}
\newacronym{pr}{PR}{Precision-Recall}
\newacronym{tpr}{TPR}{True Postive Rate}
\newacronym{fpr}{FPR}{False Postive Rate}
\newacronym{arc}{ARC}{Accuracy-Reject Curve}
\newacronym{auc}{AUC}{Area Under the ROC Curve}
\newacronym{aurc}{AURC}{Area Under the ARC Curve}



\begin{document}
\title{Machine Learning with a Reject Option: A survey}
\author{Hendrickx Kilian* \and Perini Lorenzo* \and Van der Plas Dries \and Meert Wannes \and Davis Jesse}
\authorrunning{Hendrickx K., Perini L., et al}

\institute{* These authors contributed equally to this work. \\ 
	\and
K. Hendrickx \at
              Siemens Digital Industries Software, Leuven, Belgium \\
              KU Leuven, Leuven, Belgium \\
              \email{kilian.hendrickx@cs.kuleuven.be}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
          \and
          L. Perini \at
              KU Leuven, Leuven, Belgium \\
              \email{lorenzo.perini@cs.kuleuven.be}           %  \\
          \and
          D. Van der Plas \at
              OSG bv, Natus Medical, Kontich, Belgium \\
              KU Leuven, Leuven, Belgium \\
              University of Antwerp, Antwerp, Belgium \\
              \email{dries.vanderplas@cs.kuleuven.be}           %  \\
          \and
          W. Meert \at
              KU Leuven; Leuven.AI, Leuven, Belgium \\
              \email{wannes.meert@cs.kuleuven.be}           %  \\
          \and
          J. Davis \at
              KU Leuven; Leuven.AI, Leuven, Belgium \\
              \email{jesse.davis@cs.kuleuven.be}           %  \\
              \and
              Corresponding author: Kilian Hendrickx
}

\date{Received: 23 July 2021 / Revised: 27 July 2023 \& 15 February 2024}% / Accepted: date}

\maketitle

\begin{abstract}
Machine learning models always make a prediction, even when it is likely to be inaccurate. This behavior should be avoided in many decision support applications, where mistakes can have severe consequences. Albeit already studied in 1970, machine learning with rejection recently gained interest. This machine learning subfield enables machine learning models to abstain from making a prediction when likely to make a mistake.

This survey aims to provide an overview on machine learning with rejection. We introduce the conditions leading to two types of rejection, ambiguity and novelty rejection, which we carefully formalize. Moreover, we review and categorize strategies to evaluate a model's predictive and rejective quality. Additionally, we define the existing architectures for models with rejection and describe the standard techniques for learning such models. Finally, we provide examples of relevant application domains and show how machine learning with rejection relates to other machine learning research areas. 

\keywords{Machine learning with rejection \and Supervised learning \and Trustworthy machine learning}
% \kilian{Missing keywords?}

% \PACS{PACS code1 \and PACS code2 \and more}
\subclass{68T05 \and 68T02}
% \kilian{68T05: Learning and adaptive systems in artificial intelligence\\
% 68T02: Research exposition (monographs, survey articles) pertaining to computer science, subcategory AI}
\end{abstract}

\tableofcontents
\newpage
\input{a_introduction}
\input{b_preliminaries}
\input{c_metrics}
\input{d_SeparatedRejector}
\input{e_DependentRejector}
\input{f_IntegratedRejector}
\input{g_CombineRejectors}
\input{h_applications}
\input{i_related_areas}
\input{j_conclusions}


\section*{Declarations}

% \kilian{Is the funding up-to-date for Wannes and Jesse?}
\subsection*{Funding}
Kilian Hendrickx and Dries Van der Plas received funding from VLAIO (Flemish Innovation \& Entrepreneurship) through the Baekeland PhD mandates [HBC.2017.0226] (KH) and [HBC.2019.2615] (DV). 
Lorenzo Perini received funding from FWO-Vlaanderen, aspirant grant 1166222N.
Jesse Davis is partially supported by the KU Leuven research funds [C14/17/070]. 
Lorenzo Perini, Jesse Davis and Wannes Meert received funding from the Flemish Government under the ``Onderzoeksprogramma Artifici\"{e}le Intelligentie (AI) Vlaanderen'' programme.

\subsection*{Conflict of interest}
The authors declare that they have no conflict of interest.

\subsection*{Ethics approval}
Not applicable

\subsection*{Consent to participate}
Not applicable

\subsection*{Availability of data and material}
Not applicable

\subsection*{Code availability}
Not applicable

\subsection*{Authors' contributions}
Concept: JD, WM;
Literature Study: KH, LP, DVdP; 
Categorization: KH, LP, DVdP, WM, JD;
Writing - original draft preparation: KH, LP, DVdP;
Writing - review and editing: WM, JD;
Writing - revision: LP, WM, JD, DVdP, KH;
Funding acquisition: WM, JD;
Supervision: WM, JD.


\bibliographystyle{apalike}
% \bibliographystyle{unsrtnat}
%\bibliographystyle{unsrt}
\bibliography{references}


%\input{REVIEWS}

\end{document}