\section{Related Work}

% Our work relates to data memorization, contamination detection methods, and benchmark enhancement. 
% We discuss some of the works related to ours below.

There has been interests in studying how to identify or extract training data from LLMs.
% many works studying data memorization.
% Many works focus on extracting training data from Large Language Models (LLMs). 
These work examine LLMs' memorization from the perspective of data privacy~\citep{carlini2021extracting, pan2020privacy, zanella2020analyzing, balle2022reconstructing} or discuss the boundary between generalization and memorization~\citep{zhang2017understanding, olson2018modern, recht2019imagenet,carlini2023quantifying}, but they do not focus on the context of benchmark contamination.

Some studies on contamination detection methods are conducted as well.
Some are concerned with detecting and filtering web datasets~\citep{dodge2021documenting,xu2017zipporah}, employing traditional detection techniques such as n-gram overlap.
Others explore new detection methods similar to decoding matching without access to training data.
Exchange detection~\citep{oren2023proving} considers the order of test cases within a benchmark, suggesting that if a model remembers the sequence of test cases, it may be contaminated.
% However, since training data are shuffled, this method is unlikely to detect contamination in real-world LLMs, as evidenced by its experimental results.
The min-k prob detection~\citep{shi2023detecting} uses outlier tokens to estimate LLM contamination. 
This method analyzes the token probabilities within an arbitrary text X. If the LLM exhibits excessively high probabilities for some of these tokens, it may indicate that text X has been mixed into the training set.
% This method cannot serve as definitive evidence of contamination and is of no help to model developers in cleaning datasets.

There are also related works on benchmark enhancement through perturbations~\citep{zong2023fool}, which prevents LLMs from memorizing answer patterns.
This method involves making modifications to the question and requires the LLM to output results in a specific format.
% The advantage of perturbations is that it avoids creating new benchmarks.
Another approach is to employ dynamic benchmarks~\citep{kiela2021dynabench,ma2021dynaboard}, using human-in-the-loop evaluations to reduce the risk of benchmark contamination.