\pagebreak
\section*{Previous work}
\label{sec:related}

Developing general-purpose algorithms has long been a goal of reinforcement learning research.
PPO \citep{schulman2017ppo} is one of the most widely used algorithms and is relatively robust but requires large amounts of experience and often yields lower performance than specialized alternatives.
SAC \citep{haarnoja2018sac} is a popular choice for continuous control and leverages experience replay for data-efficiency, but in practice requires tuning, especially for its entropy scale, and struggles under high-dimensional inputs \citep{yarats2019sacae}.
MuZero \citep{schrittwieser2019muzero} plans using a value prediction model and has been applied to board games and Atari, but the authors did not release an implementation and the algorithm contains several complex components, making it challenging to reproduce.
Gato \citep{reed2022gato} fits one large model to expert demonstrations of multiple tasks, but is only applicable when expert data is available.
In comparison, Dreamer masters a diverse range of environments with fixed hyperparameters, does not require expert data, and its implementation is open source.

Minecraft has been a focus of recent research. With MALMO \citep{johnson2016malmo}, Microsoft released a free version of the successful game for research purposes.
MineRL \citep{guss2019minerl} offers several competition environments, which we rely on as the basis for our experiments.
The MineRL competition supports agents in exploring and learning meaningful skills through a diverse human dataset \citep{guss2019minerl}.
Voyager obtains items at a similar depth in the technology tree as Dreamer using API calls to a language model but operates on top of the MineFlayer bot scripting layer that was specifically engineered to the game and exposes high-level actions\citep{wang2023voyager}.
VPT \citep{baker2022vpt} trained an agent to play Minecraft through behavioral cloning based on expert data of keyboard and mouse actions collected by contractors and finetuning using reinforcement learning to obtain diamonds using 720 GPUs for 9 days.
In comparison, Dreamer uses the MineRL competition action space to autonomously learn to collect diamonds from sparse rewards using 1 GPU for 9 days, without human data.
