We develop seven tasks (i.e.\ seven groups of dataset, metric, and LM program) to evaluate LM program optimizers. Table~\ref{tab:optimizer-benchmark} presents our tasks, whose full descriptions, splits, and DSPy program pseudocode are presented in Appendices~\ref{sec:task_desc}, \ref{sec:data_splits} and~\ref{sec:lm-program-appendix}, respectively. We use 500 examples for training, 500 for our development, and a test set of 2k examples (or the full test set if smaller).

As Table~\ref{tab:optimizer-benchmark} shows, we include four multi-stage and two single-stage programs. \textbf{HotPotQA}~\cite{yang-etal-2018-hotpotqa}, in the ``fullwiki'' setting, requires systems to answer factoid questions by retrieving two relevant articles from Wikipedia. We build a program with a module for generating search queries (invoked twice) and another for generating the final answer. This is a canonical test of LM program optimizers, based on~\citealt{khattab2024dspy}. 

We hypothesize that optimizing \textit{free-form instructions} can have the most impact on tasks with \textit{subtle} rules that \textit{cannot be properly inferred through a few examples}. We devise \textbf{HotPotQA Conditional} to test this: we change the answer format accepted from the program depending on whether the answer is a person, a date, a place, etc.

We also include two classical classification tasks: \textbf{Iris} (\citealt{Fisher1936THEUO}; flower classification given six real-numbered features) and \textbf{Heart Disease} (\citealt{Detrano1989InternationalAO}; binary classification given 13 categorical and continuous features). We test Iris in two settings, one with a misspelling in the prompt that may confuse the LM and one corrected.\footnote{The misspelling was initially accidental (asking to classify a flower as ``versicolour'' rather than ``versicolor''). However, it serves as a realistic test for optimization from a misspecified prompt, so we report on both settings. Future work should permit LM programming abstractions to detect such errors.} Iris can be nearly solved with a simple set of rules (not provided to the LM), so we seek to test if LM program optimizers can automatically teach LMs a Chain-of-Thought behavior to also perform well on such tasks. In contrast, it may be harder to find a small number of crucial patterns in Heart Disease, and we thus test a  program that generates three clinical opinions using Chain-of-Thought LM calls and then generates a final judgment accordingly.

To assess whether optimizers can express data-specific nuances that are not evident from the program itself, we use \textbf{ScoNe}~\citep{she-etal-2023-scone}, an entailment task in which LMs must reason about logical puzzles with nested negation. %

Lastly, we evaluate three-hop retrieval over unchecked claims using \textbf{HoVer}~\citep{jiang-etal-2020-hover}. Our LM program alternates three times between generating queries, using them for retrieval from Wikipedia, and using the results to inform future queries. We use HoVer's gold labels for the documents to be retrieved for each input claim to report Retrieval@21 with all top-10 retrieved documents across three hops. 








