\section{Discussion}

% main points to hit on:
% - what we've done: uncovered instances of phase transitions, and designed a benchmark task to help avoid them
%Designers will likely need to take greater care to specify reward functions accurately. Furthermore, the presence of phase transitions implies that even small increases in optimization power could lead to unintended consequences, placing an additional burden on safety.

In this work, we designed a diverse set of environments and proxy rewards, uncovered several instances of phase transitions, and proposed an anomaly detection task to help mitigate these transitions. Our results raise two questions: How can we not only detect phase transitions, but prevent them in the first place? And how should phase transitions shape our approach to safe ML?

On preventing phase transitions, anomaly detection already offers one path forward. Once we can detect anomalies, we can potentially prevent them, by using the detector 
to purge the unwanted behavior (e.g.~by including it in the training objective). Similar policy shaping has recently been used to 
make RL agents more ethical \citep{hendrycks2021would}. However, since the anomaly detectors will be optimized against by the RL policy, they need to be adversarially robust \citep{goodfellow2014explaining}. This motivates further work on adversarial robustness and adversarial anomaly detection. Another possible direction is optimizing policies against a distribution of rewards~\citep{brown2019bayesianrex,javed2021pgbroil}, which may prevent over-fitting to a given set of metrics.

Regarding safe ML, several recent papers propose extrapolating empirical trends to forecast future ML capabilities \citep{kaplan2020scaling,hernandez2021scaling,droppo2021scaling}, partly to avoid unforeseen consequences from ML. While we support this work, our results show that trend extrapolation alone is not enough to ensure the safety of ML systems. To complement trend extrapolation, we need better interpretability methods to identify emergent model behaviors early on, before they dominate performance \citep{olah2018building}. ML researchers should also familiarize themselves with emergent behavior in self-organizing systems \citep{yates2012self}, which often exhibit similar phase transitions \citep{anderson1972more}. Indeed, the ubiquity of phase transitions throughout science suggests that ML researchers should continue to expect surprises--and should therefore prepare for them.

% - many people have suggested studying models via empirical trend extrapolation. these results show this is not enough
% - what can we do if trend extrapolation is not enough? greater interpretability, better understanding of other self-organizing systems, entertain weird thought experiments, 
% - more prosaically, our anomaly detection offers one path forward. what's next after anomaly detection -- want actual mitigation. might need to be adversarially robust