%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

AutoML has utilized a wide array of paradigms, including growing networks neuron-by-neuron \cite{stanley2002evolving}, hyperparameter optimization \cite{snoek2012practical,loshchilov2016cma,jaderberg2017population} and, neural architecture search~\cite{zoph2016neural,real2017large}.  As discussed in Section~\ref{intro_sec}, \aml has targeted many aspects of neural networks individually, using sophisticated coarse-grained building blocks. \citeinline{mei2019atomnas}, on the other hand, perform a fine-grained search over the convolutions of a neural network. Orthogonally, a few studies benefit from extending the search space to two such aspects simultaneously \cite{zela2018towards,miikkulainen2019evolving,noy2019asap}. In our work, we perform a fine-grained search over all aspects of the algorithm. 

An important aspect of an ML algorithm is the optimization of its weights, which has been tackled by \aml in the form of numerically discovered optimizers \cite{chalmers1991evolution,andrychowicz2016learning,vanschoren2018meta}. The output of these methods is a set of coefficients or a neural network that works well but is hard to interpret. These methods are sometimes described as ``learning the learning algorithm''. However, in our work, we understand \textit{algorithm} more broadly, including the structure and initialization of the model, not just the optimizer. Additionally, our algorithm is not discovered numerically but \textit{symbolically}. A symbolically discovered optimizer, like an equation or a computer program, can be easier to interpret or transfer. An early example of a symbolically discovered optimizer is that of \citeinline{bengio1994use}, who optimize a local learning rule for a 4-neuron neural network using genetic programming \cite{holland1975adaptation,forsyth1981beagle,koza1992genetic}. Our search method is similar but represents the program as a sequence of instructions. While they use the basic operations $\{+, -, \times, \div\}$, we allow many more, taking advantage of dense hardware computations. \citet{risi2010indirectly} tackle the discovery of a biologically informed neural network learning rule too, but with a very different encoding. More recently, \citeinline{bello2017neural} also search for a symbolic optimizer, but in a restricted search space of hand-tuned operations (\eg ``apply dropout with 30\% probability'', ``clip at 0.00001'', \etc). Our search space, on the other hand, aims to minimize restrictions and manual design. Unlike these three studies, we do not even assume the existence of a neural network or of gradients.

We note that our work also relates to program synthesis efforts. Early approaches have proposed to search for programs that improve themselves \cite{lenat1983eurisko,schmidhuber1987evolutionary}. We share similar goals in searching for learning algorithms, but focus on common machine learning tasks and have dropped the self-reflexivity requirement. More recently, program synthesis has focused on solving problems like sorting~\cite{graves2014neural}, string manipulation~\cite{gulwani2017program,balog2017deepcoder}, or structured data QA~\cite{Liang2016NeuralSM}. Unlike these studies, we focus on synthesizing programs that solve the problem of \textit{doing} ML. 

Suppl.\ Section~\ref{additional_related_work} contains additional related work.