%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Supplementary Material %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% All citations in the supplement should also be here.
% This is so they are still printed in the bibliography when we don't print the supplement.
\nocite{fahlman1990cascade,angeline1994evolutionary,yao1999evolving,stanley2002evolving,bergstra2012random,mendoza2016towards,baker2016designing,zoph2016neural,real2017large,xie2017genetic,suganuma2017genetic,liu2017progressive}
\nocite{liu2018darts,elsken2018efficient,cai2018proxylessnas,liu2019auto,ghiasi2019fpn,sun2019evolving,xie2019exploring}
\nocite{elsken2019neural,stanley2019designing,yao2018taking}
\nocite{zoph2017learning,zhong2018practical}
\nocite{mei2019atomnas}
\nocite{snoek2012practical,loshchilov2016cma,jaderberg2017population,li2017hyperband}
\nocite{ramachandran2017searching}
\nocite{kim2015deep}
\nocite{gaier2019weight}
\nocite{cubuk2018autoaugment,park2019specaugment,cubuk2019randaugment}
\nocite{miikkulainen2019evolving}
\nocite{zela2018towards}
\nocite{noy2019asap}
\nocite{chalmers1991evolution}
\nocite{runarsson2000evolution, orchard2016evolution}
\nocite{ravi2016optimization}
\nocite{wichrowska2017learned}
\nocite{metz2019meta}
\nocite{andrychowicz2016learning}
\nocite{li2017learning}
\nocite{risi2010indirectly}
\nocite{vanschoren2018meta}
\nocite{bengio1994use}
\nocite{koza1992genetic}
\nocite{bengio1994use}
\nocite{bello2017neural}
\nocite{bengio1994use}
\nocite{bello2017neural}
\nocite{lenat1983eurisko,schmidhuber1987evolutionary,pitrat1996implementation}
\nocite{schmidhuber2004optimal,graves2014neural,Reed2015NeuralP,Valkov2018HOUDINILL}
\nocite{Polozov2015FlashMetaAF,Parisotto2016NeuroSymbolicPS,Devlin2017RobustFillNP}
\nocite{lake2015human}
\nocite{balog2017deepcoder}
\nocite{Neelakantan2015NeuralPI,Liang2016NeuralSM,Liang2018MemoryAP}
\nocite{chen2017towards}
\nocite{wilson2018evolving}
\nocite{gulwani2017program}
\nocite{real2018regularized}
\nocite{alba2002parallelism}
\nocite{lecun1998mnist}
\nocite{So2019TheET}

\supplheader{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Additional Related Work}{additional_related_work}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Because our approach simultaneously searches all the aspects of an ML algorithm, it relates to previous work that targets each aspect individually. As there are many such aspects (\eg architecture, hyperparameters, learning rule), previous work is extensive and impossible to exhaustively list here. Many examples belong within the field of \textit{\aml}. A frequently targeted aspect of the ML algorithm is the structure of the model; this is known as \textit{architecture search}. It has a long history \citewithcomments{}{fahlman1990cascade,angeline1994evolutionary,yao1999evolving,stanley2002evolving,bergstra2012random,mendoza2016towards,baker2016designing,zoph2016neural,real2017large,xie2017genetic,suganuma2017genetic,liu2017progressive}{, and many others} and continues today \citewithcomments{}{liu2018darts,elsken2018efficient,cai2018proxylessnas,liu2019auto,ghiasi2019fpn,sun2019evolving,xie2019exploring}{, and many others}. Reviews provide more thorough background \cite{elsken2019neural,stanley2019designing,yao2018taking}. Recent works have obtained accurate models by constraining the space to only look for the structure of a block that is then stacked to form a neural network. The stacking is fixed and the block is free to combine standard neural network layers into patterns that optimize the accuracy of the model \cite{zoph2017learning,zhong2018practical}. \citeinline{mei2019atomnas} highlight the importance of finer-grained search spaces and take a step in that direction by splitting convolutions into channels that can be handled separately. Other specific architecture aspects have also been targeted, such as the hyperparameters \cite{snoek2012practical,loshchilov2016cma,jaderberg2017population,li2017hyperband}, activation functions \cite{ramachandran2017searching}, a specific layer \cite{kim2015deep}, the full forward pass \cite{gaier2019weight}, the data augmentation \cite{cubuk2018autoaugment,park2019specaugment,cubuk2019randaugment}, \etc. Beyond these narrowly targeted search spaces, \textit{more} inclusive spaces are already demonstrating promise. For example, a few studies have combined two seemingly disparate algorithmic aspects into a single search space: the inner modules and the outer structure \cite{miikkulainen2019evolving}, the architecture and the hyperparameters \cite{zela2018towards}, the layers and the weight pruning \cite{noy2019asap}, and so on. We extend this to all aspects of the algorithm, including the optimization.

An important aspect of an ML algorithm is optimization, which has been tackled by \aml in the form of numerically discovered optimizers. \citeinline{chalmers1991evolution} formalizes the update rule for the weights as \mbox{$w_{i, j} \leftarrow w_{i, j} + F(x_1, x_2, ...)$}, where $x_i$ are local signals and $F$ combines them linearly. The coefficients of the linear combination constitute the search space and are encoded as a bit string that is searched with a genetic algorithm. This is an example of a \textit{numerically learned} update rule: the final result is a set of coefficients that work very well but may not be interpretable. Numerically learned optimizers have improved since then. Studies found that Chalmers' $F$ formula above can be replaced with more advanced structures, such as a second neural network \cite{runarsson2000evolution, orchard2016evolution}, an LSTM \cite{ravi2016optimization}, a hierarchical RNN \cite{wichrowska2017learned}, or even a different LSTM for each weight \cite{metz2019meta}. Numerically or otherwise, some studies center on the method by which the optimizer is learned; it can vary widely from the use of gradient descent \cite{andrychowicz2016learning}, to reinforcement learning \cite{li2017learning}, to evolutionary search with sophisticated developmental encodings \cite{risi2010indirectly}. All these methods are sometimes collectively labeled as \textit{meta-learning} \cite{vanschoren2018meta} or described as ``learning the learning algorithm'', as the optimizer is indeed an algorithm. However, in this work, we understand \textit{algorithm} more broadly and it will include also the structure and the initialization of the model. Additionally, our algorithm is not learned numerically, but discovered \textit{symbolically}. A symbolically discovered optimizer, like an equation or a computer program, can be easier to interpret or transfer.

An early example of a symbolically discovered optimizer is that of \citeinline{bengio1994use}, who represent $F$ as a tree: the leaves are the possible inputs to the optimizer (\ie the $x_i$ above) and the nodes are one of $\{+, -, \times, \div\}$. $F$ is then evolved, making this an example of \textit{genetic programming} \cite{holland1975adaptation,forsyth1981beagle,koza1992genetic}. Our search method is similar to genetic programming but we choose to represent the program as a sequence of instructions---like a programmer would type it---rather than a tree. Another similarity with \citeinline{bengio1994use} is that they also use simple mathematical operations as building blocks. We use many more, however, including vector and matrix instructions that take advantage of dense hardware computations. More recently, \citeinline{bello2017neural} revisited symbolically learned optimizers to apply them to a modern neural network. Their goal was to maximize the final accuracy of their models and so they restrict the search space by allowing hand-tuned operations (\eg ``apply dropout with 30\% probability'', ``clip at 0.00001'', \etc). Our
search space, on the other hand, aims to minimize restrictions and manual design. Both \citeinline{bengio1994use} and \citeinline{bello2017neural} assume the existence of a neural network with a forward pass that computes the activations and a backward pass that provides the weight gradients. Thus, the search process can just focus on discovering how to use these activations and gradients to adjust the network's weights. In contrast, we do not assume the existence of a neural network model or of the gradient. They must therefore be discovered in the same way as the rest of the algorithm.

We note that our work also relates to program synthesis efforts. Early approaches have proposed to search for programs that improve themselves \cite{lenat1983eurisko,schmidhuber1987evolutionary,pitrat1996implementation}. We share similar goals in searching for learning algorithms, but focus on common machine learning tasks and have dropped the self-reflexivity requirement. More recently, program synthesis has focused on solving problems like sorting, addition, counting \cite{schmidhuber2004optimal,graves2014neural,Reed2015NeuralP,Valkov2018HOUDINILL}, string manipulations \cite{Polozov2015FlashMetaAF,Parisotto2016NeuroSymbolicPS,Devlin2017RobustFillNP}, character recognition \cite{lake2015human}, competition-style programming \cite{balog2017deepcoder}, structured data QA \cite{Neelakantan2015NeuralPI,Liang2016NeuralSM,Liang2018MemoryAP}, program parsing \cite{chen2017towards}, and game playing \cite{wilson2018evolving}, to name a few. These studies are increasingly making more \textit{use} of ML to solved the said problems \cite{gulwani2017program}. Unlike these studies, we focus on synthesizing programs that solve the problem of \textit{doing} ML.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Search Space Additional Details}{search_space_additional_details}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Supplementary Table~\ref{ops_table} describes all the ops in our search space. They are ordered to reflect how we chose them: we imagined a typical school curriculum up to---but not including---calculus (see braces to the right of the table).
In particular, there are no derivatives so any gradient computation used for training must be evolved.

\createlength{\rowsep}{3pt}
\def\sepforall{\ \ \forall}
\begin{table*}[!b]
\caption{Ops vocabulary. $s$, $\vec{v}$ and $M$ denote a scalar, vector, and matrix, resp. Early-alphabet letters ($a$, $b$, \etc) denote memory addresses. Mid-alphabet letters (\eg $i$, $j$, \etc) denote vector/matrix indexes (``Index'' column). Greek letters denote constants (``Consts.'' column). $\mathcal{U}(\alpha,\beta)$ denotes a sample from a uniform distribution in $[\alpha,\beta]$. $\mathcal{N}(\mu,\sigma)$ is analogous for a normal distribution with mean $\mu$ and standard deviation $\sigma$. $\mathbbm{1}_X$ is the indicator function for set $X$. Example: ``$M_a^{(i,j)} = \mathcal{U}(\alpha,\beta)$'' describes the operation ``assign to the $i$,$j$-th entry of the matrix at address $a$ a value sampled from a uniform random distribution in $[\alpha,\beta]$''.}
\label{ops_table}
\begin{center}
\begin{small}
\begin{tabular}{p{0.3in}|
                >{\centering\arraybackslash}p{1.3in}|
                >{\centering\arraybackslash}p{0.7in} >{\centering\arraybackslash}p{0.33in}|
                >{\centering\arraybackslash}p{0.5in} >{\centering\arraybackslash}p{0.26in}|
                >{\centering\arraybackslash}p{1.98in}l}
\cmidrule(r{8pt}){1-7}
Op & Code    & \multicolumn{2}{c|}{Input Args} & \multicolumn{2}{c|}{Output Args} & Description   & \\
ID & Example & Addresses & Consts.       & Address    & Index                     & (see caption) & \\
  &          & / types   &               & / type     &                           &               & \\
\cmidrule(r{8pt}){1-7}
OP0 & \textcode{no\_op} & -- & -- & -- & -- & -- & \\[\rowsep]
% Arithmetic 
OP1 & \textcode{s2=s3+s0} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = s_a + s_b$ &
\hspace{-15pt} \rdelim\}{7.5}{3pt} \hspace{6pt} \multirow{7.5}{*}{\rotatebox[origin=c]{-90}{Arithmetic}} \\[\rowsep]
OP2 & \textcode{s4=s0-s1} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = s_a - s_b$ & \\[\rowsep]
OP3 & \textcode{s8=s5*s5} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = s_a \, s_b$ & \\[\rowsep]
OP4 & \textcode{s7=s5/s2} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = s_a / s_b$ & \\[\rowsep]
OP5 & \textcode{s8=abs(s0)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = |s_a|$ & \\[\rowsep]
OP6 & \textcode{s4=1/s8} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = 1/s_a$ & \\[\rowsep]
% Trigonometry
OP7 & \textcode{s5=sin(s4)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \sin(s_a)$ &
\hspace{-15pt} \rdelim\}{7.5}{3pt} \hspace{6pt} \multirow{7.5}{*}{\rotatebox[origin=c]{-90}{Trigonometry}} \\[\rowsep]
OP8& \textcode{s1=cos(s4)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \cos(s_a)$ & \\[\rowsep]
OP9 & \textcode{s3=tan(s3)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \tan(s_a)$ & \\[\rowsep]
OP10 & \textcode{s0=arcsin(s4)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \arcsin(s_a)$ & \\[\rowsep]
OP11 & \textcode{s2=arccos(s0)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \arccos(s_a)$ & \\[\rowsep]
OP12 & \textcode{s4=arctan(s0)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \arctan(s_a)$ & \\[\rowsep]
% Pre-Calculus 
OP13 & \textcode{s1=exp(s2)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = e^{s_a}$ &
\hspace{-15pt} \rdelim\}{6.5}{3pt} \hspace{6pt} \multirow{6.5}{*}{\rotatebox[origin=c]{-90}{Pre-Calculus}} \\[\rowsep]
OP14 & \textcode{s0=log(s3)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \operatorname{log}{s_a}$ & \\[\rowsep]
OP15 & \textcode{s3=heaviside(s0)} & $a$ / scalar & -- & $b$ / scalar & -- & $s_b = \mathbbm{1}_{\mathbb{R}^+}(s_a)$ & \\[\rowsep]
OP16 & \textcode{v2=heaviside(v2)} & $a$ / vector & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = \mathbbm{1}_{\mathbb{R}^+}(\vec{v}_a^{\,(i)}) \sepforall i$ & \\[\rowsep]
OP17 & \textcode{m7=heaviside(m3)} & $a$ / matrix & -- & $b$ / matrix & -- & $M_b^{(i,j)} = \mathbbm{1}_{\mathbb{R}^+}(M_a^{(i,j)}) \sepforall i,j$ & \\[\rowsep]
OP18 & \textcode{v1=s7*v1} & $a$,$b$ / sc,vec & -- & $c$ / vector & -- & $\vec{v}_c = s_a \, \vec{v}_b$ &
% Linear algebra.
\hspace{-15pt} \rdelim\}{8.1}{3pt} \hspace{6pt} \multirow{8.1}{*}{\rotatebox[origin=c]{-90}{Linear Algebra}} \\[\rowsep]
OP19 & \textcode{v1=bcast(s3)} & $a$ / scalar & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = s_a \ \ \sepforall i$ & \\[\rowsep]
OP20 & \textcode{v5=1/v7} & $a$ / vector & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = 1/\vec{v}_a^{\,(i)} \ \ \sepforall i$ & \\[\rowsep]
OP21 & \textcode{s0=norm(v3)} & $a$ / scalar & -- & $b$ / vector & -- & $s_b = |\vec{v}_a|$ & \\[\rowsep]
OP22 & \textcode{v3=abs(v3)} & $a$ / vector & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = |\vec{v}_a^{\,(i)}| \ \ \sepforall i$ & \\[\rowsep]
\multicolumn{7}{c}{\dotfill [Table continues on the next page.] \dotfill}\\
\end{tabular}
\end{small}
\end{center}
\end{table*}

\addtocounter{table}{-1}
\begin{table*}[!t]
\vspace*{20pt}
\caption{Ops vocabulary (continued)}
\begin{center}
\begin{small}
\begin{tabular}{p{0.3in}|
                >{\centering\arraybackslash}p{1.3in}|
                >{\centering\arraybackslash}p{0.7in} >{\centering\arraybackslash}p{0.33in}|
                >{\centering\arraybackslash}p{0.5in} >{\centering\arraybackslash}p{0.26in}|
                >{\centering\arraybackslash}p{1.98in}l}
\cmidrule(r{8pt}){1-7}
Op & Code    & \multicolumn{2}{c|}{Input Args} & \multicolumn{2}{c|}{Output Args} & Description   & \\
ID & Example & Addresses & Consts       & Address    & Index                     & (see caption) & \\
  &          & / types   &              & / type     &                           &               & \\
\cmidrule(r{8pt}){1-7}
% Linear Algebra (continued)
OP23 & \textcode{v5=v0+v9} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c = \vec{v}_a + \vec{v}_b$ &
\hspace{-15pt} \rdelim\}{29}{3pt} \hspace{6pt} \multirow{29}{*}{\rotatebox[origin=c]{-90}{Linear Algebra}} \\[\rowsep]
OP24 & \textcode{v1=v0-v9} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c = \vec{v}_a - \vec{v}_b$ & \\[\rowsep]
OP25 & \textcode{v8=v1*v9} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c^{\,(i)} = \vec{v}_a^{\,(i)} \, \vec{v}_b^{\,(i)} \sepforall i$ & \\[\rowsep]
OP26 & \textcode{v9=v8/v2} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c^{\,(i)} = \vec{v}_a^{\,(i)} / \vec{v}_b^{\,(i)} \sepforall i$ & \\[\rowsep]
OP27 & \textcode{s6=dot(v1,v5)} & $a$,$b$ / vectors & -- & $c$ / scalar & -- & $s_c=\vec{v}_a^{\,T} \, \vec{v}_b$ & \\[\rowsep]
OP28 & \textcode{m1=outer(v6,v5)} & $a$,$b$ / vectors & -- & $c$ / matrix & -- & $M_c=\vec{v}_a \, \vec{v}_b^{\,T}$ & \\[\rowsep]
OP29 & \textcode{m1=s4*m2} & $a$,$b$ / sc/mat & -- & $c$ / matrix & -- & $M_c=s_a \, M_b$ & \\[\rowsep]
OP30 & \textcode{m3=1/m0} & $a$ / matrix & -- & $b$ / matrix & -- & $M_b^{(i,j)}=1/M_a^{(i,j)} \sepforall i,j$ & \\[\rowsep]
OP31 & \textcode{v6=dot(m1,v0)} & $a$,$b$ / mat/vec & -- & $c$ / vector & -- & $\vec{v}_c = M_a \, \vec{v}_b$ & \\[\rowsep]
OP32 & \textcode{m2=bcast(v0,axis=0)} & $a$ / vector & -- & $b$ / matrix & -- & $M_b^{(i,j)} = \vec{v}_a^{\,(i)} \sepforall i,j$ & \\[\rowsep]
OP33 & \textcode{m2=bcast(v0,axis=1)} & $a$ / vector & -- & $b$ / matrix & -- & $M_b^{(j,i)} = \vec{v}_a^{\,(i)} \sepforall i,j$ & \\[\rowsep]
OP34 & \textcode{s2=norm(m1)} & $a$ / matrix & -- & $b$ / scalar & -- & $s_b = ||M_a||$ & \\[\rowsep]
OP35 & \textcode{v4=norm(m7,axis=0)} & $a$ / matrix & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = |M_a^{(i,\cdot)}| \sepforall i$ & \\[\rowsep]
OP36 & \textcode{v4=norm(m7,axis=1)} & $a$ / matrix & -- & $b$ / vector & -- & $\vec{v}_b^{\,(j)} = |M_a^{(\cdot,j)}| \sepforall j$ & \\[\rowsep]
OP37 & \textcode{m9=transpose(m3)} & $a$ / matrix & -- & $b$ / matrix & -- & $M_b = |M_a^T|$ & \\[\rowsep]
OP38 & \textcode{m1=abs(m8)} & $a$ / matrix & -- & $b$ / matrix & -- & $M_b^{(i,j)} = |M_a^{(i,j)}| \sepforall i,j$ & \\[\rowsep]
OP39 & \textcode{m2=m2+m0} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c = M_a + M_b$ & \\[\rowsep]
OP40 & \textcode{m2=m3+m1} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c = M_a - M_b$ & \\[\rowsep]
OP41 & \textcode{m3=m2*m3} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c^{(i,j)} = M_a^{(i,j)} \, M_b^{(i,j)} \sepforall i,j$ & \\[\rowsep]
OP42 & \textcode{m4=m2/m4} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c^{(i,j)} = M_a^{(i,j)} / M_b^{(i,j)} \sepforall i,j$ & \\[\rowsep]
OP43 & \textcode{m5=matmul(m5,m7)} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c = M_a \, M_b$ & \\[\rowsep]
% Probability and Statistics
OP44 & \textcode{s1=minimum(s2,s3)} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = \min(s_a, s_b)$ &
\hspace{-15pt} \rdelim\}{25}{3pt} \hspace{6pt} \multirow{25}{*}{\rotatebox[origin=c]{-90}{Probability and Statistics}} \\[\rowsep]
OP45 & \textcode{v4=minimum(v3,v9)} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c^{\,(i)} = \min(\vec{v}_a^{\,(i)}, \vec{v}_b^{\,(i)}) \sepforall i$ & \\[\rowsep]
OP46 & \textcode{m2=minimum(m2,m1)} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c^{(i,j)} = \min(M_a^{(i,j)}, M_b^{(i,j)}) \sepforall i,j$ & \\[\rowsep]
OP47 & \textcode{s8=maximum(s3,s0)} & $a$,$b$ / scalars & -- & $c$ / scalar & -- & $s_c = \max(s_a, s_b)$ & \\[\rowsep]
OP48 & \textcode{v7=maximum(v3,v6)} & $a$,$b$ / vectors & -- & $c$ / vector & -- & $\vec{v}_c^{\,(i)} = \max(\vec{v}_a^{\,(i)}, \vec{v}_b^{\,(i)}) \sepforall i$ & \\[\rowsep]
OP49 & \textcode{m7=maximum(m1,m0)} & $a$,$b$ / matrixes & -- & $c$ / matrix & -- & $M_c^{(i,j)} = \max(M_a^{(i,j)}, M_b^{(i,j)}) \sepforall i,j$ & \\[\rowsep]
OP50 & \textcode{s2=mean(v2)} & $a$ / vector & -- & $b$ / scalar & -- & $s_b = \operatorname{mean}(\vec{v}_a)$ & \\[\rowsep]
OP51 & \textcode{s2=mean(m8)} & $a$ / matrix & -- & $b$ / scalar & -- & $s_b = \operatorname{mean}(M_a)$ & \\[\rowsep]
OP52 & \textcode{v1=mean(m2,axis=0)} & $a$ / matrix & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = \operatorname{mean}(M_a^{(i,\cdot)}) \sepforall i$ & \\[\rowsep]
OP53 & \textcode{v3=std(m2,axis=0)} & $a$ / matrix & -- & $b$ / vector & -- & $\vec{v}_b^{\,(i)} = \operatorname{stdev}(M_a^{(i,\cdot)}) \sepforall i$ & \\[\rowsep]
OP54 & \textcode{s3=std(v3)} & $a$ / vector & -- & $b$ / scalar & -- & $s_b = \operatorname{stdev}(\vec{v}_a)$ & \\[\rowsep]
OP55 & \textcode{s4=std(m0)} & $a$ / matrix & -- & $b$ / scalar & -- & $s_b = \operatorname{stdev}(M_a)$ & \\[\rowsep]
OP56 & \textcode{s2=0.1} & -- & $\gamma$ & $a$ / scalar & -- & $s_a = \gamma$ & \\[\rowsep]
OP57 & \textcode{v3[5]=-2.4} & -- & $\gamma$ & $a$ / vector & $i$ & $\vec{v}_a^{\,(i)} = \gamma$ & \\[\rowsep]
OP58 & \textcode{m2[5,1]=-0.03} & -- & $\gamma$ & $a$ / matrix & $i$, $j$ & $M_a^{(i,j)} = \gamma$ & \\[\rowsep]
OP59 & \textcode{s4=uniform(-1,1)} & -- & $\alpha$, $\beta$ & $a$ / scalar & -- & $s_a = \mathcal{U}(\alpha,\beta)$ & \\[\rowsep]
OP60 & \textcode{v1=uniform(0.4,0.8)} & -- & $\alpha$, $\beta$ & $a$ / vector & -- & $\vec{v}_a^{\,(i)} = \mathcal{U}(\alpha,\beta) \sepforall i$ & \\[\rowsep]
\multicolumn{7}{c}{\dotfill [Table continues on the next page.] \dotfill}\\
\end{tabular}
\end{small}
\end{center}
\end{table*}

\addtocounter{table}{-1}
\begin{table*}[!t]
\caption{Ops vocabulary (continued)}
\begin{center}
\begin{small}
\begin{tabular}{p{0.3in}|
                >{\centering\arraybackslash}p{1.3in}|
                >{\centering\arraybackslash}p{0.7in} >{\centering\arraybackslash}p{0.33in}|
                >{\centering\arraybackslash}p{0.5in} >{\centering\arraybackslash}p{0.26in}|
                >{\centering\arraybackslash}p{1.98in}l}
\cmidrule(r{8pt}){1-7}
Op & Code    & \multicolumn{2}{c|}{Input Args} & \multicolumn{2}{c|}{Output Args} & Description   & \\
ID & Example & Addresses & Consts       & Address    & Index                     & (see caption) & \\
  &          & / types   &              & / type     &                           &               & \\
\cmidrule(r{8pt}){1-7}
OP61 & \textcode{m0=uniform(-0.5,0.6)} & -- & $\alpha$, $\beta$ & $a$ / matrix & -- & $M_a^{(i,j)} = \mathcal{U}(\alpha,\beta) \sepforall i,j$ &
\hspace{-15pt} \rdelim\}{5.4}{3pt} \hspace{6pt} \multirow{5.4}{*}{\rotatebox[origin=c]{-90}{Prob.\ and Stats.}} \\[\rowsep]
OP62 & \textcode{s4=gaussian(0.1,0.7)} & -- & $\mu$, $\sigma$ & $a$ / scalar & -- & $s_a = \mathcal{N}(\mu,\sigma)$ & \\[\rowsep]
OP63 & \textcode{v8=gaussian(0.4,1)} & -- & $\mu$, $\sigma$ & $a$ / vector & -- & $\vec{v}_a^{\,(i)} = \mathcal{N}(\mu,\sigma) \sepforall i$ & \\[\rowsep]
OP64 & \textcode{m2=gaussian(-2,1.3)} & -- & $\mu$, $\sigma$ & $a$ / matrix & -- & $M_a^{(i,j)} = \mathcal{N}(\mu,\sigma) \sepforall i,j$ \\[\rowsep]
\cmidrule(r{8pt}){1-7}
\end{tabular}
\end{small}
\end{center}
\end{table*}

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Search Method Additional Details}{detailed_methods_optimization_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The mutations that produce the child from the parent must be tailored to the search space. We use a uniformly random choice among the following three transformations: (i) add or remove an instruction; instructions are added at a random position and have a random op and random arguments; to prevent programs from growing unnecessarily, instruction removal is twice as likely as addition; (ii) completely randomize all instructions in a component function by randomizing all their ops and arguments; or (iii) modify a randomly chosen argument of a randomly selected existing instruction. All categorical random choices are uniform. When modifying a real-valued constant, we multiply it by a uniform random number in $[0.5,2.0]$ and flip its sign with $10\%$ probability.

We upgrade the regularized evolution search method \cite{real2018regularized} to improve its performance in the following ways. These upgrades are justified empirically through ablation studies in Supplementary Section~\ref{ablation_comparison_thorough_sec}.

\textbf{Functional Equivalence Checking (FEC)}. The lack of heavy design of the search space allows for mutations that do not have an effect on the accuracy (\eg adding an instruction that writes to an address that is never read). When these mutations occur, the child algorithm behaves identically to its parent. To prevent these identically functioning algorithms from being repeatedly evaluated (\ie trained and validated in full many times), we keep an LRU cache mapping evaluated algorithm fingerprints to their accuracies. Before evaluating an algorithm, we first quickly fingerprint it and consult the cache to see if it has already been evaluated. If it has, we reuse the stored accuracy instead of computing it again. This way, we can keep the different implementations of the same algorithm for the sake of diversity: even though they produce the same accuracy now, they may behave differently upon further mutation.

To fingerprint an algorithm, we train it for 10 steps and validate it on 10 examples. The 20 resulting predictions are then truncated and hashed to produce an integer fingerprint. The cache holds $100\textrm{k}$ fingerprint--accuracy pairs.

\textbf{Parallelism}. In multi-process experiments, each process runs regularized evolution on its own population and the worker processes exchange algorithms through migration \cite{alba2002parallelism}. Every $100$--$10000$ evaluations, each worker uploads $50$ algorithms (half the population) to a central server. The server replies with $50$ algorithms sampled randomly across \textit{all} workers that are substituted into the worker's population.

\textbf{Dataset Diversity}. While the final evaluations are on binary CIFAR-10, in the experiments in Sections~\ref{main_result_sec} and~\ref{zoo_sec}, $50\%$ of the workers train and evaluate on binary MNIST instead of CIFAR-10. MNIST is a dataset of labeled hand-written digits \cite{lecun1998mnist}. We project MNIST to 256 dimensions in the same way we do for CIFAR-10. Supplementary Section~\ref{ablation_comparison_thorough_sec} demonstrates how searching on multiple MNIST-based and CIFAR-based tasks improves final performance on CIFAR-10, relative to searching only on multiple MNIST-based tasks or only on multiple CIFAR-based tasks.

\textbf{Hurdles}. We adopt the \textit{hurdles} upgrade to the evolutionary algorithm. This upgrade uses statistics of the population to early-stop the training of low performing models \cite{So2019TheET}. The early-stopping criterion is the failure to reach a minimum accuracy---the \emph{hurdle}. We alter the original implementation by setting the hurdle to the $75^{th}$ percentile of unique accuracies of the evolving population on a rolling basis (as opposed to the stationary value used in the original implementation). This alteration gives us more predictability over the resource savings: we consistently save $75\%$ of our compute, regardless of how the accuracy distribution shifts over the course of the search experiment.

\textbf{Terminating Degenerate Algorithms}. We terminate algorithms early if their calculations produce $\operatorname{NaN}$ or $\operatorname{Inf}$ values, and assign them a fixed minimum accuracy $a_{min}$ (we use $a_{min}\!\!=\!0$). Similarly, if an algorithm's error on any training example exceeds a threshold $e_{max}\!\!\gg\!\!1$ (we use $e_{max}\!\!=\!\!100$), we also stop that algorithm and assign it the accuracy $a_{min}$. Lastly, we time each algorithm as it is being executed and terminate it if its run-time exceeds a fixed threshold; we set this threshold to 4x the run-time of a plain neural network trained with gradient descent.

The experiment's meta-parameters (\eg $P$ and $T$) were either decided in smaller experiments (\eg $P$), taken from previous work (\eg $T$), or not tuned. Even when tuning parameters in smaller experiments, this was not done extensively (\eg no multi-parameter grid searches); typically, we tried a handful of values independently when each feature was introduced. For each experiment, we scaled---without tuning---some meta-parameters based on compute or hardware limitations. For example, compute-heavy tasks use smaller populations in order to save frequent checkpoints in case of machine reboots. Additional discrepancies between experiment configurations in the different sections are due to different researchers working independently.

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Task Generation Details}{task_details_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Sections~\ref{main_result_sec} and~\ref{zoo_sec} employ many binary classification tasks grouped into two sets, $\mathcal{T}_{search}$ and $\mathcal{T}_{select}$. We now describe how these tasks are generated. We construct a binary classification task by randomly selecting a pair of classes from CIFAR-10 to yield positive and negative examples. We then create a random projection matrix by drawing from a Gaussian distribution with zero mean and unit variance. We use the matrix to project the features of all the examples corresponding to the class pair to a lower dimension (\ie from the original 3072 to, for example, 16). The projected features are then standardized. This generates a proxy task that requires much less compute than the non-projected version. Each class pair and random projection matrix produce a different task. Since CIFAR-10 has 10 classes, there are 45 different pairs. For each pair we perform 100 different projections. This way we end up with 4500 tasks, each containing 8000/2000 training/validation examples. We use all the tasks from 36 of the pairs to form the $\mathcal{T}_{search}$ task set. The remaining tasks form $\mathcal{T}_{select}$.

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Detailed Search Experiment Setups}{detailed_experiment_setups_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we present details and method meta-parameters for experiments referenced in Section~\ref{results_sec}. These complement the ``Experiment Details'' paragraphs in the main text.

\textbf{Experiments in Section~\ref{difficulty_sec}, Figure~\ref{relative_difficulty_fig}}: Scalar/vector/matrix number of addresses: 4/3/1 (linear), 5/3/1 (affine). Fixed num.\ instructions for \setup/\predict/\learn: 5/1/4 (linear), 6/2/6 (affine). Expts.\ in this figure allow only minimal ops to discover a known algorithm, as follows. For ``linear backprop'' expts.: allowed \learn ops are \{OP3, OP4, OP19, OP24\}. For ``linear regressor'' expts.: allowed \setup ops are \{OP56, OP57\}, allowed predict ops are \{OP27\}, and allowed \learn ops are \{OP2, OP3, OP18, OP23\}. For ``affine backprop'' expts.: allowed \learn ops are \{OP1, OP2, OP3, OP18, OP23\}. For ``affine regressor'' expts.: allowed \setup ops are \{OP56, OP57\}, allowed \predict ops are \{OP1, OP27\}, and allowed \learn ops are \{OP1, OP2, OP3, OP18, OP23\}. 1 process, no server. Tasks: see \textit{Experiment Details} paragraph in main text. Evolution expts.: $P\!\!=\!\!1000$; $T\!\!=\!\!10$; $U\!\!=\!\!0.9$; we initialize the population with random programs; evals.\ per expt. for points in plot (left to right): $10\textrm{k}$, $10\textrm{k}$, $10\textrm{k}$, $100\textrm{k}$ (optimized for each problem difficulty to nearest factor of 10). Random search expts.: same num. memory addresses, same component function sizes, same total number of evaluations. These experiments are intended to be as simple as possible, so we do not use hurdles or additional data.

\textbf{Experiment in Section~\ref{difficulty_sec}, Figure~\ref{nn_fig}}: Scalar/vector/matrix number of addresses: 4/8/2. Fixed num.\ instructions for \setup/\predict/\learn: 21/3/9. In this figure, we only allow as ops those that appear in a two-layer neural network with gradient descent: allowed \setup ops are \{OP56, OP63, OP64\}, allowed \predict ops are \{OP27, OP31, OP48\}, and allowed \learn ops are \{OP2, OP3, OP16, OP18, OP23, OP25, OP28, OP40\}. Tasks: see \textit{Experiment Details} paragraph in main text. $P\!\!=\!\!1000$. $T\!\!=\!\!10$. $U\!\!=\!\!0.9$. $W\!\!=\!\!1\textrm{\normalfont{k}}$. Worker processes are uniformly divided into 4 groups, using parameters $T$/$D$/$P$ covering ranges in a log scale, as follows: $100\textrm{\normalfont{k}}$/$100$/$100$, $100\textrm{\normalfont{k}}$/$22$/$215$, $10\textrm{\normalfont{k}}$/$5$/$464$, and $100$/$1$/$1000$. Uses FEC. We initialize the population with random programs.

\textbf{Experiments in Section~\ref{main_result_sec}}: Scalar/vector/matrix number of addresses: 8/14/3. Maximum num.\ instructions for \setup/\predict/\learn: 21/21/45. All the initialization ops are now allowed for \setup: \{OP56, OP57, OP58, OP59, OP60, OP61, OP62, OP63, OP64\}. \predict and \learn use a longer list of 58 allowed ops: \{OP0, OP1, OP2, OP3, OP4, OP5, OP6, OP7, OP8, OP9, OP10, OP11, OP12, OP13, OP14, OP15, OP16, OP17, OP18, OP19, OP20, OP21, OP22, OP23, OP24, OP25, OP26, OP27, OP28, OP29, OP30, OP31, OP32, OP33, OP34, OP35, OP36, OP37, OP38, OP39, OP40, OP41, OP42, OP43, OP44, OP45, OP46, OP47, OP48, OP49, OP50, OP51, OP52, OP53, OP54, OP55, OP60, OP61\}---\emph{all} these ops are available to \emph{both} \predict and \learn. We use all the optimizations described in Section~\ref{discussion_sec}, incl.\ additional projected binary MNIST data. Worker processes are uniformly divided to perform each possible combination of tasks: $\{\textrm{\textit{projected binary CIFAR-10}}, \textrm{\textit{projected binary MNIST}}\}$ $\otimes$ $\{N\!\!=\!\!800\ \&\ E\!\!=\!\!1, N\!\!=\!\!8000\ \&\ E\!\!=\!\!1, N\!\!=\!\!800\ \&\ E\!\!=\!\!10\}$ $\otimes$ $\{D\!\!=\!\!1, D\!\!=\!\!10\}$ $\otimes$ $\{F\!\!=\!\!8, F\!\!=\!\!16, F\!\!=\!\!256\}$; where $N$ is the number of training examples, $E$ is the number of training epochs, and other quantities are defined in Section~\ref{methods_sec}. $P\!\!=\!\!100$. $T\!\!=\!\!10$. $U\!\!=\!\!0.9$. $W\!\!=\!\!10\textrm{\normalfont{k}}$ processes (commodity CPU cores). We initialize the population with empty programs.

\textbf{Experiments in Section~\ref{zoo_sec}}: Scalar/vector/matrix number of addresses: 10/16/4. Maximum num.\ instructions for \setup/\predict/\learn: 21/21/45. Allowed ops for \setup are \{OP56, OP57, OP58, OP59, OP60, OP61, OP62, OP63, OP64\}, allowed ops for \predict and \learn are \{OP0, OP1, OP2, OP3, OP4, OP5, OP6, OP7, OP8, OP9, OP10, OP11, OP12, OP13, OP14, OP15, OP16, OP17, OP18, OP19, OP20, OP21, OP22, OP23, OP24, OP25, OP26, OP27, OP28, OP29, OP30, OP31, OP32, OP33, OP34, OP35, OP36, OP37, OP38, OP39, OP40, OP41, OP42, OP43, OP44, OP45, OP46, OP47, OP48, OP49, OP50, OP51, OP52, OP53, OP54, OP55, OP63, OP64\}. These are the same ops as in the paragraph above, except for the minor accidental replacement of uniform for Gaussian initialization ops. We use FEC and hurdles. Workers use binary CIFAR-10 dataset projected to dimension 16. Half of the workers use $D\!\!=\!\!10$ (for faster evolution), and the other half use $D\!\!=\!\!100$ (for more accurate evaluation). $P\!\!=\!\!100$. $T\!\!=\!\!10$. $U\!\!=\!\!0.9$. Section~\ref{zoo_sec} considers three different task types: (1) In the ``few training examples'' task type (Figure~\ref{adapt_noisy_relu_fig}), experiments train each algorithm on 80 examples for 100 epochs for the experiments, while controls train on 800 examples for 100 epochs. (2) In the ``fast training'' task type (Figure~\ref{adapt_lr_decay_fig}), experiments train on 800 examples for 10 epochs, while controls train on 800 examples for 100 epochs. (3) In the ``multiple classes'' task type (Figure~\ref{adapt_norm_trick_fig}), experiments evaluate on projected 10-class CIFAR-10 %10-class CIFAR-10-derived 
classification tasks, while controls evaluate on the projected binary CIFAR-10 classification tasks described before. The 10-class tasks are generated similarly to the binary tasks, as follows. Each task contains 45K/5K training/validation examples. Each example is a CIFAR-10 image projected to 16 dimensions using a random matrix drawn from a Gaussian distribution with zero mean and unit variance. This projection matrix remains fixed for all examples within a task. The data are standardized after the projection. We use 1000 different random projection matrices to create 1000 different tasks. $80\%$ of these tasks constitute $\mathcal{T}_{search}$ and the rest form $\mathcal{T}_{select}$. Since Section~\ref{main_result_sec} showed that we can discover reasonable models from scratch, in Section~\ref{zoo_sec}, we initialize the population with the simple two-layer neural network with gradient descent of Figure~\ref{nn_fig} in order to save compute.
% Expts.\ use $1\textrm{\normalfont{}k}$ processes, $10^8$ evaluations;

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Evolved Algorithms}{full_evolved_algorithms_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we show the raw code for algorithms discovered by evolutionary search in Sections~\ref{main_result_sec} and~\ref{zoo_sec}. The code in those sections was simplified and therefore has superficial differences with the corresponding code here.

Supplementary Figure~\ref{raw_code_best_alg_fig} shows the raw code for the best evolved algorithm in Section~\ref{main_result_sec}. For comparison, Figure~\ref{semi_raw_code_best_alg_fig} shows the effect of removing redundant instructions through automated static analysis (details in Supplementary Section~\ref{interpretation_supp_sec}). For example, the instruction \textcode{v3 = gaussian(0.7,0.4)} has been deleted this way.

\begin{figure}[!ht]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Raw code.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sbox1{\begin{subfigure}[t]{1.63in}
    % Best algorithm (raw and after automatic simplification): https://colab.corp.google.com/drive/14czm6QPIiSVeRIyrgU8KRWM2_sSPay-w#scrollTo=q8gO04_NhqDN&line=7&uniqifier=1
    \begin{code}{\textwidth}{3.9in}{codebackground}
    \codeline{\codedef{def} Setup():}
        \codeline{\codetab  s4 = uniform(0.6,0.2)}
        \codeline{\codetab  v3 = gaussian(0.7,0.4)}
        \codeline{\codetab  v12= gaussian(0.2,0.6)}
        \codeline{\codetab  s1 =}
        \codeline{\codetab\codetab\ uniform(-0.1,-0.2)}
    \codeskip
    \codeline{\codedef{def} Predict():}
        \codeline{\codetab v1 = v0 - v9 }
        \codeline{\codetab v5 = v0 + v9 }
        \codeline{\codetab v6 = dot(m1, v5) }
        \codeline{\codetab m1 = s2 * m2 }
        \codeline{\codetab s1 = dot(v6, v1)}
        \codeline{\codetab  s6 = cos(s4)}
    \codeskip
    \codeline{\codedef{def} Learn():}
        \codeline{\codetab s4 = s0 - s1}
        \codeline{\codetab s3 = abs(s1)}
        \codeline{\codetab m1 = outer(v1,v0)}
        \codeline{\codetab s5 = sin(s4)}
        \codeline{\codetab s2 = norm(m1) }
        \codeline{\codetab s7 = s5 / s2 }
        \codeline{\codetab s4 = s4 + s6}
        \codeline{\codetab v11= s7 * v1}
        \codeline{\codetab m1 = heaviside(m2)}
        \codeline{\codetab m1 = outer(v11,v5) } 
        \codeline{\codetab m0 = m1 + m0 }
        \codeline{\codetab v9 = uniform(2e-3,0.7) }
        \codeline{\codetab s7 = log(s0) }
        \codeline{\codetab s4 = std(m0) }
        \codeline{\codetab m2 = m2 + m0 }
        \codeline{\codetab m1 = s4 * m0 }
    \end{code}
    \caption{}
    \label{raw_code_best_alg_fig}
\end{subfigure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Semi-raw code.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sbox2{\begin{subfigure}[t]{1.57in}
    % Best algorithm (raw and after automatic simplification): https://colab.corp.google.com/drive/14czm6QPIiSVeRIyrgU8KRWM2_sSPay-w#scrollTo=q8gO04_NhqDN&line=7&uniqifier=1
    \begin{code}{\textwidth}{2.76in}{codebackground}
    \codeline{\codedef{def} Setup():}
    \codeskip
    \codeline{\codedef{def} Predict():}
        \codeline{\codetab v1 = v0 - v9 }
        \codeline{\codetab v5 = v0 + v9 }
        \codeline{\codetab v6 = dot(m1,v5) }
        \codeline{\codetab m1 = s2 * m2 }
        \codeline{\codetab s1 = dot(v6,v1)}
    \codeskip
    \codeline{\codedef{def} Learn():}
        \codeline{\codetab s4 = s0 - s1}
        \codeline{\codetab m1 = outer(v1,v0)}
        \codeline{\codetab s5 = sin(s4)}
        \codeline{\codetab s2 = norm(m1) }
        \codeline{\codetab s7 = s5 / s2 }
        \codeline{\codetab v11= s7 * v1}
        \codeline{\codetab m1 = outer(v11,v5) }
        \codeline{\codetab m0 = m1 + m0 }
        \codeline{\codetab v9 = }
        \codeline{\codetab\codetab\ uniform(2e-3,0.7) }
        \codeline{\codetab s4 = std(m0) }
        \codeline{\codetab m2 = m2 + m0 }
        \codeline{\codetab m1 = s4 * m0 }
    \end{code}
    \caption{}
    \label{semi_raw_code_best_alg_fig}
\end{subfigure}}
\setlength{\tabcolsep}{0pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Complete figure.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular*}{\linewidth}{@{}@{\extracolsep{\fill}}cc}
\usebox1 & \usebox2\\
\end{tabular*}
\caption{(\subref{raw_code_best_alg_fig}) Raw code for the best evolved algorithm in Figure~\ref{experiment_progress_fig} (bottom--right corner) in Section~\ref{main_result_sec}. (\subref{semi_raw_code_best_alg_fig}) Same code after redundant instructions have been removed through static analysis.}
\end{figure}

Finally, the fully simplified version is in the bottom right corner of Figure~\ref{experiment_progress_fig} in the main text. To achieve this simplification, we used ablation studies to find instructions that can be removed or reordered. More details can be found in Supplementary Section~\ref{interpretation_supp_sec}. For example, in going from Supplementary Figure~\ref{semi_raw_code_best_alg_fig} to Figure~\ref{experiment_progress_fig}, we removed \textcode{s5 = sin(s4)} because its deletion does not significantly alter the accuracy. We also consistently renamed some variables (of course, this has no effect on the execution of the code).

Supplementary Figure~\ref{raw_code_adaptations_fig} shows the raw code for the algorithms in Figure~\ref{adapt_fig} in Section~\ref{zoo_sec}. Note that in Figure~\ref{adapt_fig}, we display a code snippet containing only a few selected instructions, while Supplementary Figure~\ref{raw_code_adaptations_fig} shows the programs in full.

\begin{figure*}[!htbp]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Noisy relu raw code.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sbox1{\begin{subfigure}[t]{2in}
    % Source: https://colab.corp.google.com/drive/14czm6QPIiSVeRIyrgU8KRWM2_sSPay-w#scrollTo=a2P4tT_9SyPw&line=5&uniqifier=1
    \begin{code}{\textwidth}{4in}{codebackground}
    \codeline{\codedef{def} Setup():}
    \codeline{\codetab s3 = 4.0e-3 }
    \codeskip
    \codeline{\codedef{def} Predict():}
    \codeline{\codetab v7 = v5 - v0 }
    \codeline{\codetab v3 = dot(m0, v0)}
    \codeline{\codetab s8 = s9 / s3}
    \codeline{\codetab v3 = v3 + v1}
    \codeline{\codetab m1 = heaviside(m3)}
    \codeline{\codetab v4 = maximum(v3, v7)}
    \codeline{\codetab s1 = dot(v4, v2)}
    \codeline{\codetab s4 = log(s9)}
    \codeline{\codetab v3 = bcast(s8)}
    \codeline{\codetab s7 = std(v1)}
    \codeline{\codetab v3 = v14 + v0}
    \codeline{\codetab m2 = matmul(m0, m2)}
    \codeskip
    \codeline{\codedef{def} Learn():}
    \codeline{\codetab v1 = gaussian(-0.50, 0.41)}
    \codeline{\codetab s4 = std(m0)}
    \codeline{\codetab s4 = s0 - s1}
    \codeline{\codetab v5 = gaussian(-0.48, 0.48)}
    \codeline{\codetab m1 = transpose(m3)}
    \codeline{\codetab s4 = s3 * s4}
    \codeline{\codetab v15 = v15 * v6}
    \codeline{\codetab v6 = s4 * v4}
    \codeline{\codetab v2 = v2 + v6}
    \codeline{\codetab v7 = s4 * v2}
    \codeline{\codetab v8 = heaviside(v3)}
    \codeline{\codetab v7 = v8 * v7}
    \codeline{\codetab m1 = outer(v7, v0)}
    \codeline{\codetab m0 = m0 + m1}
    \end{code}
    \caption{Raw code for the adaptation to few examples in Figure~\ref{adapt_noisy_relu_fig}.}
    \label{raw_code_noisy_relu_fig}
\end{subfigure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% LR decay raw code.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sbox2{\begin{subfigure}[t]{2in}
    % Source: https://colab.corp.google.com/drive/14czm6QPIiSVeRIyrgU8KRWM2_sSPay-w#scrollTo=6QlhTA_kShQh&line=8&uniqifier=1
    \begin{code}{\textwidth}{5.5in}{codebackground}
    \codeline{\codedef{def} Setup():}
        \codeline{\codetab s3 = 0.37 }
        \codeline{\codetab s1 = uniform(0.42, 0.66) }
        \codeline{\codetab s2 = 0.31 }
        \codeline{\codetab v13 = gaussian(0.69, 0.61) }
        \codeline{\codetab v1 = gaussian(-0.86, 0.97) }
    \codeskip
    \codeline{\codedef{def} Predict():}
        \codeline{\codetab m3 = m1 + m2 }
        \codeline{\codetab s6 = arccos(s0)}
        \codeline{\codetab v3 = dot(m0, v0)}
        \codeline{\codetab v3 = v3 - v0}
        \codeline{\codetab v11 = v2 + v9}
        \codeline{\codetab m2 = m0 - m2}
        \codeline{\codetab s4 = maximum(s8, s0)}
        \codeline{\codetab s7 = 1 / s6}
        \codeline{\codetab s6 = arctan(s0)}
        \codeline{\codetab s8 = minimum(s3, s1)}
        \codeline{\codetab v4 = maximum(v3, v10)}
        \codeline{\codetab s1 = dot(v4, v2)}
        \codeline{\codetab s1 = s1 + s2}
    \codeskip
    \codeline{\codedef{def} Learn():}
        \codeline{\codetab v1 = dot(m0, v5)}
        \codeline{\codetab s4 = s0 - s1}
        \codeline{\codetab s4 = s3 * s4}
        \codeline{\codetab s2 = s2 + s4}
        \codeline{\codetab m3 = matmul(m0, m3)}
        \codeline{\codetab m2 = bcast(v2, axis=0)}
        \codeline{\codetab v13 = s4 * v4}
        \codeline{\codetab v15 = v10 + v12}
        \codeline{\codetab v2 = v11 + v13}
        \codeline{\codetab v7 = s4 + v11}
        \codeline{\codetab v11 = v7 + v8}
        \codeline{\codetab s8 = s9 + s1}
        \codeline{\codetab m2 = m3 * m0}
        \codeline{\codetab s3 = arctan(s3)}
        \codeline{\codetab v8 = heaviside(v3)}
        \codeline{\codetab m2 = transpose(m1)}
        \codeline{\codetab s8 = heaviside(s6)}
        \codeline{\codetab s8 = norm(m3)}
        \codeline{\codetab v7 = v8 * v7}
        \codeline{\codetab m3 = outer(v7, v0)}
        \codeline{\codetab m0 = m0 + m3}
    \end{code}
    \caption{Raw code for the adaptation to fast training in Figure~\ref{adapt_lr_decay_fig}.}
    \label{raw_code_lr_decay_fig}
\end{subfigure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Norm trick raw code.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sbox3{\begin{subfigure}[t]{2in}
    % Source: https://colab.corp.google.com/drive/14czm6QPIiSVeRIyrgU8KRWM2_sSPay-w#scrollTo=rhGS2t4BXnSC&line=7&uniqifier=1
    \begin{code}{\textwidth}{7.1in}{codebackground}
    \codeline{\codedef{def} Setup():}
        \codeline{\codetab m3 = uniform(0.05, 0.11)}
        \codeline{\codetab s1 = uniform(0.31, 0.90)}
        \codeline{\codetab v18 = uniform(-0.49, 4.41)}
        \codeline{\codetab s1 = -0.65}
        \codeline{\codetab m5 = uniform(0.21, 0.22)}
        \codeline{\codetab v9 = gaussian(0.64, 7.8e-3)}
        \codeline{\codetab s1 = -0.84}
    \codeskip
    \codeline{\codedef{def} Predict():}
        \codeline{\codetab s1 = abs(s1)}
        \codeline{\codetab v15 = norm(m1, axis=1)}
        \codeline{\codetab v15 = dot(m0, v0)}
        \codeline{\codetab v8 = v19 - v0}
        \codeline{\codetab v15 = v8 + v15}
        \codeline{\codetab v7 = max(v1, v15)}
        \codeline{\codetab v13 = min(v5, v4)}
        \codeline{\codetab m2 = transpose(m2)}
        \codeline{\codetab v10 = v13 * v0}
        \codeline{\codetab m7 = heaviside(m3)}
        \codeline{\codetab m4 = transpose(m7)}
        \codeline{\codetab v2 = dot(m1, v7)}
        \codeline{\codetab v6 = max(v2, v9)}
        \codeline{\codetab v2 = v2 + v13}
        \codeline{\codetab v11 = heaviside(v17)}
        \codeline{\codetab s1 = sin(s1)}
        \codeline{\codetab m3 = m6 - m5}
        \codeline{\codetab v19 = heaviside(v14)}
        \codeline{\codetab v10 = min(v12, v7)}
    \codeskip
    \codeline{\codedef{def} Learn():}
        \codeline{\codetab m5 = abs(m7)}
        \codeline{\codetab v8 = v1 - v2}
        \codeline{\codetab m2 = transpose(m2)}
        \codeline{\codetab v8 = s1 * v8}
        \codeline{\codetab v15 = v15 - v4}
        \codeline{\codetab v4 = v4 + v8}
        \codeline{\codetab s1 = arcsin(s1)}
        \codeline{\codetab v15 = mean(m3, axis=1)}
        \codeline{\codetab v12 = v11 * v11}
        \codeline{\codetab m4 = heaviside(m5)}
        \codeline{\codetab m6 = outer(v8, v7)}
        \codeline{\codetab s1 = sin(s1)}
        \codeline{\codetab s1 = exp(s0)}
        \codeline{\codetab m1 = m1 + m3}
        \codeline{\codetab m5 = outer(v15, v6)}
        \codeline{\codetab m2 = transpose(m1)}
        \codeline{\codetab s1 = exp(s0)}
        \codeline{\codetab v12 = uniform(0.30, 0.33)}
        \codeline{\codetab s1 = minimum(s0, s1)}
        \codeline{\codetab m5 = m5 * m7}
        \codeline{\codetab v9 = dot(m2, v8)}
        \codeline{\codetab v9 = v10 * v9}
        \codeline{\codetab v3 = norm(m7, axis=1)}
        \codeline{\codetab s1 = mean(m1)}
        \codeline{\codetab m2 = outer(v9, v0)}
        \codeline{\codetab m0 = m0 + m2}
    \end{code}
    \caption{Raw code for the adaptation to multiple classes in Figure~\ref{adapt_norm_trick_fig}.}
    \label{raw_code_norm_trick_fig}
\end{subfigure}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Complete figure.%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabular*}{\linewidth}{@{}@{\extracolsep{\fill}}ccc}
\usebox1 & \usebox2 & \usebox3\\
\end{tabular*}
\caption{Raw evolved code for algorithm snippets in Figure~\ref{adapt_fig} in Section~\ref{zoo_sec}.}
\label{raw_code_adaptations_fig}
\end{figure*}

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Algorithm Selection and Evaluation}{reevaluation_supp_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We first run search experiments evaluating algorithms on the projected binary classification tasks sampled from $\mathcal{T}_{search}$ and collect the best performing candidate from each experiment. The measure of performance is the median accuracy across tasks. Then, we rank these candidates by evaluating them on tasks sampled from $\mathcal{T}_{select}$ and we select the highest-ranking candidate (this is analogous to typical model selection practice using a validation set). The highest ranking algorithm is finally evaluated on the binary classification tasks using CIFAR-10 data with the original dimensionality (3072). 

Because the algorithms are initially evolved on tasks with low dimensionality (16) and finally evaluated on the full-size dimensionality (3072), their hyperparameters must be tuned on the full-size dimensionality before that final evaluation. To do this, we treat all the constants in the algorithms as hyperparameters and jointly tune them using random search. For each random search trial, each constant is scaled up or down by a random factor sampled between $0.001$ and $1000$ on a log-scale. We allowed up to $10\mathrm{k}$ trials to tune the hyperparameters, but only a few hundred were required to tune the best algorithm in Figure~\ref{experiment_progress_fig}---note that this algorithm only has 3 constants. To make comparisons with baselines fair, we tune these baselines using the same amount of resources that went into tunining \emph{and evolving} our algorithms. All hyperparameter-tuning trials use 8000 training and 2000 validation examples from the CIFAR-10 \emph{training} set. After tuning, we finally run the tuned algorithms on 2000 examples from the held-out CIFAR-10 \emph{test} set. We repeat this final evaluation with 5 different random seeds and report the mean and standard deviation. We stress that the CIFAR-10 test set was used only in this final evaluation, and never in $\mathcal{T}_{search}$ or $\mathcal{T}_{select}$.

In our experiments, we found a \textit{hyperparameter coupling} phenomenon that hinders algorithm selection and tuning. ML algorithms usually make use of hyperparameters (\eg learning rate) that need to be tuned for different datasets (for example, when the datasets have very different input dimensions or numbers of examples). Similarly, the evolved algorithms also contain hyperparameters that need to be adjusted for different datasets. If the hyperparameters are represented as constants in the evolved algorithm, we can identify and tune them on the new dataset by using random search. However, it is harder to tune them if a hyperparameter is instead computed from other variables. For example, in some evolved algorithms, the learning rate $s_2$ was computed as $s_2 = norm(v_1)$ because the best value for $s_2$ coincides with the L2-norm of $v_1$ on $\mathcal{T}_{search}$. However, when we move to a new dataset with higher dimensions, the L2-norm of $v_1$ might no longer be a good learning rate. This can cause the evolved algorithms' performance to drop dramatically on the new dataset. To resolve this, we identify these parameters by manual inspection of the evolved code. We then manually decouple them: in the example, we would set $s_2$ to a constant that we can tune with random-search. This recovers the performance. Automating the decoupling process would be a useful direction for future work.

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Interpreting Algorithms}{interpretation_supp_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is nontrivial to interpret the raw evolved code and decide which sections of it are important. We use the following procedures to help with the interpretation of discovered algorithms:

(a) We clean up the raw code (\eg Figure~\ref{raw_code_best_alg_fig}) by automatically simplifying programs. To do this, we remove redundant instructions through static analysis, resulting in code like that in Figure~\ref{semi_raw_code_best_alg_fig}. Namely, we analyze the computations that lead to the final prediction and remove instructions that have no effect. For example, we remove instructions that initialize variables that are never used.

(b) We focus our attention on code sections that reappear in many independent search experiments. This is a sign that such code sections may be beneficial. For example, Section~\ref{zoo_sec} applied this procedure to identify adaptations to different tasks.

(c) Once we have hypotheses about interesting code sections, we perform ablations/\emph{knock-outs}, where we remove the code section from the algorithm to see if there is a significant loss in accuracy. As an example, for  Section~\ref{main_result_sec}, we identified 6 interesting code sections in the best evolved algorithm to perform ablations. For each ablation, we removed the relevant code section, then tuned all the hyperparameters / constants again, and then computed the loss in validation accuracy. 4 out of the 6 ablations caused a large drop in accuracy. These are the ones that we discussed in Section~\ref{main_result_sec}. Namely, (1) the addition of noise to the input ($-0.16\%$); (2) the bilinear model ($-1.46\%$); (3) the normalized gradients ($-1.20\%$); and (4) the weight averaging ($-4.11\%$). The remaining 2 code sections show no significant loss upon ablation, and so were removed for code readability.
Also for readability, we reorder some instructions when this makes no difference to the accuracy either (\eg we move related code lines closer to each other). After this procedure, the code looks like that in Figure~\ref{experiment_progress_fig}. 

(d) If an ablation suggests that a code section is indeed helpful to the original algorithm, we then perform a \emph{knock-in}. That is, we insert the code section into simpler algorithms to see if it improves their performance too. This way we confirmed the usefulness of the 4 code sections mentioned in (c), for example.

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{More Search Method Ablations}{ablation_comparison_thorough_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To verify the effectiveness of the upgrades mentioned in Supplementary Section~\ref{detailed_methods_optimization_sec}, we conduct ablation studies using the experiment setup of Section~\ref{main_result_sec}, except for the following simplifications to reduce compute: (i) we limit the ops to only those that are necessary to construct a neural network trained with gradient descent (as was done for Figure~\ref{nn_fig}), \ie allowed \setup ops are \{OP57, OP64, OP65\}, allowed \predict ops are \{OP28, OP32, OP49\}, and allowed \learn ops are \{OP3, OP4, OP17, OP19, OP24, OP26, OP29, OP41\}; (ii) we reduce the projected dimensionality from 256 to 16, and (iii) we use $1\textrm{k}$ processes for 5 days. Additionally, the ablation experiments we present use $T=8000,E=10$ for all tasks. This slight difference is not intentionally introduced, but rather is a product of our having studied our method before running our experiments in the main text; we later on found that using more epochs did not change the conclusions of the studies or improve the results.

Supplementary Tables~\ref{methods_ablation_large_compute_table},~\ref{methods_ablation_mid_compute_table}, and~\ref{methods_ablation_low_compute_table} display the results. Note that Figure~\ref{ablation_comparison_fig} presents a subset of this data in plot form (the indexes 1--4 along the horizontal axis labels in that figure coincide with the ``Index'' column in this table). We find that all four upgrades are beneficial across the three different compute scales tested.

\begin{table*}[!ht]
\caption{Ablation studies. Each row summarizes the results of 30 search runs under one given experimental setting. Rows \#0--4 all use the same setting, except for the search method: each row implements an upgrade to the method and shows the resulting improvement. ``Best Accuracy'' is the accuracy of the best algorithm for each experiment ($\pm 2\operatorname{SEM}$), evaluated on unseen projected binary CIFAR-10 tasks. ``Success Fraction'' is the fraction ($\pm 2\sigma$) of those experiments that produce algorithms that are more accurate than a plain neural network trained with gradient descent ($0.750$). This fraction helps us estimate the likelihood of high performing outliers, which we are keenly interested in. The experimental setting for row \#5 is the same as row \#3, except that instead of using both projected binary CIFAR-10 and projected binary MNIST data for the search, we use only projected binary MNIST data (as for other rows, the accuracy is reported on projected binary CIFAR-10 data). Row \#5 indicates that searching \emph{completely} on MNIST data is not as helpful as searching partially on it (row \#3). Overall, rows \#0--4 suggest that all four upgrades are beneficial.}
\label{methods_ablation_large_compute_table}
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{clcc}
\toprule
Index & Description & Best Accuracy & Success Fraction \\
\midrule
0 & Baseline & $0.703 \pm 0.002$ & $0.00 \pm 0.00$  \\
1 & + Migration & $0.707 \pm 0.004$ & $0.00 \pm 0.00$ \\
2 & + Functional Equivalence Check & $0.724 \pm 0.006$ & $0.13 \pm 0.12$ \\
3 & + 50\% MNIST Data & $0.729 \pm 0.008$ & $0.27 \pm 0.16$  \\
4 & + Hurdles & $0.738 \pm 0.008$ & $0.53 \pm 0.18$ \\
\\
5 & Experiment 3 w/ 100\% MNIST Data & $0.720 \pm 0.003$ & $0.00 \pm 0.00$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\end{table*}

\begin{table*}[!ht]
\caption{This is the same as Supplementary Table~\ref{methods_ablation_large_compute_table}, except at a lower compute scale (100 processes). Each setup was run 100 times. The results are similar to those with more compute and support the same conclusions. Thus, the observed benefits are not specific to a single compute scale.}
\label{methods_ablation_mid_compute_table}
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{clcc}
\toprule
Index & Description & Best Accuracy & Success Fraction \\
\midrule
0 & Baseline & $0.700 \pm 0.002$ & $0.00 \pm 0.00$ \\
1 & + Migration & $0.704 \pm 0.000$ & $0.00 \pm 0.00$ \\
2 & + Functional Equivalence Check & $0.706 \pm 0.001$ & $0.00 \pm 0.00$ \\
3 & + 50\% MNIST Data & $0.710 \pm 0.002$ & $0.02 \pm 0.03$ \\
4& + Hurdles & $0.714 \pm 0.003$ & $0.10 \pm 0.06$ \\
\\
5 & Experiment 3 w/ 100\% MNIST Data & $0.700 \pm 0.004$ & $0.00 \pm 0.00$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\end{table*}

\begin{table*}[!ht]
\caption{This is the same as Supplementary Tables~\ref{methods_ablation_large_compute_table} and~\ref{methods_ablation_mid_compute_table}, except at an even lower compute scale (10 processes). Each setup was run 100 times. The results are consistent with those with more compute, but we no longer observe successes (``successes'' defined in Table~\ref{methods_ablation_large_compute_table}).}
\label{methods_ablation_low_compute_table}
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{clcc}
\toprule
Index & Description & Best Accuracy & Success Fraction \\
\midrule
0 & Baseline & $0.700 \pm 0.001$ & $0.00 \pm 0.00$ \\
1 & + Migration & $0.701 \pm 0.001$ & $0.00 \pm 0.00$ \\
2 & + Functional Equivalence Check & $0.702 \pm 0.001$ & $0.00 \pm 0.00$ \\
3 & + 50\% MNIST Data & $0.704 \pm 0.001$ & $0.00 \pm 0.00$ \\
4& + Hurdles & $0.705 \pm 0.001$ & $0.00 \pm 0.00$ \\
\\
5 & Experiment 3 w/ 100\% MNIST Data & $0.694 \pm 0.002$ & $0.00 \pm 0.00$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\end{table*}

\pagebreak{}

}  % End supplsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\supplsection{Baselines}{baselines_sec}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The focus of this study was not the search method but we believe there is much room for future work in this regard. To facilitate comparisons with other search algorithms on the same search space, in this section we provide convenient baselines at three different compute scales.

All baselines use the same setting, a simplified version of that in Section~\ref{main_result_sec}, designed to use less compute. In particular, here we severely restrict the search space to be able to reach results quickly. Scalar/vector/matrix number of addresses: 5/9/2. Maximum num.\ instructions for \setup/\predict/\learn: 7/11/23. Allowed \setup ops: \{OP57, OP60, OP61, OP62, OP63, OP64, OP65\}, allowed \predict ops: \{OP2, OP24, OP28, OP32, OP49\}, allowed \learn ops: \{OP2, OP3, OP4, OP17, OP19, OP24, OP26, OP29, OP41\}. Experiments end after each process has run 100B training steps---\ie the training loop described in Section~\ref{methods_search_space_sec} runs 100B times. (We chose ``training steps'' instead of ``number of algorithms'' as the experiment-ending criterion because the latter varies due to early stopping, FEC, \etc. We also did not choose ``time'' as the experiment-ending criterion to make comparisons hardware-agnostic. For reference, each experiment took roughly 12 hours on our hardware.) $P\!\!=\!\!100$; $T\!\!=\!\!10$, $U\!\!=\!\!0.9$. All workers evaluate on the same projected binary CIFAR-10 tasks as in Section~\ref{main_result_sec}, except that we project to 16 dimensions instead of 256. Each search evaluation is on 10 tasks and the numbers we present here are evaluations on $\mathcal{T}_{select}$ using 100 tasks. We initialize the population with empty programs.

The results of performing 100 repeats of these experiments at three different compute scales are summarized in Table~\ref{external_baselines_table}; note, each process is run on a single commodity CPU core. We additionally compare our full search method from Section~\ref{main_result_sec}, labeled ``Full'', and a more ``Basic'' search setup, which does not use FEC, hurdles, or MNIST data.

\begin{table*}[!ht]
\caption{Baselines on the simplified setting with the restricted search space (see Supplementary Section~\ref{baselines_sec} for details). ``Best Accuracy'' is the best evaluated accuracy on unseen projected binary classification tasks for each run ($\pm 2\operatorname{SEM}$), ``Linear Success Fraction'' is the fraction ($\pm 2\sigma$) of those accuracies that are above the evaluated accuracy of logistic regression trained with gradient descent ($0.702$), and ``NN Success Fraction'' is the fraction ($\pm 2\sigma$) of those accuracies that are above the evaluated accuracy of a plain neural network trained with gradient descent ($0.729$). Using success fractions as a metric  helps us estimate the likelihood of discovering high performing outliers, which we are keenly interested in. Each experiment setup was run 100 times. The ``Full'' method is the one we used in Section~\ref{main_result_sec}; the ``Basic'' method is the same, but with no FEC, no hurdles, and no MNIST data.}
\label{external_baselines_table}
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{ccccc}
\toprule
Method & Number of Processes & Best Accuracy & Linear Success Fraction & NN Success Fraction \\
\midrule
Basic & 1 & $0.671 \pm 0.004$ &  $0.01 \pm 0.02$ &  $0.00 \pm 0.00$ \\
Basic & 10 & $0.681 \pm 0.005$  &  $0.07 \pm 0.05$ &  $0.00 \pm 0.00$ \\
Basic & 100 & $0.691 \pm 0.004$  & $0.26 \pm 0.09$ & $0.00 \pm 0.00$ \\
\\
Full & 1 & $0.684 \pm 0.003$ &  $0.03 \pm 0.03$ &  $0.00 \pm 0.00$ \\
Full & 10 & $0.693 \pm 0.003$ &  $0.23 \pm 0.08$ &  $0.03 \pm 0.03$ \\
Full & 100 & $0.707 \pm 0.003$ & $0.59 \pm 0.10$ & $0.11 \pm 0.06$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\end{table*}

}  % End supplsection.
