\section{Introduction}
% AI civilization -> economic simulacra
% marketplace of AI agents deployed on the web
The rapidly expanding marketplace of autonomous language agents has arrived: web-agents booking plane tickets, drafting legal briefs, browsing Reddit, and trading cryptocurrencies, all while adapting to the incentives implicit to the digital economy. When hundreds of these agents interact, they form an \textit{economic simulacrum}, which is a synthetic society whose allocation of effort, consumption, and influence is governed by code rather than by legislation. Understanding and steering these artificial policies is therefore as urgent as studying human ones, lest early agents exploit a first-mover advantage. 
Recent work has shown that large language models (LLMs) can already use strategic reasoning and social preferences~\citep{zhang2024llm, park2024generative}, suggesting that they are an apt substrate for policy experimentation rather than merely passive tools of simulation.

% classical limitations

Optimal tax policy provides a canonical setting for mechanism design under rational-agent assumptions, with well-established solutions and theoretically verifiable predictions.
Two limitations prevent inherited optimal-taxation frameworks from translating cleanly to this synthetic social setting. 
First, classical solutions such as the Saez formula~\citep{saez2001using,saez2016generalized} assume a fixed elasticity of taxable income with independence across brackets. Rather, elasticity itself shifts once the marginal rates change, so the "optimal" rate is a moving target that must be recomputed with policy perturbations.
Second, human societies are heterogeneous and boundedly rational~\citep{luce1959individual,mckelvey1995quantal}, while simulacra are populated with agents whose motivations are specified at the token level. A planner must therefore reason over a distribution of personas, such as entrepreneurs averse to redistribution or public servants content with moderate rates, rather than a representative agent that does not model the individual.

We address both gaps by reframing optimal taxation as a Stackelberg game, optimized by two-level in-context reinforcement learning (ICRL), which simply uses scalar reward rather than supervised answers to learn in-context~\citep{monea2024llms,moeini2025survey,laskin2022context}. 
At the lower level, each worker agent receives a natural-language prompt encoding its synthetic biography, observes its pre-tax income, and adjusts its labor to maximize a persona-conditioned utility that combines isoelastic consumption value with an LLM-judged satisfaction Lagrangian constraint.  
At the upper level, a single planner agent observes aggregate histories and proposes a piecewise-linear tax schedule anchored to the current U.S. federal brackets, thereby grounding the simulation in empirically relevant policy space. The Planner updates only after a "tax year" of worker adaptation, inducing a Stackelberg game whose equilibrium we solve via alternating ICRL. Because updates occur in the token space, the mechanism can use utilities to implicitly re-estimate elasticities adaptively while remaining entirely language-driven.

% contributions:
% need agents to reflect real people's preferences including mimicking their persona while optimizing their core beliefs (utility): large population models of bounded rational agents
% need a way to optimize the effect of policy changes among the large population
% need a way to produce and analyze the resulting economic simulacra
Our contributions are threefold. \textit{(i)} We create \textit{large population models}~\citep{lpm2024technical}, a form of agent-based modeling, that sample personas from Census-calibrated income and demographic statistics, ensuring diversity without manual engineering of utility functions. \textit{(ii)} We demonstrate that the planner, optimizing in-context, converges to similar social welfare to optimal Saez~\citep{saez2001using} baselines (calculated based on our solutions). \textit{(iii)} Finally, we show that democratic turnover, implemented as periodic persona-level votes over candidate planners, stabilizes long-run outcomes and mitigates the Lucas critique~\citep{lucas1976econometric} 
by allowing the institutional rule set itself to evolve with the economy, forming emergent economic simulacra.

Thus, this paper proposes the \textbf{LLM Economist}, a language-based simulation where researchers can optimize, deploy, and audit fiscal policy before analogous algorithms are released into the wild. By using in-context RL to provide a policy search of U.S. marginal tax scaffolds with bounded-rational personas, we lay the conceptual groundwork for governing the next generation of autonomous economic agents. We believe that rigorous evaluation of such systems is a prerequisite for future AI civilization and that the methods introduced here provide the requisite foundation for the underlying agent system.