\section{Scaling}

\paragraph{LLM Brain Swap:} By swapping the LLM used in the simulation, we can investigate the innate exploration and exploitation capabilities of the in-context optimization capability of the LLM for multi-agent systems. Table~\ref{tab:scale} presents a comparison of different LLM models' performance in our economic simulation framework.

\begin{table}[h]
\centering
\caption{\textbf{LLM Performance Comparison}}
\label{tab:scale}
\begin{tabular}{lcc}
\toprule[1.5pt]
\textbf{LLM Model} & \textbf{Steps} & \textbf{\% Max SWF} \\
\midrule[1pt]
Llama 3.1:8b & 5000 & 90.0\\
GPT-3.5 Turbo & 5000 & 97.84 \\
GPT-4o & 5000 & 98.20 \\
\bottomrule[1.5pt]
\end{tabular}
\end{table}

The results in Table~\ref{tab:scale} reveal a clear trend in performance across different LLM models. Llama 3.1:8b achieves a respectable 90.0\% of maximum Social Welfare Function (SWF) in 5000 steps. However, GPT 3.5 Turbo significantly outperforms Llama, reaching 97.84\% of maximum SWF. GPT-4o further improves upon this, achieving an impressive 98.20\% of maximum SWF.

These findings suggest that more advanced LLM models possess superior in-context optimization capabilities, allowing them to more effectively navigate the complex economic landscape of our simulation. The substantial performance gap between Llama 3.1:8b and the GPT models indicates that the choice of LLM can significantly impact the quality of economic policies derived from these simulations.

\paragraph{Scaling \# of Agents:} We test scaling the number of agents in the simulation up to 1000 agents locally with Llama 3.1:8b with 8 A6000 Adas. Table~\ref{tab:scalability} presents our scalability analysis, showing convergence time and computational resource utilization as we increase the number of agents.

\begin{table}[h]
\centering
\caption{\textbf{Scalability Analysis: Convergence Time and Computational Resources}}
\label{tab:scalability}
\begin{tabular}{lrrr}
\toprule[1.5pt]
\textbf{\# Workers} & \textbf{APS} & \textbf{FPS} & \textbf{Baseline FPS} \\
\midrule[1pt]
3 & 3.47 & 1.16 & 0.86 \\
5 & 5.59 & 1.12 & 0.48 \\
10 & 5.82 & 0.58 & 0.30 \\
50 & 19.27 & 0.39 & 0.11 \\
100 & 24.57 & 0.25 & 0.05 \\
1000 & 53.62 & 0.05 & 0.01\\
\bottomrule[1.5pt]
\end{tabular}
\end{table}

In Table~\ref{tab:scalability}, we observe the scaling behavior of our framework as we increase the number of agents from 3 to 1000. The metrics reported are Actions Per Second (APS), Frames Per Second (FPS), and Baseline FPS. APS represents the total number of agent actions processed per second, while FPS indicates the number of complete simulation steps (frames) processed per second. Baseline FPS provides a reference point for comparison.

As we scale from 3 to 1000 agents, we observe a significant increase in APS from 3.47 to 53.62, demonstrating our framework's ability to handle a large number of agent actions concurrently. However, this comes at the cost of reduced FPS, which decreases from 1.16 to 0.05 as the number of agents increases. This trade-off between APS and FPS is expected, as processing more agents within each simulation step naturally leads to slower overall simulation progression.

Notably, our framework consistently outperforms the baseline FPS across all scales, with the performance gap widening as the number of agents increases. At 1000 agents, our framework achieves an FPS 5 times higher than the baseline (0.05 vs 0.01), highlighting the efficiency of our implementation.

These scalability results provide strong evidence for the practical applicability of our LLM Economist framework to large-scale economic simulations. By demonstrating the ability to handle up to 1000 agents while maintaining performance above the baseline, we show that our approach can potentially model complex, real-world economic scenarios with numerous interacting agents.