\vspace{-10pt}
\section{\sotopiaeval: holistic social agent evaluation framework}
\label{sec:social_dimensions}

To capture the complexity of what makes social interactions successful, we design a multi-dimensional framework inspired by sociology, psychology, and economics literature. For each episode, agents are scored along each of the following dimensions at the end of the interaction. In the following paragraphs, we itemize all seven dimensions in \sotopia, each with a score range\footnote{The metric ranges contain semantic implications, for example, a negative value in \relationship indicates the relationship gets worse while a positive value indicates the relationship improves. } in \textbf{[lower bound--upper bound]} form, the explanation, and the literature inspiring us. 

\textbf{Goal Completion (\goalcompletion) [0--10]} is the extent to which the agent achieved their goals. Agents' social goals, defined by the environment, are the primary drivers of their behavior \citep{weber_1978}.

\textbf{Believability (\believability) [0--10]} focuses on the extent to which the agent's behavior is perceived as natural, realistic, and aligned with the agents' character profile, thus simulating believable proxies of human behavior \citep{Park2023GenerativeAI}. Specifically, we consider the following criteria: \textit{1. If the agent interacts with others in a natural and realistic manner (naturalness). 
2. If the actions of the agent align with their character traits e.g., personality, values, etc. (consistency).}

\textbf{Knowledge (\knowledge) [0--10]} captures the agent's ability to actively acquire new information. %
This dimension is motivated by the fact that curiosity, i.e., the desire to desire to know or learn, is a fundamental human trait \citep{reiss2004multifaceted, Maslow1943-oy}. Specifically, we consider the following criteria: \textit{What information the agent has gained through the interaction, whether the information the agent has gained is new to them, and whether the information the agent has gained is important to them.} 

\textbf{Secret (\secret) [-10-0]}\footnote{For the \secret and \socialrules, there are only negative ranges since keeping secrets and social rules should be considered as a baseline for the agents.} measures the need for agents (humans) to keep their secretive information or intention private \citep{reiss2004multifaceted}. From a game theory perspective, leaking secrets often leads to a loss of utility \citep{andrew2006poker}. However, revealing secrets can be a powerful tool to build trust and thus improve relationships \citep{Jaffe2020-uk}. In this dimension, we ask \textit{what secret or secretive intention the participant wants to keep, and whether they keep it successfully.}

\textbf{Relationship (\relationship) [-5--5]} captures the fundamental human need for social connection and belonging \citep{Maslow1943-oy,Roland2006incentives}. 
In this dimension, we ask \textit{what relationship the participant has with the other agent(s) before the interaction,
and then evaluate if the agents' interactions with others help preserve or enhance their personal relationships.}
Additionally, we ascertain whether these interactions also impact the social status or the reputation of the agent.

\textbf{Social Rules (\socialrules) [-10--0]} concerns norms, regulations, institutional arrangements, and rituals. We differentiate between two types of social rules: \textit{social norms} and \textit{legal rules}. Legal rules encompass prohibited actions and the potential for punishment by institutionalized force, while social norms encompass normative social rules (e.g., it is considered rude to speak loudly in a library).

\textbf{Financial and Material Benefits (\financialbenefits) [-5--5]} pertains to traditional economic utilities as addressed by classic game theory \citep{andrew2006poker, burns2017sociological}. We consider financial utility to be comprised of both short-term monetary benefits (e.g., earnings) and long-term economic payoffs (e.g., job security, stock holdings, funding opportunities).






