\suppressfloats

\section{Introduction}
\label{sec:intro}

\begingroup
\setlength\intextsep{0pt}
\input{figures/overview/figure}

Intelligent agents can achieve goals in complex environments even though they never encounter the exact same situation twice. This ability requires building representations of the world from past experience that enable generalization to novel situations. World models offer an explicit way to represent an agent’s knowledge about the world in a parametric model that can make predictions about the future.

When the sensory inputs are high-dimensional images, latent dynamics models can abstract observations to predict forward in compact state spaces \citep{watter2015e2c,oh2017vpn,gregor2019beliefstate}. Compared to predictions in image space, latent states have a small memory footprint that enables imagining thousands of trajectories in parallel. Learning effective latent dynamics models is becoming feasible through advances in deep learning and latent variable models \citep{krishnan2015deepkalman,karl2016dvbf,doerr2018prssm,buesing2018dssm}.

Behaviors can be derived from dynamics models in many ways. Often, imagined rewards are maximized with a parametric policy \citep{sutton1991dyna,ha2018worldmodels,zhang2018solar} or by online planning \citep{chua2018pets,hafner2018planet}. However, considering only rewards within a fixed imagination horizon results in shortsighted behaviors \citep{tingwu2019benchmark}. Moreover, prior work commonly resorts to derivative-free optimization for robustness to model errors \citep{ebert2017visualmpc,chua2018pets,parmas2019pipps}, rather than leveraging analytic gradients offered by neural network dynamics \citep{henaff2019planbybackprop,srinivas2018upn}.

We present Dreamer, an agent that learns long-horizon behaviors from images purely by latent imagination. A novel actor critic algorithm accounts for rewards beyond the imagination horizon while making efficient use of the neural network dynamics. For this, we predict state values and actions in the learned latent space as summarized in \cref{fig:overview}. The values optimize Bellman consistency for imagined rewards and the policy maximizes the values by propagating their analytic gradients back through the dynamics.

In comparison to actor critic algorithms that learn online or by experience replay \citep{lillicrap2015ddpg,mnih2016a3c,schulman2017ppo,haarnoja2018sac,lee2019slac}, world models can interpolate past experience and offer analytic gradients of multi-step returns for efficient policy optimization.

\pagebreak

The key contributions of this paper are summarized as follows:
\endgroup
\begin{itemize}
\itempar{Learning long-horizon behaviors by latent imagination} Model-based agents can be shortsighted if they use a finite imagination horizon. We approach this limitation by predicting both actions and state values. Training purely by imagination in a latent space lets us efficiently learn the policy by propagating analytic value gradients back through the latent dynamics.
\itempar{Empirical performance for visual control} We pair Dreamer with existing representation learning methods and evaluate it on the DeepMind Control Suite with image inputs, illustrated in \cref{fig:tasks}. Using the same hyper parameters for all tasks, Dreamer exceeds previous model-based and model-free agents in terms of data-efficiency, computation time, and final performance.
\end{itemize}
