\section{Related Work}
\label{sec:related}

Prior works learn latent dynamics for visual control by derivative-free policy learning or online planning, augment model-free agents with multi-step predictions, or use analytic gradients of Q-values or multi-step rewards, often for low-dimensional tasks. In comparison, Dreamer uses analytic gradients to efficiently learn long-horizon behaviors for visual control purely by latent imagination.

\paragraph{Control with latent dynamics}

E2C \citep{watter2015e2c} and RCE \citep{banijamali2017rce} embed images to predict forward in a compact space to solve simple tasks. World Models \citep{ha2018worldmodels} learn latent dynamics in a two-stage process to evolve linear controllers in imagination. PlaNet \citep{hafner2018planet} learns them jointly and solves visual locomotion tasks by latent online planning. SOLAR \citep{zhang2018solar} solves robotic tasks via guided policy search in latent space. I2A \citep{weber2017i2a} hands imagined trajectories to a model-free policy, while \citet{lee2019slac} and \citet{gregor2019beliefstate} learn belief representations to accelerate model-free agents.

\paragraph{Imagined multi-step returns}

VPN \citep{oh2017vpn}, MVE \citep{feinberg2018mve}, and STEVE \citep{buckman2018steve} learn dynamics for multi-step Q-learning from a replay buffer. AlphaGo \citep{silver2017alphago} combines predictions of actions and state values with planning, assuming access to the true dynamics. Also assuming access to the dynamics, POLO \citep{lowrey2018polo} plans to explore by learning a value ensemble. MuZero \citep{schrittwieser2019muzero} learns task-specific reward and value models to solve challenging tasks but requires large amounts of experience. PETS \citep{chua2018pets}, VisualMPC \citep{ebert2017visualmpc}, and PlaNet \citep{hafner2018planet} plan online using derivative-free optimization. POPLIN \citep{wang2019poplin} improves over online planning by self-imitation. \citet{piergiovanni2018dreaming} learn robot policies by imagination with a latent dynamics model. Planning with neural network gradients was shown on small problems \citep{schmidhuber1990diffmodel,henaff2018planbybackprop} but has been challenging to scale \citep{parmas2019pipps}.

\paragraph{Analytic value gradients}

DPG \citep{silver2014dpg}, DDPG \citep{lillicrap2015ddpg}, and SAC \citep{haarnoja2018sac} leverage gradients of learned immediate action values to learn a policy by experience replay. SVG \citep{heess2015svg} reduces the variance of model-free on-policy algorithms by analytic value gradients of one-step model predictions. Concurrent work by \citet{byravan2019ivg} uses latent imagination with deterministic models for navigation and manipulation tasks. ME-TRPO \citep{kurutach2018modeltrpo} accelerates an otherwise model-free agent via gradients of predicted rewards for proprioceptive inputs. DistGBP \citep{henaff2017planbybackprop,henaff2019planbybackprop} uses model gradients for online planning in simple tasks.