\section{Conclusions \& Future Work}
\label{sec:conclusion}
We  presented Learning with Opponent-Learning Awareness (LOLA), a learning method for multi-agent settings that considers the learning processes of other agents. We show that when both agents have access to exact value functions and apply the LOLA learning rule, cooperation emerges based on tit-for-tat in the infinitely repeated iterated prisoners' dilemma while independent naive learners defect. We also find that LOLA leads to stable learning of the Nash equilibrium in IMP. In our round-robin tournament against other multi-agent learning algorithms we show that exact LOLA agents achieve the highest average returns on the IPD and respectable performance on IMP. We also derive a policy gradient-based version of LOLA, applicable to a deep RL setting. Experiments on the IPD and IMP demonstrate similar learning behavior to the setting with exact value function. 

In addition, we scale the policy gradient-based version of LOLA to the Coin Game, a multi-step game that requires deep recurrent policies. LOLA agents learn to cooperate, as agents pick up coins of their own colour with high probability while naive learners pick up coins indiscriminately. We further remove agents' access to the opponent agents' policy parameters and replace with opponent modeling. While less reliable, LOLA agents with opponent modeling also learn to cooperate. 

We briefly address the exploitability of LOLA agents. Empirical results show that in the IPD both agents are incentivised to use LOLA, while higher order exploits show no further gain. 

In the future, we would like to continue to address the exploitability of LOLA, when adversarial agents explicitly aim to take advantage of a LOLA learner using global search methods rather than just gradient-based methods. Just as LOLA is a way to exploit a naive learner, there should be means of exploiting LOLA learners in turn, unless LOLA is itself an equilibrium learning strategy. 

\section*{Acknowledgements} 
This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement number 637713) and from the National Institutes of Health (grant agreement number R01GM114311).
It was also supported by the Oxford-Google DeepMind Graduate Scholarship and a generous equipment grant from NVIDIA.
We would like to thank Jascha Sohl-Dickstein, David Balduzzi, Karl Tuyls, Marc Lanctot, Michael Bowling, Ilya Sutskever, Bob McGrew, and Paul Cristiano for fruitful discussion. We would like to thank Michael Littman for providing feedback on an early version of the manuscript. We would like to thank our reviewers for constructive and thoughtful feedback.
