\section{Related work}
In this section we are going to cover two closest concepts to \md~from existing literature: catastrophic forgetting and data poisoning. Neither is able to explain the phenomenon of \md~fully, as the setting is fundamentally different, but they provide another perspective on the observed phenomenon. 
\subsection{Continual learning and catastrophic forgetting}
Unlike traditional machine learning which seeks to learn from a static data distribution, \emph{continual learning} attempts to learn from a dynamic one, where data are supplied in a sequential fashion \citep{van2019three}. This tends to be task-based, where data are provided with delineated task boundaries; \eg, classifying dogs from cats and recognising handwritten digits. Our work is more similar to task-free continual learning \citep{aljundi2019task} where data distributions gradually change without the notion of separate tasks. Our work examines a particular scenario in which the changed data distributions arise from the model itself, as a result of training in the previous iteration.



\myexample{Example of text outputs of an OPT-125m model affected by~\Md -- models degrade over generations, where each new generation is trained on data produced by the previous generation.}{
\begin{description}
    \item \textbf{Input:} some started before 1360 — was typically accomplished by a master mason and a small team of itinerant masons, supplemented by local parish labourers, according to Poyntz Wright. But other authors reject this model, suggesting instead that leading architects designed the parish church towers based on early examples of Perpendicular
    \item \textbf{Outputs:}
    
    \item \textbf{~Gen 0:} Revival architecture such as St. John's Cathedral in London. The earliest surviving example of Perpendicular Revival architecture is found in the 18th @-@ century Church of Our Lady of Guernsey, which dates from the late 19th century. There are two types of perpendicular churches : those

    \item \textbf{~Gen 1:}  architecture such as St. Peter's Basilica in Rome or St. Peter's Basilica in Buenos Aires. There is no evidence that any of these buildings were built during the reign of Pope Innocent III, but it is possible that they may have been built during the reign of his successor, Pope Innocent



    \item \textbf{~Gen 7:}  architecture in England. In an interview with The New York Times, Wright said : " I don 't think there is anything wrong with me being able to do what I want to do. It just doesn 't work for me. " He added : " I don 't know if you can call it funny,

    \item \textbf{~Gen 9:} architecture. In addition to being home to some of the world's largest populations of black @-@ tailed jackrabbits, white @-@ tailed jackrabbits, blue @-@ tailed jackrabbits, red @-@ tailed jackrabbits, yellow @-
\end{description}
}

A typical challenge in continual learning is that the model forgets previous samples when learning new information; this is known as \emph{catastrophic forgetting} \citep{kirkpatrick2017overcoming}. A typical way of preventing it is to use regularisations (Memory Aware Synpass \citep{aljundi2018memory}) or just rely on data (\eg~Learning without Forgetting \citep{li2017learning}). This has an indirect connection to our work, yet differs since the data in the process of \md~are generated by different generations of models.


\subsection{Data poisoning}
Poisoning attacks are crafted and inserted during training in order to degrade the model's performance when deployed~\citep{biggio2012poisoning}. Malicious data can be inserted into training data to induce unintended behaviors that can be activated by special triggers~\citep{gu2017badnets}. The early literature on data poisoning focused mainly on supervised learning, where classifiers are trained with labeled samples. But with the emergence of contrastive learning~\citep{radford2021learning} and LLMs~\citep{brown2020language}, more recent models are trained with large-scale web crawls, making data poisoning attacks more feasible on these untrustworthy web sources. Recent studies have demonstrated that web-scale datasets can be poisoned by introducing malicious data into a small percentage of samples~\citep{carlini2021poisoning, carlini2023poisoning}.
