\FloatBarrier

\section{Related Work}

\textbf{Diffusion for Decision-Making\ \ }
Many works utilise diffusion models for generating actions~\citep{pearce2023imitating, janner2022planning}. However, the focus of our work is on generating action-conditioned synthetic data for world modelling~\citep{ha2018world}, which can be used downstream for planning~\citep{hafner2021mastering}.
SynTHER~\citep{lu2024synthetic} employs an unconditional diffusion model to generate synthetic data for reinforcement learning (RL). Other works~\citep{alonso2024diffusion, yang2024learning, rigter2024world, hu2023gaia, zhang2024learning} utilise diffusion models to train action-conditioned world models. All of these works train the diffusion model from scratch. In our work, the focus is on making effective use of a pretrained video diffusion model to leverage web-scale pretraining. Most related is Pandora~\citep{xiang2024pandora} which integrates an LLM and text-to-video diffusion model to generate videos conditioned on actions described as natural language. While natural language is suitable for describing high-level actions, it is inadequate for our goal of modelling low-level actions~\citep{mccarthy2024towards}.

\textbf{Video Pre-Training for World Models\ \ }
To address the scarcity of action-labeled real-world data, several studies have investigated using unlabeled videos to enhance the efficiency of world model training. \citet{seo2022reinforcement} and \citet{wu2024pre} pre-train an autoregressive video prediction model, which is later fine-tuned with action-labeled data. \citet{mendonca2023structured} develop a world model from videos of humans by defining a high-level action space that is shared between both embodiments. Another approach involves learning latent actions from videos~\citep{bruce2024genie, schmidt2024learning}. Our work integrates video pre-training by utilizing a pre-trained video diffusion model, with the distinction that we do not have access to the weights of the original model.

\textbf{Adding Controllability to Diffusion Models\ \ } Classifier guidance~\citep{dhariwal2021diffusion} adds conditioning to a pretrained diffusion model using  a separate classifier. Classifier-free guidance~\citep{ho2022classifier} achieves stronger empirical performance but requires the model to be trained with conditioning signals, rendering it unsuitable for post-hoc application to a pretrained model.

Recent advancements include ControlNet~\citep{zhang2023adding} and T2I-Adapter~\citep{mou2024t2i}, which introduce conditional control to pretrained diffusion models by freezing the original UNet and injecting additive signals into the pretrained network. ControlNet-XS~\citep{zavadski2023controlnet} extends this concept by increasing the interactions between the pretrained and adapter networks. \citet{li2023gligen} incorporates additional trainable layers into the frozen pretrained UNet. These techniques have been applied to introduce controls such as language~\citep{xing2024aid}, optical flow~\citep{hu2023videocontrolnet}, and depth maps~\citep{chen2023control} into video models. However, they are not applicable in our context as they require access to the original model’s weights, which we assume are inaccessible. Textual inversion~\citep{gal2023image} and null text inversion~\citep{mokady2023null} optimize text embeddings to add controllability to text-conditioned diffusion models. However, this  requires backpropagation through the pretrained model which is not feasible in our setting. Cascaded diffusion models~\citep{ho2022imagen, ho2022cascaded}, train a sequence of diffusion models, which each condition on the outputs of the previous diffusion model. However, the focus of these works is improving the spatial and temporal resolution at each step, whereas our focus is on incorporating a new conditioning signal, actions, that was absent in the pretrained model.


%Another related line of research involves decomposing video generation into content and motion generation~\citep{ni2023conditional, yu2024efficient,  shen2024decouple, wang2023videocomposer}. However, these methods do not make use of frozen pre-trained models. 

\textbf{Compositional Generative Models\ } Our work is related to compositional generative models, where generative models are combined probabilistically~\citep{liu2022compositional, nie2021controllable, du2020compositional}. RoboDreamer applies this idea to world modeling by decomposing language conditioning into multiple components to generate several predictions that are then combined~\citep{zhou2024robodreamer}.~\cite{yang2024probabilistic} modifies the style of a pretrained video diffusion model by combining it's output with a domain-specific diffusion model that is trained independently. Unlike~\cite{yang2024probabilistic}, the focus of our work is on adding action-conditioning to a pretrained model, and our experiments demonstrate that the approach proposed by~\cite{yang2024probabilistic} works poorly in our setting.