\section{Supplementary material}

\subsection{Experimental details}
\subsubsection{Physics engine details}
Every simulated trajectory contained the states of the objects in the
system on each frame of a sequence of 1000 one-millisecond time
steps. The parameters of each system were chosen so that a diverse set
of dynamics could unfold within the trajectory. On each step, the
physics engine took as input the current state of the system,
calculated the forces associated with each inter-entity interaction,
and applied them to the individual entities as accelerations by
dividing by the entity's mass, parameterized as inverse-mass, $a = F
m^{-1}$ in both the engine and model input. This also allows static
objects to be represented as having $m^{-1}=0$. The previous positions
and velocities, and newly computed accelerations, were input to an
Euler integrator to update the current velocities and positions of the
entities. By using a custom engine we were able to have perfect
control over the details of the simulation, and use one engine for all
physical domains. It produced trajectory rollouts that were
indistinguishable from those of an off-the-shelf simulation engine,
but was highly efficient because it could perform thousands of runs in
parallel on a GPU, allowing millions of simulated steps to be
generated each second.

\subsubsection{Physical domains}
\paragraph{n-body}
All objects in n-body systems exerted gravitational forces on each
other, which were a function of the objects' pairwise distances and
masses, giving rise to very complex dynamics that are highly sensitive
to initial conditions. Across simulation runs, the objects' masses
varied, while all other non-dynamic variables were held constant. The
gravitational constant was set to ensure that objects could move
across several hundred meters within the 1000 step rollout. The
training scenes always included 6 objects, and for testing we used 3,
6, and 12 objects. The masses were uniformly sampled from $[0.02,9]$
kg, their shapes were points, and their initial positions were
randomly sampled from all angles, with a distance in $[10,100]$ m. We
included two classes of scenes. The first, orbit systems, had one
object (the star), initialized at position $(0,0)$, with zero velocity
and a mass of $100$ kg. The planets' velocities were initialized such
that they would have stable orbits around the star, if not for their
interactions with other planets. The second, non-orbit systems,
sampled initial $x$- and $y$-velocity components from $[-3,3]$
m/s. The objects would typically begin attracting, and gave rise to
complex semi-periodic behavior.

An n-body system is a highly nonlinear (chaotic) dynamical system,
which means they are highly sensitive to initial conditions and
extended predictions of their states are not possible under even small
perturbations. The relations between the objects corresponded to
gravitational attraction. Between simulation runs, the masses of the
objects were varied, while all other non-dynamic variables were held
constant (e.g., gravitational constant) or were not meaningful (e.g.,
object scales and shapes). The gravitational force from object $i$ to
$j$ was computed as, $F_{ij}=\frac{G m_i m_j (x_i - x_j)}{\|x_i -
x_j\| ^ 3}$, where $G$ is the gravitational constant. The denominator
was clipped so that forces could not go too high as the distances
between objects went to zero. All forces applied to each object were
summed to yield the per-object total forces.

\paragraph{Bouncing balls}
The bouncing balls domain still had all-to-all object
relations--collisions--and any object could collide with any other,
including the walls. But colliding objects are more difficult to
simulate than the gravitational interactions in n-body systems, and
our bouncing balls domain also included more variability in object
attributes, such as shape, scale, and mass (as before), as well as
relation attributes, such as the coefficient of restitution. The data
distribution was much more challenging: for more than 99\% of the time
steps, a ball was not in contact with any others, and its next-step
velocity equaled its current velocity. For the remaining steps,
however, collisions caused next-step velocities that was a complex
function of its state and the state of the object it collides
with. The training scene contained 6 balls inside a box with 4 walls,
and test scenes contained either 3, 6, or 9 balls. The balls' radii
were sampled uniformly from $[0.1,0.3]$ m, and masses from
$[0.75,1.25]$ kg. The walls were static rectangular boxes, positioned
so that the horizontal and vertical lengths of area they enclosed
varied independently between $[1,3]$ m. The balls' initial positions
were randomly sampled so that all balls fit within the box and did not
interpenetrate any other object, with initial $x$- and $y$-velocity
components sampled uniformly from $[-5,5]$ m/s. The restitutions, an
attribute of their collision relations, was sampled uniformly from
$[0.4,1]$.

Rigid body collision systems are highly nonlinear (chaotic) dynamical
systems, as well. Collision forces were applied between objects when
they began to interpenetrate, using two-step process: collision
detection between all objects, and resolution of detected
collisions. A detected collision between two objects meant that their
shapes overlapped and their velocities were causing them to approach
each other. To resolve a partially inelastic collision, the
post-collision velocities of each object were computed, and forces
appropriate to effect these velocities on the subsequent time step
were then calculated and applied the the objects. This resulted in
realistic bouncing ball trajectories.

\paragraph{String}
Our string domain used multiple types of relations (springs and
collisions), relation structures that were more sparse and specific
than all-to-all, and variable external effects. Each scene contained
one string, comprised of point masses connected by springs, and one
static, rigid circle positioned below the string. Gravitational
acceleration, varied across simulation runs, was applied so that the
string always fell, usually colliding with the static object. Each
training scene contained a string with 15 point masses, and test
scenes contained either 5, 15, or 30 mass strings. In training, one of
the point masses at the end of the string, chosen at random, was
always held static, as if pinned to the wall, while the other masses
were free to move. In the test conditions, we also included strings
that had both ends pinned, and no ends pinned, to evaluate
generalization. The string's masses were sampled from $[0.05,0.15]$
kg. The springs' rest lengths were set to $0.2$ m, spring constants to
$100$, and damping factors to $0.001$. The static object's
$x$-position was sampled from $[-0.5,0.5]$ m, $y$-position was sampled
from $[-1,-0.5]$ m, and radius from $[0.2,0.4]$ m. The string
mass-rigid object coefficient of restitution was sampled from
$[0,1]$. The gravitational acceleration applied to all non-static
objects was sampled from $[-30,-5]$ m/s$^2$.

The spring force from object $i$ to $j$ was computed using Hooke's law
as, $F = C_{s} (1 - \frac{L}{\|x_i - x_j\|}) (x_i - x_j)$, where
$C_{s}$ is the spring constant and $L$ is the spring's rest length. A
damping factor, which was proportional to the difference in the
objects' velocities, was also applied. Collision forces between the
string's masses and the static, rigid object were calculated as
described in the bouncing balls section above.


\subsection{Results details}
\begin{table}[t]
  \caption{Prediction experiments - Generalization MSEs}
  \label{tab:mse-gen}
  \centering
  \begin{tabular}{lccccccccccccc}
    \toprule
    & \multicolumn{2}{c}{n-body} & \multicolumn{2}{c}{Balls} & \multicolumn{4}{c}{String} \\
    \cmidrule(lr){2-3}
    \cmidrule(lr){4-5}
    \cmidrule(lr){6-9}
    Model & 3 & 12 & 3  & 9 & 5, 1 & 30, 1 & 15, 0 & 15, 2 \\
    \midrule
    Const. vel. & 45 & 166 & 0.054 & 0.084 & 0.0080 & 0.010 & 0.020 & 0.012 \\
    IN (within) & 0.21 & \textbf{5.2} & \textbf{0.0053} & \textbf{0.0019} & 0.0030 & \textbf{0.00066} & \textbf{0.0010} & \textbf{0.00097} \\
    IN (transfer) & \textbf{0.052} & 7.8 & \textbf{0.0053} & 0.004 & \textbf{0.00052} & 0.00074 & 0.0014 & \textbf{0.00097} \\
    \bottomrule
  \end{tabular}
\end{table}
The prediction experiment's generalization performance MSEs are shown
Table~\ref{tab:mse-gen}.
%
The URL links for the videos associated with all still frames in
Figure~\ref{fig:rollouts} are in Table~\ref{tab:videos}.
