\saveSpaceSec
\section{Related Works}
\saveSpaceSec
\paragraph{Large Language Models:}
LLMs such as GPT-3~\citep{brown2020language}, OPT~\citep{zhang2022opt}, and FLAN-T5~\citep{chung2022scaling} have made remarkable strides in a broad spectrum of natural language processing tasks in recent years. Recently, cutting-edge closed-source language models, like PaLM~\citep{chowdhery2022palm}, GPT-4 \citep{openai2023gpt4} and ChatGPT~\citep{chatgpt}, continue to display substantial flexibility, adapting to a wide variety of domains. They have increasingly become daily decision-making aids for many people. 
However, the close-source nature of these models prohibit the researchers and companies to study the inner mechanism of LLMs and built domain-adapted applications. Therefore, many open-source LLMs emerged in the community, like LLaMa~\citep{touvron2023llama}, ChatGLM~\citep{zeng2022glm} and Alpaca~\citep{alpaca}. For more details, we refer readers to this comprehensive review: \citet{zhao2023survey}.
Nevertheless, these models still have shortcomings. A noticeable gap lies in their deficiency in a robust long-term memory function. This limitation hinders their ability to maintain context over a long period and retrieve pertinent information from past interactions. Our research steps in here, with the primary objective of developing long-term memory mechanism for LLMs.

\saveSpaceSec
\paragraph{Long-term Memory Mechanisms:}
Numerous attempts have been made to enhance the memory capabilities of neural models. Memory-augmented networks (MANNs)~\citep{meng2018dialogue,graves2014neural} like Neural Turing Machines (NTMs)\citep{graves2014neural} is an example of this, designed to increase the memory capacity of neural networks. These models are structured to interact with an external memory matrix, enabling them to handle tasks that necessitate the maintenance and manipulation of stored information over extended periods. Despite showing potential, these methods have not fully addressed the need for a reliable and adaptable long-term memory function in LLMs.
There have also been studies focusing on long-range conversations~\citep{xu2021beyond,xu2022long}. For instance, \citet{xu2021beyond} introduced a new English dataset comprised of multi-session human-human crowdworker chats for long-term conversations. However, these conversations are generally restricted to a few rounds of conversation, which can not align with the application scenarios of long-term AI companions. Moreover, these models often fail to create a detailed user portrait and lack a human-like memory updating mechanism, both crucial for facilitating more natural interactions.
The concept of memory updating has been extensively researched in psychology. The Forgetting Curve theory by \cite{ebbinghaus1964memory} offers valuable insights into the pattern of memory retention and forgetting over time. Taking inspiration from this theory, we integrate a memory updating mechanism into \method to bolster its long-term memory function.

In summary, while significant progress has been made in the field of LLMs, there is still a need for  long-term memory mechanism to empower LLMs in the scenarios requiring personalized and persistent interactions.
Our work presents \method as a novel approach to address this challenge.