% \section{Discussion}
% \begin{itemize}
%     \item Interpretation of results
%     \item Implications of \method~ on AI companions
%     \item Potential applications of \method~ in other areas
% \end{itemize}

\saveSpaceSec
\section{Conclusion}
\saveSpaceSec
We present \method, a novel long-term memory mechanism designed to address the memory limitation of LLMs. 
\method enhances the ability to maintain context over time, recall relevant information, and understand user personality. 
Besides, the memory updating mechanism of \method draws inspiration from the Ebbinghaus Forgetting Curve theory, a psychological principle that describes the nature of memory retention and forgetting over time. 
This design improves the anthropomorphism of AI in long-term interactions scenarios. The versatility of \method is demonstrated through its accommodation of both open-source models such as ChatGLM and BELLE, and close-source models like ChatGPT. 

We further illustrate the practical application of \method through the development of SiliconFriend, an LLM-based chatbot designed to serve as a long-term AI companion. Equipped with \method, SiliconFriend can establish a deeper understanding of users, offering more personalized and meaningful interactions, emphasizing the potential for \method to humanize AI interactions. The tuning of SiliconFriend with psychological dialogue data enables it to provide empathetic emotional support. Extensive experiments including both qualitative and quantitative methods validate the effectiveness of \method. The findings demonstrate that \method empowers \chatbot with memory recall capabilities and deepens the understanding of user behaviors. Besides, \chatbot can provide empathetic companionship of higher quality.

% \begin{itemize}
%     \item[1.] Summary of the paper
%     \item[2.] Restatement of the problem and the proposed solution
%     \item[3.] Overview of the results and their significance
%     \item[4.] Future work and potential improvements on \method~
% \end{itemize}
% In this paper, we contribute to the field of AI research in several significant ways:

% 1. **Introduction of \method~**: We present a novel long-term memory mechanism for Large Language Models (LLMs) called \method~, designed to address the prevalent issue of memory limitation in LLMs. This new mechanism allows LLMs to maintain context over time, recall relevant memory, understand user portraits, enhancing their ability to interact meaningfully with users in long-term scenarios. \method~ also draws inspiration from the Ebbinghaus Forgetting Curve theory, a psychological principle that describes the nature of memory retention and forgetting over time. This approach helps bridge the gap between AI and cognitive psychology, bringing a more human-like memory function to AI systems.

% **Versatility of Application**: We show that \method~ can be applied to both open-source models (such as ChatGLM and BELLE) and closed-source models (like ChatGPT), demonstrating its versatility and potential for wider application in the field of AI.


% 2. **Development of SiliconFriend**: We demonstrate the application of \method~ through the development of SiliconFriend, a chatbot tuned with psychological dialog data. SiliconFriend showcases the practicality and effectiveness of \method~. Empowered with \method~, SliconFriend has the ability to provide long-term companion, and strengthen the understanding about user, offering a more personable and empathetic user experience..


% 4. **Extensive Testing and Analysis**: We provide comprehensive testing and analysis, including both qualitative and quantitative methods, The results validate the effectiveness of our proposed memory mechanism in enhancing memory recall, providing empathetic companionship, and understanding user behaviors.


% Overall, this paper offers an innovative solution to a significant challenge in LLMs and paves the way for more engaging, personable, and effective AI systems.