\vspace{-0.3cm}
\section{Related Work}
\vspace{-0.3cm}







\textbf{Reward Design.} 
Reward engineering is a long-standing challenge in reinforcement learning~\citep{singh2010where, sutton2018reinforcement}. The most common reward design method is manual trial-and-error~\citep{knox2023reward, booth2023perils}. Inverse reinforcement learning (IRL) infers reward functions from demonstrations~\citep{abbeel2004apprenticeship, ziebart2008maximum, ho2016generative}, but it requires expensive expert data collection, which may not be available, and outputs non-interpretable black-box reward functions. Several prior works have studied automated reward search through evolutionary algorithms~\citep{niekum2010genetic, chiang2019learning, faust2019evolving}. These early attempts are limited to task-specific implementations of evolutionary algorithms that search over only parameters within provided reward templates. Recent works have also proposed using pretrained foundation models that can produce reward functions for new tasks~\citep{ma2022vip, ma2023liv, fan2022minedojo, du2023vision, karamcheti2023language, du2023guiding, kwon2023reward}. Most of these approaches output \textit{scalar} rewards that lack interpretability and do not naturally admit the capability to improve or adapt rewards on-the-fly. In contrast, \ourmethod adeptly generates free-form, white-box reward code and effectively in-context improves. 










\textbf{Code Large Language Models for Decision Making.}
Recent works have considered using coding LLMs~\citep{austin2021program, chen2021evaluating, roziere2023code} to generate grounded and structured programmatic output for decision making and robotics problems~\citep{liang2023code, singh2023progprompt, wang2023demo2code, huang2023instruct2act, wang2023voyager, liu2023llm+, silver2023generalized, ding2023task, lin2023text2motion, xie2023translating}. However, most of these works rely on known motion primitives to carry out robot actions and do not apply to robot tasks that require low-level skill learning, such as dexterous manipulation. The closest to our work is a recent work~\citep{yu2023language} that also explores using LLMs to aid reward design. Their approach, however, requires domain-specific task descriptions and reward templates.















